### 2020-02-11 manuscript/mnras_version/manuscript.tex

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% my commands
\newcommand{\lcdm}{$\Lambda$CDM}
\newcommand{\hst}{{\it HST}}
\newcommand{\efr}{$R_{\mathrm{eff}}$}
\newcommand{\galfit}{{\sc Galfit}}
\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\lhost}{$L_{\rm host}$}
\newcommand{\mr}{$Mag_{\rm ~R}$}
\newcommand{\halpha}{${\it H}\alpha$}
\newcommand{\hbeta}{${\it H}\beta$}
\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{{\sc Lenstronomy}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\kmsMpc}{km~s$^{\rm -1}$~Mpc$^{\rm -1}$}
\newcommand{\kms}{\ifmmode{\,\rm{km}\, \rm{s}^{-1}}\else{$\,$km$\,$s$^{-1}$}\fi}
\newcommand{\sigstar}{{$\sigma_*$}}
\newcommand{\mstar}{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
%\newcommand{\farcs}{\mbox{\ensuremath{.\!\!^{\prime\prime}}}}% fractional arcsecond symbol: 0.''0
\newcommand{\sam}{\texttt{SAM}}
\newcommand{\mbii}{\texttt{MBII}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}} 
\newcommand{\red}[1]{{ \textcolor{red}{#1}}}
\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}

% Allow "Thomas van Noord" and "Simon de Laguarde" and alike to be sorted by "N" and "L" etc. in the bibliography.
% Write the name in the bibliography as "\VAN{Noord}{Van}{van} Noord, Thomas"
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[lens source reconstruction]{H0LiCOW xxx: correlation between black hole mass and host galaxy luminosity}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
Tommaso Treu,$^{1}$
Simon Birrer$^{1, 2}$
and et al. $^{3}$
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$xxx
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2020}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
Strong lensed AGN has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies. In this work, we have adopted eight strongly lensed system from the H0LiCOW collaboration. The deep \hst\ data and adopt the \lenstronomy\ to reconstruct the image of the source. The \mbh\ are estimated using the board emission line. We compare our inference to the once in the literature and find a consistent result. Combining them together, we are able to constrain the $\gamma$ to xxx. Our our demonstrate is demonstrate the power of using strong lensed AGNs. The sample of the data are supposed to increase rapidly.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
galaxies: evolution -- galaxies: active -- gravitational lensing: strong
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}
Structure:

[] What is scaling relations.

[] Strong lensing provide a tool to study to higher redshift.

[] Previous work. H0LiCOW XI. H0LiCOW XII. In these two works, the host galaxy is first reconstructed using the pixellation. Then, the host image are inferred in the source plan by fitting as a Sersic model. This means, the two-step inference of the host information.

[] In this work, we adopt an independent tool and carry out a direct inference of the host properties.

[]This paper is organized as follows. Zeropoint are defined in the AB systems.

\section{Sample Selection}
The eight lens systems are selected from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ~1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information of the observations for these eight systems are given in Table~1 therein.

Rather than infer the host properties from the side produces. 
We focus on source reconstruction in this paper, 
%[]The comparison sample (32 QSO paper)
To expend the sample size, we select the recent efforts by Ding2019, including 32 QSO at redshift  range 1.2<z<1.9, with the local sample.

\section{Surface photometry}
We describe the measurement of the host galaxy in this section. We use adopt the lensing techniques to reconstruct the host galaxy and recover the host magnitude in the source plane. We then obtain the color of the host to derive the rest-frame R band magnitude and estimate the stellar mass.

\subsection{Lensing host reconstruction}
Lensing modeling technique.

[] We define the light profile of the source and lensing galaxy can be described by Sersic profile. The deflector mass are described by the power law.

[] We adopt the \lenstronomy~to perform the modeling task. The detail of the fitting settings: gamma as 1.9, 2.0, 2.1. The mask. Two approaches including QSO mask and PSF reconstruction. Subgrid with 2 and 3 are selected to describe the Sersic profile.

[] Top rank result combined to get the inference of the host galaxies and the way of weighting flux to get magnitude.

We present the fitting for the eight systems in the following sub-sections.

\subsubsection{HE0435}
The results of HE0435. A table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic.

\subsubsection{RXJ1131}

\subsubsection{WFI2033}

The comparison to the previous fitting.

We summarized the inference for the eight systems in the table.
name--Setts--BestFitChisq--Totalflux--Reff--Sersicn--magnitude

\subsection{k-correction and stellar mass estimates}
For those ones have multibands. For those only have one bands.

How do we infer the color? All the available bands? Which is dominating the scatter?

\section{Black Hole mass estimates}
We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. [] The recipes. [] The board lines and the resulting BH mass and listed in the table.

\section{Results}

Selection effect? We only select 8 sample?

The last numbered section should briefly summarize what has been done, and describe
the final conclusions which the authors draw from their work.

\section{Discussion and Conclusion}

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{reference} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
%\begin{thebibliography}{99}
%\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
%Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
%\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
%Others S., 2012, Journal of Interesting Stuff, 17, 198
%\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Color inference of the host}
We took the other band data and get the only arc image. We adopt these image and do the SED fitting to get the color information.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2020-02-11 0_HE0435/f555w_model/0_cutout.py
push pkl

@@ -1,0 +1,125 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 10:11:32 2019
+
+@author: Dartoon
+
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../my_code/py_tools/')
+from cut_image import sub_bkg, cut_center_bright, cut_image, save_loc_png
+from mask_objects import mask_obj
+from flux_profile import flux_profile, profiles_compare
+ID = 'HE0435'
+
+#==============================================================================
+# Cut out the lens image
+#==============================================================================
+filename = '../data/HE0435_F555W_sci.fits'
+fitsFile = pyfits.open(filename)
+
+from my_astro_func import read_pixel_scale
+pixscl = read_pixel_scale(filename)  #Should be 0.03 here, drizzed from 0.05
+print "pixscl", pixscl
+# img = fitsFile[0].data # check the back grounp
+# img[img==0.] = np.nan
+# img_sub, bkg_light = sub_bkg(img)
+# pyfits.PrimaryHDU(img_sub).writeto('../data/HE0435_F555W_sci_sublight.fits',overwrite=True)
+img_sub = pyfits.getdata('../data/HE0435_F555W_sci_sublight.fits')
+
+#%%
+center_QSO = np.array([3641-1,2288-1]) #c_psf_list[QSO_loc]
+lens_image = cut_image(img_sub, center_QSO, 100)
+
+plt.imshow(lens_image[98:-98,98:-98], norm=LogNorm(),origin='low')
+plt.colorbar()
+plt.close()
+#lens_bkg_light = cut_image(bkg_light, center_QSO, 100)
+#plt.imshow(lens_bkg_light, norm=LogNorm(),origin='low')
+#plt.colorbar()
+#plt.show()
+
+#%%
+#==============================================================================
+# #Estimate the exposure time and error map:
+#==============================================================================
+from my_astro_func import read_fits_exp
+exp = read_fits_exp(filename) #9712.0
+mean_wht = exp * (pixscl/0.05)**2  #!!! Still need to confirm
+wht =pyfits.getdata('../data/HE0435_F555W_wht.fits')
+exp_map = exp * wht/mean_wht
[…]

### 2020-02-11 0_HE0435/f555w_model/1_clean_save_PSF.py

@@ -1,0 +1,60 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Dec  9 14:41:16 2019
+
+@author: Dartoon
+
+Clean the PSF then saved, make it to be loaded easier for the future.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../my_code/py_tools/')
+from mask_objects import mask_obj
+from flux_profile import profiles_compare
+import glob
+
+psfname_list = glob.glob('PSF?.fits') 
+psfname_list.sort()
+psfs = []
+for i in range(len(psfname_list)):
+    psf_i = pyfits.getdata(psfname_list[i])
+    print psfname_list[i]
+    _, psf_mask = mask_obj(img=psf_i,snr=1.0,exp_sz=1.7,pltshow=0)
+    if 1 in psf_mask[0]:
+        if len(psf_mask) > 1:
+            psf_mask = np.sum(np.asarray(psf_mask),axis=0)
+        elif len(psf_mask) == 1:
+            psf_mask = psf_mask[0]
+        psf_mask = (1 - (psf_mask != 0)*1.)
+        psf_clear = copy.deepcopy(psf_i)
+        for i in range(len(psf_i)):
+            for j in range(len(psf_i)):
+                if psf_mask[i, j] == 0:
+                    psf_clear[i, j] = (psf_i[-i-1, -j-1]*psf_mask[-i-1, -j-1])
+        print "plot PSF after clear:"
+        psf_i = psf_clear
+    plt.imshow(psf_i, origin = 'low', norm=LogNorm())
+    plt.show()
+    psfs.append(psf_i)
+##%%
+#fig = profiles_compare(psfs, scal_list=np.ones(len(psfs)),
+#                       prf_name_list=['PSF'+str(i) for i in range(len(psfs))],
+#                       gridspace = 'log', if_annuli=True)
+#fig.savefig("PSFs_profile.pdf")
+#fig.show()
+#    
+for i in range(len(psfs)):
+   psfs[i] = psfs[i]/np.sum(psfs[i])
+   pyfits.PrimaryHDU(psfs[i]).writeto('PSF{0}_clean.fits'.format(i),overwrite=True) 
+
+##%%
[…]

### 2020-02-11 0_HE0435/f555w_model/fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py

@@ -1,0 +1,328 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+Modelling the HE0435
+
+Trying to recover the H0LiCOW_IV's host flux ~47.
+
+In this script, fix gamma as Ken's results. Use, psf mask.
+Use PSF reconstruction.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+from mask_objects import mask_obj, detect_obj
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+import os
+path = os.getcwd()
+
+ID = 'HE0435'
+
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))
+lens_mask = cr_mask(lens_image, '../circle_mask.reg')
+
+framesize = 99
+ct = (len(lens_image) - framesize)/2
+lens_image = lens_image[ct:-ct,ct:-ct]
+lens_rms = lens_rms[ct:-ct,ct:-ct]
+lens_mask = (1-lens_mask)[ct:-ct,ct:-ct]
+
[…]

### 2020-02-11 0_HE0435/f814w_model/0_cutout.py

@@ -1,0 +1,122 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 10:11:32 2019
+
+@author: Dartoon
+
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../my_code/py_tools/')
+from cut_image import sub_bkg, cut_center_bright, cut_image, save_loc_png
+from mask_objects import mask_obj
+from flux_profile import flux_profile, profiles_compare
+ID = 'HE0435'
+
+#==============================================================================
+# Cut out the lens image
+#==============================================================================
+filename = '../data/HE0435_F814W_sci.fits'
+fitsFile = pyfits.open(filename)
+
+from my_astro_func import read_pixel_scale
+pixscl = read_pixel_scale(filename)  #Should be 0.03 here, drizzed from 0.05
+print "pixscl", pixscl
+# img = fitsFile[0].data # check the back grounp
+# img[img==0.] = np.nan
+# img_sub, bkg_light = sub_bkg(img)
+# pyfits.PrimaryHDU(img_sub).writeto('../data/HE0435_F814W_sci_sublight.fits',overwrite=True)
+img_sub = pyfits.getdata('../data/HE0435_F814W_sci_sublight.fits')
+
+#%%
+center_QSO = np.array([3641-1,2288-1]) #c_psf_list[QSO_loc]
+lens_image = cut_image(img_sub, center_QSO, 100)
+
+plt.imshow(lens_image[98:-98,98:-98], norm=LogNorm(),origin='low')
+plt.colorbar()
+plt.show()
+#lens_bkg_light = cut_image(bkg_light, center_QSO, 100)
+#plt.imshow(lens_bkg_light, norm=LogNorm(),origin='low')
+#plt.colorbar()
+#plt.show()
+
+#%%
+#==============================================================================
+# #Estimate the exposure time and error map:
+#==============================================================================
+from my_astro_func import read_fits_exp
+exp = read_fits_exp(filename) #9712.0
+mean_wht = exp * (pixscl/0.05)**2  #!!! Still need to confirm
+wht =pyfits.getdata('../data/HE0435_F814W_wht.fits')
+exp_map = exp * wht/mean_wht
[…]

### 2020-02-11 0_HE0435/f814w_model/fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py

@@ -1,0 +1,328 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+Modelling the HE0435
+
+Trying to recover the H0LiCOW_IV's host flux ~47.
+
+In this script, fix gamma as Ken's results. Use, psf mask.
+Use PSF reconstruction.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+from mask_objects import mask_obj, detect_obj
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+import os
+path = os.getcwd()
+
+ID = 'HE0435'
+
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))
+lens_mask = cr_mask(lens_image, '../circle_mask.reg')
+
+framesize = 99
+ct = (len(lens_image) - framesize)/2
+lens_image = lens_image[ct:-ct,ct:-ct]
+lens_rms = lens_rms[ct:-ct,ct:-ct]
+lens_mask = (1-lens_mask)[ct:-ct,ct:-ct]
+
[…]

### 2020-02-11 0_HE0435/model/3_read_result.py

@@ -14,12 +14,13 @@ import pickle
 from matplotlib.colors import LogNorm
 import copy
 import sys
-sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+sys.path.insert(0,'../../../my_code/py_tools/')
 from flux_profile import cr_mask
 
 
 #readfile = 'fit_PSFi_PSFrecons/result_PSF0_PSFrecons_gammafix1.9_subg2.pkl'
-readfile = 'fit_PSFi_QSOmask/result_PSF3_QSOmask_gammafix1.9_subg2.pkl'
+readfile = '2nd_fit_PSFi_PSFrecons/result_PSF3_PSFrecons_gammafix1.9_subg2.pkl'
+# readfile = '2nd_fit_PSFi_QSOmask/result_PSF2_QSOmask_gammafix1.9_subg2.pkl'
 result = pickle.load(open(readfile,'rb'))
 fit_result, trans_result, kwargs_material, model_lists  = result
 
@@ -38,13 +39,7 @@ from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
 from lenstronomy.Plots import chain_plot
 import lenstronomy.Plots.chain_plot as out_plot
 #%%
-#!!! For the Lenstronomy version 1.3.0
 kwargs_result, chain_list = fit_result
-if 'e1' in kwargs_result['kwargs_lens'][1].keys():
-    g1 = kwargs_result['kwargs_lens'][1]['e1']
-    g2 = kwargs_result['kwargs_lens'][1]['e2']
-    del kwargs_result['kwargs_lens'][1]
-    kwargs_result['kwargs_lens'].append({'gamma1': g1, 'gamma2': g2})
 
 sampler_type, samples_mcmc, param_mcmc, dist_mcmc  = chain_list[-1]    
 lens_result = kwargs_result['kwargs_lens']
@@ -70,27 +65,33 @@ kwargs_result = kwargs_result
 image_band = [kwargs_data, kwargs_psf, kwargs_numerics]
 multi_band_list = [image_band]
 
+
 #%%
 modelPlot = ModelPlot(multi_band_list, kwargs_model, kwargs_result, 
                       arrow_size=0.02, cmap_string="gist_heat", likelihood_mask_list=[lens_mask])
 #param_class = fitting_seq.param_class
 #print(param_class.num_param())
 #print(chain_list)
+'''
 for i in range(len(chain_list)):
     chain_plot.plot_chain_list(chain_list, i)
-
+'''
+#%%
[…]

### 2020-02-11 0_HE0435/model/3_read_result_.py

@@ -1,0 +1,140 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Jan 25 10:44:07 2019
+
+@author: Dartoon
+
+Test load text from PDF
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+from matplotlib.colors import LogNorm
+import copy
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+from flux_profile import cr_mask
+
+
+#readfile = 'fit_PSFi_PSFrecons/result_PSF0_PSFrecons_gammafix1.9_subg2.pkl'
+readfile = 'fit_PSFi_QSOmask/result_PSF3_QSOmask_gammafix1.9_subg2.pkl'
+result = pickle.load(open(readfile,'rb'))
+fit_result, trans_result, kwargs_material, model_lists  = result
+
+kwargs_data, kwargs_psf_updated, kwargs_numerics, kwargs_model, lens_mask = kwargs_material
+lens_model_list, source_model_list, lens_light_model_list, point_source_list = model_lists
+
+#%%
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.Data.imaging_data import ImageData as Data
+from lenstronomy.Data.psf import PSF
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+from lenstronomy.Plots import chain_plot
+import lenstronomy.Plots.chain_plot as out_plot
+#%%
+#!!! For the Lenstronomy version 1.3.0
+kwargs_result, chain_list = fit_result
+if 'e1' in kwargs_result['kwargs_lens'][1].keys():
+    g1 = kwargs_result['kwargs_lens'][1]['e1']
+    g2 = kwargs_result['kwargs_lens'][1]['e2']
+    del kwargs_result['kwargs_lens'][1]
+    kwargs_result['kwargs_lens'].append({'gamma1': g1, 'gamma2': g2})
+
+sampler_type, samples_mcmc, param_mcmc, dist_mcmc  = chain_list[-1]    
+lens_result = kwargs_result['kwargs_lens']
[…]

### 2020-02-11 1_RXJ1131/model/auto_run.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+fixg_i=2
+#target="2_WFI2033"
+cd ./2nd_fit_PSFi_QSOmask/
+#echo "2nd_fit_PSFi_QSOmask/"
+python 2_modelling_fix_gamma_QSO_mask.py ${fixg_i}
+#cd ../2nd_fit_PSFi_PSFrecons/
+#echo "2nd_fit_PSFi_PSFrecons/"
+#python 2_modelling_fix_gamma_PSF_recons.py ${fixg_i}
+

### 2020-02-11 2_WFI2033/f125w_model/0_cutout.py

@@ -1,0 +1,129 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 10:11:32 2019
+
+@author: Dartoon
+
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../my_code/py_tools/')
+from cut_image import sub_bkg, cut_center_bright, cut_image, save_loc_png
+from mask_objects import mask_obj
+from flux_profile import flux_profile, profiles_compare
+ID = 'WFI2033'
+
+#==============================================================================
+# Cut out the lens image
+#==============================================================================
+filename = '../data/WFI2033_added/f125w_drz_sci.fits'
+fitsFile = pyfits.open(filename)
+
+from my_astro_func import read_pixel_scale
+pixscl = read_pixel_scale(filename)
+
+# img = fitsFile[0].data # check the back grounp
+# img[img==0.] = np.nan
+# img_sub, bkg_light = sub_bkg(img)
+# pyfits.PrimaryHDU(img_sub).writeto('../data/WFI2033_added/f125w_drz_sci_sublight.fits',overwrite=True)
+img_sub = pyfits.getdata('../data/WFI2033_added/f125w_drz_sci_sublight.fits')
+
+#%%
+center_QSO = np.array([785-1,853-1]) #c_psf_list[QSO_loc]
+lens_image = cut_image(img_sub, center_QSO, 100)
+
+# plt.imshow(lens_image, norm=LogNorm(),origin='low')
+# plt.colorbar()
+# plt.show()
+#lens_bkg_light = cut_image(bkg_light, center_QSO, 100)
+#plt.imshow(lens_bkg_light, norm=LogNorm(),origin='low')
+#plt.colorbar()
+#plt.show()
+
+#%%
+#==============================================================================
+# #Estimate the exposure time and error map:
+#==============================================================================
+from my_astro_func import read_fits_exp
+exp = read_fits_exp(filename) #9712.0
+mean_wht = exp * (pixscl/0.12825)**2  #!!! Still need to confirm
+taka_lens_rms =pyfits.getdata('../data/WFI2033_added/f125w_drz_rms.fits')
+wht = (1/taka_lens_rms)**2
[…]

### 2020-02-11 2_WFI2033/f125w_model/1_clean_save_PSF.py

@@ -1,0 +1,60 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Dec  9 14:41:16 2019
+
+@author: Dartoon
+
+Clean the PSF then saved, make it to be loaded easier for the future.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../my_code/py_tools/')
+from mask_objects import mask_obj
+from flux_profile import profiles_compare
+import glob
+
+psfname_list = glob.glob('PSF?.fits') 
+psfname_list.sort()
+psfs = []
+for i in range(len(psfname_list)):
+    psf_i = pyfits.getdata(psfname_list[i])
+    print psfname_list[i]
+    _, psf_mask = mask_obj(img=psf_i,snr=1.0,exp_sz=1.7,pltshow=0)
+    if 1 in psf_mask[0]:
+        if len(psf_mask) > 1:
+            psf_mask = np.sum(np.asarray(psf_mask),axis=0)
+        elif len(psf_mask) == 1:
+            psf_mask = psf_mask[0]
+        psf_mask = (1 - (psf_mask != 0)*1.)
+        psf_clear = copy.deepcopy(psf_i)
+        for i in range(len(psf_i)):
+            for j in range(len(psf_i)):
+                if psf_mask[i, j] == 0:
+                    psf_clear[i, j] = (psf_i[-i-1, -j-1]*psf_mask[-i-1, -j-1])
+        print "plot PSF after clear:"
+        psf_i = psf_clear
+    plt.imshow(psf_i, origin = 'low', norm=LogNorm())
+    plt.show()
+    psfs.append(psf_i)
+
+fig = profiles_compare(psfs, scal_list=np.ones(len(psfs)),
+                       prf_name_list=['PSF'+str(i) for i in range(len(psfs))],
+                       gridspace = 'log', if_annuli=True)
+fig.savefig("PSFs_profile.pdf")
+fig.show()
+   
+for i in range(len(psfs)):
+   psfs[i] = psfs[i]/np.sum(psfs[i])
+   pyfits.PrimaryHDU(psfs[i]).writeto('PSF{0}_clean.fits'.format(i),overwrite=True) 
+
+#%%
+import os   
[…]

### 2020-02-11 2_WFI2033/f125w_model/fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py

@@ -1,0 +1,386 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+Modelling the HE0435
+
+Trying to recover the H0LiCOW_IV's host flux ~47.
+
+In this script, fix gamma as Ken's results. Use, psf mask.
+Use PSF reconstruction.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+#sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+from mask_objects import mask_obj
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+
+filename = '../../data/WFI2033_added/f125w_drz_sci.fits'
+fitsFile = pyfits.open(filename)
+from my_astro_func import read_pixel_scale
+pixscl = read_pixel_scale(filename)
+
+t1 = time.time()
+
+lens_image = pyfits.getdata('../WFI2033_cutout.fits')   #!!!need to change
+lens_rms = pyfits.getdata('../WFI2033_stdd.fits')    #!!!need to change
+
+lens_mask = 1-cr_mask(lens_image, filename='../lens_mask.reg')
[…]

### 2020-02-11 2_WFI2033/f140w_model/fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py

@@ -100,273 +100,273 @@ plt.imshow(lens_image*lens_mask, origin='low', norm=LogNorm())
 plt.close()
 
 #Things should be changed:
-id_ind = int(sys.argv[1])
-fix_gamma = [1.9, 2.0, 2.1][id_ind]
-for psf_id in [0]:#[1,2,3,4,5,6]: 
-    for subg in [3,2]: #[3,2]
-        picklename='result_PSF{0}_PSFrecons_gammafix{1}_subg{2}.pkl'.format(psf_id, fix_gamma, subg)        
-        if glob.glob(picklename) != []:
-            continue
-        print "psf_id:", psf_id, "fix_gamma:", fix_gamma, "subg:", subg
-        psf = pyfits.getdata('../PSF{0}_clean.fits'.format(psf_id))
-        numPix = len(lens_image)  # cutout pixel size
-        deltaPix = pixscl
-        kwargs_data = sim_util.data_configure_simple(numPix, deltaPix,inverse=True)
-        kwargs_data['image_data'] = lens_image
-        kwargs_data['noise_map'] = lens_rms
-        data_class = ImageData(**kwargs_data)
-        kwargs_psf = {'psf_type': 'PIXEL', 'kernel_point_source': psf, 'pixel_size': deltaPix}
-        psf_class = PSF(**kwargs_psf)
-        
-        #%%This part would be different for lens to lens:
-        # =============================================================================
-        # Setting up the fitting list, and guess parameter to set up the fitting parameter.
-        # =============================================================================
-        lens_model_list = ['SPEMD', 'SHEAR']
-        lens_model_class = LensModel(lens_model_list=lens_model_list)
-        lens_light_model_list = ['SERSIC_ELLIPSE'] * 3
-        lens_light_model_class = LightModel(light_model_list=lens_light_model_list)
-        source_model_list = ['SERSIC_ELLIPSE']
-        source_model_class = LightModel(light_model_list=source_model_list)
-        point_source_list = ['LENSED_POSITION']
-        point_source_class = PointSource(point_source_type_list=point_source_list, fixed_magnification_list=[False])
-        
-        kwargs_numerics = {'supersampling_factor': subg, 'supersampling_convolution': False}
-        imageModel = ImageModel(data_class, psf_class, lens_model_class, source_model_class,
-                                        lens_light_model_class,
-                                        point_source_class, kwargs_numerics=kwargs_numerics)
[…]

### 2020-02-11 2_WFI2033/f160w_model/0_cutout.py

@@ -1,0 +1,134 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 10:11:32 2019
+
+@author: Dartoon
+
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../my_code/py_tools/')
+from cut_image import sub_bkg, cut_center_bright, cut_image, save_loc_png
+from mask_objects import mask_obj
+from flux_profile import flux_profile, profiles_compare
+ID = 'WFI2033'
+
+#==============================================================================
+# Cut out the lens image
+#==============================================================================
+filename = '../data/WFI2033_added/f160w_drz_sci.fits'
+fitsFile = pyfits.open(filename)
+
+from my_astro_func import read_pixel_scale
+pixscl = read_pixel_scale(filename)
+
+# img = fitsFile[0].data # check the back grounp
+# img[img==0.] = np.nan
+# img_sub, bkg_light = sub_bkg(img)
+# pyfits.PrimaryHDU(img_sub).writeto('../data/WFI2033_added/f160w_drz_sci_sublight.fits',overwrite=True)
+img_sub = pyfits.getdata('../data/WFI2033_added/f160w_drz_sci_sublight.fits')
+
+#%%
+center_QSO = np.array([1298-1,1205-1]) #c_psf_list[QSO_loc]
+lens_image = cut_image(img_sub, center_QSO, 100)
+
+plt.imshow(lens_image[98:-98,98:-98], norm=LogNorm(),origin='low')
+plt.colorbar()
+plt.close()
+# lens_bkg_light = cut_image(bkg_light, center_QSO, 100)
+# plt.imshow(lens_bkg_light, norm=LogNorm(),origin='low')
+# plt.colorbar()
+# plt.show()
+
+#%%
+#==============================================================================
+# #Estimate the exposure time and error map:
+#==============================================================================
+from my_astro_func import read_fits_exp
+exp = read_fits_exp(filename) #9712.0
+mean_wht = exp * (pixscl/0.12825)**2  #!!! Still need to confirm
+taka_lens_rms =pyfits.getdata('../data/WFI2033_added/f160w_drz_rms.fits')
[…]

### 2020-02-11 2_WFI2033/f160w_model/1_clean_save_PSF.py

@@ -1,0 +1,60 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Dec  9 14:41:16 2019
+
+@author: Dartoon
+
+Clean the PSF then saved, make it to be loaded easier for the future.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'../../../my_code/py_tools/')
+from mask_objects import mask_obj
+from flux_profile import profiles_compare
+import glob
+
+psfname_list = glob.glob('PSF?.fits') 
+psfname_list.sort()
+psfs = []
+for i in range(len(psfname_list)):
+    psf_i = pyfits.getdata(psfname_list[i])
+    print psfname_list[i]
+    _, psf_mask = mask_obj(img=psf_i,snr=1.0,exp_sz=1.7,pltshow=0)
+    if 1 in psf_mask[0]:
+        if len(psf_mask) > 1:
+            psf_mask = np.sum(np.asarray(psf_mask),axis=0)
+        elif len(psf_mask) == 1:
+            psf_mask = psf_mask[0]
+        psf_mask = (1 - (psf_mask != 0)*1.)
+        psf_clear = copy.deepcopy(psf_i)
+        for i in range(len(psf_i)):
+            for j in range(len(psf_i)):
+                if psf_mask[i, j] == 0:
+                    psf_clear[i, j] = (psf_i[-i-1, -j-1]*psf_mask[-i-1, -j-1])
+        print "plot PSF after clear:"
+        psf_i = psf_clear
+    plt.imshow(psf_i, origin = 'low', norm=LogNorm())
+    plt.show()
+    psfs.append(psf_i)
+
+fig = profiles_compare(psfs, scal_list=np.ones(len(psfs)),
+                       prf_name_list=['PSF'+str(i) for i in range(len(psfs))],
+                       gridspace = 'log', if_annuli=True)
+fig.savefig("PSFs_profile.pdf")
+fig.show()
+   
+for i in range(len(psfs)):
+   psfs[i] = psfs[i]/np.sum(psfs[i])
+   pyfits.PrimaryHDU(psfs[i]).writeto('PSF{0}_clean.fits'.format(i),overwrite=True) 
+
+# #%%
+# import os   
[…]

### 2020-02-11 2_WFI2033/f160w_model/fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py

@@ -1,0 +1,386 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+Modelling the HE0435
+
+Trying to recover the H0LiCOW_IV's host flux ~47.
+
+In this script, fix gamma as Ken's results. Use, psf mask.
+Use PSF reconstruction.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+#sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+from mask_objects import mask_obj
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+
+filename = '../../data/WFI2033_added/f160w_drz_sci.fits'
+fitsFile = pyfits.open(filename)
+from my_astro_func import read_pixel_scale
+pixscl = read_pixel_scale(filename)
+
+t1 = time.time()
+
+lens_image = pyfits.getdata('../WFI2033_cutout.fits')   #!!!need to change
+lens_rms = pyfits.getdata('../WFI2033_stdd.fits')    #!!!need to change
+
+lens_mask = 1-cr_mask(lens_image, filename='../lens_mask.reg')
[…]

### 2020-02-11 3_SDSS1206/model/auto_run.sh

@@ -1,0 +1,10 @@
+#!/bin/bash
+fixg_i=2
+#target="2_WFI2033"
+cd ./singel_fit_PSFi_QSOmask/
+echo "singel_fit_PSFi_QSOmask/"
+python 2_modelling_fix_gamma_QSO_mask.py ${fixg_i}
+cd ../singel_fit_PSFi_PSFrecons/
+echo "singel_fit_PSFi_PSFrecons/"
+python 2_modelling_fix_gamma_PSF_recons.py ${fixg_i}
+

### 2020-02-11 share_tools/read_chisq.py

@@ -11,8 +11,8 @@ import matplotlib.pyplot as plt
 import pickle
 import sys
 import lenstronomy.Util.class_creator as class_creator
-sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools')
-from flux_profile import cr_mask
+sys.path.insert(0,'../py_tools')
+#from flux_profile import cr_mask
 
 def return_chisq(filename, lens_mask = None, fair_mask=True, fair_PSF =False, if_reduce=True):
     result = pickle.load(open(filename,'rb'))

### 2020-02-20 manuscript/manuscript.tex
Upload manuscript

--- 2020-02-11 manuscript/mnras_version/manuscript.tex
@@
 \newcommand{\todo}[1]{\textcolor{red}{[{\bf Todo}: #1]}}  
-\newcommand{\aklant}[1]{\textcolor{blue}{[{\bf AKB}: #1]}} 
 \newcommand{\red}[1]{{ \textcolor{red}{#1}}}
@@
 % Keep the title short and informative.
-\title[lens source reconstruction]{H0LiCOW xxx: correlation between black hole mass and host galaxy luminosity}
+\title[lens source reconstruction]{H0LiCOW: correlation between black hole mass and host galaxy luminosity}
 
@@
 \section{Sample Selection}
-The eight lens systems are selected from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914.
-For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ~1131).
+We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914.
+For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131).
 In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
-The detailed information of the observations for these eight systems are given in Table~1 therein.
+The detailed information of the observations for these eight systems are given in Table~1 therein~\ding{Maybe we can re-summarized it again here}.
+We analyzed the HST imaging data of the sample and the observation has been introduced by~\citet{Ding2017a}.
+Moreover, three quadruply-imaged AGNs (HE0435, RXJ1131 and WFI2033) have HST imaging data at multi-bands from which we could infer the color of the host galaxy and obtain more accurate stellar template.
 
-Rather than infer the host properties from the side produces. 
-We focus on source reconstruction in this paper, 
 %[]The comparison sample (32 QSO paper)
-To expend the sample size, we select the recent efforts by Ding2019, including 32 QSO at redshift  range 1.2<z<1.9, with the local sample.
+To exam the evolution of the lensed system, we aim to compare....
+expend the sample size and the data resolution, we adopt the recent efforts by~\citet{Ding2020}, including 32 QSO at redshift range $1.2<z<1.9$, with the local sample.
 
 \section{Surface photometry}
-We describe the measurement of the host galaxy in this section.
-We use adopt the lensing techniques to reconstruct the host galaxy and recover the host magnitude in the source plane.
-We then obtain the color of the host to derive the rest-frame R band magnitude and estimate the stellar mass.
+We describe the reconstruction of the lensed host galaxy in this section.
+For part of the lensed systems, the lens models have been derived with host galaxies reconstructed ref[].
+Aiming at the time-delay cosmography, these works focused on deriving the precise and accurate lens models, while the reconstructed the host galaxy is only a by-product.
+Thus, in this work, we apply our own approach to infer the photometry of the host galaxy in the source plane.
+As will show, we compare our inference to the previous ones for cross check purpose.
 
-\subsection{Lensing host reconstruction}
-Lensing modeling technique.
+%We then obtain the color of the host to derive the rest-frame R band magnitude and estimate the stellar mass.
 
-[] We define the light profile of the source and lensing galaxy can be described by Sersic profile. The deflector mass are described by the power law.
+\subsection{Lens model inference and host reconstruction}
+We simultaneously carry out the fitting process to derive the lens model, subtract the central AGN light and reconstruct the host galaxy in the source plan.
+We follow the common practice and assume the photometry of the galaxies (including the lensing galaxy and source galaxy) follows the 2-D elliptical \sersic\ profile, which defines the host flux as consistent to the comparison sample.
+The bright AGNs are unsolved and described by a scaled PSF.
+We adopt the elliptical power-law models to describe the surface mass density of the deflector.
 
-[] We adopt the \lenstronomy~to perform the modeling task.
-The detail of the fitting settings: gamma as 1.9, 2.0, 2.1.
-The mask.
+%The one of the fitting setting 
+[] We adopt the \lenstronomy~ref[] to perform the modeling task. We draw the mask to define the fitting region. The nearby object are considered as extended source and fitted as \sersic.
+
+%Different settings to do the rank.
+[] We cut out the available PSFs in the files.
 Two approaches including QSO mask and PSF reconstruction.
 Subgrid with 2 and 3 are selected to describe the Sersic profile.
+The detail of the fitting settings: gamma as 1.9, 2.0, 2.1.
 
+%How to do the rank.
 [] Top rank result combined to get the inference of the host galaxies and the way of weighting flux to get magnitude.
@@
 The results of HE0435. A table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic. 
+Comparison to the previous inference.
+
+The other two band.
 
@@
 
+\subsubsection{SDSS1206}
+
+\subsubsection{HE1104}
+
+\subsubsection{SDSS0246}
+
+\subsubsection{HE0047}
+
+\subsubsection{HS2209}
+
 The comparison to the previous fitting.
@@
 We summarized the inference for the eight systems in the table.
-name--Setts--BestFitChisq--Totalflux--Reff--Sersicn--magnitude
+name--Setts--BestFitChisq--Totalflux-- Host ratio --Reff--Sersicn--magnitude - Stellar mass
 
-\subsection{k-correction and stellar mass estimates}
-For those ones have multibands. For those only have one bands.
+\subsection{Stellar mass estimates}
+For those ones have multi-bands, we attempt to infer the color of the host in the image plane.
 
@@
 \section{Black Hole mass estimates}
-We use viral method to estimate the mass of the black hole.
-The board-line adopted.
-We aim to adopt the self-consistent to recalibrate the \mbh~of our sample.
-[] The recipes.
-[] The board lines and the resulting BH mass and listed in the table.
+We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. 
+[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.
 
@@
 
-Selection effect? We only select 8 sample?
-
-The last numbered section should briefly summarize what has been done, and describe
-the final conclusions which the authors draw from their work.
+\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}
 
 \section{Discussion and Conclusion}
+[] This work confirm the bright future of lensing.
 

### 2020-02-21 manuscript/manuscript.tex
Keep on writting

@@
 % Keep the title short and informative.
-\title[lens source reconstruction]{H0LiCOW: correlation between black hole mass and host galaxy luminosity}
+\title[lens source reconstruction]{H0LiCOW: correlation between black hole mass and host galaxy luminosity.}
 
@@
 Tommaso Treu,$^{1}$
-Simon Birrer$^{1, 2}$
+Simon Birrer,$^{1, 2}$
+Dominique Sluse,\newauthor
+Chris Fassnacht,
 and et al. $^{3}$
@@
 In these two works, the host galaxy is first reconstructed using the pixellation.
-Then, the host image are inferred in the source plan by fitting as a Sersic model.
+Then, the host image are inferred in the source plan by fitting as a \sersic\ model.
 This means, the two-step inference of the host information.
@@
 In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
-The detailed information of the observations for these eight systems are given in Table~1 therein~\ding{Maybe we can re-summarized it again here}.
-We analyzed the HST imaging data of the sample and the observation has been introduced by~\citet{Ding2017a}.
-Moreover, three quadruply-imaged AGNs (HE0435, RXJ1131 and WFI2033) have HST imaging data at multi-bands from which we could infer the color of the host galaxy and obtain more accurate stellar template.
+The detailed information for the information of these eight systems are given in Table~1 therein.
+Besides, half of the systems, including HE0435, RXJ1131, WFI2033 and HE1104 have \hst\ imaging data in multi-bands.
+To estimate the \mbh, we adopt the spectra information as inferred by \citet{Sluse2012, Peng2006, Shen2011}.
+We use a Table[] to summarize the data information.
+\ding{table should including the redshift, filter/Camera, the drizzled pixel size.}
 
+While we note that our sample size included eight systems, which is a limited sample to constrain the evolution of the scaling relation.
+In this particular work, we simply aim to plot the scaling relation of our sample and make comparison to the ones in the literature.
 %[]The comparison sample (32 QSO paper)
-To exam the evolution of the lensed system, we aim to compare....
-expend the sample size and the data resolution, we adopt the recent efforts by~\citet{Ding2020}, including 32 QSO at redshift range $1.2<z<1.9$, with the local sample.
+We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 redshift QSO and 55 local measurements.
 
-\section{Surface photometry}
+We adopt a class of consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample. \ding{Do we want to include the detailed information here?}
+
+\section{surface photometry with lensing technique}
 We describe the reconstruction of the lensed host galaxy in this section.
@@
 Aiming at the time-delay cosmography, these works focused on deriving the precise and accurate lens models, while the reconstructed the host galaxy is only a by-product.
-Thus, in this work, we apply our own approach to infer the photometry of the host galaxy in the source plane.
-As will show, we compare our inference to the previous ones for cross check purpose.
+Thus, in this paper, we apply our own approach to infer the photometry of the host galaxy in the source plane.
+For cross check purpose, we will compare our inference to the reconstructions by the previous works.
 
-%We then obtain the color of the host to derive the rest-frame R band magnitude and estimate the stellar mass.
+\subsection{Model Choice}
+We carry out the fitting process to subtract the central AGN light, constrain the lens model, and reconstruct the host galaxy in the source plan, simultaneously.
+We assume the photometry of the galaxies (including the lensing galaxy and source galaxy) is described by the 2-D elliptical \sersic\ profile.
+We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component.
+By this definition, we could infer the host flux as consistent to our comparison sample.
+The bright AGNs are unsolved and modelled by a scaled point spread function (PSF).
+We adopt the elliptical power-law model to describe the surface mass density of the deflector.
+An external shear component is also considered.
 
-\subsection{Lens model inference and host reconstruction}
-We simultaneously carry out the fitting process to derive the lens model, subtract the central AGN light and reconstruct the host galaxy in the source plan.
-We follow the common practice and assume the photometry of the galaxies (including the lensing galaxy and source galaxy) follows the 2-D elliptical \sersic\ profile, which defines the host flux as consistent to the comparison sample.
-The bright AGNs are unsolved and described by a scaled PSF.
-We adopt the elliptical power-law models to describe the surface mass density of the deflector.
+We employ the imaging modelling tool \lenstronomy~ref[] to perform the fitting task.
+The input ingredients include the lensing imaging data, noise level map and a PSF, as is described by~\citet{Ding2020}.
+We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood.
+For any objects which is close to the lens, we model its light as one extended source described by \sersic\ profile.
 
-%The one of the fitting setting 
-[] We adopt the \lenstronomy~ref[] to perform the modeling task. We draw the mask to define the fitting region. The nearby object are considered as extended source and fitted as \sersic.
+For each lens systems, we adopt different choices to perform the fitting.
+The distribution of the fitting inference are assumed to sufficiently cover the truth.
+We then apply a statistical measurement to weighting for the final inference and estimate the uncertainty level.
+The different choice of the fitting including the following.
+\begin{enumerate}
+\item  We select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is input as the initial PSF to perform the fitting.
+\item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF.
+To avoid overfitting the noise, we choose to either manually boost the noise estimate in the central area to effectively infinite, or perform the iterative PSF estimation ref[].
+\item To perform the ray tracing through a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
+\item Since using the lensing imaging alone is difficult to constrain the power-law slope, we choose to fixed the slope values with three options $[1.9, 2.0, 2.1]$.
+\end{enumerate}
 
-%Different settings to do the rank.
-[] We cut out the available PSFs in the files.
-Two approaches including QSO mask and PSF reconstruction.
-Subgrid with 2 and 3 are selected to describe the Sersic profile.
-The detail of the fitting settings: gamma as 1.9, 2.0, 2.1.
+For a lens system with a number of $N$ initial PSFs, there are in total $N\times12$ (i.e., $2 \times2 \times3$) fittings.
+After the all sets of fittings are completed, we rank the performance of each choice based on their best-fitted $\chi^2$ value.
+We adopt the weighting algorithm as introduced by ~\citet{Ding2020} and combine the top eight choices to derive the final inference.
 
-%How to do the rank.
-[] Top rank result combined to get the inference of the host galaxies and the way of weighting flux to get magnitude.
+\subsection{Photometry Inference}
+In this section, we describe the details of the fitting for each systems and present the corresponding inference of the host photometry information.
 
-We present the fitting for the eight systems in the following sub-sections.
+%remember to present a table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic. 
+\subsubsection{HE0435}
+This system has been modeled.
 
-\subsubsection{HE0435}
-The results of HE0435. A table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic. 
+We choose five isolated stars in this field to input as the initial PSFs. 
 Comparison to the previous inference.
+The fitting image and inferred parameter, including: Einstein Radius, host n, host Reff, host flux, host flux ratio.
 
-The other two band.
+Besides the F160W band, HE0435 has also been observed by the \hst\ through F814W and F555W.
+We carry out the similar steps to modeling at the two band.
+Given that the data quality and the host flux is less bright in these two bands, we only focus on modeling lensed arcs in the image plane.
+Based on the obtained color information, we estimate the stellar template and derive the stellar mass based on the intrinsic magnitude inferred by the F160W band.
 
@@
 \section{Results}
+%estimate the black hole mass.
+
+%scaling relation and compare to the Ding+20
 

### 2020-02-22 manuscript/manuscript.tex
Update tex and upload figure

@@
 \usepackage[T1]{fontenc}
+\usepackage{subfig} %for figure subplot
 
@@
 We use a Table[] to summarize the data information.
-\ding{table should including the redshift, filter/Camera, the drizzled pixel size.}
+\ding{table should include the redshift, filter/Camera, the drizzled pixel size.}
 
@@
 
-We adopt a class of consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample. \ding{Do we want to include the detailed information here?}
+We adopt a class of consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample.
+\ding{Do we want to include the detailed information such as recipe and the other things here?}
 
@@
 We carry out the fitting process to subtract the central AGN light, constrain the lens model, and reconstruct the host galaxy in the source plan, simultaneously.
-We assume the photometry of the galaxies (including the lensing galaxy and source galaxy) is described by the 2-D elliptical \sersic\ profile.
+For all the systems, we assume the photometry of the galaxies (including the lensing galaxy and source galaxy) is described by the 2-D elliptical \sersic\ profile.
 We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component.
+For single \sersic\ case, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference.
 By this definition, we could infer the host flux as consistent to our comparison sample.
@@
 We employ the imaging modelling tool \lenstronomy~ref[] to perform the fitting task.
-The input ingredients include the lensing imaging data, noise level map and a PSF, as is described by~\citet{Ding2020}.
+We following the standard procedure as introduced by~\citet{Ding2020} to produce the fitting ingredients including the lensing imaging data, noise level map and the PSF condition.
 We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood.
-For any objects which is close to the lens, we model its light as one extended source described by \sersic\ profile.
 
@@
 After the all sets of fittings are completed, we rank the performance of each choice based on their best-fitted $\chi^2$ value.
-We adopt the weighting algorithm as introduced by ~\citet{Ding2020} and combine the top eight choices to derive the final inference.
+We adopt the weighting algorithm as introduced by ~\citet{Ding2020} and combine the top eight choices to derive the final inference and estimate the uncertainties.
 
 \subsection{Photometry Inference}
-In this section, we describe the details of the fitting for each systems and present the corresponding inference of the host photometry information.
+In the result of this section, we describe the details of the fitting for each systems and present the corresponding inference of the host photometry information.
 
@@
 \subsubsection{HE0435}
-This system has been modeled.
+We follow Ken[] and assuming light of the deflector are composed of two elliptical \sersic\ with index value $n$ fixed to $1$ and $4$ to represent the disk and bulge components
 
-We choose five isolated stars in this field to input as the initial PSFs. 
-Comparison to the previous inference.
+We select five isolated stars in this field initial PSFs to input to the fitting thus, we have in total 60 fittings for this case.
+The best-fit models are present in the Figure~\ref{fig:image_inference}-(a).
+Using the top eight inference, we use weighting to combining them and inferred the results.
 The fitting image and inferred parameter, including: Einstein Radius, host n, host Reff, host flux, host flux ratio.
+
+Note that the residual maps are appears to be less ideal than the ones as presented by Ken[].
+The major reason is the definition of the host galaxy.
+We compare the result with the inferred host galaxy by Ken[] and Ding+2017.
 
@@
 
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_best_inference.pdf}}&
+\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_best_inference.pdf}}\\
+\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_best_inference.pdf}}&
+\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_best_inference.pdf}}\\
+\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_best_inference.pdf}}&
+\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_best_inference.pdf}}\\
+\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_best_inference.pdf}}&
+\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_best_inference.pdf}}\\
+\end{tabular}
+\caption{\label{fig:image_inference} 
+Something}
+\end{figure*}
+
 \subsubsection{RXJ1131}
@@
 \subsubsection{WFI2033}
+The objects which is close to the lens, we model its light as one extended source described by \sersic\ profile.
 
@@
 
-\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}
+%\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}
 

### 2020-02-22 0_HE0435/model/3_read_result_.py
Produce the fitting image to show in the paper.

@@ -14,13 +14,13 @@ import pickle
 from matplotlib.colors import LogNorm
 import copy
 import sys
-sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
 from flux_profile import cr_mask
 
 
 #readfile = 'fit_PSFi_PSFrecons/result_PSF0_PSFrecons_gammafix1.9_subg2.pkl'
 readfile = 'fit_PSFi_QSOmask/result_PSF3_QSOmask_gammafix1.9_subg2.pkl'
-result = pickle.load(open(readfile,'rb'))
+result = pickle.load(open(readfile,'rb') ,encoding="latin1")
 fit_result, trans_result, kwargs_material, model_lists  = result
 
 kwargs_data, kwargs_psf_updated, kwargs_numerics, kwargs_model, lens_mask = kwargs_material

### 2020-02-22 material/model_band_plot(Xuheng_mod).py

@@ -1,0 +1,598 @@
+
+import lenstronomy.Util.util as util
+import matplotlib.pyplot as plt
+import numpy as np
+from mpl_toolkits.axes_grid1 import make_axes_locatable
+from lenstronomy.ImSim.MultiBand.single_band_multi_model import SingleBandMultiModel
+from lenstronomy.LensModel.lens_model_extensions import LensModelExtensions
+from lenstronomy.Data.coord_transforms import Coordinates
+from lenstronomy.Plots import plot_util
+
+
+class ModelBandPlot(object):
+    """
+    class to plot a single band given the modeling results
+
+    """
+    def __init__(self, multi_band_list, kwargs_model, model, error_map, cov_param, param, kwargs_params,
+                 likelihood_mask_list=None, band_index=0, arrow_size=0.02, cmap_string="gist_heat"):
+
+        self.bandmodel = SingleBandMultiModel(multi_band_list, kwargs_model,
+                                                  likelihood_mask_list=likelihood_mask_list, band_index=band_index)
+        self._kwargs_special_partial = kwargs_params.get('kwargs_special', None)
+        kwarks_lens_partial, kwargs_source_partial, kwargs_lens_light_partial, kwargs_ps_partial, self._kwargs_extinction_partial = self.bandmodel.select_kwargs(**kwargs_params)
+        self._kwargs_lens_partial, self._kwargs_source_partial, self._kwargs_lens_light_partial, self._kwargs_ps_partial = self.bandmodel.update_linear_kwargs(param, kwarks_lens_partial, kwargs_source_partial, kwargs_lens_light_partial, kwargs_ps_partial)
+        self._norm_residuals = self.bandmodel.reduced_residuals(model, error_map=error_map)
+        self._reduced_x2 = self.bandmodel.reduced_chi2(model, error_map=error_map)
+        print("reduced chi^2 of data ", band_index, "= ", self._reduced_x2)
+
+        self._model = model
+        self._cov_param = cov_param
+        self._param = param
+        
+        self.multi_band_list = multi_band_list
+
+        self._lensModel = self.bandmodel.LensModel
+        self._lensModelExt = LensModelExtensions(self._lensModel)
+        log_model = np.log10(model)
+        log_model[np.isnan(log_model)] = -5
+        self._v_min_default = max(np.min(log_model), -5)
+        self._v_max_default = min(np.max(log_model), 10)
+        self._coords = self.bandmodel.Data
+        self._data = self._coords.data
+        self._deltaPix = self._coords.pixel_width
[…]

### 2020-02-22 material/plot_fitting.py

@@ -1,0 +1,153 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Feb 21 11:50:31 2020
+
+@author: Dartoon
+"""
+
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+from matplotlib.colors import LogNorm
+import copy
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
+from flux_profile import cr_mask
+import glob
+
+#%% Find the one with lowest Chisq
+IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
+
+
+#for i in range(len(IDs)):
+#    print(i, ':', IDs[i])
+#inp = int(input("Which source:\n"))
+inp = 3
+ID = IDs[inp][2:]
+if ID != 'SDSS1206':
+    folder_0 = '_2nd_run_summary.pkl'
+    folder_1 = '2nd_fit'
+elif ID == 'SDSS1206':
+    folder_0 = '_singel_host_run_summary.pkl'
+    folder_1 = 'singel_fit'
+filename = '../share_tools/'+ ID+ folder_0
+result = pickle.load(open(filename,'rb') ,encoding="latin1") 
+fit_values, chisq, labels, _ = result
+chisq = [float(chisq[i]) for i in range(len(chisq))]
+idx = np.where(chisq == np.min(chisq))[0][0]
+label = labels[idx]
+label = label.split(', ')
+
+filename = glob.glob('../'+IDs[inp]+'/model/{4}_PSFi_{0}/result_{1}_*_gammafix{2}_subg{3}.pkl'.format(label[-1], label[0], label[1][-3:], label[2][-1],folder_1) )
+readfile = filename[0]
+
+#%%
+##
+result = pickle.load(open(readfile,'rb') ,encoding="latin1")
+fit_result, trans_result, kwargs_material, model_lists  = result
+kwargs_data, kwargs_psf_updated, kwargs_numerics, kwargs_model, lens_mask = kwargs_material
+lens_model_list, source_model_list, lens_light_model_list, point_source_list = model_lists
+if label[-1] == 'PSFrecons':
+    print("Change PSFs and ")
[…]

### 2020-02-25 manuscript/manuscript.tex
Create the table generator

@@
 \usepackage{subfig} %for figure subplot
+\usepackage{graphicx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{xspace}
 
@@
 We use a Table[] to summarize the data information.
-\ding{table should include the redshift, filter/Camera, the drizzled pixel size.}
 
@@
 We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 redshift QSO and 55 local measurements.
+
+\begin{table}
+\centering
+\caption{Summary of lensed AGN information.}\label{data_set}
+%\resizebox{18cm}{!}{
+     \begin{tabular}{ccccc}
+        \hline
+Object ID & camera & Filter & exposure & pixel scale \\
+ & & & time (s) & (drizzled) \\ \hline
+HE0435$-$1223 & WFC3-IR & F160W & 9340 & $0\farcs{}08$ \\
+RXJ1131$-$1231 & ACS & F814W & 1980 & $0\farcs{}05$ \\
+WFI2033$-$4723 & WFC3-IR & F160W & 26257 & $0\farcs{}08$ \\
+SDSS1206$+$4332 & WFC3-IR & F160W & 8457 & $0\farcs{}08$ \\
+HE1104$-$1805 & WFC3-IR & F160W & 14698 & $0\farcs{}08$ \\
+SDSS0246$-$0825 & WFC3-UVIS & F814W & 8481 & $0\farcs{}03$ \\
+HS2209$+$1914 & WFC3-UVIS & F814W & 14238 & $0\farcs{}03$ \\
+HE0047$-$1756 & WFC3-UVIS & F814W & 9712 & $0\farcs{}03$ \\
+        \hline
+     \end{tabular}
+    %}
+    \begin{tablenotes}
+      \small
+      \item Note - To be written.
+    \end{tablenotes} 
+\end{table}
 
@@
 
-Note that the residual maps are appears to be less ideal than the ones as presented by Ken[].
-The major reason is the definition of the host galaxy.
+Note that the residual level reveals in the inference figures are appears to be larger than the ones as presented by Ken[].
+The major reason is the definition of the host galaxy in the models.
+Without using sophisticated models such as shepelet or pixellized ones, we will be able to infer directly the \sersic\ flux of the host galaxy.
+
 We compare the result with the inferred host galaxy by Ken[] and Ding+2017.
@@
 name--Setts--BestFitChisq--Totalflux-- Host ratio --Reff--Sersicn--magnitude - Stellar mass
+
+\begin{table*}
+\centering
+%\resizebox{12cm}{!}{
+     \begin{tabular}{ccccccc}
+\hline
+Object ID & Magnitude & Host-Total Flux Ratio & Reff & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
+ & (AB system) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
+HE0435 & $21.332\substack{+0.208\\-0.175}$ & $62.471\pm10.893$ & $0.298\pm0.027$ & $2.829\pm0.251$ & $1.500$ & $10.978$ \\
+RXJ1131$_{\rm bulge}$ & $22.074\substack{+0.164\\-0.142}$ & $91.573\pm11.280$ & $0.106\pm0.007$ & fix to 4 & $3.000$ & $10.276$ \\
+RXJ1131$_{\rm disk}$ & $19.305\substack{+0.154\\-0.135}$ & $91.573\pm11.280$ & $0.875\pm0.062$ & fix to 1 & $1.500$ & $11.091$ \\
+WFI2033 & $21.404\substack{+0.167\\-0.145}$ & $35.723\pm5.093$ & $0.294\pm0.025$ & $0.528\pm0.011$ & $0.625$ & $10.662$ \\
+SDSS1206 & $21.287\substack{+0.222\\-0.184}$ & $32.286\pm5.977$ & $0.110\pm0.020$ & $4.526\pm0.555$ & $0.625$ & $10.781$ \\
+HE1104 & $21.274\substack{+0.188\\-0.160}$ & $14.142\pm2.250$ & $0.265\pm0.026$ & $1.033\pm0.034$ & $0.625$ & $11.039$ \\
+SDSS0246 & $23.575\substack{+0.394\\-0.289}$ & $3.756\pm1.143$ & $0.381\pm0.098$ & $4.963\pm0.048$ & $0.626$ & $10.690$ \\
+HS2209 & $20.385\substack{+0.262\\-0.211}$ & $19.454\pm4.165$ & $1.921\pm1.070$ & $2.953\pm0.438$ & $1.001$ & $11.177$ \\
+HE0047 & $22.972\substack{+0.626\\-0.394}$ & $2.496\pm1.093$ & $0.282\pm0.176$ & $3.603\pm1.533$ & $0.625$ & $10.888$ \\
+\hline
+\end{tabular}
+    %}
+\caption{Summary of lensed AGN inference.}\label{data_set}    
+\small
+\end{table*}
 

### 2020-02-25 material/plot_fitting.py

@@ -112,7 +112,7 @@ modelPlot.decomposition_plot(ax=axes[1,1], text='Modelled source light', source_
 modelPlot.source_plot(ax=axes[1, 2], deltaPix_source=0.01, numPix=100,text='Reconstrucerd host, source plane')
 #f.tight_layout()
 f.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0., hspace=0.05)
-plt.savefig('{0}_best_inference.pdf'.format(ID))
+#plt.savefig('{0}_best_inference.pdf'.format(ID))
 plt.show()
 
 #f, axes = plt.subplots(2, 3, figsize=(16, 8), sharex=False, sharey=False)

### 2020-02-25 material/print_table.py

@@ -1,0 +1,116 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Feb 24 09:41:40 2020
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+
+import glob
+import sys
+sys.path.insert(0,'../share_tools/')
+
+from read_inference import read_inf
+from lens_information import zeropoint_dict, filter_dict
+
+IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
+
+full_name = ['HE0435$-$1223', 'RXJ1131$-$1231', 'WFI2033$-$4723', 'SDSS1206$+$4332', 
+			 'HE1104$-$1805', 'SDSS0246$-$0825', 'HS2209$+$1914', 'HE0047$-$1756']
+
+
+Camera = ['WFC3-IR', 'ACS', 'WFC3-IR', 'WFC3-IR', 'WFC3-IR', 'WFC3-UVIS', 'WFC3-UVIS', 'WFC3-UVIS']
+
+Filter = ['F160W', 'F814W', 'F160W', 'F160W', 'F160W', 'F814W','F814W','F814W']
+
+path = "/Volumes/Seagate_Expansion_Drive/Projects_backup/lens_host_reconstruction/"
+exp_list = [9340.4, 1980.0, 26257.0, 8456.9, 14698.3, 8481.0, 4542.0+9696.0, 9712.0]
+
+resolution = ['$0\\farcs{}08$', '$0\\farcs{}05$', '$0\\farcs{}08$', '$0\\farcs{}08$',
+			  '$0\\farcs{}08$', '$0\\farcs{}03$', '$0\\farcs{}03$', '$0\\farcs{}03$']
+
+##%%Table 1 :
+#print("Object ID & camera & Filter & exposure & pixel scale \\\\")
+#print(" & & & time (s) & (drizzled) \\\\ \\hline")
+#for i in range(len(IDs)):
+##    files = glob.glob(path+IDs[i]+'/data/*sci.fits')
+##    if len(files)>1:
+##        print('Some thing is wrong!!! in:', IDs[i])
+##    datafile = files[0]
+##    fitsFile = pyfits.open(datafile)
[…]

### 2020-02-25 share_tools/lens_information.py

@@ -16,3 +16,9 @@ pixel_scale = {'HE0435' : 0.08, 'RXJ1131' : 0.05, 'WFI2033' : 0.08, 'SDSS1206': 
 
 lens_redshift = {'HE0435' : 1.69, 'RXJ1131' : 0.65, 'WFI2033' : 1.66, 'SDSS1206': 1.79, 'HE1104': 2.32,
                'SDSS0246':  1.68, 'HS2209': 1.07, 'HE0047' : 1.66}
+
+filter_dict = {'HE0435': 'F160W', 'RXJ1131': 'ACS_F814W', 'WFI2033': 'F160W', 'SDSS1206': 'F160W', 
+               'HE1104': 'F160W', 'SDSS0246': 'F814W', 'HS2209': 'F814W', 'HE0047': 'F814W'}
+
+zeropoint_dict = {'F814W' :25.110, 'F555W': 25.807,'F125W': 26.2303,'F140W': 26.4524, 
+                  'F160W':25.9463,'ACS_F814W': 25.957}

### 2020-02-25 share_tools/plot_host_infernece.py

@@ -1,0 +1,79 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Feb 24 11:44:45 2020
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+import glob
+import copy
+IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
+
+weighted_value_list, rms_value_list = [], []
+
+prop = int(input('flux input 0 ; Reff input 1 ; host flux image_plane 2:\n'))
+
+#%%
+for i in range(len(IDs)):
+	ID = IDs[i][2:]
+	if ID == "SDSS1206" :
+		filename = ID+'_singel_host_run_summary.pkl'
+	else:
+		filename = ID+'_2nd_run_summary.pkl'
+	result = pickle.load(open(filename,'rb'),encoding="latin1")
+	fit_values, chisq, labels, pick_names = result
+	sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
+	fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values
+	for i in range(len(labels)):
+		if labels[i][-17:] != sort_label_type[i%4]:
+			raise ValueError("The labels is wrong for some reason")
+	if prop == 0 :
+		if 'Disk' in pick_names[2]:
+			pick = 4
+		else:
+			pick = 3
+	elif prop == 1:
+		if 'Disk' in pick_names[2]:
+			pick = 6
+		else:
+			pick = 5
+	elif prop == 2:
+			pick = 1  #Flux in the image plane
+	print(ID, pick_names)
+	fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
+	fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
+	fit_value_h = [fit_value_h_list[i][pick] for i in range(len(labels))]
+	count_n = 8
+	chisq = [float(chisq[i]) for i in range(len(chisq))]
+	sort_chisq = np.argsort(np.asarray(chisq))    
+	Chisq_best = chisq[sort_chisq[0]]
[…]

### 2020-02-25 share_tools/read_inference.py

@@ -1,0 +1,72 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Feb 24 11:44:45 2020
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+import glob
+import copy
+
+def read_inf(ID, prop=0 , count_n=8, rod = 3):
+	if ID == "SDSS1206" :
+		filename = ID+'_singel_host_run_summary.pkl'
+	else:
+		filename = ID+'_2nd_run_summary.pkl'
+	result = pickle.load(open('../share_tools/'+filename,'rb'),encoding="latin1")
+	fit_values, chisq, labels, pick_names = result
+	sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
+	fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values
+	for i in range(len(labels)):
+		if labels[i][-17:] != sort_label_type[i%4]:
+			raise ValueError("The labels is wrong for some reason")
+	if prop == 0 :  #Flux
+		if 'Disk' in pick_names[2]:
+			picks = [4,5]
+		else:
+			picks = [3]
+	elif prop == 1: #Reff
+		if 'Disk' in pick_names[2]:
+			picks = [6,7]
+		else:
+			picks = [5]
+	elif prop == 2: #Sersic n
+		if 'Disk' in pick_names[2]:
+			picks = []
+		else:
+			picks = [4]
+	elif prop == 3: #AGN flux
+		if 'Disk' in pick_names[2]:
+			picks = [3]
+		else:
+			picks = [2]
+			
+#	print(ID, pick_names)
+	result = []
+	for pick in picks:
+		fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
+		count_n = count_n
+		
+		chisq = [float(chisq[i]) for i in range(len(chisq))]
+		sort_chisq = np.argsort(np.asarray(chisq))    
+		Chisq_best = chisq[sort_chisq[0]]
+		#Chisq_last= chisq[sort_chisq[-1]]
+		Chisq_last= chisq[sort_chisq[count_n-1]]
+		weight = np.zeros(len(chisq))
+		inf_alp = (Chisq_last-Chisq_best) / (2*2.* Chisq_best)
[…]

### 2020-02-25 share_tools/weighting_inference.py

@@ -1,72 +1,0 @@
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-import pickle
-import glob
-import copy
-IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
-
-weighted_value_list, rms_value_list = [], []
-
-prop = input('flux input 0 ; Reff input 1 ; host flux image_plane 2:\n')
-
-#%%
-for i in range(len(IDs)):
-	ID = IDs[i][2:]
-	if ID == "SDSS1206" :
-		filename = ID+'_singel_host_run_summary.pkl'
-	else:
-		filename = ID+'_2nd_run_summary.pkl'
-	# filename = ID+'_2nd_run_summary.pkl'	
- 	result = pickle.load(open(filename,'rb'))
- 	fit_values, chisq, labels, pick_names = result
- 	sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
- 	fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values
- 	for i in range(len(labels)):
- 	    if labels[i][-17:] != sort_label_type[i%4]:
- 	        raise ValueError("The labels is wrong for some reason")
- 	if prop == 0 :
-		if 'Disk' in pick_names[2]:
- 			pick = 4
-		else:
- 			pick = 3
- 	elif prop == 1:
-		if 'Disk' in pick_names[2]:
- 			pick = 6
-		else:
- 			pick = 5
- 	elif prop == 2:
- 			pick = 1  #Flux in the image plane
- 	print(ID, pick_names)
- 	fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
- 	fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
- 	fit_value_h = [fit_value_h_list[i][pick] for i in range(len(labels))]
- 	count_n = 8
- 	chisq = [float(chisq[i]) for i in range(len(chisq))]
- 	sort_chisq = np.argsort(np.asarray(chisq))    
- 	Chisq_best = chisq[sort_chisq[0]]
- 	#Chisq_last= chisq[sort_chisq[-1]]
- 	Chisq_last= chisq[sort_chisq[count_n-1]]
[…]

### 2020-02-25 manuscript/manuscript.tex
Update table print_table

--- 2020-02-22 manuscript/manuscript.tex
@@
 We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 redshift QSO and 55 local measurements.
+
+\begin{table}
+\centering
+%\begin{threeparttable}
+\caption{Summary of lensed AGN information.}\label{data_set}
+\resizebox{9cm}{!}{
+     \begin{tabular}{cccccc}
+        \hline
+Object ID & z & camera & Filter & exposure & pixel scale \\
+ & & & & time (s) & (drizzled) \\ \hline
+HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & $0\farcs{}08$ \\
+RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & $0\farcs{}05$ \\
+WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & $0\farcs{}08$ \\
+SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & $0\farcs{}08$ \\
+HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & $0\farcs{}08$ \\
+SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & $0\farcs{}03$ \\
+HS2209$+$1914 & 1.07 & WFC3-UVIS & F814W & 14238 & $0\farcs{}03$ \\
+HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & $0\farcs{}03$ \\
+        \hline
+     \end{tabular}
+    }
+\begin{tablenotes}
+      \small
+      \item Note: $-$ If any
+\end{tablenotes}  
+%\end{threeparttable}
+\end{table}
 
@@
 name--Setts--BestFitChisq--Totalflux-- Host ratio --Reff--Sersicn--magnitude - Stellar mass
+
+\begin{table*}
+\renewcommand{\arraystretch}{1.5}
+%\setlength{\tabcolsep}{20pt}
+\centering
+  \begin{threeparttable}
+\caption{Summary of lensed AGN inference.}\label{data_set}    
+%\resizebox{12cm}{!}{
+     \begin{tabular}{ccccccc}
+\hline
+Object ID & Magnitude & Host-Total Flux Ratio & Reff & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
+ & (AB system) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
+HE0435 & $21.332\substack{+0.208\\-0.175}$ & $62.471\pm10.893$ & $0.298\pm0.027$ & $2.829\pm0.251$ & $1.500$ & $10.98\substack{+0.07\\-0.08}$ \\
+RXJ1131$_{\rm bulge}$ & $22.074\substack{+0.164\\-0.142}$ & $6.634\pm0.929$ & $0.106\pm0.007$ & fix to 4 & $3.000$ & $1.01\substack{+0.06\\-0.07}$ \\
+RXJ1131$_{\rm disk}$ & $19.305\substack{+0.154\\-0.135}$ & $84.939\pm11.241$ & $0.875\pm0.062$ & fix to 1 & $1.500$ & $1.04\substack{+0.05\\-0.06}$ \\
+WFI2033 & $21.404\substack{+0.167\\-0.145}$ & $35.723\pm5.093$ & $0.294\pm0.025$ & $0.528\pm0.011$ & $0.625$ & $10.66\substack{+0.06\\-0.07}$ \\
+SDSS1206 & $21.287\substack{+0.222\\-0.184}$ & $32.286\pm5.977$ & $0.110\pm0.020$ & $4.526\pm0.555$ & $0.625$ & $10.78\substack{+0.07\\-0.09}$ \\
+HE1104 & $21.274\substack{+0.188\\-0.160}$ & $14.142\pm2.250$ & $0.265\pm0.026$ & $1.033\pm0.034$ & $0.625$ & $11.04\substack{+0.06\\-0.08}$ \\
+SDSS0246 & $23.575\substack{+0.394\\-0.289}$ & $3.756\pm1.143$ & $0.381\pm0.098$ & $4.963\pm0.048$ & $0.626$ & $10.69\substack{+0.12\\-0.16}$ \\
+HS2209 & $20.385\substack{+0.262\\-0.211}$ & $19.454\pm4.165$ & $1.921\pm1.070$ & $2.953\pm0.438$ & $1.001$ & $11.18\substack{+0.08\\-0.10}$ \\
+HE0047 & $22.972\substack{+0.626\\-0.394}$ & $2.496\pm1.093$ & $0.282\pm0.176$ & $3.603\pm1.533$ & $0.625$ & $10.89\substack{+0.16\\-0.25}$ \\
+\hline
+\end{tabular}
+%}
+\begin{tablenotes}
+      \small
+      \item Note: $-$ If any
+\end{tablenotes}    
+\end{threeparttable}
+\end{table*}
 

### 2020-02-25 material/print_table.py

@@ -15,7 +15,7 @@ import sys
 sys.path.insert(0,'../share_tools/')
 
 from read_inference import read_inf
-from lens_information import zeropoint_dict, filter_dict
+from lens_information import zeropoint_dict, filter_dict, lens_redshift
 
 IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
 
@@ -33,17 +33,17 @@ exp_list = [9340.4, 1980.0, 26257.0, 8456.9, 14698.3, 8481.0, 4542.0+9696.0, 971
 resolution = ['$0\\farcs{}08$', '$0\\farcs{}05$', '$0\\farcs{}08$', '$0\\farcs{}08$',
 			  '$0\\farcs{}08$', '$0\\farcs{}03$', '$0\\farcs{}03$', '$0\\farcs{}03$']
 
-##%%Table 1 :
-#print("Object ID & camera & Filter & exposure & pixel scale \\\\")
-#print(" & & & time (s) & (drizzled) \\\\ \\hline")
-#for i in range(len(IDs)):
-##    files = glob.glob(path+IDs[i]+'/data/*sci.fits')
-##    if len(files)>1:
-##        print('Some thing is wrong!!! in:', IDs[i])
-##    datafile = files[0]
-##    fitsFile = pyfits.open(datafile)
-##    exp_list.append(round(fitsFile[0].header['EXPTIME'],1))
-#    print(full_name[i], '&', Camera[i], '&', Filter[i] , '&', round(exp_list[i]), '&', resolution[i], "\\\\")
+#%%Table 1 :
+print("Object ID & z & camera & Filter & exposure & pixel scale \\\\")
+print(" & & & & time (s) & (drizzled) \\\\ \\hline")
+for i in range(len(IDs)):
+#    files = glob.glob(path+IDs[i]+'/data/*sci.fits')
+#    if len(files)>1:
+#        print('Some thing is wrong!!! in:', IDs[i])
+#    datafile = files[0]
+#    fitsFile = pyfits.open(datafile)
+#    exp_list.append(round(fitsFile[0].header['EXPTIME'],1))
[…]

### 2020-02-25 manuscript/manuscript.tex
write MBH table producer

@@
 \newcommand{\mr}{$Mag_{\rm ~R}$}
-\newcommand{\halpha}{${\it H}\alpha$}
-\newcommand{\hbeta}{${\it H}\beta$}
+\newcommand{\halpha}{H$_{\alpha}$}
+\newcommand{\Hb}{H$_{\beta}$}
 \newcommand{\sersic}{S\'ersic}
@@
         \hline
-Object ID & z & camera & Filter & exposure & pixel scale \\
+Object ID & $z$ & camera & Filter & exposure & pixel scale \\
  & & & & time (s) & (drizzled) \\ \hline
@@
       \small
-      \item Note: $-$ If any
+      \item Note: $-$ The observational information is presented in~\citet{Ding2017a}.
 \end{tablenotes}  
@@
 \ding{Do we want to include the detailed information such as recipe and the other things here?}
+
+\begin{table}
+\centering
+%\begin{threeparttable}
+\caption{Summary of lensed \mbh\ estimates.}\label{data_set}
+\resizebox{8.5cm}{!}{
+     \begin{tabular}{ccccc}
+        \hline
+Object ID & Line(s) used & FWHM & log($L_\lambda$) & $\log$\mbh \\
+& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
+HE0435 & \Mgii & 4930 & 45.14 & 8.54 \\
+RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 \\
+WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
+SDSS1206 & \Mgii & 5632 & 45.61 & 8.88 \\
+HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
+SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
+HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
+        \hline
+     \end{tabular}
+    }
+\begin{tablenotes}
+      \small
+      \item Note: $-$ The masses
+\end{tablenotes}  
+%\end{threeparttable}
+\end{table}
 

### 2020-02-25 material/print_table.py

@@ -34,7 +34,7 @@ resolution = ['$0\\farcs{}08$', '$0\\farcs{}05$', '$0\\farcs{}08$', '$0\\farcs{}
 			  '$0\\farcs{}08$', '$0\\farcs{}03$', '$0\\farcs{}03$', '$0\\farcs{}03$']
 
 #%%Table 1 :
-print("Object ID & z & camera & Filter & exposure & pixel scale \\\\")
+print("Object ID & $z$ & camera & Filter & exposure & pixel scale \\\\")
 print(" & & & & time (s) & (drizzled) \\\\ \\hline")
 for i in range(len(IDs)):
 #    files = glob.glob(path+IDs[i]+'/data/*sci.fits')
@@ -45,7 +45,28 @@ for i in range(len(IDs)):
 #    exp_list.append(round(fitsFile[0].header['EXPTIME'],1))
     print(full_name[i], '&',lens_redshift[IDs[i][2:]]  , '&', Camera[i], '&', Filter[i] , '&', round(exp_list[i]), '&', resolution[i], "\\\\")
 
-#%%Table 2:    
+#%%Table 2
+#Pring BH information
+sys.path.insert(0,'../MBH_estimator/')
+from est_MBH import BL_info, cal_MBH
+print("Object ID & Line(s) used & FWHM & log($L_\\lambda$) & $\\log$\\mbh \\\\")
+print("& & (\\kms) & ($[\\rm erg~s^[-1]]$) & (M$_{\\odot}$) \\\\ \\hline")
+for ID in ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '7_HE0047']:
+	ID = ID[2:]
+	line_infor = BL_info[ID]
+#	for key in BL_info[ID].keys():
+	if len(BL_info[ID].keys()) == 1:
+		key = list(BL_info[ID].keys())[0]
+		print(ID, '&', '\\{0}'.format(key), '&', '{0:.0f}'.format(BL_info[ID][key]['FWHM']), '&',
+		'{0:.2f}'.format(np.mean(BL_info[ID][key]['L'])), '&', '{0:.2f}'.format(cal_MBH(key, np.mean(BL_info[ID][key]['L']), BL_info[ID][key]['FWHM'])) ,"\\\\" )
+	elif len(BL_info[ID].keys()) == 2:
[…]

### 2020-02-29 6_HS2209/model_05data/3_summary.py
Update HS2209 model_vis05

@@ -1,0 +1,191 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Jan 25 15:58:15 2019
+
+@author: Dartoon
+
+Summarize the fitting result
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+import glob
+import sys
+import copy
+from adjustText import adjust_text   # avoid the overlapping while ploting
+sys.path.insert(0,'../../share_tools/')
+from read_chisq import return_chisq 
+
+pkl_folderfiles = glob.glob("fit_PSFi_PSFrecons/result_PSF*.pkl")
+pkl_files = [pkl_folderfiles[i].split('/')[1] for i in range(len(pkl_folderfiles))]
+
+if float(len(pkl_files)/6) != len(pkl_files)/6. :
+    raise ValueError("The number of the pickle result is the Multiples of six")
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-2]
+
+#%%
+
+#PSFno_ = range(psf_num)
+
+
+#The values to pick up:
+filename = pkl_folderfiles[0]
+result = pickle.load(open(filename,'rb'),encoding="latin1") 
+fit_result, trans_result, kwargs_material, model_lists  = result
+pick_names = trans_result[-1]
+
+_, _, _, _, lens_mask = kwargs_material
+stdd_file = glob.glob('fit_PSFi_QSOmask/*_stdd_boost.fits')
+if len(stdd_file)>1:
+    raise ValueError("More than on *_stdd_boost.fits exits") 
+rms_boost = pyfits.getdata(stdd_file[0])
+lens_mask[rms_boost == rms_boost.max()] = 0
+plt.imshow(lens_mask,origin='low')
+plt.show()
+
+fair_PSF = True
+
+labels = []
+fit_value_l_list, fit_value_m_list, fit_value_h_list, = [], [], []
+chisq = []
+fixgamma_list = []
+
+folder_i = ['fit_PSFi_QSOmask', 'fit_PSFi_PSFrecons']
+for folder in folder_i:
+#    if folder == 'fit_PSFi_QSOmask':
+#        filenames = glob.glob('{0}/result_PSF?_S*'.format(folder))
+#    elif 'fit_PSFi_PSFrecons':
+    filenames = glob.glob('{0}/result_PSF?_*'.format(folder))        
+    filenames.sort()
+    for filename in filenames:
[…]

### 2020-02-29 manuscript/manuscript.tex
Update before pull from overleaf

@@
 
-We adopt a class of consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample.
-\ding{Do we want to include the detailed information such as recipe and the other things here?}
+To assure the validity of the comparison, we adopt a class of self-consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample.
+For the overall systems, we adopt the following virial formalism:
+\begin{eqnarray}
+\label{recipe}
+\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
+&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
+\end {eqnarray}
+%
+with a\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
+b\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
+$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
+%
+Having achieved a consistent cross-calibration, we adopt the board line information from the literature to estimate the \mbh.
+The information are presented in Table~\ref{mbh}.
+The uncertainty of the \mbh\ are expected as $0.4$~dex.
 
@@
 %\begin{threeparttable}
-\caption{Summary of lensed \mbh\ estimates.}\label{data_set}
+\caption{Summary of lensed \mbh\ estimates.}\label{mbh}
 \resizebox{8.5cm}{!}{
@@
       \small
-      \item Note: $-$ The masses
+      \item Note: $-$ The reference for the board line information. For SDSS1206, we follow Birrer2018 and consider the magnification effect to correct the L.
 \end{tablenotes}  
@@
 \subsubsection{RXJ1131}
+The RXJ1131 is the other system that has been studied in \citet{Ding2017b}.
+The host galaxy is lensed to a extended arc with a feature of bulge $+$ disk clearly appeared, we consider them both in the fitting.
+
+We compare to the previous reconstructions. The bulge are consistent, however, our inferred disk are brighter.
 
@@
 \subsection{Stellar mass estimates}
-For those ones have multi-bands, we attempt to infer the color of the host in the image plane.
+[] Color inference for the first three cases to decide their stellar template.
 
-How do we infer the color? All the available bands? Which is dominating the scatter?
+[] For the other systems, we follow Ding to assume their age based on their redshift.
 
-\section{Black Hole mass estimates}
-We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. 
-[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.
+The uncertainty of the \mstar\ are considered as 0.2 dex, and as studied in~\citet{Ding2017a}, we expect that the uncertainty of the \mbh\ dominate the error budget.
+
+%\section{Black Hole mass estimates}
+%We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. 
+%[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.
 
 \section{Results}
-%estimate the black hole mass.
-
-%scaling relation and compare to the Ding+20
-
-%\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}
+Derive the the inference of our sample, we over plot our measurements on top of the measurements by \citet{Ding2020}, shown in Figure.
+The result demonstrate an excellent consistency.
+and the result support the evolution.
 
@@
 [] This work confirm the bright future of lensing.
+
+Look at the future? JWST and TDCOSMO will extend the sample size.
 

### 2020-03-02 manuscript/manuscript.tex
Update manuscript.tex

@@
 SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
+HS2209 & xxx & xxx & xxx &  xxx  \\
 HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
@@
       \small
-      \item Note: $-$ The reference for the board line information. For SDSS1206, we follow Birrer2018 and consider the magnification effect to correct the L.
+      \item Note: $-$ The reference for the board line information. For SDSS1206, we follow Birrer2018~ref[] and consider the magnification effect to correct the L.
 \end{tablenotes}  
@@
 \section{surface photometry with lensing technique}
-We describe the reconstruction of the lensed host galaxy in this section.
-For part of the lensed systems, the lens models have been derived with host galaxies reconstructed ref[].
-Aiming at the time-delay cosmography, these works focused on deriving the precise and accurate lens models, while the reconstructed the host galaxy is only a by-product.
-Thus, in this paper, we apply our own approach to infer the photometry of the host galaxy in the source plane.
-For cross check purpose, we will compare our inference to the reconstructions by the previous works.
+We present the lensed host galaxy source reconstruction to derive their intrinsic photometry in this section.
+Our lensed AGN systems are from the H0LiCOW project, and the lens models of four systems have been derived with host galaxies reconstructed ref[].
+Aiming at time-delay cosmography, these works focused on deriving the precise and accurate lens models, while the reconstruction of the host galaxy is only a by-product.
+In this paper, we apply the state-of-the-art lens modeling technique and dedicate to recovering the photometry of the host galaxy.
+As will show, approach would allow us to obtain a one-step host magnitude defined by \sersic\ profile, which is consistent to the definitions in the literature.
+%Furthermore, for cross check purpose, we compare our inference to the reconstructions by the previous works.
 
@@
 We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component.
-For single \sersic\ case, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference.
-By this definition, we could infer the host flux as consistent to our comparison sample.
+For single \sersic\ case, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in ref[] that this prior value would result in a consistent host magnitude inference as to fix n to its true value.}.
 The bright AGNs are unsolved and modelled by a scaled point spread function (PSF).
-We adopt the elliptical power-law model to describe the surface mass density of the deflector.
+We adopt the elliptical Power-law model to describe the surface mass density of the deflector.
 An external shear component is also considered.
@@
 We employ the imaging modelling tool \lenstronomy~ref[] to perform the fitting task.
-We following the standard procedure as introduced by~\citet{Ding2020} to produce the fitting ingredients including the lensing imaging data, noise level map and the PSF condition.
-We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood.
+We following the standard procedure as described by~\citet{Ding2020} to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information.
+The imaging data are drizzled to a higher resolution by setting a Gaussian kernel; the adopted final resolution are listed in Table~\ref{data_set}.
+We then adopt the {\sc photutils} by Python to model the 2-D global background light using SExtractor algorithm.
+We then remove the background light and cut the clear image data into postage stamp at a suitable size.
+We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood; see Figure~\ref{fig:image_inference}.
 
-For each lens systems, we adopt different choices to perform the fitting.
+For each lens system, we adopt different choices to perform the fitting.
 The distribution of the fitting inference are assumed to sufficiently cover the truth.
@@
 \begin{enumerate}
-\item  We select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is input as the initial PSF to perform the fitting.
+\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF.
+Each selected star is consider as the initial PSF to input to the fitting, which is considered as different choice.
 \item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF.
-To avoid overfitting the noise, we choose to either manually boost the noise estimate in the central area to effectively infinite, or perform the iterative PSF estimation ref[].
-\item To perform the ray tracing through a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
-\item Since using the lensing imaging alone is difficult to constrain the power-law slope, we choose to fixed the slope values with three options $[1.9, 2.0, 2.1]$.
+To avoid overfitting the noise, we adopt two modeling choices.
+1)~manually boost the noise estimate in the central area to effectively infinite; 2)~perform the iterative PSF estimation as introduced by ref[].
+\item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
+\item Using the lensing imaging alone is difficult to constrain the power-law slope.
+To avoid any overfitting, we fix the slope values during the lens modelling with three optional value $[1.9, 2.0, 2.1]$.
 \end{enumerate}
 
-For a lens system with a number of $N$ initial PSFs, there are in total $N\times12$ (i.e., $2 \times2 \times3$) fittings.
-After the all sets of fittings are completed, we rank the performance of each choice based on their best-fitted $\chi^2$ value.
-We adopt the weighting algorithm as introduced by ~\citet{Ding2020} and combine the top eight choices to derive the final inference and estimate the uncertainties.
+All in all, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting.
+After  all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value.
+Finally, we adopt the weighting algorithm as introduced by Equations (3)$-$(6) in~\citet{Ding2020} and combine the top eight choices to derive the final value and evaluate the uncertainties.
 
 \subsection{Photometry Inference}
-In the result of this section, we describe the details of the fitting for each systems and present the corresponding inference of the host photometry information.
+In this subsection, we describe the details of the fitting for each systems and present our inference of the host galaxy photometry.
 
-%remember to present a table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic. 
 \subsubsection{HE0435}
-We follow Ken[] and assuming light of the deflector are composed of two elliptical \sersic\ with index value $n$ fixed to $1$ and $4$ to represent the disk and bulge components
+The modeling is set up based on the descriptions in the last section.
+We select five isolated stars in this field initial PSFs to input to the fitting with in total of 60 fittings for this system.
+Based on the top-eight choices, we perform the weighting algorithm and measure the host-to-total flux ratio, host magnitude, effective radius and \sersic\ index.
+The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(5) columns.
 
-We select five isolated stars in this field initial PSFs to input to the fitting thus, we have in total 60 fittings for this case.
-The best-fit models are present in the Figure~\ref{fig:image_inference}-(a).
-Using the top eight inference, we use weighting to combining them and inferred the results.
-The fitting image and inferred parameter, including: Einstein Radius, host n, host Reff, host flux, host flux ratio.
+The lens model inference based on the best-fit result for HE0435 is drawn in Figure~\ref{fig:image_inference}-(a).
+Not surprisingly, we note that the residual level reveals are appears to be larger than the ones as presented by Ken[] or Simon[].
+This is due to the fact that the definition of the host galaxy in our models is a 2-D \sersic\ model which is relatively simple compare to the pixellated reconstruction technique by {\sc Glee} or the shapelet functions as adopted by \lenstronomy.
+The smooth feature of our model couldn't capture the clumps in the host of the star-forming regions, however, our model is more effective to derive the global host light as function of the \sersic\ which is consistent to measurements in the comparison sample.
 
-Note that the residual level reveals in the inference figures are appears to be larger than the ones as presented by Ken[].
-The major reason is the definition of the host galaxy in the models.
-Without using sophisticated models such as shepelet or pixellized ones, we will be able to infer directly the \sersic\ flux of the host galaxy.
-
-We compare the result with the inferred host galaxy by Ken[] and Ding+2017.
+As a cross check, we compare our host magnitude to the measurement in Ding+2017[], in which they model the reconstructed host galaxy as \sersic\ based on Galfit [].
+The host magnitude measured in that paper is: $mag = 21.75 \pm 0.13$%, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
+which is slightly fainter than our results, i.e. $mag = 21.33 \pm 0.2$. \ding{Some discussion of the origin of this offset?}
+Still, the center mismatch is only $0.15$~dex, which is a little of the total error budget.
 
@@
 We carry out the similar steps to modeling at the two band.
-Given that the data quality and the host flux is less bright in these two bands, we only focus on modeling lensed arcs in the image plane.
-Based on the obtained color information, we estimate the stellar template and derive the stellar mass based on the intrinsic magnitude inferred by the F160W band.
+The inferred host magnitudes are xxx and xxx, respectively.
+Nevertheless, given that the data quality and the host flux is less bright in these two bands, we only combining the modeling lensed arcs in the image plane to inference the color of the host galaxy and we use {\sc Gsf} code to fit the color and find a 1.5 Gyr stellar template with solar metallicity could well match this color.
+This stellar template would be adopted to infer the \mstar\ in the next section.
 
@@
 \caption{\label{fig:image_inference} 
-Something}
+Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
 \end{figure*}
@@
 \subsubsection{RXJ1131}
-The RXJ1131 is the other system that has been studied in \citet{Ding2017b}.
-The host galaxy is lensed to a extended arc with a feature of bulge $+$ disk clearly appeared, we consider them both in the fitting.
+The RXJ1131 has been well studied in many reference.
+The host galaxy of this system is lensed to a spacious arc with a boundary line between the dominated area of bulge and disk could be clearly seen.
+Thus, we set the host galaxy is composed of two \sersic\ with index value $n$ fixed to $1$ and $4$ to mimic the light distribution of the disk and bulge, respectively.
+Besides, same as suyu[], we consider the perturbations by the small object in the north and fitting it as a SIS and \sersic\ for its mass and light.
 
-We compare to the previous reconstructions. The bulge are consistent, however, our inferred disk are brighter.
+The inference of the RXJ1131 based on three initial PSFs are summarized in Table~\ref{tab:host_measure}, with the best-fit result drawn in Figure~\ref{fig:image_inference}-~(b).
+
+We also compare our measurement to the previous reconstructions in Ding.
+Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{disk} = 20.07\pm0.06$ and $mag_{bulge} = 21.81 \pm 0.28$.
+Compared to our inference in Table~\ref{tab:host_measure}, our bulge flux is consistent $\sim0.25$ dex, however, while the inferred disk light is much brighter by $\sim 0.7$ dex.
+
+Due to the arc is extend and resolved to the PSF, one can directly perform the SED fitting of the arc in the image plane.
+Based on the inference in Ding[], we adopt 3 Gyr and 1.5 Gyr stellar template to its disk and bulge respectively.
 
@@
   \begin{threeparttable}
-\caption{Summary of lensed AGN inference.}\label{data_set}    
+\caption{Summary of lensed AGN inference.}\label{tab:host_measure}    
 %\resizebox{12cm}{!}{
@@
 
-\subsection{Stellar mass estimates}
+\section{Results}
+In this section, we present the inference of the stellar mass to derive the scaling relations. We compare our measurements to the ones by the  literature samples to study their evolution.
+
+\subsection{Stellar mass}
 [] Color inference for the first three cases to decide their stellar template.
@@
 %[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.
-
-\section{Results}
-Derive the the inference of our sample, we over plot our measurements on top of the measurements by \citet{Ding2020}, shown in Figure.
+Deriving the the inference of our sample, we over plot our measurements on top of the measurements by \citet{Ding2020}, shown in Figures.
 The result demonstrate an excellent consistency.
 and the result support the evolution.
+
+\subsection{The \mbh-\mstar\ relation}
+We combine the \mstar\ to their \mbh\ and compare to the ones in the literature.
 

### 2020-03-02 0_HE0435/model/3_summary.py
for python 3

@@ -33,7 +33,7 @@ ID = path.split('/')[-2]
 PSFno_ = range(psf_num)
 #The values to pick up:
 filename = pkl_folderfiles[0]
-result = pickle.load(open(filename,'rb'))
+result = pickle.load(open(filename,'rb'),encoding="latin1") 
 fit_result, trans_result, kwargs_material, model_lists  = result
 pick_names = trans_result[-1]
 
@@ -68,8 +68,8 @@ for folder in folder_i:
             fixgamma = (filename.split('gammafix')[1]).split('_subg')[0]
             if fixgamma not in fixgamma_list:
                 fixgamma_list.append(fixgamma)
-            print filename
-            result = pickle.load(open(filename,'rb'))
+            print(filename)
+            result = pickle.load(open(filename,'rb'),encoding="latin1") 
             fit_result, trans_result, kwargs_material, model_lists  = result
             fit_value_l_i, fit_value_m_i, fit_value_h_i, = [], [], []
             for pick in range(len(pick_names)):
@@ -99,9 +99,9 @@ for i in range(len(labels)):
         raise ValueError("The labels is wrong for some reason")
         
 for i in range(len(pick_names)):
-    print i, ':', pick_names[i]
-print pick_names
-pick = input('select the names to plot?:\n')
+    print(i, ':', pick_names[i])
+print(pick_names)
+pick = int(input('select the names to plot?:\n'))
 
 fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
 fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
@@ -122,11 +122,11 @@ label0 = [labels[i].split(',')[0] for i in index0]
 index1 = [i*12+11 for i in range(len(bars))]
 label1 = [labels[i].split(',')[0] for i in index1]
 if label0 != label1 or bars!= label0:
-    print label0, label1
+    print(label0, label1)
     raise ValueError("The labels is wrong for some reason")
 color = ['green', 'orange']
 
-count_n =len(labels) * 20 /100
+count_n = 8 #len(labels) * 20 /100
 chisq = [float(chisq[i]) for i in range(len(chisq))]
 sort_chisq = np.argsort(np.asarray(chisq))    
 Chisq_best = chisq[sort_chisq[0]]
@@ -140,7 +140,7 @@ for i in sort_chisq[:count_n]:
[…]

### 2020-03-02 1_RXJ1131/model/3_summary.py
Update for Python3

@@ -34,7 +34,7 @@ ID = path.split('/')[-2]
 PSFno_ = range(psf_num)
 #The values to pick up:
 filename = pkl_folderfiles[0]
-result = pickle.load(open(filename,'rb'))
+result = pickle.load(open(filename,'rb'),encoding="latin1") 
 fit_result, trans_result, kwargs_material, model_lists  = result
 pick_names = trans_result[-1]
 
@@ -69,8 +69,8 @@ for folder in folder_i:
             fixgamma = (filename.split('gammafix')[1]).split('_subg')[0]
             if fixgamma not in fixgamma_list:
                 fixgamma_list.append(fixgamma)
-            print filename
-            result = pickle.load(open(filename,'rb'))
+            print(filename)
+            result = pickle.load(open(filename,'rb'),encoding="latin1") 
             fit_result, trans_result, kwargs_material, model_lists  = result
             fit_value_l_i, fit_value_m_i, fit_value_h_i, = [], [], []
             for pick in range(len(pick_names)):
@@ -95,9 +95,9 @@ labels = [x for _,x in sorted(zip(labels,labels))]  # Sort the label at the last
 #%% Still needs to be tested:
 labels = copy.deepcopy(labels)
 for i in range(len(pick_names)):
-    print i, ':', pick_names[i]
-print pick_names
-pick = input('select the names to plot?:\n')
+    print(i, ':', pick_names[i])
+print(pick_names)
+pick = int(input('select the names to plot?:\n'))
 
 fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
 fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
@@ -112,7 +112,7 @@ label0 = [labels[i].split(',')[0] for i in index0]
 index1 = [i*12+11 for i in range(psf_num)]
 label1 = [labels[i].split(',')[0] for i in index1]
 if label0 != label1 or bars!= label0:
-    print label0, label1
+    print(label0, label1)
     raise ValueError("The labels is wrong for some reason")
 color = ['green', 'orange']
 
@@ -138,7 +138,7 @@ def plt_result(fixgamma, chisq=chisq, ID = ID):
     adjust_text(texts, arrowprops=dict(arrowstyle='->', color='red'))            
     
     xs = np.linspace(x_pos[0], x_pos[-1])
[…]

### 2020-03-02 2_WFI2033/model/3_summary.py

@@ -33,7 +33,7 @@ ID = path.split('/')[-2]
 PSFno_ = range(psf_num)
 #The values to pick up:
 filename = pkl_folderfiles[0]
-result = pickle.load(open(filename,'rb'))
+result = pickle.load(open(filename,'rb'),encoding="latin1") 
 fit_result, trans_result, kwargs_material, model_lists  = result
 pick_names = trans_result[-1]
 
@@ -68,8 +68,8 @@ for folder in folder_i:
             fixgamma = (filename.split('gammafix')[1]).split('_subg')[0]
             if fixgamma not in fixgamma_list:
                 fixgamma_list.append(fixgamma)
-            print filename
-            result = pickle.load(open(filename,'rb'))
+            print(filename)
+            result = pickle.load(open(filename,'rb'),encoding="latin1") 
             fit_result, trans_result, kwargs_material, model_lists  = result
             fit_value_l_i, fit_value_m_i, fit_value_h_i, = [], [], []
             for pick in range(len(pick_names)):
@@ -99,9 +99,9 @@ for i in range(len(labels)):
         raise ValueError("The labels is wrong for some reason")
         
 for i in range(len(pick_names)):
-    print i, ':', pick_names[i]
-print pick_names
-pick = input('select the names to plot?:\n')
+    print(i, ':', pick_names[i])
+print(pick_names)
+pick = int(input('select the names to plot?:\n'))
 
 fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
 fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
@@ -115,7 +115,7 @@ label0 = [labels[i].split(',')[0] for i in index0]
 index1 = [i*12+11 for i in range(len(bars))]
 label1 = [labels[i].split(',')[0] for i in index1]
 if label0 != label1 or bars!= label0:
-    print label0, label1
+    print(label0, label1)
     raise ValueError("The labels is wrong for some reason")
 color = ['green', 'orange']
 
@@ -131,7 +131,7 @@ for i in range(len(sort_chisq)):
     weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best))
 weighted_value = np.sum(np.array(fit_value_m)*weight) / np.sum(weight)
[…]

### 2020-03-02 3_SDSS1206/model/3_summary.py

@@ -18,7 +18,7 @@ from adjustText import adjust_text   # avoid the overlapping while ploting
 sys.path.insert(0,'../../share_tools/')
 from read_chisq import return_chisq 
 
-pre_head = '2nd_'
+pre_head = 'singel_'
 
 pkl_folderfiles = glob.glob(pre_head+"fit_PSFi_PSFrecons/result_PSF*.pkl")
 pkl_files = [pkl_folderfiles[i].split('/')[1] for i in range(len(pkl_folderfiles))]
@@ -37,7 +37,7 @@ ID = path.split('/')[-2]
 
 #The values to pick up:
 filename = pkl_folderfiles[0]
-result = pickle.load(open(filename,'rb'))
+result = pickle.load(open(filename,'rb'),encoding="latin1") 
 fit_result, trans_result, kwargs_material, model_lists  = result
 pick_names = trans_result[-1]
 
@@ -72,8 +72,8 @@ for folder in folder_i:
         fixgamma = (filename.split('gammafix')[1]).split('_subg')[0]
         if fixgamma not in fixgamma_list:
             fixgamma_list.append(fixgamma)
-        print filename
-        result = pickle.load(open(filename,'rb'))
+        print(filename)
+        result = pickle.load(open(filename,'rb'),encoding="latin1") 
         fit_result, trans_result, kwargs_material, model_lists  = result
         fit_value_l_i, fit_value_m_i, fit_value_h_i, = [], [], []
         for pick in range(len(pick_names)):
@@ -103,9 +103,9 @@ for i in range(len(labels)):
         raise ValueError("The labels is wrong for some reason")
         
 for i in range(len(pick_names)):
-    print i, ':', pick_names[i]
-print pick_names
-pick = input('select the names to plot?:\n')
+    print(i, ':', pick_names[i])
+print(pick_names)
+pick = int(input('select the names to plot?:\n'))
 
 fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
 fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
@@ -120,7 +120,7 @@ label0 = [labels[i].split(',')[0] for i in index0]
 index1 = [i*12+11 for i in range(len(bars))]
 label1 = [labels[i].split(',')[0] for i in index1]
 if label0 != label1 or bars!= label0:
-    print label0, label1
[…]

### 2020-03-02 manuscript/manuscript.tex
Update manuscript.tex

@@
 % Keep the title short and informative.
-\title[lens source reconstruction]{H0LiCOW: correlation between black hole mass and host galaxy luminosity.}
+\title[Mass relations by lensed AGN hosts]{The Mass Relations between Supermassive Black Holes and Their Host Galaxies by Eight Strongly Lensed AGN Systems.}
 
@@
 Chris Fassnacht,
+Matthew W. Auger,
+Sherry H. Suyu,
+Kenneth C. Wong,\newauthor
+Takahiro Morshita,
 and et al. $^{3}$
@@
 The bright AGNs are unsolved and modelled by a scaled point spread function (PSF).
-We adopt the elliptical Power-law model to describe the surface mass density of the deflector.
-An external shear component is also considered.
+We also joint the fitting of the AGN position to the center of its host.
+ We adopt the elliptical Power-law model to describe the surface mass density of the deflector; an external shear component is also added.
 
@@
 Thus, we set the host galaxy is composed of two \sersic\ with index value $n$ fixed to $1$ and $4$ to mimic the light distribution of the disk and bulge, respectively.
-Besides, same as suyu[], we consider the perturbations by the small object in the north and fitting it as a SIS and \sersic\ for its mass and light.
+Besides, same as suyu[], we consider the perturbations by the small object ($0\farcs{5}$ in the north) and fitting as the SIS and \sersic\ for its mass and light, respectively.
 
@@
 We also compare our measurement to the previous reconstructions in Ding.
-Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{disk} = 20.07\pm0.06$ and $mag_{bulge} = 21.81 \pm 0.28$.
-Compared to our inference in Table~\ref{tab:host_measure}, our bulge flux is consistent $\sim0.25$ dex, however, while the inferred disk light is much brighter by $\sim 0.7$ dex.
+Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{\rm disk} = 20.07\pm0.06$ and $mag_{\rm bulge} = 21.81 \pm 0.28$.
+Compared to our inference in Table~\ref{tab:host_measure}, our inferred bulge flux is consistent at $\sim0.25$ dex level, however, while the inferred disk light is much brighter by $\sim 0.7$ dex.
 
-Due to the arc is extend and resolved to the PSF, one can directly perform the SED fitting of the arc in the image plane.
-Based on the inference in Ding[], we adopt 3 Gyr and 1.5 Gyr stellar template to its disk and bulge respectively.
+Due to the fact that the arc is very extended in the image plane which is resolved to the AGNs, one could directly perform the SED fitting of the arc in the image plane.
+Combining the HST imaging data through F814W and F555W, Ding[] has inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its disk and bulge, respectively.
 
 \subsubsection{WFI2033}
-The objects which is close to the lens, we model its light as one extended source described by \sersic\ profile.
+WFI2033 is the last quads which has also been carefully studied recently in Ken[].
+There is a satellite galaxy in the north.
+However, as noted by Ken[], it has a much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using a \sersic\ model.
+There are in total of eight PSF stars are selected to modelling this system.
+
+The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-~(c).
+We also compare the inference to the reconstructions by Ken.
+Fitting their reconstruction as a \sersic\ profile, we have inferred that $mag = 21.98 \pm 0.15$ which is slightly fainter than our inference by $\sim0.2$~dex.
+
+Besides the F160W filter, there are also four other filters by F125W, F140W, F555W and F814W was available in the HST.
+We perform the lens model inference for all the filter and infer the host color through five band in the image plane.
+We find a stellar template with 0.625 Gyr could well match their color.
 
 \subsubsection{SDSS1206}
+SDSS1206 is a special system -- the AGN is a doubly images while most of the host is falls inside the inner caustic thus being quadruply imaged.
+We consider the galaxy triplet group at the north-west and use a single SIS model to denote their over all mass perturbations.
+Moreover, as noted by Simon[] (Figure 1 therein), a sub-clump is located in the north which is hardly visible.
+We model it as a SIS mass model and circular \sersic\ light model with joint centroids.
+Though we see the visible residuals in the fitted arcs using a single \sersic\ model, we find a double \sersic\ could help significantly improve the goodness of the fitting.
+Thus, we adopt the single \sersic\ model in our final inference.
+
+The results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-~(d).
+\todo{Ask Simon for the reconstruction image to compare.}
+
+Beside F160W, there is no other \hst\ imaging data for this system and the color.
+For such case, we adopt the criteria by Ding2020[] to define the stellar template, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
+Since the source redshfit of SDSS1206 is at 1.79, a 0.625 Gyr is selected.
 
@@
 HE0435 & $21.332\substack{+0.208\\-0.175}$ & $62.471\pm10.893$ & $0.298\pm0.027$ & $2.829\pm0.251$ & $1.500$ & $10.98\substack{+0.07\\-0.08}$ \\
-RXJ1131$_{\rm bulge}$ & $22.074\substack{+0.164\\-0.142}$ & $6.634\pm0.929$ & $0.106\pm0.007$ & fix to 4 & $3.000$ & $1.01\substack{+0.06\\-0.07}$ \\
-RXJ1131$_{\rm disk}$ & $19.305\substack{+0.154\\-0.135}$ & $84.939\pm11.241$ & $0.875\pm0.062$ & fix to 1 & $1.500$ & $1.04\substack{+0.05\\-0.06}$ \\
+RXJ1131$_{\rm bulge}$ & $22.074\substack{+0.164\\-0.142}$ & $6.634\pm0.929$ & $0.106\pm0.007$ & fix to 4 & $3.000$ & $10.28\substack{+0.06\\-0.07}$ \\
+RXJ1131$_{\rm disk}$ & $19.305\substack{+0.154\\-0.135}$ & $84.939\pm11.241$ & $0.875\pm0.062$ & fix to 1 & $1.500$ & $11.09\substack{+0.05\\-0.06}$ \\
 WFI2033 & $21.404\substack{+0.167\\-0.145}$ & $35.723\pm5.093$ & $0.294\pm0.025$ & $0.528\pm0.011$ & $0.625$ & $10.66\substack{+0.06\\-0.07}$ \\
@@
 We took the other band data and get the only arc image. We adopt these image and do the SED fitting to get the color information.
+\subsection{HE0435}
+The HE0435 system has been modelled through three band. In the Figure, we demonstrate the host inference in the image plance for the three bands.
+
+\subsection{WFI2033}
+The WFI2033 system has been modelled through five band.
 

### 2020-03-02 material/print_table.py
Correct the RXJ1131 Mstar

@@ -126,7 +126,7 @@ for i in range(len(IDs)):
 			table = hdul[1].data	
 			tab_name = hdul[1].columns
 			mstar_idx = [ii for ii in range(len(tab_name)) if 'Mstel' in str(tab_name[ii])][0]
-			m_star =  round(table[1][mstar_idx],3)
+			m_star =  10**table[1][mstar_idx]
 			age_idx = [ii for ii in range(len(tab_name)) if 'T_MW' in str(tab_name[ii])][0]
 			age = round(10**table[1][age_idx],3)
 

### 2020-03-04 MBH_estimator/est_MBH.py
Update for easier load fitting results

@@ -62,7 +62,7 @@ def est_MBH(ID):
 MBH_dic = {}
 for key in MBH_by_Domini.keys():
     MBH_dic[key] = np.mean(est_MBH(key))
-    print(key, est_MBH(key), MBH_by_Domini[key][0])
+#    print(key, est_MBH(key), MBH_by_Domini[key][0])
     
 #MBH_dic =     {'HE0435': 8.543644440905101,
 # 'RXJ1131': 8.347036339665747,

### 2020-03-04 Stellar_mass_estimate/host_fnu_inference.py

@@ -4,72 +4,13 @@ import matplotlib.pyplot as plt
 import pickle
 import glob
 import copy
-IDs = ['0_HE0435', '1_RXJ1131', '1_RXJ1131_disk', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
+IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
 
-weighted_value_list, rms_value_list = [], []
 
-prop = 0
 
-#%%
-for i in range(len(IDs)):
-	ID = IDs[i][2:]
-	if ID == "SDSS1206" :
-		filename = ID+'_singel_host_run_summary.pkl'
-	else:
-		filename = ID+'_2nd_run_summary.pkl'
-	disk_note = 0
-	if ID == "RXJ1131_disk" :
-		ID = 'RXJ1131'
-		filename = ID+'_2nd_run_summary.pkl'
-		disk_note = 1
-	# filename = ID+'_2nd_run_summary.pkl'	
-	result = pickle.load(open("../share_tools/"+filename,'rb'),encoding="latin1") 
-	fit_values, chisq, labels, pick_names = result
-	sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
-	fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values
-	for i in range(len(labels)):
-		if labels[i][-17:] != sort_label_type[i%4]:
-			raise ValueError("The labels is wrong for some reason")
-	if 'Disk' in pick_names[2]:
-		pick = 4
-	else:
-		pick = 3
-	if disk_note == 1:
-		pick = 5
-	# print(ID, pick_names)
-	fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
-	fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
-	fit_value_h = [fit_value_h_list[i][pick] for i in range(len(labels))]
-	count_n = 8
-	chisq = [float(chisq[i]) for i in range(len(chisq))]
-	sort_chisq = np.argsort(np.asarray(chisq))    
-	Chisq_best = chisq[sort_chisq[0]]
-	#Chisq_last= chisq[sort_chisq[-1]]
[…]

### 2020-03-04 share_tools/read_inference.py

@@ -13,60 +13,161 @@ import pickle
 import glob
 import copy
 
-def read_inf(ID, prop=0 , count_n=8, rod = 3):
-	if ID == "SDSS1206" :
-		filename = ID+'_singel_host_run_summary.pkl'
-	else:
-		filename = ID+'_2nd_run_summary.pkl'
-	result = pickle.load(open('../share_tools/'+filename,'rb'),encoding="latin1")
-	fit_values, chisq, labels, pick_names = result
-	sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
-	fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values
-	for i in range(len(labels)):
-		if labels[i][-17:] != sort_label_type[i%4]:
-			raise ValueError("The labels is wrong for some reason")
-	if prop == 0 :  #Flux
-		if 'Disk' in pick_names[2]:
-			picks = [4,5]
-		else:
-			picks = [3]
-	elif prop == 1: #Reff
-		if 'Disk' in pick_names[2]:
-			picks = [6,7]
-		else:
-			picks = [5]
-	elif prop == 2: #Sersic n
-		if 'Disk' in pick_names[2]:
-			picks = []
-		else:
-			picks = [4]
-	elif prop == 3: #AGN flux
-		if 'Disk' in pick_names[2]:
-			picks = [3]
-		else:
-			picks = [2]
-			
-#	print(ID, pick_names)
-	result = []
-	for pick in picks:
-		fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
-		count_n = count_n
-		
-		chisq = [float(chisq[i]) for i in range(len(chisq))]
-		sort_chisq = np.argsort(np.asarray(chisq))    
-		Chisq_best = chisq[sort_chisq[0]]
-		#Chisq_last= chisq[sort_chisq[-1]]
-		Chisq_last= chisq[sort_chisq[count_n-1]]
-		weight = np.zeros(len(chisq))
-		inf_alp = (Chisq_last-Chisq_best) / (2*2.* Chisq_best)
-		for i in sort_chisq[:count_n]:
-		#for i in range(len(sort_chisq)):
-		#    weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best))
[…]

### 2020-03-04 relation_plots/MM_32QSO.py
Update the figure with new way of weighting

@@ -301,15 +301,15 @@ plt.errorbar(Mstar,MBs, xerr=[np.abs(Mstar_err)[:,0], np.abs(Mstar_err)[:,1]], y
 #folders = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
 h0licow = ['HE0435', 'RXJ1131', 'WFI2033', 'SDSS1206', 'HE1104', 'SDSS0246', 'HE0047']#, 'HS2209']
 sys.path.insert(0,'../Stellar_mass_estimate')
-from mstar_inference import mstar_dict
+#from mstar_inference import mstar_dict
+sys.path.insert(0,'../share_tools')
+from read_inference import read_mstar
 sys.path.insert(0,'../MBH_estimator')
 from est_MBH import MBH_dic
 texts = []
 for ID in h0licow:
-    Mstar = mstar_dict[ID]
+    Mstar = np.log10(read_mstar(ID, count_n=[4, 4])[0][0])
     MBs = MBH_dic[ID]
-    if ID == 'RXJ1131':
-        Mstar = np.log10(10**Mstar[0])# + 10**Mstar[1])
     plt.scatter(Mstar, MBs, c='blue',s=580,marker=".",zorder=100, edgecolors='k')
     texts.append( plt.text(Mstar, MBs, ID, fontsize=15, zorder=200) )
 adjust_text(texts, arrowprops=dict(arrowstyle='->', color='red')) 

### 2020-03-04 relation_plots/MM_vz_32QSO.py

@@ -422,13 +422,14 @@ sys.path.insert(0,'../MBH_estimator')
 from est_MBH import MBH_dic
 sys.path.insert(0,'../share_tools')
 from lens_information import lens_redshift
+from read_inference import read_mstar
 
 texts = []
 for ID in h0licow:
     Mstar = mstar_dict[ID]
     MBs = MBH_dic[ID]
     if ID == 'RXJ1131':
-        Mstar = np.log10(10**Mstar[0])# + 10**Mstar[1])
+        Mstar = np.log10(read_mstar(ID, count_n=[4, 4])[0][0])
 #    plt.scatter(Mstar, MBs[0], c='blue',s=580,marker=".",zorder=100, edgecolors='k')
     plt.scatter(np.log10(1+lens_redshift[ID]),MBs-(m_ml*Mstar+b_ml),c='blue',
             s=280,marker="*",zorder=300, vmin=0.3, vmax=5, edgecolors='k')

### 2020-03-04 6_HS2209/model/1_clean_save_PSF.py
Update HS2209 fitting

@@ -21,9 +21,9 @@ psfname_list = glob.glob('PSF?.fits')
 psfname_list.sort()
 psfs = []
 for i in range(len(psfname_list)):
-    print "PSF:", psfname_list[i]
+    print("PSF:", psfname_list[i])
     psf_i = pyfits.getdata(psfname_list[i])
-    print psf_i.sum()
+    print(psf_i.sum())
     mask_files = glob.glob('PSF{0}_mask*.reg'.format(i))
     if mask_files != []:
         psf_mask = cr_mask_img(psf_i, mask_list=mask_files)
@@ -33,7 +33,7 @@ for i in range(len(psfname_list)):
             for j in range(len(psf_i)):
                 if psf_mask[i, j] == 0:
                     psf_clear[i, j] = (psf_i[-i-1, -j-1]*psf_mask[-i-1, -j-1])
-        print "plot PSF after clear:"
+        print("plot PSF after clear:")
         psf_i = psf_clear
     plt.imshow(psf_i, origin = 'low', norm=LogNorm())
     plt.show()
@@ -45,8 +45,8 @@ for i in range(len(psfname_list)):
 #fig.savefig("PSFs_profile.pdf")
 #fig.show()
 
-framesize = 81
-ct = (len(psfs[0]) - framesize)/2    
+framesize = 111
+ct = int((len(psfs[0]) - framesize)/2)
 for i in range(len(psfs)):
     psfs[i] = psfs[i][ct:-ct,ct:-ct]
     psfs[i] = psfs[i]/np.sum(psfs[i])

### 2020-03-04 6_HS2209/model/3rd_fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py

@@ -1,0 +1,325 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+In this script, fix gamma as Ken's results. Use, psf mask.
+Use PSF reconstruction.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+#sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+from mask_objects import mask_obj
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+
+old_folder = '../2nd_fit_PSFi'+path.split('fit_PSFi')[1]
+
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))   #!!!need to change
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))    #!!!need to change
+
+lens_mask = 1-cr_mask(lens_image, filename='../lens_mask.reg')
+
+framesize = 101
+ct = (len(lens_image) - framesize)/2
+lens_image = lens_image[ct:-ct,ct:-ct]
+lens_rms = lens_rms[ct:-ct,ct:-ct]
[…]

### 2020-03-04 6_HS2209/model/3rd_fit_PSFi_QSOmask/2_modelling_fix_gamma_QSO_mask.py

@@ -1,0 +1,324 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+The QSO center noise level is boost to inf.
+psf_error_map not taken.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+#sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+from mask_objects import mask_obj, find_loc_max
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+
+old_folder = '../2nd_fit_PSFi'+path.split('fit_PSFi')[1]
+
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))   #!!!need to change
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))    #!!!need to change
+
+lens_mask = 1-cr_mask(lens_image, filename='../lens_mask.reg')
+
+framesize = 101
+ct = (len(lens_image) - framesize)/2
+lens_image = lens_image[ct:-ct,ct:-ct]
+lens_rms = lens_rms[ct:-ct,ct:-ct]
[…]

### 2020-03-04 6_HS2209/model_05data/3_read_result.py

@@ -18,8 +18,8 @@ sys.path.insert(0,'/Users/Dartoon/Astro/projects/my_code/py_tools/')
 from flux_profile import cr_mask
 
 
-#readfile = 'fit_PSFi_PSFrecons/result_PSF0_PSFrecons_gammafix1.9_subg2.pkl'
-readfile = '2nd_fit_PSFi_QSOmask/result_PSF2_QSOmask_gammafix1.9_subg3.pkl'
+readfile = 'fit_PSFi_PSFrecons/result_PSF0_PSFrecons_gammafix1.9_subg2.pkl'
+#readfile = 'fit_PSFi_QSOmask/result_PSF2_QSOmask_gammafix1.9_subg3.pkl'
 result = pickle.load(open(readfile,'rb'),encoding="latin1") 
 fit_result, trans_result, kwargs_material, model_lists  = result
 

### 2020-03-04 manuscript/manuscript.tex
Update manuscripts, figures and tables.

@@
 % Keep the title short and informative.
-\title[Mass relations by lensed AGN hosts]{The Mass Relations between Supermassive Black Holes and Their Host Galaxies by Eight Strongly Lensed AGN Systems.}
+\title[Mass relations by lensed AGN hosts]{The Mass Relations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGN Systems.}
 
@@
 In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
-The detailed information for the information of these eight systems are given in Table~1 therein.
-Besides, half of the systems, including HE0435, RXJ1131, WFI2033 and HE1104 have \hst\ imaging data in multi-bands.
-To estimate the \mbh, we adopt the spectra information as inferred by \citet{Sluse2012, Peng2006, Shen2011}.
-We use a Table[] to summarize the data information.
+The detailed information of the observational conditions of our eight systems are given in Table~\ref{data_set}.
+Besides the adopted filter shown therein, some systems also observed by \hst\ by different bands.
+As will shown in Section~\ref{sec:mstar}, the multi-band information enables us to apply the stellar population, hence a more accurate \mstar\ estimation.
 
@@
 %
-Having achieved a consistent cross-calibration, we adopt the board line information from the literature to estimate the \mbh.
+Having achieved a consistent cross-calibration, we adopt the board line information from the literature \citep{Sluse2012, Peng2006, Shen2011} to estimate the \mbh.
 The information are presented in Table~\ref{mbh}.
@@
 The modeling is set up based on the descriptions in the last section.
-We select five isolated stars in this field initial PSFs to input to the fitting with in total of 60 fittings for this system.
+We select 5 isolated stars in this field initial PSFs to input to the fitting with in total of 60 fittings for this system.
 Based on the top-eight choices, we perform the weighting algorithm and measure the host-to-total flux ratio, host magnitude, effective radius and \sersic\ index.
@@
 
-Besides the F160W band, HE0435 has also been observed by the \hst\ through F814W and F555W.
-We carry out the similar steps to modeling at the two band.
-The inferred host magnitudes are xxx and xxx, respectively.
-Nevertheless, given that the data quality and the host flux is less bright in these two bands, we only combining the modeling lensed arcs in the image plane to inference the color of the host galaxy and we use {\sc Gsf} code to fit the color and find a 1.5 Gyr stellar template with solar metallicity could well match this color.
-This stellar template would be adopted to infer the \mstar\ in the next section.
-
 \begin{figure*}
@@
 \begin{tabular}{c c}
-\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_best_inference.pdf}}&
-\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_best_inference.pdf}}\\
-\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_best_inference.pdf}}&
-\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_best_inference.pdf}}\\
-\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_best_inference.pdf}}&
-\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_best_inference.pdf}}\\
-\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_best_inference.pdf}}&
-\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_best_inference.pdf}}\\
+\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_inference.png}}&
+\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_inference.png}}\\
+\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_inference.png}}&
+\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_inference.png}}\\
+\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_inference.png}}&
+\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_inference.png}}\\
+\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_inference.png}}&
+\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_inference.png}}\\
 \end{tabular}
@@
 \subsubsection{RXJ1131}
-The RXJ1131 has been well studied in many reference.
+The image of RXJ1131 observed with ACS/F814W has been well studied in many reference.
 The host galaxy of this system is lensed to a spacious arc with a boundary line between the dominated area of bulge and disk could be clearly seen.
@@
 
-The inference of the RXJ1131 based on three initial PSFs are summarized in Table~\ref{tab:host_measure}, with the best-fit result drawn in Figure~\ref{fig:image_inference}-~(b).
+The inference of the RXJ1131 is based on 4 initial PSFs which is summarized in Table~\ref{tab:host_measure}, with the best-fit result drawn in Figure~\ref{fig:image_inference}-(b).
 
@@
 
-Due to the fact that the arc is very extended in the image plane which is resolved to the AGNs, one could directly perform the SED fitting of the arc in the image plane.
-Combining the HST imaging data through F814W and F555W, Ding[] has inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its disk and bulge, respectively.
-
 \subsubsection{WFI2033}
@@
 However, as noted by Ken[], it has a much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using a \sersic\ model.
-There are in total of eight PSF stars are selected to modelling this system.
+There are in total of 8 PSF stars are selected to modelling this system.
 
-The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-~(c).
+The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c).
 We also compare the inference to the reconstructions by Ken.
 Fitting their reconstruction as a \sersic\ profile, we have inferred that $mag = 21.98 \pm 0.15$ which is slightly fainter than our inference by $\sim0.2$~dex.
-
-Besides the F160W filter, there are also four other filters by F125W, F140W, F555W and F814W was available in the HST.
-We perform the lens model inference for all the filter and infer the host color through five band in the image plane.
-We find a stellar template with 0.625 Gyr could well match their color.
 
@@
 
-The results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-~(d).
+Due to limit of stars in the filed of view, there are only 2 stars available as initial PSF.
+To expand the volume of choice options, we also take the stack of the two bright stars as derived by Simon[] as a third initial PSF.
+Finally, the results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(d).
 \todo{Ask Simon for the reconstruction image to compare.}
 
-Beside F160W, there is no other \hst\ imaging data for this system and the color.
-For such case, we adopt the criteria by Ding2020[] to define the stellar template, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
-Since the source redshfit of SDSS1206 is at 1.79, a 0.625 Gyr is selected.
-
 \subsubsection{HE1104}
+As a typical doubly lensed image, the lens model of HE1104 is modelled by us for the first time.
+We have selected in total of 5 initial PSFs to perform the fitting.
+The inference of the image is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
+With the best-fitting model, the lensed arcs could be clearly seen from the bottom-left panel, indicating a strong evidence of the detection of the host.
 
 \subsubsection{SDSS0246}
+Imaged with WFC3-UVIS/F814W, the resolution of the data is much higher.
+However, the arc is much fainter compare to the IR band and the available pixels that could be used to fitting the arc is quite limited.
+With in total 3 initial PSF selected, the host is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) with inference list in Table~\ref{tab:host_measure}.
+A template of 0.625 Gyr stellar population would be adopt.
+
+\subsubsection{HS2209}
+The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g).
+\ding{The host magnitude might be overestimated.
+The QSO is over bright with a positive background light.
+Xuheng is Re-fitting this image.}
 
 \subsubsection{HE0047}
-
-\subsubsection{HS2209}
-
-The comparison to the previous fitting.
-
-We summarized the inference for the eight systems in the table.
-name--Setts--BestFitChisq--Totalflux-- Host ratio --Reff--Sersicn--magnitude - Stellar mass
+HE0047 is the most challenging system in our sample.
+The results, based on three PSFs, are summarized in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
+From the subtracted-everything-except-arc image, the lensed host is only half-seen among the large residuals.
+Thus, the inference of the HE0047 should be taken with larger scatters, or as upper limit.
 
 \begin{table*}
-\renewcommand{\arraystretch}{1.5}
+\renewcommand{\arraystretch}{1.25}
 %\setlength{\tabcolsep}{20pt}
@@
 \hline     
-Object ID & Magnitude & Host-Total Flux Ratio & Reff & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
+(1) & (2) & (3) & (4) & (5) & (6) & (7) \\    
+Object ID & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
  & (AB system) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
-HE0435 & $21.332\substack{+0.208\\-0.175}$ & $62.471\pm10.893$ & $0.298\pm0.027$ & $2.829\pm0.251$ & $1.500$ & $10.98\substack{+0.07\\-0.08}$ \\
-RXJ1131$_{\rm bulge}$ & $22.074\substack{+0.164\\-0.142}$ & $6.634\pm0.929$ & $0.106\pm0.007$ & fix to 4 & $3.000$ & $10.28\substack{+0.06\\-0.07}$ \\
-RXJ1131$_{\rm disk}$ & $19.305\substack{+0.154\\-0.135}$ & $84.939\pm11.241$ & $0.875\pm0.062$ & fix to 1 & $1.500$ & $11.09\substack{+0.05\\-0.06}$ \\
-WFI2033 & $21.404\substack{+0.167\\-0.145}$ & $35.723\pm5.093$ & $0.294\pm0.025$ & $0.528\pm0.011$ & $0.625$ & $10.66\substack{+0.06\\-0.07}$ \\
-SDSS1206 & $21.287\substack{+0.222\\-0.184}$ & $32.286\pm5.977$ & $0.110\pm0.020$ & $4.526\pm0.555$ & $0.625$ & $10.78\substack{+0.07\\-0.09}$ \\
-HE1104 & $21.274\substack{+0.188\\-0.160}$ & $14.142\pm2.250$ & $0.265\pm0.026$ & $1.033\pm0.034$ & $0.625$ & $11.04\substack{+0.06\\-0.08}$ \\
-SDSS0246 & $23.575\substack{+0.394\\-0.289}$ & $3.756\pm1.143$ & $0.381\pm0.098$ & $4.963\pm0.048$ & $0.626$ & $10.69\substack{+0.12\\-0.16}$ \\
-HS2209 & $20.385\substack{+0.262\\-0.211}$ & $19.454\pm4.165$ & $1.921\pm1.070$ & $2.953\pm0.438$ & $1.001$ & $11.18\substack{+0.08\\-0.10}$ \\
-HE0047 & $22.972\substack{+0.626\\-0.394}$ & $2.496\pm1.093$ & $0.282\pm0.176$ & $3.603\pm1.533$ & $0.625$ & $10.89\substack{+0.16\\-0.25}$ \\
+HE0435 & $21.492\substack{+0.402\\-0.293}$ & $35.981\pm11.127$ & $0.279\pm0.023$ & $2.710\pm0.204$ & $1.500$ & $10.91\substack{+0.12\\-0.16}$ \\
+RXJ1131$_{\rm bulge}$ & $22.092\substack{+0.221\\-0.183}$ & $6.658\pm1.225$ & $0.107\pm0.014$ & fix to 4 & $3.000$ & $10.27\substack{+0.07\\-0.09}$ \\
+RXJ1131$_{\rm disk}$ & $19.495\substack{+0.159\\-0.138}$ & $72.816\pm9.892$ & $0.845\pm0.049$ & fix to 1 & $1.500$ & $11.01\substack{+0.06\\-0.06}$ \\
+WFI2033 & $21.781\substack{+0.285\\-0.225}$ & $19.645\pm4.534$ & $0.280\pm0.017$ & $0.524\pm0.013$ & $0.625$ & $10.51\substack{+0.09\\-0.11}$ \\
+SDSS1206 & $21.310\substack{+0.232\\-0.191}$ & $33.302\pm6.413$ & $0.112\pm0.021$ & $4.568\pm0.530$ & $0.625$ & $10.77\substack{+0.08\\-0.09}$ \\
+HE1104 & $21.252\substack{+0.163\\-0.142}$ & $13.990\pm1.953$ & $0.270\pm0.023$ & $1.048\pm0.045$ & $0.625$ & $11.05\substack{+0.06\\-0.07}$ \\
+SDSS0246 & $23.437\substack{+0.279\\-0.222}$ & $3.978\pm0.901$ & $0.436\pm0.084$ & $4.964\pm0.081$ & $0.626$ & $10.75\substack{+0.09\\-0.11}$ \\
+HS2209 & $20.200\substack{+0.128\\-0.114}$ & $21.108\pm2.348$ & $3.116\pm1.834$ & $3.302\pm0.521$ & $1.001$ & $11.25\substack{+0.05\\-0.05}$ \\
+HE0047 & $22.923\substack{+0.485\\-0.334}$ & $2.347\pm0.845$ & $0.319\pm0.146$ & $4.176\pm0.750$ & $0.625$ & $10.91\substack{+0.13\\-0.19}$ \\
 \hline
@@
 
-\section{Results}
-In this section, we present the inference of the stellar mass to derive the scaling relations. We compare our measurements to the ones by the  literature samples to study their evolution.
+\section{Results}\label{sec:result}
+In this section, we describe the approaches and assumptions to adopt the stellar population to our sample.
+We then derive their stellar mass of our sample and study the  the scaling relation by connecting them to their \mbh.
+We compare our measurements by our sample to the ones in the literature to study their evolution.
 
-\subsection{Stellar mass}
-[] Color inference for the first three cases to decide their stellar template.
+\subsection{Population and stellar mass}\label{sec:mstar}
+%[] Color inference for the first three cases to decide their stellar template. 
+Besides the band we imaging data at the given band we studied in last section, some of the systems also have other band observations by the \hst, which provides the color information of the host galaxy.
+Given that the other band data has less exposure time with lower single to noise level, we highlight that we only study the color to find a decent stellar template.
+Then, it would be adopted to the host photometry obtained in last section to infer the final stellar mass.
 
-[] For the other systems, we follow Ding to assume their age based on their redshift.
+{\bf HE0435} ~ Besides WFC3/F160W, HE0435 has also been observed by the \hst\ through ACS/F814W and ACS/F555W (GO-xxxx; PI: xxxx).
+We adopted the same approaches to modeling the data separately at these two band.
+% The inferred host magnitudes are xxx and xxx, respectively.
+Considering that the lensed arcs is mainly inferred by the subtraction of the AGNs and deflectors light, it is less dependent on the lens model and thus can be obtained more accurately.
+Thus, we infer the color of the lensed arcs in the image plane.
+We use {\sc Gsf} code to fit the magnitude of the lensed host and find a 1.5 Gyr stellar template with solar metallicity could well match this color.
+More details of the information could be found in the Appendix~\ref{app:HE0435}.
 
+{\bf RXJ1131} ~ For this system, the lensed arc is very extended in the image plane which is resolved to the AGNs, one could directly perform the SED fitting of the arc in the image plane.
+Combining the \hst\ imaging data through F814W and F555W (GO-9744; PI: C.
+S.
+Kochanek), we inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its disk and bulge, respectively (see Appendix~\ref{app:RXJ1131} for the inference).
+
+{\bf WFI2033} ~ Besides the F160W filter, four filters including F125W, F140W, F555W and F814W has been employed to obtain the imaging data.
+We perform the lens model inference for all the filter and infer the host color through five band in the image plane.
+We find a stellar template with 0.625 Gyr could well match their color (Appendix~\ref{app:WFI2033}).
+
+{\bf HE1104 and other systems} ~ The HE1104 has been observed through F555W and F814W band.
+However, given the faint and the limited exposure time, the signal of the lensed arcs at the other band is not visible.
+There is no other band for the other systems.
+For these systems, we adopt the criteria by Ding2020[] to assign their stellar population, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
+
+A summary of the adopted stellar populations is given in Table~\ref{tab:host_measure}, column~(7).
+Applying these templates to the filter magnitudes obtained in last section, we obtain the stellar mass of our system.
 The uncertainty of the \mstar\ are considered as 0.2 dex, and as studied in~\citet{Ding2017a}, we expect that the uncertainty of the \mbh\ dominate the error budget.
 
-%\section{Black Hole mass estimates}
-%We use viral method to estimate the mass of the black hole. The board-line adopted. We aim to adopt the self-consistent to recalibrate the \mbh~of our sample. 
-%[] The recipes. [] The board lines and the resulting BH mass and listed in the table. []The summarizing table.
-Deriving the the inference of our sample, we over plot our measurements on top of the measurements by \citet{Ding2020}, shown in Figures.
+\subsection{The \mbh-\mstar\ relation}\label{sec:relation}
+We combine the measured \mstar\ to their \mbh\ and plot their scaling relations among the recent measurements by \citet{Ding2020}, shown in Figures.
 The result demonstrate an excellent consistency.
 and the result support the evolution.
-
-\subsection{The \mbh-\mstar\ relation}
 We combine the \mstar\ to their \mbh\ and compare to the ones in the literature.
@@
 We took the other band data and get the only arc image. We adopt these image and do the SED fitting to get the color information.
-\subsection{HE0435}
+\subsection{HE0435}\label{app:HE0435}
 The HE0435 system has been modelled through three band. In the Figure, we demonstrate the host inference in the image plance for the three bands.
 
-\subsection{WFI2033}
-The WFI2033 system has been modelled through five band.
+\begin{figure*}
+\centering
+\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
+\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}
+\caption{\label{fig:app_HE0435} 
+Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
+\end{figure*}
 
+\subsection{RXJ1131}\label{app:RXJ1131}
+We directly preform the SED fitting in the imaging plane. The inferred AGN information is obtain in the Figure.
+
+\subsection{WFI2033}\label{app:WFI2033}
+Similar to Section~\ref{app:HE0435}, the lensed color of WFI2033 has been modelled through five band which are illustrated in the Figure.
+
+\begin{figure*}
+\centering
+\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
+\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
+\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
+\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}
+\caption{\label{fig:app_WFI2033} 
+Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
+\end{figure*} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-04 material/plot_fitting.py
Updates the way to generate the figures and tables.

@@ -42,6 +42,8 @@ label = labels[idx]
 label = label.split(', ')
 
 filename = glob.glob('../'+IDs[inp]+'/model/{4}_PSFi_{0}/result_{1}_*_gammafix{2}_subg{3}.pkl'.format(label[-1], label[0], label[1][-3:], label[2][-1],folder_1) )
+#filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_PSFrecons/result_PSF0_*_gammafix2.1_subg2.pkl')
+#filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_QSOmask/result_PSF0_QSOmask_gammafix2.1_subg2.pkl')
 readfile = filename[0]
 
 #%%
@@ -107,12 +109,18 @@ f, axes = plt.subplots(2, 3, figsize=(16, 8), sharex=False, sharey=False)
 modelPlot.data_plot(ax=axes[0,0])
 modelPlot.model_plot(ax=axes[0,1])
 modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6)
-modelPlot.subtract_from_data_plot(ax=axes[1, 0], v_max=1, point_source_add=True,lens_light_add=True, source_add=False, text='Subtracted host')
+modelPlot.subtract_from_data_plot(ax=axes[1, 0], #v_max=1, 
+                                  point_source_add=True,lens_light_add=True, source_add=False, 
+                                  text='Residual of lensed arcs')
 modelPlot.decomposition_plot(ax=axes[1,1], text='Modelled source light', source_add=True)
-modelPlot.source_plot(ax=axes[1, 2], deltaPix_source=0.01, numPix=100,text='Reconstrucerd host, source plane')
+#modelPlot.decomposition_plot(ax=axes[1,2], text='Source light', source_add=True, unconvolved=True)
+#modelPlot.magnification_plot(ax=axes[1, 2])
+delta_list = [0.02, 0.1, 0.02, 0.05, 0.06, 0.02, 0.02, 0.02, 0.02]
+modelPlot.source_plot(ax=axes[1, 2], deltaPix_source=delta_list[inp], numPix=100, scale_size=0.5,
+                      text='Reconstrucerd host, source plane',with_caustics=True)
 #f.tight_layout()
 f.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0., hspace=0.05)
[…]

### 2020-03-04 material/print_table.py

@@ -14,13 +14,13 @@ import glob
 import sys
 sys.path.insert(0,'../share_tools/')
 
-from read_inference import read_inf
+from read_inference import read_inf, read_mstar
 from lens_information import zeropoint_dict, filter_dict, lens_redshift
 
 IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
 
 full_name = ['HE0435$-$1223', 'RXJ1131$-$1231', 'WFI2033$-$4723', 'SDSS1206$+$4332', 
-			 'HE1104$-$1805', 'SDSS0246$-$0825', 'HS2209$+$1914', 'HE0047$-$1756']
+             'HE1104$-$1805', 'SDSS0246$-$0825', 'HS2209$+$1914', 'HE0047$-$1756']
 
 
 Camera = ['WFC3-IR', 'ACS', 'WFC3-IR', 'WFC3-IR', 'WFC3-IR', 'WFC3-UVIS', 'WFC3-UVIS', 'WFC3-UVIS']
@@ -31,7 +31,7 @@ path = "/Volumes/Seagate_Expansion_Drive/Projects_backup/lens_host_reconstructio
 exp_list = [9340.4, 1980.0, 26257.0, 8456.9, 14698.3, 8481.0, 4542.0+9696.0, 9712.0]
 
 resolution = ['$0\\farcs{}08$', '$0\\farcs{}05$', '$0\\farcs{}08$', '$0\\farcs{}08$',
-			  '$0\\farcs{}08$', '$0\\farcs{}03$', '$0\\farcs{}03$', '$0\\farcs{}03$']
+              '$0\\farcs{}08$', '$0\\farcs{}03$', '$0\\farcs{}03$', '$0\\farcs{}03$']
 
 #%%Table 1 :
 print("Object ID & $z$ & camera & Filter & exposure & pixel scale \\\\")
@@ -52,100 +52,99 @@ from est_MBH import BL_info, cal_MBH
 print("Object ID & Line(s) used & FWHM & log($L_\\lambda$) & $\\log$\\mbh \\\\")
 print("& & (\\kms) & ($[\\rm erg~s^[-1]]$) & (M$_{\\odot}$) \\\\ \\hline")
[…]

### 2020-03-04 material/plot_append_HE0435.py
To create appendix figures.

@@ -1,0 +1,145 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Feb 21 11:50:31 2020
+
+@author: Dartoon
+"""
+
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+from matplotlib.colors import LogNorm
+import copy
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
+from flux_profile import cr_mask
+import glob
+
+#%% Find the one with lowest Chisq
+IDs = ['0_HE0435']
+
+
+#for i in range(len(IDs)):
+#    print(i, ':', IDs[i])
+#0 = int(0ut("Which source:\n"))
+ID = IDs[0][2:]
+file_160w = '/model/2nd_fit_PSFi_PSFrecons/result_PSF0_*_gammafix2.1_subg2.pkl'
+file_555w = '/f555w_model/fit_PSFi_PSFrecons/result_PSF0_*_gammafix1.9*.pkl'
+file_814w = '/f814w_model/fit_PSFi_PSFrecons/result_PSF1_*_gammafix1.9*.pkl'
+#
+filename = glob.glob('../'+IDs[0]+file_814w )
+#filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_PSFrecons/result_PSF0_*_gammafix2.1_subg2.pkl')
+#filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_QSOmask/result_PSF0_QSOmask_gammafix2.1_subg2.pkl')
+readfile = filename[0]
+
+#%%
+##
+result = pickle.load(open(readfile,'rb') ,encoding="latin1")
+fit_result, trans_result, kwargs_material, model_lists  = result
+kwargs_data, kwargs_psf_updated, kwargs_numerics, kwargs_model, lens_mask = kwargs_material
+lens_model_list, source_model_list, lens_light_model_list, point_source_list = model_lists
+#if label[-1] == 'PSFrecons':
+#    print("Change PSFs and ")
+#    filename = glob.glob('../'+IDs[0]+'/model/{4}_PSFi_{0}/result_{1}_*_gammafix{2}_subg{3}.pkl'.format("QSOmask", label[0], label[1][-3:], label[2][-1],folder_1) )
+#    readfile = filename[0]
[…]

### 2020-03-04 material/plot_append_WFI2033.py

@@ -1,0 +1,148 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Feb 21 11:50:31 2020
+
+@author: Dartoon
+"""
+
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+from matplotlib.colors import LogNorm
+import copy
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
+from flux_profile import cr_mask
+import glob
+
+#%% Find the one with lowest Chisq
+IDs = ['2_WFI2033']
+
+
+#for i in range(len(IDs)):
+#    print(i, ':', IDs[i])
+#0 = int(0ut("Which source:\n"))
+ID = IDs[0][2:]
+filters = ['f125w', 'f140w', 'f555w', 'f814w'] 
+file_info = '/{0}_model/fit_PSFi_PSFrecons/result_PSF0_*_gammafix1.9*.pkl'.format(filters[3])
+#
+filename = glob.glob('../'+IDs[0]+file_info )
+#filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_PSFrecons/result_PSF0_*_gammafix2.1_subg2.pkl')
+#filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_QSOmask/result_PSF0_QSOmask_gammafix2.1_subg2.pkl')
+readfile = filename[0]
+
+#%%
+##
+result = pickle.load(open(readfile,'rb') ,encoding="latin1")
+fit_result, trans_result, kwargs_material, model_lists  = result
+kwargs_data, kwargs_psf_updated, kwargs_numerics, kwargs_model, lens_mask = kwargs_material
+lens_model_list, source_model_list, lens_light_model_list, point_source_list = model_lists
+#if label[-1] == 'PSFrecons':
+#    print("Change PSFs and ")
+#    filename = glob.glob('../'+IDs[0]+'/model/{4}_PSFi_{0}/result_{1}_*_gammafix{2}_subg{3}.pkl'.format("QSOmask", label[0], label[1][-3:], label[2][-1],folder_1) )
+#    readfile = filename[0]
+#    result = pickle.load(open(readfile,'rb') ,encoding="latin1")
+#    _, trans_result, kwargs_material, model_lists  = result
[…]

### 2020-03-09 1_RXJ1131/model/3rd_fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py
RXJ1113, 3rd fitting

@@ -1,0 +1,372 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+Modelling the HE0435
+
+Trying to recover the H0LiCOW_IV's host flux ~47.
+
+In this script, fix gamma as Ken's results. Use, psf mask.
+Use PSF reconstruction.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+from mask_objects import mask_obj, detect_obj
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+
+old_folder = '../2nd_fit_PSFi'+path.split('fit_PSFi')[1]
+
+#%%
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))
+lens_mask = cr_mask(lens_image, '../circle_mask.reg')
+lens_mask = (1-lens_mask)
+
+#framesize = 201
+#ct = (len(lens_image) - framesize)/2
+#lens_image = lens_image[ct:-ct,ct:-ct]
[…]

### 2020-03-09 1_RXJ1131/model/3rd_fit_PSFi_QSOmask/2_modelling_fix_gamma_QSO_mask.py

@@ -1,0 +1,374 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+Modelling the HE0435
+
+Trying to recover the H0LiCOW_IV's host flux ~47.
+
+The QSO center noise level is boost to inf.
+psf_error_map not taken.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+from mask_objects import mask_obj, find_loc_max
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+
+old_folder = '../2nd_fit_PSFi'+path.split('fit_PSFi')[1]
+
+#%%
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))
+lens_mask = cr_mask(lens_image, '../circle_mask.reg')
+lens_mask = (1-lens_mask)
+
+stdd_boost_filename = '../fit_PSFi_QSOmask/'+'{0}_stdd_boost.fits'.format(ID)
+if glob.glob(stdd_boost_filename) == []: 
+    print "re-run the rms boost process"
[…]

### 2020-03-09 manuscript/manuscript.tex
update paper

@@
 Matthew W. Auger,
-Sherry H. Suyu,
-Kenneth C. Wong,\newauthor
+Kenneth C. Wong,
+Sherry H. Suyu,\newauthor
 Takahiro Morshita,
@@
 The deep \hst\ data and adopt the \lenstronomy\ to reconstruct the image of the source.
+Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on the assumed stellar population.
 The \mbh\ are estimated using the board emission line.
-We compare our inference to the once in the literature and find a consistent result.
-Combining them together, we are able to constrain the $\gamma$ to xxx.
-Our our demonstrate is demonstrate the power of using strong lensed AGNs.
+We compare our inference to the ones in the literature and find a consistent result.
+The consistent scaling resolutions derived from our sample confirm the evolution conclusion and confirm the the power of using strong lensed AGNs.
 The sample of the data are supposed to increase rapidly.
@@
 \section{Introduction}
-Structure:
+The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution.
 
-[] What is scaling relations.
+The origin of these relations is till unclear so far.
+In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection or having them share a common gas supply.
+On the other hand, without any physical coupling, the pure statistical convergence by galaxy mergers alone could also reproduce the observed correlations at local universe.
+It is crucial to extend the correlation studies to higher redshift and understand their evolution as a function of redshift.
+Recently, \citet{Ding2020} measured the scaling relations at redshift range of $1.2<z<1.7$ based on a sample of 32 AGNs using \hst/WFC3.
+Comparing to the published samples at local and intermediate redshift range, they confirm the an evolution scenario that the growth of BHs evolution predates than the host galaxy bulge.
+In the following up work, \citet{Ding2020b} used the measurements of the high-$z$ AGNs and compare to numerical simulations including the hydrodynamic simulation MassiveBlackII (MBII) and a semi-analytic model (SAM).
+The tightness of the scaling relation at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations.
+A larger sample at higher redshift would be even more beneficial to confirm this scenario.
 
-[] Strong lensing provide a tool to study to higher redshift.
+Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs provide a unique tool to make progress in this study (ref[Peng2006]), 
+provided that the lens modelling is accurate.
+\citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in H0LiCOW collaboration.
+This work has confirm the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
+As a following up effort, \citet{Ding2017b} has applied the advanced techniques to two strongly lensed systems to study their \mbh-\lhost\ relations and obtained consistent results to the ones in the literature.
 
-[] Previous work.
-H0LiCOW XI.
-H0LiCOW XII.
-In these two works, the host galaxy is first reconstructed using the pixellation.
-Then, the host image are inferred in the source plan by fitting as a \sersic\ model.
-This means, the two-step inference of the host information.
+In this work, we aim to make progress by completing the analysis of the entire eight systems.
+We have developed an independent approach to achieve a one-step inference of the host photometry.
+We adopt the a set of extended modelling choices to assure the accuracy of our measurements.
+Moreover, we comparing our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross check.
+3/8 of our objects have multi-band \hst\ imaging and we are able to infer their host color to assess an accurate inference of the stellar mass.
+The extended range of the eight systems would help us to make a direct comparison to the latest measurements by \citet{Ding2020}.
+We also adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample.
 
-[] In this work, we adopt an independent tool and carry out a direct inference of the host properties.
+This paper is organized as follows xxx. Zeropoint are defined in the AB systems. A Chabrier initial mass function (IMF) is employed consistently.
 
-[]This paper is organized as follows. Zeropoint are defined in the AB systems.
-
-\section{Sample Selection}
-We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914.
+\section{Sample Selection}\label{sec:sample_select}
+We adopt the eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914.
 For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131).
@@
 %[]The comparison sample (32 QSO paper)
-We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 redshift QSO and 55 local measurements.
+We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 intermediate redshift QSO and 55 local measurements.
+It is worth noticing that they are so far the largest \hst\ imaging AGN samples with redshift range from 1.9 to the local.
 
@@
 \item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF.
-To avoid overfitting the noise, we adopt two modeling choices.
-1)~manually boost the noise estimate in the central area to effectively infinite; 2)~perform the iterative PSF estimation as introduced by ref[].
+To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite; 2)~perform the iterative PSF estimation as introduced by ref[].
 \item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
@@
 After  all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value.
-Finally, we adopt the weighting algorithm as introduced by Equations (3)$-$(6) in~\citet{Ding2020} and combine the top eight choices to derive the final value and evaluate the uncertainties.
+Finally, we adopt the weighting algorithm as introduced by Equations (3)$-$(6) in~\citet{Ding2020}.
+Since there is no obvious evidence of better perform between QSO mask or PSF iteration, we selected each top-4 fitting by these to choice and combining them equally to derive the final results and to evaluate the uncertainties.
 
-\subsection{Photometry Inference}
+\subsection{Photometry Inference}\label{sec:photometry}
 In this subsection, we describe the details of the fitting for each systems and present our inference of the host galaxy photometry.
@@
 As a cross check, we compare our host magnitude to the measurement in Ding+2017[], in which they model the reconstructed host galaxy as \sersic\ based on Galfit [].
-The host magnitude measured in that paper is: $mag = 21.75 \pm 0.13$%, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
-which is slightly fainter than our results, i.e. $mag = 21.33 \pm 0.2$. \ding{Some discussion of the origin of this offset?}
-Still, the center mismatch is only $0.15$~dex, which is a little of the total error budget.
+The host magnitude measured in that paper is: $mag = 21.75 \pm 0.13$, %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
+which is slightly fainter than our inference, i.e. $mag = 21.50 \pm 0.35$. The offset is within $1-\sigma$ level.
 
@@
 We also compare our measurement to the previous reconstructions in Ding.
-Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{\rm disk} = 20.07\pm0.06$ and $mag_{\rm bulge} = 21.81 \pm 0.28$.
-Compared to our inference in Table~\ref{tab:host_measure}, our inferred bulge flux is consistent at $\sim0.25$ dex level, however, while the inferred disk light is much brighter by $\sim 0.7$ dex.
+Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$.
+Compared to our inference in Table~\ref{tab:host_measure}, the bulge flux is very consistent, however, while our inferred disk is brighter by $\sim 0.5$ mag.
+\ding{Some discussion of this offset.}
 
@@
 We also compare the inference to the reconstructions by Ken.
-Fitting their reconstruction as a \sersic\ profile, we have inferred that $mag = 21.98 \pm 0.15$ which is slightly fainter than our inference by $\sim0.2$~dex.
+Fitting their reconstruction as a \sersic\ profile, we have inferred that $mag = 21.98 \pm 0.15$ which is also consistent to our inference.
 
@@
 We consider the galaxy triplet group at the north-west and use a single SIS model to denote their over all mass perturbations.
-Moreover, as noted by Simon[] (Figure 1 therein), a sub-clump is located in the north which is hardly visible.
+Moreover, as noted by Simon[], a sub-clump is located in the north which is hardly visible  (i.e., Figure 1 in that paper).
 We model it as a SIS mass model and circular \sersic\ light model with joint centroids.
@@
 \subsubsection{HS2209}
+HS2209 imaging data have two visits. We modelled both two visited drizzling data.
 The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g).
@@
 %\resizebox{12cm}{!}{
-     \begin{tabular}{ccccccc}
+     \begin{tabular}{cccccccc}
 \hline     
-(1) & (2) & (3) & (4) & (5) & (6) & (7) \\    
-Object ID & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
- & (AB system) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
-HE0435 & $21.492\substack{+0.402\\-0.293}$ & $35.981\pm11.127$ & $0.279\pm0.023$ & $2.710\pm0.204$ & $1.500$ & $10.91\substack{+0.12\\-0.16}$ \\
-RXJ1131$_{\rm bulge}$ & $22.092\substack{+0.221\\-0.183}$ & $6.658\pm1.225$ & $0.107\pm0.014$ & fix to 4 & $3.000$ & $10.27\substack{+0.07\\-0.09}$ \\
-RXJ1131$_{\rm disk}$ & $19.495\substack{+0.159\\-0.138}$ & $72.816\pm9.892$ & $0.845\pm0.049$ & fix to 1 & $1.500$ & $11.01\substack{+0.06\\-0.06}$ \\
-WFI2033 & $21.781\substack{+0.285\\-0.225}$ & $19.645\pm4.534$ & $0.280\pm0.017$ & $0.524\pm0.013$ & $0.625$ & $10.51\substack{+0.09\\-0.11}$ \\
-SDSS1206 & $21.310\substack{+0.232\\-0.191}$ & $33.302\pm6.413$ & $0.112\pm0.021$ & $4.568\pm0.530$ & $0.625$ & $10.77\substack{+0.08\\-0.09}$ \\
-HE1104 & $21.252\substack{+0.163\\-0.142}$ & $13.990\pm1.953$ & $0.270\pm0.023$ & $1.048\pm0.045$ & $0.625$ & $11.05\substack{+0.06\\-0.07}$ \\
-SDSS0246 & $23.437\substack{+0.279\\-0.222}$ & $3.978\pm0.901$ & $0.436\pm0.084$ & $4.964\pm0.081$ & $0.626$ & $10.75\substack{+0.09\\-0.11}$ \\
-HS2209 & $20.200\substack{+0.128\\-0.114}$ & $21.108\pm2.348$ & $3.116\pm1.834$ & $3.302\pm0.521$ & $1.001$ & $11.25\substack{+0.05\\-0.05}$ \\
-HE0047 & $22.923\substack{+0.485\\-0.334}$ & $2.347\pm0.845$ & $0.319\pm0.146$ & $4.176\pm0.750$ & $0.625$ & $10.91\substack{+0.13\\-0.19}$ \\
+(1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) \\    
+Object ID & intrinsic Magnitude & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
+ & (source plane) & (image plane) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
+HE0435 & $21.49\substack{+0.40\\-0.29}$ & $18.58\substack{+0.30\\-0.23}$ & $36.0\pm11.1$ & $0.28\pm0.02$ & $2.71\pm0.20$ & $1.50$ & $10.91\substack{+0.12\\-0.16}$ \\
+RXJ1131$_{\rm bulge}$ & $21.80\substack{+0.23\\-0.19}$ & $18.70\substack{+0.07\\-0.06}$ & $7.1\pm1.4$ & $0.13\pm0.02$ & fix to 4 & $3.00$ & $10.39\substack{+0.08\\-0.09}$ \\
+RXJ1131$_{\rm disk}$ & $19.33\substack{+0.17\\-0.15}$ & $17.14\substack{+0.08\\-0.07}$ & $69.2\pm10.1$ & $0.90\pm0.06$ & fix to 1 & $1.50$ & $11.08\substack{+0.06\\-0.07}$ \\
+WFI2033 & $21.78\substack{+0.28\\-0.23}$ & $19.07\substack{+0.35\\-0.26}$ & $19.6\pm4.5$ & $0.28\pm0.02$ & $0.52\pm0.01$ & $0.62$ & $10.51\substack{+0.09\\-0.11}$ \\
+SDSS1206 & $21.31\substack{+0.23\\-0.19}$ & $18.30\substack{+0.05\\-0.05}$ & $33.3\pm6.4$ & $0.11\pm0.02$ & $4.57\pm0.53$ & $0.62$ & $10.77\substack{+0.08\\-0.09}$ \\
+HE1104 & $21.25\substack{+0.16\\-0.14}$ & $19.16\substack{+0.02\\-0.02}$ & $14.0\pm2.0$ & $0.27\pm0.02$ & $1.05\pm0.04$ & $0.63$ & $11.05\substack{+0.06\\-0.07}$ \\
+SDSS0246 & $23.44\substack{+0.28\\-0.22}$ & $20.85\substack{+0.08\\-0.07}$ & $4.0\pm0.9$ & $0.44\pm0.08$ & $4.96\pm0.08$ & $0.63$ & $10.75\substack{+0.09\\-0.11}$ \\
+HS2209 & $20.72\substack{+0.26\\-0.21}$ & $19.20\substack{+0.04\\-0.04}$ & $12.5\pm2.7$ & $1.96\pm1.28$ & $3.15\pm1.40$ & $1.00$ & $11.04\substack{+0.08\\-0.10}$ \\
+HE0047 & $22.92\substack{+0.48\\-0.33}$ & $20.37\substack{+0.20\\-0.17}$ & $2.3\pm0.8$ & $0.32\pm0.15$ & $4.18\pm0.75$ & $0.62$ & $10.91\substack{+0.13\\-0.19}$ \\
 \hline
@@
 
-\subsection{Population and stellar mass}\label{sec:mstar}
+\subsection{Stellar population and mass}\label{sec:mstar}
 %[] Color inference for the first three cases to decide their stellar template. 
@@
 
-{\bf HE0435} ~ Besides WFC3/F160W, HE0435 has also been observed by the \hst\ through ACS/F814W and ACS/F555W (GO-xxxx; PI: xxxx).
-We adopted the same approaches to modeling the data separately at these two band.
+{\bf HE0435} ~ Besides the imaging data by F160W, this system has also been observed by the \hst\ through F814W and F555W band.
+We adopted the same approach to modelling the data separately at these two band.
 % The inferred host magnitudes are xxx and xxx, respectively.
-Considering that the lensed arcs is mainly inferred by the subtraction of the AGNs and deflectors light, it is less dependent on the lens model and thus can be obtained more accurately.
-Thus, we infer the color of the lensed arcs in the image plane.
+Considering that the lensed host in the image plane is majorly inferred by the subtraction of the AGNs and deflectors light, which it is less dependent on the lens model.
+We expect it can be obtained with more accuracy.
+Thus, we infer the color based on the magnitude of the lensed arcs in the image plane.
 We use {\sc Gsf} code to fit the magnitude of the lensed host and find a 1.5 Gyr stellar template with solar metallicity could well match this color.
@@
 {\bf RXJ1131} ~ For this system, the lensed arc is very extended in the image plane which is resolved to the AGNs, one could directly perform the SED fitting of the arc in the image plane.
-Combining the \hst\ imaging data through F814W and F555W (GO-9744; PI: C.
-S.
-Kochanek), we inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its disk and bulge, respectively (see Appendix~\ref{app:RXJ1131} for the inference).
+Combining the \hst\ imaging data through three filter F814W and F555W and F160W, we inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its bulge and disk, respectively (see Appendix~\ref{app:RXJ1131} for the inference).
 
-{\bf WFI2033} ~ Besides the F160W filter, four filters including F125W, F140W, F555W and F814W has been employed to obtain the imaging data.
+{\bf WFI2033} ~ Besides the F160W filter, four other filters including F125W, F140W, F555W, F814W are also available in the \hst\ archive, which has been employed to obtain the color of the host galaxy.
 We perform the lens model inference for all the filter and infer the host color through five band in the image plane.
@@
 
-{\bf HE1104 and other systems} ~ The HE1104 has been observed through F555W and F814W band.
-However, given the faint and the limited exposure time, the signal of the lensed arcs at the other band is not visible.
-There is no other band for the other systems.
-For these systems, we adopt the criteria by Ding2020[] to assign their stellar population, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
+{\bf HE1104 and the other systems} ~ The imaging data of HE1104 has been observed through F555W and F814W band.
+However, given limited exposure time, the signal of the lensed arcs is too faint to be detected at this two bands.
+Due to this limitation, we couldn't infer the color of the host for HE1104.
+For this case, the other systems, we adopt the criteria by Ding2020[] to assign their stellar population, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
 
@@
 Applying these templates to the filter magnitudes obtained in last section, we obtain the stellar mass of our system.
-The uncertainty of the \mstar\ are considered as 0.2 dex, and as studied in~\citet{Ding2017a}, we expect that the uncertainty of the \mbh\ dominate the error budget.
+Considering that we have obtained very consistent host photometry for the HE0435, RXJ1131 and WFI2033 to previous results using the independent approach, the fidelity of the inferred magnitude are considered to be high.
+The uncertainty of the \mstar\ estimation are considered as the typical level $0.2$~dex.
+Same as the comparison, we expect that the uncertainty of the \mbh\ would dominate the error budget in the overall scaling relation obtained in next section.
 
 \subsection{The \mbh-\mstar\ relation}\label{sec:relation}
-We combine the measured \mstar\ to their \mbh\ and plot their scaling relations among the recent measurements by \citet{Ding2020}, shown in Figures.
-The result demonstrate an excellent consistency.
-and the result support the evolution.
-We combine the \mstar\ to their \mbh\ and compare to the ones in the literature.
+Having obtained the \mstar\ of each individual system, we combine them with their \mbh\ to reveal the scaling relations.
+We expect to compare our high redshift lensed sample to the comparison sample as introduced in Section~\ref{sec:sample_select}.
+We plot the entire measurement together with and present in Figures~\ref{fig:scaling_relation}-(a).
+Following~\citet{Ding2020}, we fit the \mbh-\mstar\ data with a linear relation as:
+\begin{eqnarray}
+\label{eq:MMlocal}
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}).
+\end {eqnarray}
+We find that our lensed systems appeared to have a slimier offset to the local relations which is consistent to the 32 QSOs by~\citet{Ding2020} at similar redshift range.
+
+To this evolution trend based on the sample redshift, we parameterize the evolution term as the linear relation by:
+\begin{eqnarray}
+\label{eq:offset}
+\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
+\end{eqnarray} 
+from which we recover the offset plot, i.e., Figure~8, in~\citet{Ding2020}.
+We then add the measurements by our lensed systems and show in Figure~\ref{fig:scaling_relation}-(b).
+We find that the evolution of the offset our sample are well matched to the evolution trend as discovered by the previous inference.
+Given that we only obtain the measurements from eight lens systems, it is insufficient to fit the offset value quantitively.
+Nevertheless, the obvious consistency between the sample confirm the fidelity of our measurement and verify previous offset conclusions by~\citet{Ding2020}.
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar.pdf}}&
+{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
+\end{tabular}
+\caption{\label{fig:scaling_relation} 
+\todo{This Figures are still ugly so far, which need to be updated.}}
+\end{figure*}
 
@@
 [] This work confirm the bright future of lensing.
+
+Finally, we did not consider the selection effect.
+Besides the mass function, the selection function of the lensed AGNs is also non-trivial.
+We note that these effects will have to be modelled in the future if the lensed sample is used to infer the evolution.
 
@@
 \section{Color inference of the host}
-We took the other band data and get the only arc image. We adopt these image and do the SED fitting to get the color information.
+We describe the details of the stellar population inference in this section. The template would be then adopted to the photometry by Section~\ref{sec:photometry} to infer the stellar mass.
 \subsection{HE0435}\label{app:HE0435}
-The HE0435 system has been modelled through three band. In the Figure, we demonstrate the host inference in the image plance for the three bands.
+The HE0435 system are also modelled through ACS/F814W and ACS/F555W (GO-9744; PI: C.
+S.
+Kochanek).
+We derive the magnitude of the lensed galaxy and infer the color of the host in the image plane.
+We illustrate the lens model for the other two band in Figure~\ref{fig:app_HE0435}.
+The inferred magnitude of the host galaxy in the image plane is quite robust.
+Having obtained the magnitude of the lensed host at three band, we use {\sc gsf} package to select the best stellar population from a range of [0.625, 0.8, 1.0, 1.5, 2.0, 3.0] Gyr with solar metallicity.
+Finally, a template with ago of 1.5 Gyr is selected.
 
@@
 \caption{\label{fig:app_HE0435} 
-Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
+Illustrations of the inference of HE0435 at the other two band. }
 \end{figure*}
@@
 \subsection{RXJ1131}\label{app:RXJ1131}
-We directly preform the SED fitting in the imaging plane. The inferred AGN information is obtain in the Figure.
+Using the three band data including  ACS/F814W and ACS/F555W and NIC2/F160W (GO-9744; PI: C.
+S.
+Kochanek), we preform the SED fitting in the imaging plane directly pixel by pixel in Figure~\ref{fig:app_RXJ1131}.
+\ding{This part is actually done by Takahiro in~\citep{Ding2017b}.
+The image of the fitted age looks noisy, but it is in the range of the [9.25 - 9.50] (logAge), i.e.
+[1.5, 3.0] (Gyr).
+We can remove this A2 but only mention the fitting is done 2017 in that paper.}
+\begin{figure}
+\centering
+{\includegraphics[width=0.25\textwidth]{fig/map_age_zRXJ_1131.pdf}}\\
+\caption{\label{fig:app_RXJ1131} 
+Illustrations of the SED fitting of the galaxy age pixel by pixel.  }
+\end{figure}
 
 \subsection{WFI2033}\label{app:WFI2033}
-Similar to Section~\ref{app:HE0435}, the lensed color of WFI2033 has been modelled through five band which are illustrated in the Figure.
+WFI2033 is also observed by other four band data including WFC3/F125W (GO-12874; PI: D.
+Floyd), WFC3/F140W (GO-13732; PI: A.
+Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C.
+S.
+Kochanek).
+The data quality by F125W is limited by its exposure time; and the host information is not well extracted.
+We does not take it into account in the color inference.
+Similar to Section~\ref{app:HE0435}, the lensed color of WFI2033 has been modelled through five band. The lensed models are presented in the~Figure~\ref{fig:app_WFI2033}.
 
@@
 \centering
-\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
-\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
+\subfloat[WFI2033 F125W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
+\subfloat[WFI2033 F140W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
 \subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
@@
 \caption{\label{fig:app_WFI2033} 
-Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
+Illustrations of the inference of WFI2033 at the other two band.  }
 \end{figure*} 

### 2020-03-09 material/plot_fitting.py
Update for paper

@@ -25,14 +25,17 @@ IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS02
 #for i in range(len(IDs)):
 #    print(i, ':', IDs[i])
 #inp = int(input("Which source:\n"))
-inp = 3
+inp = 1
 ID = IDs[inp][2:]
-if ID != 'SDSS1206':
-    folder_0 = '_2nd_run_summary.pkl'
-    folder_1 = '2nd_fit'
-elif ID == 'SDSS1206':
+if ID == 'SDSS1206':
     folder_0 = '_singel_host_run_summary.pkl'
     folder_1 = 'singel_fit'
+if ID == 'HS2209' or ID == 'RXJ1131':
+    folder_0 = '_3rd_run_summary.pkl'
+    folder_1 = '3rd_fit'    
+else:
+    folder_0 = '_2nd_run_summary.pkl'
+    folder_1 = '2nd_fit'
 filename = '../share_tools/'+ ID+ folder_0
 result = pickle.load(open(filename,'rb') ,encoding="latin1") 
 fit_values, chisq, labels, _ = result
@@ -44,8 +47,8 @@ label = label.split(', ')
 filename = glob.glob('../'+IDs[inp]+'/model/{4}_PSFi_{0}/result_{1}_*_gammafix{2}_subg{3}.pkl'.format(label[-1], label[0], label[1][-3:], label[2][-1],folder_1) )
 #filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_PSFrecons/result_PSF0_*_gammafix2.1_subg2.pkl')
 #filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_QSOmask/result_PSF0_QSOmask_gammafix2.1_subg2.pkl')
-readfile = filename[0]
-
+readfile = filename[0] #'../6_HS2209/model/3rd_fit_PSFi_QSOmask/result_PSF2_QSOmask_gammafix2.1_subg2.pkl'
+#readfile = '../2_WFI2033/model/2nd_fit_PSFi_PSFrecons/result_PSF1_PSFrecons_gammafix1.9_subg2.pkl'
 #%%
 ##
 result = pickle.load(open(readfile,'rb') ,encoding="latin1")

### 2020-03-09 material/print_table.py

@@ -68,11 +68,12 @@ for ID in ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SD
 
 #%%Table 3:    
 #Get the infernece from pickle: 
-print("Object ID & Magnitude & Host-Total Flux Ratio & Reff & \\sersic\\ $n$ & adopted AGE & $\\log (M_{*}$)  \\\\")
-print(" & (AB system) & ($\\%$) & (arcsec) & & (Gyr) & (M$_{\\odot}$) \\\\ \\hline")
+#print("Object ID & Magnitude & Host-Total Flux Ratio & Reff & \\sersic\\ $n$ & adopted AGE & $\\log (M_{*}$)  \\\\")
+#print(" & (AB system) & ($\\%$) & (arcsec) & & (Gyr) & (M$_{\\odot}$) \\\\ \\hline")
 for i in range(len(IDs)):
     ID = IDs[i][2:]
     host_flux_list = read_inf(IDs[i][2:],prop=0)
+    host_lensed_flux_list = read_inf(IDs[i][2:],prop=4, count_n=[4, 4])
     AGN_flux_list = read_inf(IDs[i][2:],prop=3)
     Reff_list  = read_inf(IDs[i][2:],prop=1)
     n_list  = read_inf(IDs[i][2:],prop=2)
@@ -92,20 +93,26 @@ for i in range(len(IDs)):
         age = 10**table[1][age_idx]
         
         host_flux_hml = [host_flux_list[idx][0]+ host_flux_list[idx][1], host_flux_list[idx][0], host_flux_list[idx][0] - host_flux_list[idx][1]]
+        mag = [-2.5* np.log10(flux) + zp for flux in host_flux_hml]
+        mag_mul = [(mag[1]), (mag[2]-mag[1]), (mag[0]-mag[1])]  #median, upper, lower
+        
         m_star_result = read_mstar(ID,  count_n=[4,4])[0]
         m_star_lmh = [ np.log10(m_star_result[0] - m_star_result[1]), np.log10(m_star_result[0]), np.log10(m_star_result[0] + m_star_result[1]) ]
         m_star_mul = [ m_star_lmh[1], (m_star_lmh[2] - m_star_lmh[1]), (m_star_lmh[1] - m_star_lmh[0])]
+
[…]

### 2020-03-09 relation_plots/MM_32QSO.py
temp update for paper

@@ -140,8 +140,7 @@ for i in range(100):
     m=np.percentile(samples,posi,axis=0)[0]
     b=samples[:,1][samples[:,0]==find_n(samples[:,0],m)][0]   #may find out many numbers
     plt.plot(xl, m*xl+b, color="lightgray", alpha=0.2,linewidth=7.0,zorder=-1000)
-
-plt.text(9.3, 6.24, r"log(M$_{\rm BH}/$10$^{7}$M$_{\odot}$)=%s+%slog(M$_*/$10$^{10}$M$_{\odot}$)"%(round(b_ml+m_ml*10-7,2),round(m_ml,2)),color='blue',fontsize=25)
+#plt.text(9.3, 6.24, r"log(M$_{\rm BH}/$10$^{7}$M$_{\odot}$)=%s+%slog(M$_*/$10$^{10}$M$_{\odot}$)"%(round(b_ml+m_ml*10-7,2),round(m_ml,2)),color='blue',fontsize=25)
 
 #%%
 inp_SS13 = 1
@@ -294,8 +293,8 @@ Mstar_err = np.array([[-0.15,  0.19], [-0.15,  0.19], [-0.14,  0.16], [-0.14,  0
                       [-0.12,  0.12], [-0.24,  0.48], [-0.17,  0.23], [-0.12,  0.12], 
                       [-0.14,  0.16], [-0.19,  0.28], [-0.25,  0.53], [-0.14,  0.16], 
                       [-0.18,  0.25], [-0.18,  0.24], [-0.15,  0.18], [-0.15,  0.18]])
-plt.scatter(Mstar,MBs,c='tomato',s=280,marker="*",zorder=100, edgecolors='k')
-plt.errorbar(Mstar,MBs, xerr=[np.abs(Mstar_err)[:,0], np.abs(Mstar_err)[:,1]], yerr=0.4, color='blue',ecolor='orange', fmt='.',zorder=-500,markersize=1)
+plt.scatter(Mstar,MBs,c='lawngreen',s=320,marker="*",zorder=100, edgecolors='k')
+#plt.errorbar(Mstar,MBs, xerr=[np.abs(Mstar_err)[:,0], np.abs(Mstar_err)[:,1]], yerr=0.4, color='blue',ecolor='orange', fmt='.',zorder=-500,markersize=1)
 
 #%%
[…]

### 2020-03-09 relation_plots/MM_vz_32QSO.py

@@ -322,17 +322,17 @@ plt.errorbar(np.log10(1+cis11[:,0]),cis11[:,1]-(m_ml*cis11[:,2]+b_ml),yerr=(0.4*
 #    plt.errorbar(np.log10(1+Knud[:,0]),Knud[:,2]-(m_ml*Knud[:,4]+b_ml),yerr=0,fmt='o',color='blue',markersize=9) 
 
 
-plt.scatter(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),c='tomato',
+plt.scatter(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),c='lawngreen',
             s=280,marker="*",zorder=300, vmin=0.3, vmax=5, edgecolors='k')
 plt.errorbar(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),
              yerr= yerr_highz,
-             color='tomato',ecolor='orange', fmt='.',markersize=1)    
+             color='lawngreen',ecolor='olivedrab', fmt='.',markersize=1)    
 
-plt.scatter(np.log10(1+zs[9]),0,facecolors='none',
-            s=280,marker="o",zorder=900, edgecolors='blue', linewidth=6, alpha=0.5)    
-plt.scatter(np.log10(1+zs[9]),0+0.21,facecolors='none',
-            s=280,marker="o",zorder=900, edgecolors='blue', linewidth=6, alpha=0.5)    
-plt.arrow(np.log10(1+zs[9]),0, 0, +0.19, zorder=800, head_length=0.05,head_width=0.005,fc='k',ec='k')
+#plt.scatter(np.log10(1+zs[9]),0,facecolors='none',
+#            s=280,marker="o",zorder=900, edgecolors='blue', linewidth=6, alpha=0.5)    
+#plt.scatter(np.log10(1+zs[9]),0+0.21,facecolors='none',
+#            s=280,marker="o",zorder=900, edgecolors='blue', linewidth=6, alpha=0.5)    
+#plt.arrow(np.log10(1+zs[9]),0, 0, +0.19, zorder=800, head_length=0.05,head_width=0.005,fc='k',ec='k')
 
 #####fit the evolution##########
 ################################
@@ -426,13 +426,14 @@ from read_inference import read_mstar
 
 texts = []
 for ID in h0licow:
-    Mstar = mstar_dict[ID]
-    MBs = MBH_dic[ID]
[…]

### 2020-03-09 share_tools/plot_host_infernece.py
Update for paper

@@ -20,58 +20,58 @@ prop = int(input('flux input 0 ; Reff input 1 ; host flux image_plane 2:\n'))
 
 #%%
 for i in range(len(IDs)):
-	ID = IDs[i][2:]
-	if ID == "SDSS1206" :
-		filename = ID+'_singel_host_run_summary.pkl'
-	else:
-		filename = ID+'_2nd_run_summary.pkl'
-	result = pickle.load(open(filename,'rb'),encoding="latin1")
-	fit_values, chisq, labels, pick_names = result
-	sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
-	fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values
-	for i in range(len(labels)):
-		if labels[i][-17:] != sort_label_type[i%4]:
-			raise ValueError("The labels is wrong for some reason")
-	if prop == 0 :
-		if 'Disk' in pick_names[2]:
-			pick = 4
-		else:
-			pick = 3
-	elif prop == 1:
-		if 'Disk' in pick_names[2]:
-			pick = 6
-		else:
-			pick = 5
-	elif prop == 2:
-			pick = 1  #Flux in the image plane
-	print(ID, pick_names)
-	fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
-	fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
-	fit_value_h = [fit_value_h_list[i][pick] for i in range(len(labels))]
-	count_n = 8
-	chisq = [float(chisq[i]) for i in range(len(chisq))]
-	sort_chisq = np.argsort(np.asarray(chisq))    
-	Chisq_best = chisq[sort_chisq[0]]
-	#Chisq_last= chisq[sort_chisq[-1]]
-	Chisq_last= chisq[sort_chisq[count_n-1]]
-	weight = np.zeros(len(chisq))
-	inf_alp = (Chisq_last-Chisq_best) / (2*2.* Chisq_best)
-	for i in sort_chisq[:count_n]:
-	#for i in range(len(sort_chisq)):
-	#    weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best))
-		weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best* inf_alp))
-	weighted_value = np.sum(np.array(fit_value_m)*weight) / np.sum(weight)
[…]

### 2020-03-09 share_tools/plot_using_sum_pickle.py

@@ -1,0 +1,162 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Jan 25 15:58:15 2019
+
+@author: Dartoon
+
+Summarize the fitting result
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+import glob
+import copy
+from adjustText import adjust_text   # avoid the overlapping while ploting
+from read_chisq import return_chisq 
+
+IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
+folder_type = '2nd_fit_'
+# IDs = ['3_SDSS1206']
+# folder_type = 'singel_fit_'
+#IDs = ['6_HS2209']
+#folder_type = '3rd_fit_'
+#%%
+for i in range(len(IDs)):
+    print(i, ':', IDs[i])
+inp = int(input("Which source:\n"))
+ID = IDs[inp][2:]
+filename = ID+'_' +folder_type[:4] + 'run_summary.pkl'
+# filename = ID+'_singel_host_run_summary.pkl'
+result = pickle.load(open(filename,'rb') ,encoding="latin1") 
+fit_values, chisq, labels, pick_names = result
+fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values
+
+sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
+#if labels[0][-17:]!='subg_2, PSFrecons' or labels[1][-15:]!='subg_2, QSOmask' or labels[0][-17:]!='subg_3, PSFrecons' or labels[1][-15:]!='subg_3, QSOmask'
+for i in range(len(labels)):
+    if labels[i][-17:] != sort_label_type[i%4]:
+        raise ValueError("The labels is wrong for some reason")
+        
+for i in range(len(pick_names)):
+    print(i, ':', pick_names[i])
+print(pick_names)
+pick = int(input('select the names to plot?:\n'))
+
+fit_value_l = [fit_value_l_list[i][pick] for i in range(len(labels))]
+fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
+fit_value_h = [fit_value_h_list[i][pick] for i in range(len(labels))]
+
+zp = 24. #!!!
[…]

### 2020-03-09 share_tools/read_chisq.py

@@ -14,8 +14,11 @@ import lenstronomy.Util.class_creator as class_creator
 sys.path.insert(0,'../py_tools')
 #from flux_profile import cr_mask
 
-def return_chisq(filename, lens_mask = None, fair_mask=True, fair_PSF =False, if_reduce=True):
-    result = pickle.load(open(filename,'rb'),encoding="latin1") 
+def return_chisq(filename, lens_mask = None, fair_mask=True, fair_PSF =False, if_reduce=True, py_version = 3):
+    if py_version ==3:
+        result = pickle.load(open(filename,'rb'),encoding="latin1") 
+    elif py_version ==2:
+        result = pickle.load(open(filename,'rb'))
     fit_result, trans_result, kwargs_material, model_lists  = result
 
     kwargs_data, kwargs_psf_updated, kwargs_numerics, kwargs_model, lens_mask_saved = kwargs_material

### 2020-03-09 share_tools/read_inference.py

@@ -26,6 +26,8 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
     '''
     if ID == "SDSS1206" :
         filename = ID+'_singel_host_run_summary.pkl'
+    elif ID == 'HS2209' or ID == 'RXJ1131':
+        filename = ID+'_3rd_run_summary.pkl'
     else:
         filename = ID+'_2nd_run_summary.pkl'
     result = pickle.load(open('../share_tools/'+filename,'rb'),encoding="latin1")
@@ -55,9 +57,14 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
             picks = [3]
         else:
             picks = [2]
-            
-#   print(ID, pick_names)
+    elif prop == 4 :  #Flux
+        if 'Disk' in pick_names[2]:
+            picks = [1,2]
+        else:
+            picks = [1]            
+#    print(ID, pick_names)
     result = []
+#    print(filename)
     for pick in picks:
         if isinstance(count_n, list) == False:
             fit_value_m = [fit_value_m_list[i][pick] for i in range(len(labels))]
@@ -98,7 +105,9 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
             result.append([round(weighted_value,rod), round(rms_value,rod)])            
     return result
 #result = read_inf('HE0435', prop = 0)
-#print(read_inf('RXJ1131', prop = 0))
+#print(read_inf('RXJ1131', prop = 4, count_n=[4, 4]))
+#print(read_inf('HS2209', prop = 1, count_n=8))
+
 
 filter_dict = {'HE0435': 'F160W', 'RXJ1131': 'ACS_F814W', 'WFI2033': 'F160W', 'SDSS1206': 'F160W', 
                'HE1104': 'F160W', 'SDSS0246': 'F814W', 'HS2209': 'F814W', 'HE0047': 'F814W'}

### 2020-03-09 share_tools/gene_overall_pickle_plot.py
Update gene_overall_pickle_plot.py

@@ -6,6 +6,8 @@ Created on Fri Jan 25 15:58:15 2019
 @author: Dartoon
 
 Summarize the fitting result
+
+Based on python 2
 """
 import numpy as np
 import astropy.io.fits as pyfits
@@ -13,218 +15,80 @@ import matplotlib.pyplot as plt
 import pickle
 import glob
 import copy
-from adjustText import adjust_text   # avoid the overlapping while ploting
+#from adjustText import adjust_text   # avoid the overlapping while ploting
 from read_chisq import return_chisq 
 
-IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
-folder = '2nd_fit_'
+#IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
+#folder_type = '2nd_fit_'
 # IDs = ['3_SDSS1206']
 # folder_type = 'singel_fit_'
-
-
-# for i in range(len(IDs)):
-#     ID = IDs[i][2:]
-#     root = '../'+ IDs[i]+ '/model/'
-#     pkl_folderfiles = glob.glob(root+folder_type+"PSFi_PSFrecons/result_PSF*.pkl")
-#     pkl_files = [pkl_folderfiles[i].split('/')[-1] for i in range(len(pkl_folderfiles))]
-#     psf_num = np.max([int(pkl_files[i].split('_PSF')[1]) for i in range(len(pkl_files))]) + 1
-    
-#     if float(len(pkl_files)/6) != len(pkl_files)/6. :
-#         raise ValueError("The number of the pickle result is the Multiples of six")
-    
-#     PSFno_ = range(psf_num)
-#     #The values to pick up:
-#     filename = pkl_folderfiles[0]
-#     result = pickle.load(open(filename,'rb'))
-#     fit_result, trans_result, kwargs_material, model_lists  = result
-#     pick_names = trans_result[-1]
-#     _, _, _, _, lens_mask = kwargs_material
-#     stdd_file = glob.glob(root+'fit_PSFi_QSOmask/*_stdd_boost.fits')
-#     if len(stdd_file)>1:
-#         raise ValueError("More than one *_stdd_boost.fits exits") 
-#     rms_boost = pyfits.getdata(stdd_file[0])
-#     lens_mask[rms_boost == rms_boost.max()] = 0
[…]

### 2020-03-13 manuscript/manuscript.tex
update paper draft
almost finished but need revise

@@
 \newcommand{\hst}{{\it HST}}
+\newcommand{\hc}{$H_0$}
 \newcommand{\efr}{$R_{\mathrm{eff}}$}
@@
 The consistent scaling resolutions derived from our sample confirm the evolution conclusion and confirm the the power of using strong lensed AGNs.
-The sample of the data are supposed to increase rapidly.
+The number of the detection of the lensed AGNs are supposed to increase rapidly leave this topic with a bright future...
 \end{abstract}
@@
 %%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
+\section{Introduction}
+\todo{Check abbreviation}\\
+The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}.
+The origin of the scaling relations is till unclear so far.
+In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
+On the other hand, without any physical coupling, the pure statistical convergence by galaxy mergers alone could also reproduce the observed correlations at local universe~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
 
-\section{Introduction}
-The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution.
+It is crucial to extend the correlation studies to higher redshift to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}.
+Recently, based on a sample of 32 AGNs, \citet{Ding2020a} (hereafter, D20) measured the scaling relations at redshift range up to $1.2<z<1.7$ using \hst/WFC3.
+Comparing to the published samples at local and intermediate redshift range, they confirm the an evolution scenario that the growth of BHs evolution predates than the host galaxy bulge.
+In a following up work, \citep{Ding2020b} compared their measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
+The tightness of the observed scaling relations at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations.
+Apparently, a larger sample at higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
 
-The origin of these relations is till unclear so far.
-In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection or having them share a common gas supply.
-On the other hand, without any physical coupling, the pure statistical convergence by galaxy mergers alone could also reproduce the observed correlations at local universe.
-It is crucial to extend the correlation studies to higher redshift and understand their evolution as a function of redshift.
-Recently, \citet{Ding2020} measured the scaling relations at redshift range of $1.2<z<1.7$ based on a sample of 32 AGNs using \hst/WFC3.
-Comparing to the published samples at local and intermediate redshift range, they confirm the an evolution scenario that the growth of BHs evolution predates than the host galaxy bulge.
-In the following up work, \citet{Ding2020b} used the measurements of the high-$z$ AGNs and compare to numerical simulations including the hydrodynamic simulation MassiveBlackII (MBII) and a semi-analytic model (SAM).
-The tightness of the scaling relation at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations.
-A larger sample at higher redshift would be even more beneficial to confirm this scenario.
-
-Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs provide a unique tool to make progress in this study (ref[Peng2006]), 
-provided that the lens modelling is accurate.
-\citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in H0LiCOW collaboration.
-This work has confirm the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
+Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs provide a unique tool to make progress in this study~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
+To test the fidelity of the modern lens modelling technique, \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration.
+This work verified that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
 As a following up effort, \citet{Ding2017b} has applied the advanced techniques to two strongly lensed systems to study their \mbh-\lhost\ relations and obtained consistent results to the ones in the literature.
@@
 In this work, we aim to make progress by completing the analysis of the entire eight systems.
-We have developed an independent approach to achieve a one-step inference of the host photometry.
+We would adopt a new independent approach to achieve a one-step inference of the photometry of the eight lensed host galaxies.
 We adopt the a set of extended modelling choices to assure the accuracy of our measurements.
-Moreover, we comparing our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross check.
-3/8 of our objects have multi-band \hst\ imaging and we are able to infer their host color to assess an accurate inference of the stellar mass.
-The extended range of the eight systems would help us to make a direct comparison to the latest measurements by \citet{Ding2020}.
+We will compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check.
+Besides, 3/8 of our objects have available multi-band \hst\ imaging and we are able to infer their host color so as to assess an accurate inference of the stellar mass.
 We also adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample.
+The extended range of the eight systems would help us to make a direct comparison to the latest measurements by D20.
 
-This paper is organized as follows xxx. Zeropoint are defined in the AB systems. A Chabrier initial mass function (IMF) is employed consistently.
+This paper is structured as follows.
+In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and their BH masses.
+In Section~\ref{sec:lens_model}, we describe our approach that designed to infer the lens models and reconstruct the host galaxy.
+We use the inferred photometry  to derive the stellar mass and the scaling relations to compare to the contrast sample in Section~\ref{sec:result}.
+The discussion and conclusions are drawed in Section~\ref{sec:diss&conc}.
+Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
+Magnitudes are presented in the AB system.
+A Chabrier initial mass function (IMF) is employed for the entire sample consistently.
 
 \section{Sample Selection}\label{sec:sample_select}
-We adopt the eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914.
-For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131).
-In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
-The detailed information of the observational conditions of our eight systems are given in Table~\ref{data_set}.
-Besides the adopted filter shown therein, some systems also observed by \hst\ by different bands.
-As will shown in Section~\ref{sec:mstar}, the multi-band information enables us to apply the stellar population, hence a more accurate \mstar\ estimation.
+We adopt eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914.
+We refer to ref[H0licow1 and Ding2017a] for the descriptions of these data.
+We summarized the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
+For conciseness, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).
 
-While we note that our sample size included eight systems, which is a limited sample to constrain the evolution of the scaling relation.
-In this particular work, we simply aim to plot the scaling relation of our sample and make comparison to the ones in the literature.
-%[]The comparison sample (32 QSO paper)
-We adopt the recent efforts by~\citet{Ding2020}, including 32 AGNs at redshift range $1.2<z<1.9$, 79 intermediate redshift QSO and 55 local measurements.
-It is worth noticing that they are so far the largest \hst\ imaging AGN samples with redshift range from 1.9 to the local.
+Based on the observational data of these eight systems, \citet{Ding2017a} has performed the extensive and realistic simulation exercise to understand the fidelity of the source reconstruction and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
+Thus, this work is mainly based on the imaging data listed in Table~\ref{data_set}.
+Moreover, as will show in Section~\ref{sec:mstar}, 3/8 systems also have the multi-band \hst\ imaging data which  enables us to apply more accurate stellar population to estimate their \mstar.
 
-\begin{table}
+While we note that the sample size by this work (i.e., eight systems) is quite limited.
+Rather than using them to constrain the evolution of the scaling relation, we simply derive their scaling relations so as to make a direct comparison to the recent efforts in D20, which includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}.
+It is worth noting that they are so far the largest \hst\ imaging AGN samples with redshift range up to $z\sim1.9$.
+
+\begin{table*}
 \centering
 %\begin{threeparttable}
-\caption{Summary of lensed AGN information.}\label{data_set}
-\resizebox{9cm}{!}{
-     \begin{tabular}{cccccc}
+\caption{Summary of lensed AGN observational details.}\label{data_set}
+\resizebox{13cm}{!}{
+     \begin{tabular}{cccccccc}
         \hline
-Object ID & $z$ & camera & Filter & exposure & pixel scale \\
- & & & & time (s) & (drizzled) \\ \hline
-HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & $0\farcs{}08$ \\
-RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & $0\farcs{}05$ \\
-WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & $0\farcs{}08$ \\
-SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & $0\farcs{}08$ \\
-HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & $0\farcs{}08$ \\
-SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & $0\farcs{}03$ \\
-HS2209$+$1914 & 1.07 & WFC3-UVIS & F814W & 14238 & $0\farcs{}03$ \\
-HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & $0\farcs{}03$ \\
+Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale \\
+ & & & & time (s) &&& (drizzled) \\ \hline
+HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
+RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ \\
+WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
+SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ \\
+HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ \\
+SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$ \\
+HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ \\
+HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ \\
         \hline
@@
       \small
-      \item Note: $-$ The observational information is presented in~\citet{Ding2017a}.
+      \item Note: $-$ The observational information is also presented in~\citet{Ding2017a}. 
+      \item $^a$: For HS2209, it is visited by \hst\ twice ({\it vis05} and {\it vis06}). The exposure time is thus given separately.
 \end{tablenotes}  
 %\end{threeparttable}
-\end{table}
+\end{table*}
 
-To assure the validity of the comparison, we adopt a class of self-consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample.
-For the overall systems, we adopt the following virial formalism:
+To assure the validity of the comparison, we adopt a class of self-consistent recipes to estimate the \mbh\ of our sample.
+For the entire systems, we follow D20 and adopt the following virial formalism:
 \begin{eqnarray}
@@
 %
-with a\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
-b\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
+with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
+$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
 $\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
 %
-Having achieved a consistent cross-calibration, we adopt the board line information from the literature \citep{Sluse2012, Peng2006, Shen2011} to estimate the \mbh.
-The information are presented in Table~\ref{mbh}.
+The board line information of our samples are adopted from the literature \citep{Sluse2012, Peng2006, Shen2011}.
+The \mbh\ measurement, together with the properties of the board-line are listed in Table~\ref{mbh}.
 The uncertainty of the \mbh\ are expected as $0.4$~dex.
@@
 %\begin{threeparttable}
-\caption{Summary of lensed \mbh\ estimates.}\label{mbh}
+\caption{Summary of \mbh\ estimates.}\label{mbh}
 \resizebox{8.5cm}{!}{
@@
 WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
-SDSS1206 & \Mgii & 5632 & 45.61 & 8.88 \\
+SDSS1206 & \Mgii & 5632 & 45.61$^a$ & 8.88 \\
 HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
@@
 \begin{tablenotes}
-      \small
-      \item Note: $-$ The reference for the board line information. For SDSS1206, we follow Birrer2018~ref[] and consider the magnification effect to correct the L.
+\item Note: $-$ The reference for the board line information. \\
+$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect.
 \end{tablenotes}  
@@
 
-\section{surface photometry with lensing technique}
-We present the lensed host galaxy source reconstruction to derive their intrinsic photometry in this section.
-Our lensed AGN systems are from the H0LiCOW project, and the lens models of four systems have been derived with host galaxies reconstructed ref[].
-Aiming at time-delay cosmography, these works focused on deriving the precise and accurate lens models, while the reconstruction of the host galaxy is only a by-product.
-In this paper, we apply the state-of-the-art lens modeling technique and dedicate to recovering the photometry of the host galaxy.
-As will show, approach would allow us to obtain a one-step host magnitude defined by \sersic\ profile, which is consistent to the definitions in the literature.
-%Furthermore, for cross check purpose, we compare our inference to the reconstructions by the previous works.
+\section{surface photometry with lensing technique}\label{sec:lens_model}
+We perform the study of the lens modelling to reconstruct the photometry of the lensed host galaxies in this section.
+Our lens systems are a part of the H0LiCOW project, and the lens models of 4/8 systems, including HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019}, have been derived.
+Aiming at the strong lensing time-delay cosmography~\citet{Treu2016}, these works mainly focused on deriving the precise and accurate lens models, while the reconstruction of the reconstructed host galaxies for these works can be considered as a by-product.
+In this work, we apply the state-of-the-art lens modelling technique and perform an independent effort focusing on recovering the photometry of the host galaxy.
+As will show, our approach would allow us to obtain a one-step host magnitude as defined by \sersic\ surface brightness profile; thus our measurements would be more consistent to the ones in the literature.
+Furthermore, for the 4/8 systems which has been studied in H0LiCOW project, we will make comparison to understand the accuracy of our analysis.
 
-\subsection{Model Choice}
-We carry out the fitting process to subtract the central AGN light, constrain the lens model, and reconstruct the host galaxy in the source plan, simultaneously.
-For all the systems, we assume the photometry of the galaxies (including the lensing galaxy and source galaxy) is described by the 2-D elliptical \sersic\ profile.
+\subsection{Data Preparation and Modelling Setup}
+We following the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information.
+The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}.
+We then adopt the {\sc photutils} by Python to model the 2-D global background light using SExtractor algorithm based on {\sc photutils} by Python.
+We remove the background light and cut the clear image data into postage stamp at a suitable size.
+We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see Figure~\ref{fig:image_inference}.
+
+We carry out the forward modelling process to constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy, simultaneously.
+For any extended objects including the lensing galaxy and source galaxy, we assume their photometry can be described by the 2-D elliptical \sersic\ profile.
 We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component.
-For single \sersic\ case, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in ref[] that this prior value would result in a consistent host magnitude inference as to fix n to its true value.}.
+For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in~\citet{Ding2017a} that setting \sersic\ $n$ as this prior value would result in a consistent host magnitude inference compared to a prior with fixing $n$ to the truth.}.
 The bright AGNs are unsolved and modelled by a scaled point spread function (PSF).
-We also joint the fitting of the AGN position to the center of its host.
+We also jointly fit the AGN position to the center of its host galaxy.
 We adopt the elliptical Power-law model to describe the surface mass density of the deflector; an external shear component is also added.
 
-We employ the imaging modelling tool \lenstronomy~ref[] to perform the fitting task.
-We following the standard procedure as described by~\citet{Ding2020} to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information.
-The imaging data are drizzled to a higher resolution by setting a Gaussian kernel; the adopted final resolution are listed in Table~\ref{data_set}.
-We then adopt the {\sc photutils} by Python to model the 2-D global background light using SExtractor algorithm.
-We then remove the background light and cut the clear image data into postage stamp at a suitable size.
-We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood; see Figure~\ref{fig:image_inference}.
-
-For each lens system, we adopt different choices to perform the fitting.
-The distribution of the fitting inference are assumed to sufficiently cover the truth.
-We then apply a statistical measurement to weighting for the final inference and estimate the uncertainty level.
-The different choice of the fitting including the following.
+We employ the imaging modelling tool \lenstronomy~\citep{lenstronomy} to perform the fitting task.
+For each system, we adopt different modelling choices to perform the fitting.
+The distribution of the fitting inference by the overall choices are supposed to sufficiently cover the truth.
+We then apply a statistical measurement and perform weighting algorithm to derive the final inference and the uncertainty level.
+The different modelling choices are selected based on the following options:
 \begin{enumerate}
 \item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF.
-Each selected star is consider as the initial PSF to input to the fitting, which is considered as different choice.
+Each selected star is considered as a initial PSF choice to input to the fitting.
 \item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF.
-To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite; 2)~perform the iterative PSF estimation as introduced by ref[].
+To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite (noise boost); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} (PSF iteration).
 \item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
-\item Using the lensing imaging alone is difficult to constrain the power-law slope.
-To avoid any overfitting, we fix the slope values during the lens modelling with three optional value $[1.9, 2.0, 2.1]$.
+\item Using the lensing imaging alone is difficult to constrain the power-law slope. To mitigate the overfitting of the slope value, we fix it with three optional values $[1.9, 2.0, 2.1]$.
 \end{enumerate}
 
-All in all, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting.
+In general, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting.
 After all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value.
-Finally, we adopt the weighting algorithm as introduced by Equations (3)$-$(6) in~\citet{Ding2020}.
-Since there is no obvious evidence of better perform between QSO mask or PSF iteration, we selected each top-4 fitting by these to choice and combining them equally to derive the final results and to evaluate the uncertainties.
+Since there is no evidence of any better performance for the options between noise boost and PSF iteration, we selected top-4 fittings from both of them and combining these two options equally to derive the final results and to evaluate the uncertainties.
+The weighting algorithm is introduced by D20 defined as follows:
+\begin{eqnarray}
+\label{eq:weights}
+w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
+\end{eqnarray} 
+where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter literally means that it has to be larger than~$1$.
+If $\alpha<1$, introducing the $\alpha$ would have a side-effect because the relative likelihood between different the selected choices would be too close.} so that when $i=4$:
+\begin{eqnarray}
+\label{eq:alpha}
+\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
+\end{eqnarray} 
+We aim to use this recipe to weight each choice based on their relative goodness of fit, while ensuring at least 8 (i.e., $4+4$) are used to capture the range of systematic uncertainties.
+Similar to Ding20, we also tested that our finally inference would not change significantly if we chose a different number of top ranked choices.
+
+Finally, the value of host properties and the root-mean-square error (i.e., $\sigma$ level) would be calculated based on the weights of the 8 top ranked choices by:
+\begin{eqnarray}
+\label{eq:infer_value}
+\bar{x}  =  \frac{  \sum_{i=1}^{N}   x_i * w_i  }{\Sigma w_i} ,
+\end{eqnarray} 
+\begin{eqnarray}
+\label{eq:infer_scatter}
+\sigma =   \sqrt{ \frac{  \sum_{i=1}^{N}   (x_i -  \bar{x} ) ^2 * w_i  }{\Sigma w_i} }.
+\end{eqnarray}
 
 \subsection{Photometry Inference}\label{sec:photometry}
-In this subsection, we describe the details of the fitting for each systems and present our inference of the host galaxy photometry.
+In this subsection, we describe the details of the fitting for each system and present the inference of the photometry of the host galaxy.
 
 \subsubsection{HE0435}
-The modeling is set up based on the descriptions in the last section.
+The modelling of HE0435 is performed based on the approach described in the previous section.
 We select 5 isolated stars in this field initial PSFs to input to the fitting with in total of 60 fittings for this system.
@@
 
-The lens model inference based on the best-fit result for HE0435 is drawn in Figure~\ref{fig:image_inference}-(a).
-Not surprisingly, we note that the residual level reveals are appears to be larger than the ones as presented by Ken[] or Simon[].
-This is due to the fact that the definition of the host galaxy in our models is a 2-D \sersic\ model which is relatively simple compare to the pixellated reconstruction technique by {\sc Glee} or the shapelet functions as adopted by \lenstronomy.
-The smooth feature of our model couldn't capture the clumps in the host of the star-forming regions, however, our model is more effective to derive the global host light as function of the \sersic\ which is consistent to measurements in the comparison sample.
+The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a).
+Not surprisingly, we note that the residual level reveals are appears to be larger than the ones as presented by~\citet{Wong2017}.
+This is majorly due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique by {\sc Glee} or the shapelet functions as adopted by \lenstronomy~\citep{Refregier2003, Birrer2015}.
+The smooth feature of \sersic\ profile could not capture the clumps in the host galaxy such as the star-forming regions.
+Nevertheless, our approach is more effective to derive the global host light in terms of the \sersic\ flux, which is consistent to measurements in the comparison sample.
 
-As a cross check, we compare our host magnitude to the measurement in Ding+2017[], in which they model the reconstructed host galaxy as \sersic\ based on Galfit [].
-The host magnitude measured in that paper is: $mag = 21.75 \pm 0.13$, %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
-which is slightly fainter than our inference, i.e. $mag = 21.50 \pm 0.35$. The offset is within $1-\sigma$ level.
+For cross-check propose, we compare our host magnitude to the inference in~\citet{Ding2017b}, in which they inferred the \sersic\ magnitude of the pixelized host galaxy as reconstructed by~\citet{Wong2017}.
+The host magnitude measured in ~\citet{Ding2017b} is: $mag = 21.75 \pm 0.13$, %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
+Compared to our inference, i.e. $mag = 21.50 \pm 0.35$, the offset is well within $1-\sigma$ level.
+
+\subsubsection{RXJ1131}
+The lens model of RXJ1131 observed with ACS/F814W has been well studied in~\citet{Suyu2013}.
+The host galaxy of this system is lensed to a spacious arc with a boundary line between the dominated area of bulge and disk could be clearly seen.
+Thus, we set the host galaxy is composed of two \sersic\ with index value $n$ fixed to $1$ and $4$ to mimic the light distribution of the disk and bulge, respectively.
+Besides, same as~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and fitting as the SIS and \sersic\ for its mass and light, respectively.
+
+The photometry of the RXJ1131 host galaxy is inferred using 4 initial PSFs.
+The results is summarized in Table~\ref{tab:host_measure}, with the best-fit result shown in Figure~\ref{fig:image_inference}-(b).
+
+We also compare our measurement to the previous reconstructions in \citet{Ding2017b}.
+Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$.
+Compared to our inference in Table~\ref{tab:host_measure}, our inferred bulge magnitude ($21.80\pm0.21$) are very consistent.
+However, we our inferred disk magnitude ($19.33\pm0.16$) is much brighter.
+This is probably because the definition of our host galaxy have extended regions to collect the disk light till larger radius compared to Glee by~\citet{Suyu2013} who perform the lens modelling using a smaller lens mask (see Figure~4 therein).
+
+\subsubsection{WFI2033}
+WFI2033 is the last quads in our sample whose lens model has been recently investigated by~\citet{Rusu2019}.
+There is a satellite galaxy in the north.
+However, as noted in~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light based on the \sersic\ model.
+We select in total of 8 initial PSF-stars selected to modelling this system.
+
+The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c).
+We compare our inference to the previous reconstructed host galaxies.
+Fitting the reconstructed host by~\citet{Rusu2019}, (i.e., the Figure 4 bottom-right plane) as a \sersic\ profile, we infer the $mag = 21.98 \pm 0.15$, which is consistent to our inference (i.e., $mag = 21.78 \pm 0.25$).
+
+\subsubsection{SDSS1206}
+SDSS1206 is an unique system -- the AGN is a doubly images by the deflector while most of the host is falls inside the inner caustic thus being quadruply imaged.
+Same as~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbations.
+Moreover, as noted in~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible (see Figure 1 in that paper).
+We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids.
+One can see the visible residuals in the fitted lensed arcs using a single \sersic\ model as host, however, we find a double \sersic\ couldn't significantly improve the goodness of the fitting.
+Thus, we adopt the single \sersic\ model in our final inference.
+
+Due to limit of stars in the filed of view, there are only 2 stars available as initial PSF.
+To expand the volume of modelling options, we also take the stack of the two bright stars as derived by~\citet{Birrer2019}, as a third initial PSF.
+It is worth noting that we adopt the same imaging modelling tool with~\citet{Birrer2019} using a similar manner.
+Our inferred results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(d).
+
+\subsubsection{HE1104}
+As a typical doubly lensed image, the lens model of HE1104 is modelled by us for the first time.
+We have selected in total of 5 initial PSFs to perform the fitting.
+The inference of the image is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
+With the best-fitting model, the lensed arcs could be clearly seen from the bottom-left panel, indicating a strong evidence of the detection of the host galaxy.
+
+\subsubsection{SDSS0246}
+Imaged with WFC3-UVIS/F814W, the resolution of the remaining three systems are much higher with drizzled pixel scaled as $0\farcs{}03$.
+However, their arc is much fainter compare to the IR band and the available pixels that could be used to fitting the arc are much limited.
+With in total 3 initial PSF selected, the host is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) with inference list in Table~\ref{tab:host_measure}.
+
+\subsubsection{HS2209}
+HS2209 imaging data have be observed by \hst\ with two visits.
+We modelled both two visited data separately and find that the identical host magnitude could be obtained.
+Moreover, we note that the data by the {\it vis06} can be derived with better goodness level, and thus the result by {\it vis06} was finally adopted (based on 7 intial PSF stars), as listed in Table~\ref{tab:host_measure}.
+The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g).
+
+\subsubsection{HE0047}
+HE0047 is the most challenging system in our sample with the lowest SNR of the lensed arcs.
+The results, based on 3 initial PSFs, are summarized in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
+The subtracted lensed host in the residual map its only half-seen among the noises.
+Thus, the host magnitude of the HE0047 should be taken with larger error budget.
 
@@
 \caption{\label{fig:image_inference} 
-Illustrations of the inference for each system. On the top: (left to right): . On the bottom: (left to right.) }
+Illustrations of the inference using the best-fit lens model for each system using AGN center noise level boosted approach.
+For each figure, the panels from left to right are the follows: Top raw: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the variance; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
+Across all the systems, the lensed arc image can be clearly seen by in the fifth panel, indicating a strong evidence of a detection.
+}
 \end{figure*}
-
-\subsubsection{RXJ1131}
-The image of RXJ1131 observed with ACS/F814W has been well studied in many reference.
-The host galaxy of this system is lensed to a spacious arc with a boundary line between the dominated area of bulge and disk could be clearly seen.
-Thus, we set the host galaxy is composed of two \sersic\ with index value $n$ fixed to $1$ and $4$ to mimic the light distribution of the disk and bulge, respectively.
-Besides, same as suyu[], we consider the perturbations by the small object ($0\farcs{5}$ in the north) and fitting as the SIS and \sersic\ for its mass and light, respectively.
-
-The inference of the RXJ1131 is based on 4 initial PSFs which is summarized in Table~\ref{tab:host_measure}, with the best-fit result drawn in Figure~\ref{fig:image_inference}-(b).
-
-We also compare our measurement to the previous reconstructions in Ding.
-Based on the reconstructions by Suyu[], the inference of the host magnitude by Ding[] is $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$.
-Compared to our inference in Table~\ref{tab:host_measure}, the bulge flux is very consistent, however, while our inferred disk is brighter by $\sim 0.5$ mag.
-\ding{Some discussion of this offset.}
-
-\subsubsection{WFI2033}
-WFI2033 is the last quads which has also been carefully studied recently in Ken[].
-There is a satellite galaxy in the north.
-However, as noted by Ken[], it has a much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using a \sersic\ model.
-There are in total of 8 PSF stars are selected to modelling this system.
-
-The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c).
-We also compare the inference to the reconstructions by Ken.
-Fitting their reconstruction as a \sersic\ profile, we have inferred that $mag = 21.98 \pm 0.15$ which is also consistent to our inference.
-
-\subsubsection{SDSS1206}
-SDSS1206 is a special system -- the AGN is a doubly images while most of the host is falls inside the inner caustic thus being quadruply imaged.
-We consider the galaxy triplet group at the north-west and use a single SIS model to denote their over all mass perturbations.
-Moreover, as noted by Simon[], a sub-clump is located in the north which is hardly visible  (i.e., Figure 1 in that paper).
-We model it as a SIS mass model and circular \sersic\ light model with joint centroids.
-Though we see the visible residuals in the fitted arcs using a single \sersic\ model, we find a double \sersic\ could help significantly improve the goodness of the fitting.
-Thus, we adopt the single \sersic\ model in our final inference.
-
-Due to limit of stars in the filed of view, there are only 2 stars available as initial PSF.
-To expand the volume of choice options, we also take the stack of the two bright stars as derived by Simon[] as a third initial PSF.
-Finally, the results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(d).
-\todo{Ask Simon for the reconstruction image to compare.}
-
-\subsubsection{HE1104}
-As a typical doubly lensed image, the lens model of HE1104 is modelled by us for the first time.
-We have selected in total of 5 initial PSFs to perform the fitting.
-The inference of the image is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
-With the best-fitting model, the lensed arcs could be clearly seen from the bottom-left panel, indicating a strong evidence of the detection of the host.
-
-\subsubsection{SDSS0246}
-Imaged with WFC3-UVIS/F814W, the resolution of the data is much higher.
-However, the arc is much fainter compare to the IR band and the available pixels that could be used to fitting the arc is quite limited.
-With in total 3 initial PSF selected, the host is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) with inference list in Table~\ref{tab:host_measure}.
-A template of 0.625 Gyr stellar population would be adopt.
-
-\subsubsection{HS2209}
-HS2209 imaging data have two visits. We modelled both two visited drizzling data.
-The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g).
-\ding{The host magnitude might be overestimated.
-The QSO is over bright with a positive background light.
-Xuheng is Re-fitting this image.}
-
-\subsubsection{HE0047}
-HE0047 is the most challenging system in our sample.
-The results, based on three PSFs, are summarized in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
-From the subtracted-everything-except-arc image, the lensed host is only half-seen among the large residuals.
-Thus, the inference of the HE0047 should be taken with larger scatters, or as upper limit.
 
@@
   \begin{threeparttable}
-\caption{Summary of lensed AGN inference.}\label{tab:host_measure}    
+\caption{Summary of lensed AGN host inference.}\label{tab:host_measure}    
 %\resizebox{12cm}{!}{
@@
       \small
-      \item Note: $-$ If any
+      \item Note: $-$ Inference of the host galaxy properties.
+Column (2)-(6): photometry inference derived using the imaging data in Table~\ref{data_set}.
+Column (7): age of adopted stellar population with stellar metallicity.
+Column (8): inferred stellar mass.
 \end{tablenotes}    
@@
 \section{Results}\label{sec:result}
-In this section, we describe the approaches and assumptions to adopt the stellar population to our sample.
-We then derive their stellar mass of our sample and study the  the scaling relation by connecting them to their \mbh.
-We compare our measurements by our sample to the ones in the literature to study their evolution.
+In this section, we describe the approaches and assumptions to estimate the stellar populations to our sample.
+Then, we adopt the populations to derive their stellar mass of our sample.
+We study the \mbh-\mstar\ scaling relations and compare our measurements to the ones the literature to study the evolution.
 
@@
 %[] Color inference for the first three cases to decide their stellar template. 
-Besides the band we imaging data at the given band we studied in last section, some of the systems also have other band observations by the \hst, which provides the color information of the host galaxy.
-Given that the other band data has less exposure time with lower single to noise level, we highlight that we only study the color to find a decent stellar template.
-Then, it would be adopted to the host photometry obtained in last section to infer the final stellar mass.
+Besides the imaging data we studied in last section, some of the systems also have other band observations by the \hst, which could provide the color information.
+Given that the data observed by other band has less exposure time with lower SNR, we note that we only study the color of the lensed host to determine a decent stellar populations for these systems.
+Then, these templates would be applied to the inferred host photometry in Table~\ref{tab:host_measure} column (2), to derive the final stellar mass.
 
-{\bf HE0435} ~ Besides the imaging data by F160W, this system has also been observed by the \hst\ through F814W and F555W band.
+{\bf HE0435} ~ Besides the imaging data by F160W, this system has been observed by the \hst\ through F814W and F555W filters.
 We adopted the same approach to modelling the data separately at these two band.
-% The inferred host magnitudes are xxx and xxx, respectively.
-Considering that the lensed host in the image plane is majorly inferred by the subtraction of the AGNs and deflectors light, which it is less dependent on the lens model.
-We expect it can be obtained with more accuracy.
-Thus, we infer the color based on the magnitude of the lensed arcs in the image plane.
-We use {\sc Gsf} code to fit the magnitude of the lensed host and find a 1.5 Gyr stellar template with solar metallicity could well match this color.
-More details of the information could be found in the Appendix~\ref{app:HE0435}.
+Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light, it should be less dependent on the lens model.
+We expect its magnitude in the image plane could be obtained with higher accuracy.
+Thus, we infer the color of the lensed arcs in the image plane.
+Having derived their magnitudes, we find a 1.5 Gyr stellar population with solar metallicity could well match this color.
+More detailed information is presented in Appendix~\ref{app:HE0435}.
 
-{\bf RXJ1131} ~ For this system, the lensed arc is very extended in the image plane which is resolved to the AGNs, one could directly perform the SED fitting of the arc in the image plane.
-Combining the \hst\ imaging data through three filter F814W and F555W and F160W, we inference the color and we adopt the stellar templates 3 Gyr and 1.5 Gyr with solar metallicity stellar to its bulge and disk, respectively (see Appendix~\ref{app:RXJ1131} for the inference).
+{\bf RXJ1131} ~ The host galaxy of RXJ1131 is lensed to a very extended arc in the image plane, which is resolved to the AGNs.
+We directly perform the SED fitting of the arc in the image plane.
+Combining the \hst\ imaging data through three filter F814W and F555W and F160W, we adopt the SED fitting by~\citet{Ding2017b} with the stellar populations of 3 Gyr and 1.5 Gyr and solar metallicity for its bulge and disk, respectively.
 
-{\bf WFI2033} ~ Besides the F160W filter, four other filters including F125W, F140W, F555W, F814W are also available in the \hst\ archive, which has been employed to obtain the color of the host galaxy.
-We perform the lens model inference for all the filter and infer the host color through five band in the image plane.
-We find a stellar template with 0.625 Gyr could well match their color (Appendix~\ref{app:WFI2033}).
+{\bf WFI2033} ~ Besides the F160W filter, four filters including F125W, F140W, F555W, F814W are also available in the \hst\ archive, which has been employed to obtain the color of the host galaxy.
+Same as the analysis of HE0435, we derive the host magnitude and infer the host color through five band in the image plane.
+We find a stellar popultion with 0.625 Gyr could well match its color (Appendix~\ref{app:WFI2033}).
 
-{\bf HE1104 and the other systems} ~ The imaging data of HE1104 has been observed through F555W and F814W band.
-However, given limited exposure time, the signal of the lensed arcs is too faint to be detected at this two bands.
-Due to this limitation, we couldn't infer the color of the host for HE1104.
-For this case, the other systems, we adopt the criteria by Ding2020[] to assign their stellar population, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
+{\bf HE1104 and the other systems} ~ The imaging data of HE1104 has also been observed by \hst\ through F555W and F814W band.
+However, given limited exposure time in these two bands, the lensed arcs is too faint to be detected; thus, we couldn't infer the color of the host for HE1104.
+For the other systems, they only have the single band data and the color information is also unknown.
+For these cases, we adopt the criteria by D20 to assign their stellar populations, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
 
 A summary of the adopted stellar populations is given in Table~\ref{tab:host_measure}, column~(7).
-Applying these templates to the filter magnitudes obtained in last section, we obtain the stellar mass of our system.
-Considering that we have obtained very consistent host photometry for the HE0435, RXJ1131 and WFI2033 to previous results using the independent approach, the fidelity of the inferred magnitude are considered to be high.
+Applying these templates to the filter magnitudes obtained in last section, we derive the stellar mass of our system.
+Considering that we are able to obtain the very consistent host magnitude for the HE0435, RXJ1131 and WFI2033 to previous results using the independent approach, the fidelity of the inferred magnitude are considered to be high.
 The uncertainty of the \mstar\ estimation are considered as the typical level $0.2$~dex.
-Same as the comparison, we expect that the uncertainty of the \mbh\ would dominate the error budget in the overall scaling relation obtained in next section.
 
 \subsection{The \mbh-\mstar\ relation}\label{sec:relation}
-Having obtained the \mstar\ of each individual system, we combine them with their \mbh\ to reveal the scaling relations.
-We expect to compare our high redshift lensed sample to the comparison sample as introduced in Section~\ref{sec:sample_select}.
-We plot the entire measurement together with and present in Figures~\ref{fig:scaling_relation}-(a).
-Following~\citet{Ding2020}, we fit the \mbh-\mstar\ data with a linear relation as:
+We plot the scaling relation of the \mstar-\mbh\ of our sample, together with the comparison sample as introduced in Section~\ref{sec:sample_select} in Figures~\ref{fig:scaling_relation}-(a).
+For the entire sample, we expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget.
+Following D20, we fit the local \mbh-\mstar\ sample as the baseline with a linear relation as:
 \begin{eqnarray}
@@
 \end {eqnarray}
-We find that our lensed systems appeared to have a slimier offset to the local relations which is consistent to the 32 QSOs by~\citet{Ding2020} at similar redshift range.
-
-To this evolution trend based on the sample redshift, we parameterize the evolution term as the linear relation by:
+Comparing with the local sample, we find that our lensed systems appeared to have a slimier offset to the local relations which is consistent to the 32 AGNs by D20 with similar redshift range, indicating a trend of evolution.
+To study the evolution based on the sample redshift, we parameterize the evolution term as the linear relation by:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-from which we recover the offset plot, i.e., Figure~8, in~\citet{Ding2020}.
-We then add the measurements by our lensed systems and show in Figure~\ref{fig:scaling_relation}-(b).
+where the $\Delta \log \mathcal M_{\rm BH}$ if the offset of the \mbh\ to the local baseline.
+To make a direct comparison, we first recover the offset plot of Figure~8 in D20.
+We add the plot using our new measurement and show in Figure~\ref{fig:scaling_relation}-(b).
 We find that the evolution of the offset our sample are well matched to the evolution trend as discovered by the previous inference.
 Given that we only obtain the measurements from eight lens systems, it is insufficient to fit the offset value quantitively.
-Nevertheless, the obvious consistency between the sample confirm the fidelity of our measurement and verify previous offset conclusions by~\citet{Ding2020}.
+Nevertheless, the obvious consistency between the sample confirm the fidelity of our measurement and verify previous offset conclusions by D20.
 
@@
 \caption{\label{fig:scaling_relation} 
-\todo{This Figures are still ugly so far, which need to be updated.}}
+(left): BH masses vs. stellar mass relations (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval based on the Equation~\ref{eq:MMlocal}.
+(right): offset of $\log(\mathcal M_{\rm BH})$ (vs.
+\mstar) as a function of redshift based on the D20 data using Equation~\ref{eq:offset}.
+We then plot our new measurement on top of the figure to make direct comparison.
+\todo{This Figures are still ugly so far, which need to be updated. Errorbar needs to be considered}}
 \end{figure*}
 
-\section{Discussion and Conclusion}
-[] This work confirm the bright future of lensing.
+\section{Systematic Errors}\label{sec:diss}
+We selected to use a set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices.
+In particular, we treat the two different modelling approaches, i.e., central mask and PSF iteration equally, to derive the averaged results.
+Of course, with different weighting manner, the combined result would be different.
+However, as we inspected the results on each choices for each systems, the dispersion of the results by the top ranked choices is usually small and the effect by different weighting choice is quite limited ($<0.1$~dex).
+Moreover, we adopt simple stellar population to derive their stellar mass.
+5/8 systems in our sample doesn't have the color information, and a criteria was adopted to define their stellar population would could also introduce the uncertainty in the inferred \mstar.
 
-Finally, we did not consider the selection effect.
+In any case, we point out that it is the uncertainty of the single-epoch black hole mass estimates (i.e., 0.4~dex) that dominate the error budget in the scaling relations.
+
+\section{Conclusion}\label{sec:con}
+Using eight strongly lensed AGN systems from the H0LiCOW collaboration, we presented the new measurements of the correlations of the supermassive black hole masses and the stellar masses of their host galaxy.
+We adopt the modern lens modelling techniques to estimate the magnitude host galaxy, defined by the \sersic\ profile.
+We estimated the \mbh\ of our sample using a set of self-consistent single-epoch estimators to assure the consistency.
+
+We directly compare our sample to the recent measurements by~\citet{Ding2020a}, who used the similar approaches to derive the \mstar\ and calibrated the \mbh\ using the consistent recipes.
+The \mbh-\mstar\ of our sample shows the very consistent evolution trend as discovered by D20, as shown in Figure~\ref{fig:scaling_relation}.
+The consistent result by our sample confirm the evolution of the D20 that the growth of a black hole predates that of its host galaxy.
+
+Our work, once again, confirmed the fidelity of using strong lensing as a tool to study the scaling relation at high redshift.
+The lensed AGN host galaxy can be accurately recovered using the state-of-the-art lens modelling technique.
+Even more, with a higher lens magnification effect, the lensed arc by the quadruply imaged sample has demonstrate the higher SNR level (see the Figure~\ref{fig:image_inference}, ``Residual of the lensed arcs'' panel).
+Apparently, the lensed AGNs have a great potential  to extend to study the \mbh-\mstar\ at even higher redshift range.
+
+%Finally, we did not consider the selection effect.
 Besides the mass function, the selection function of the lensed AGNs is also non-trivial.
 We note that these effects will have to be modelled in the future if the lensed sample is used to infer the evolution.
-
-Look at the future? JWST and TDCOSMO will extend the sample size.
+\todo{polish the re-writting:} Looking at the future, the sample of lensed quasars that can be analyzed with high fidelity is going to grow.
+The sample of lensed quasars and their hosts that can be studied at high fidelity is likely to continue to grow as more such systems are discovered in wide field imaging and spectroscopic surveys~\citep[e.g.][]{Agn++15,Mor++16,Sch++16,Ost++17}.
+The forthcoming launch of the James Webb Space Telescope and the first light of adaptive optics-assisted extremely large telescopes may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$).
 
 \section*{Acknowledgements}
+%This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib} and standard Python libraries.
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+This work is based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+X.D., S.B., and T.T.
+acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
+\todo{update the Acknowledgements}
 
@@
 %\end{thebibliography}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Color inference of the host}
-We describe the details of the stellar population inference in this section. The template would be then adopted to the photometry by Section~\ref{sec:photometry} to infer the stellar mass.
+We describe the details of the inference of the stellar population in this section. The template would be then adopted to the photometry by Section~\ref{sec:photometry} to infer the stellar mass.
 \subsection{HE0435}\label{app:HE0435}
@@
 We derive the magnitude of the lensed galaxy and infer the color of the host in the image plane.
-We illustrate the lens model for the other two band in Figure~\ref{fig:app_HE0435}.
-The inferred magnitude of the host galaxy in the image plane is quite robust.
+To save computer time, we only adopt the PSF iteration approach and fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}.
+We illustrate the lens model for the other two band in Figure~\ref{fig:app_HE0435}, (a), (b).
+The inferred magnitude of the host galaxy in the image plane is considered to be robust, and we consider them the have the same uncertainty as the F160W band inference.
 Having obtained the magnitude of the lensed host at three band, we use {\sc gsf} package to select the best stellar population from a range of [0.625, 0.8, 1.0, 1.5, 2.0, 3.0] Gyr with solar metallicity.
-Finally, a template with ago of 1.5 Gyr is selected.
+Finally, a stellar population with age of 1.5 Gyr demonstrated the best matching to the color, which is selected to the final inference, see Figure~\ref{fig:app_HE0435}, (c).
 
@@
 \subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
-\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}
+\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}\\
+\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/HE0435_host_color.pdf}}\\
 \caption{\label{fig:app_HE0435} 
-Illustrations of the inference of HE0435 at the other two band. }
+Illustrations of the inference of HE0435 using the data at the other two bands.
+Top two panels: best-fit model of the lensed arcs shown as Figure~\ref{fig:image_inference}.
+Bottom panel: SED inference of the color using the three band inference.}
 \end{figure*}
 
-\subsection{RXJ1131}\label{app:RXJ1131}
-Using the three band data including  ACS/F814W and ACS/F555W and NIC2/F160W (GO-9744; PI: C.
+%\subsection{RXJ1131}\label{app:RXJ1131}
+%Using the three band data including  ACS/F814W and ACS/F555W and NIC2/F160W (GO-9744; PI: C.
 S.
@@
 We can remove this A2 but only mention the fitting is done 2017 in that paper.}
-\begin{figure}
-\centering
-{\includegraphics[width=0.25\textwidth]{fig/map_age_zRXJ_1131.pdf}}\\
-\caption{\label{fig:app_RXJ1131} 
-Illustrations of the SED fitting of the galaxy age pixel by pixel.  }
-\end{figure}
+%\begin{figure}
+%\centering
+%{\includegraphics[width=0.25\textwidth]{fig/map_age_zRXJ_1131.pdf}}\\
+%\caption{\label{fig:app_RXJ1131} 
+%Illustrations of the SED fitting of the galaxy age pixel by pixel.  }
+%\end{figure}
 
@@
 Kochanek).
-The data quality by F125W is limited by its exposure time; and the host information is not well extracted.
-We does not take it into account in the color inference.
-Similar to Section~\ref{app:HE0435}, the lensed color of WFI2033 has been modelled through five band. The lensed models are presented in the~Figure~\ref{fig:app_WFI2033}.
-
+Similar to Section~\ref{app:HE0435}, the inference of the lensed arcs of WFI2033 have been fitted through five band.
+The lensed models are presented in the Figure~\ref{fig:app_WFI2033}, (a)-(d).
+Note that, limited by its exposure time, the data quality by F125W is quite poora and the host information is not well extracted.
+Thus, we does not take the inference by F125W into account in the color inference.
+We find the stellar population with 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}, (e).
 \begin{figure*}
@@
 \subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
-\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}
+\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
+\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
 \caption{\label{fig:app_WFI2033} 
-Illustrations of the inference of WFI2033 at the other two band.  }
+Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The inference of the lensed arcs is not clear in the F125W data, and thus the SED fitting is done through the other four bands.}
 \end{figure*} 

### 2020-03-13 Stellar_mass_estimate/0_HE0435_filter_plot/plot_spec_filter.py
Include the errorbar of the plots

@@ -1,0 +1,83 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Feb 25 10:13:22 2020
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from specutils import Spectrum1D
+import glob
+
+#%%To estimate the AB mag for a given stellar template
+#filename  = 'SED_files/summary_*_PA00.fits'
+#filename = glob.glob(filename)[0]
+#hdul_sum = pyfits.open(filename)
+#name_sum = hdul_sum[1].columns
+#table_sum = hdul_sum[1].data
+#z_idx = [i for i in range(len(name_sum)) if 'zmc' in str(name_sum[i])][0]
+#mel_idx = [i for i in range(len(name_sum)) if 'logZsun' in str(name_sum[i])][0]
+#z = table_sum[1][z_idx] #Redshift
+#mel = table_sum[1][mel_idx] #Metallicity 
+filename_p  = '../0_HE0435_color/SFH_*_PA00_param.fits'
+filename_p = glob.glob(filename_p)[0]
+hdul = pyfits.open(filename_p)
+table = hdul[1].data
+name = hdul[1].columns
+age_idx = [i for i in range(len(name)) if 'T_MW' in str(name[i])][0]
+age = str(round(10**table[1][age_idx],3)) # 'AGE:' Gyr
+z_idx = [i for i in range(len(name)) if 'zmc' in str(name[i])][0]
+z = str(round(table[1][z_idx],2))
+mel_idx = [i for i in range(len(name)) if 'Z_MW' in str(name[i])][0]
+mel = str(round(10**table[1][mel_idx],3)) # 'Mel:' Z*/Z_sun
+
+#%%
+spec1d = hdul_sum = pyfits.open("/Users/Dartoon/Astro/Packages/gsf/gsf/example/templates/gsf_spec_0435.fits")  
+name_spec = spec1d[1].columns
+table_spec = spec1d[1].data
+array_spec = np.zeros((len(table_spec), 7))
+for i in range(len(table_spec)):
+    array_spec[i, :] = table_spec[i]
+
+#%%
+plt.figure(figsize=(10, 6))
[…]

### 2020-03-13 Stellar_mass_estimate/2_WFI2033_filter_plot/plot_spec_filter.py

@@ -1,0 +1,88 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Feb 25 10:13:22 2020
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from specutils import Spectrum1D
+import glob
+
+#%%To estimate the AB mag for a given stellar template
+#filename  = 'SED_files/summary_*_PA00.fits'
+#filename = glob.glob(filename)[0]
+#hdul_sum = pyfits.open(filename)
+#name_sum = hdul_sum[1].columns
+#table_sum = hdul_sum[1].data
+#z_idx = [i for i in range(len(name_sum)) if 'zmc' in str(name_sum[i])][0]
+#mel_idx = [i for i in range(len(name_sum)) if 'logZsun' in str(name_sum[i])][0]
+#z = table_sum[1][z_idx] #Redshift
+#mel = table_sum[1][mel_idx] #Metallicity 
+filename_p  = '../2_WFI2033_color/SFH_*_PA00_param.fits'
+filename_p = glob.glob(filename_p)[0]
+hdul = pyfits.open(filename_p)
+table = hdul[1].data
+name = hdul[1].columns
+age_idx = [i for i in range(len(name)) if 'T_MW' in str(name[i])][0]
+age = str(round(10**table[1][age_idx],3)) # 'AGE:' Gyr
+z_idx = [i for i in range(len(name)) if 'zmc' in str(name[i])][0]
+z = str(round(table[1][z_idx],2))
+mel_idx = [i for i in range(len(name)) if 'Z_MW' in str(name[i])][0]
+mel = str(round(10**table[1][mel_idx],3)) # 'Mel:' Z*/Z_sun
+
+#%%
+spec1d = hdul_sum = pyfits.open("/Users/Dartoon/Astro/Packages/gsf/gsf/example/templates/gsf_spec_2033.fits")  
+name_spec = spec1d[1].columns
+table_spec = spec1d[1].data
+array_spec = np.zeros((len(table_spec), 7))
+for i in range(len(table_spec)):
+    array_spec[i, :] = table_spec[i]
+
+#%%
+plt.figure(figsize=(10, 6))
[…]

### 2020-03-13 Stellar_mass_estimate/HE0435_color_inference.py
Minor Update

@@ -64,6 +64,7 @@ for i in range(len(filter_list)):
 	zp = zeropoint_dict[filter_list[i]]
 	mag = -2.5*np.log10(weighted_value_list[i]) + zp
 	fnu = 10 ** ((mag-25)/(-2.5))
+#	print(filter_list[i], round(mag,3)) 
 	print(filter_list[i], round(fnu,3), '+-', round(fnu*uncer,3))
 	
 #%%After runing the fit:

### 2020-03-13 share_tools/read_inference.py

@@ -57,7 +57,7 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
             picks = [3]
         else:
             picks = [2]
-    elif prop == 4 :  #Flux
+    elif prop == 4 :  #Flux image plane
         if 'Disk' in pick_names[2]:
             picks = [1,2]
         else:
@@ -107,7 +107,7 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
 #result = read_inf('HE0435', prop = 0)
 #print(read_inf('RXJ1131', prop = 4, count_n=[4, 4]))
 #print(read_inf('HS2209', prop = 1, count_n=8))
-
+#print(read_inf('HS2209',  count_n=8))    
 
 filter_dict = {'HE0435': 'F160W', 'RXJ1131': 'ACS_F814W', 'WFI2033': 'F160W', 'SDSS1206': 'F160W', 
                'HE1104': 'F160W', 'SDSS0246': 'F814W', 'HS2209': 'F814W', 'HE0047': 'F814W'}
@@ -137,6 +137,7 @@ def read_fnu(ID, count_n=[4, 4]):
     return result
 #result = read_fnu('HE0435',  count_n=[4, 4])
 #print(read_fnu('HE0435',  count_n=[4, 4]))
+
 
 
 def read_mstar(ID, count_n=[4, 4], rod = 5):

### 2020-03-17 6_HS2209/model_05data_redo/0_cutout.py
Update the HS2209 analysis

@@ -1,0 +1,137 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 10:11:32 2019
+
+@author: Dartoon
+
+1. Remove SDSS1206 background light.
+2. Cutout SDSS1206 image.
+3. Select potential PSFs and compare the SDSS1206 ones.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
+from cut_image import sub_bkg, cut_center_bright, cut_image, save_loc_png
+from mask_objects import mask_obj
+from flux_profile import flux_profile, profiles_compare
+ID = 'HS2209_vis05_redo'
+
+#==============================================================================
+# Cut out the lens image
+#==============================================================================
+fitsFile = pyfits.open('../data/HS2209+1914_F814W_vis05_redo_sci.fits')
+
+from my_astro_func import read_pixel_scale
+pixscl = read_pixel_scale('../data/HS2209+1914_F814W_vis05_redo_sci.fits')
+
+
+# img = fitsFile[0].data # check the back grounp
+# img[img==0.] = np.nan
+# img_sub, bkg_light = sub_bkg(img)
+# pyfits.PrimaryHDU(img_sub).writeto('../data/HS2209_vis05_redo_sublight.fits',overwrite=True)
+img_sub = pyfits.getdata('../data/HS2209_vis05_redo_sublight.fits')
+#%%
+center_QSO = np.array([4888-1,5022-1]) #c_psf_list[QSO_loc]
+lens_image = cut_image(img_sub, center_QSO, 100)
+plt.imshow(lens_image, norm=LogNorm(),origin='low')
+plt.colorbar()
+plt.show()
+#lens_bkg_light = cut_image(bkg_light, center_QSO, 100)
+#plt.imshow(lens_bkg_light, norm=LogNorm(),origin='low')
+#plt.colorbar()
+#plt.show()
+
+#%%
+#==============================================================================
+# #Estimate the exposure time and error map:
+#==============================================================================
+from my_astro_func import read_fits_exp
[…]

### 2020-03-17 6_HS2209/model_05data_redo/1_clean_save_PSF.py

@@ -1,0 +1,60 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Dec  9 14:41:16 2019
+
+@author: Dartoon
+
+Clean the PSF then saved, make it to be loaded easier for the future.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import copy
+from matplotlib.colors import LogNorm
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
+from flux_profile import profiles_compare, cr_mask_img
+import glob
+
+psfname_list = glob.glob('PSF?.fits') 
+psfname_list.sort()
+psfs = []
+for i in range(len(psfname_list)):
+    print "PSF:", psfname_list[i]
+    psf_i = pyfits.getdata(psfname_list[i])
+    print psf_i.sum()
+    mask_files = glob.glob('PSF{0}_mask*.reg'.format(i))
+    if mask_files != []:
+        psf_mask = cr_mask_img(psf_i, mask_list=mask_files)
+#        psf_mask = (1 - (psf_mask != 0)*1.)
+        psf_clear = copy.deepcopy(psf_i)
+        for i in range(len(psf_i)):
+            for j in range(len(psf_i)):
+                if psf_mask[i, j] == 0:
+                    psf_clear[i, j] = (psf_i[-i-1, -j-1]*psf_mask[-i-1, -j-1])
+        print "plot PSF after clear:"
+        psf_i = psf_clear
+    plt.imshow(psf_i, origin = 'low', norm=LogNorm())
+    plt.show()
+    psfs.append(psf_i)
+
+#fig = profiles_compare(psfs, scal_list=np.ones(len(psfs)),
+#                       prf_name_list=['PSF'+str(i) for i in range(len(psfs))],
+#                       gridspace = 'log', if_annuli=True)
+#fig.savefig("PSFs_profile.pdf")
+#fig.show()
+
+framesize = 111
+ct = (len(psfs[0]) - framesize)/2    
+for i in range(len(psfs)):
+    psfs[i] = psfs[i][ct:-ct,ct:-ct]
+    psfs[i] = psfs[i]/np.sum(psfs[i])
[…]

### 2020-03-17 6_HS2209/model_05data_redo/3_read_result.py

@@ -1,0 +1,149 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Jan 25 10:44:07 2019
+
+@author: Dartoon
+
+Test load text from PDF
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+from matplotlib.colors import LogNorm
+import copy
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/projects/my_code/py_tools/')
+from flux_profile import cr_mask
+
+
+readfile = 'fit_PSFi_PSFrecons/result_PSF0_PSFrecons_gammafix1.9_subg2.pkl'
+#readfile = 'fit_PSFi_QSOmask/result_PSF2_QSOmask_gammafix1.9_subg3.pkl'
+result = pickle.load(open(readfile,'rb'),encoding="latin1") 
+fit_result, trans_result, kwargs_material, model_lists  = result
+
+kwargs_data, kwargs_psf_updated, kwargs_numerics, kwargs_model, lens_mask = kwargs_material
+lens_model_list, source_model_list, lens_light_model_list, point_source_list = model_lists
+
+#%%
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.Data.imaging_data import ImageData as Data
+from lenstronomy.Data.psf import PSF
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+from lenstronomy.Plots import chain_plot
+import lenstronomy.Plots.chain_plot as out_plot
+#%%
+kwargs_result, chain_list = fit_result
+
+sampler_type, samples_mcmc, param_mcmc, dist_mcmc  = chain_list[-1]    
+
+share_i = [i for i in range(len(lens_model_list)) if lens_model_list[i]=='SHEAR'][0]
+if 'e1' in kwargs_result['kwargs_lens'][share_i].keys():
+    g1 = kwargs_result['kwargs_lens'][share_i]['e1']
+    g2 = kwargs_result['kwargs_lens'][share_i]['e2']
+    kwargs_result['kwargs_lens'][share_i]={'gamma1': g1, 'gamma2': g2}
+
[…]

### 2020-03-17 6_HS2209/model_05data_redo/3_summary.py

@@ -55,7 +55,7 @@ fit_value_l_list, fit_value_m_list, fit_value_h_list, = [], [], []
 chisq = []
 fixgamma_list = []
 
-folder_i = ['3rd_fit_PSFi_QSOmask', '3rd_fit_PSFi_PSFrecons']
+folder_i = ['fit_PSFi_QSOmask', 'fit_PSFi_PSFrecons']
 for folder in folder_i:
 #    if folder == 'fit_PSFi_QSOmask':
 #        filenames = glob.glob('{0}/result_PSF?_S*'.format(folder))
@@ -150,8 +150,9 @@ def plt_result(fixgamma, chisq=chisq, ID = ID):
     weighted_value = np.sum(np.array(fit_value_m)*weight) / np.sum(weight)
     rms_value = np.sqrt(np.sum((np.array(fit_value_m)-weighted_value)**2*weight) / np.sum(weight))
     print(weighted_value, rms_value)
-    plt.plot(xs, xs*0+(weighted_value - rms_value), xs, xs*0+weighted_value, xs, xs*0+(weighted_value + rms_value),color = 'red')
-    plt.fill_between(xs, weighted_value - rms_value, weighted_value + rms_value, facecolor='red', alpha = 0.1)    
+#    print weighted_value, rms_value
+#    plt.plot(xs, xs*0+(weighted_value - rms_value), xs, xs*0+weighted_value, xs, xs*0+(weighted_value + rms_value),color = 'red')
+#    plt.fill_between(xs, weighted_value - rms_value, weighted_value + rms_value, facecolor='red', alpha = 0.1)    
     
     ##If want to put horizontal line:
 #    fill_ref = True

### 2020-03-17 6_HS2209/model_05data_redo/auto_run.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+fixg_i=2
+cd ./fit_PSFi_QSOmask/
+echo "fit_PSFi_QSOmask/"
+python 2_modelling_fix_gamma_QSO_mask.py ${fixg_i}
+cd ../fit_PSFi_PSFrecons/
+echo "fit_PSFi_PSFrecons/"
+python 2_modelling_fix_gamma_PSF_recons.py ${fixg_i}
+

### 2020-03-17 6_HS2209/model_05data_redo/fit_PSFi_PSFrecons/2_modelling_fix_gamma_PSF_recons.py

@@ -1,0 +1,313 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+In this script, fix gamma as Ken's results. Use, psf mask.
+Use PSF reconstruction.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+#sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+from mask_objects import mask_obj
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+ID = ID+'_vis05_redo'
+
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))   #!!!need to change
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))    #!!!need to change
+lens_mask = 1-cr_mask(lens_image, filename='../lens_mask.reg')
+
+framesize = 101
+ct = (len(lens_image) - framesize)/2
+lens_image = lens_image[ct:-ct,ct:-ct]
+lens_rms = lens_rms[ct:-ct,ct:-ct]
+lens_mask = lens_mask[ct:-ct,ct:-ct]
+
[…]

### 2020-03-17 6_HS2209/model_05data_redo/fit_PSFi_QSOmask/2_modelling_fix_gamma_QSO_mask.py

@@ -1,0 +1,339 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Jan 14 17:30:19 2019
+
+@author: Dartoon
+
+The QSO center noise level is boost to inf.
+psf_error_map not taken.
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+import pickle
+import sys
+sys.path.insert(0,'../../../../my_code/py_tools/')
+#sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+from mask_objects import mask_obj, find_loc_max
+import copy, corner 
+from psfs_average import psf_ave
+from flux_profile import cr_mask
+import glob
+
+sys.path.insert(0,'../../../share_tools/')
+from lens_information import pixel_scale
+
+import lenstronomy.Util.simulation_util as sim_util
+from lenstronomy.Data.imaging_data import ImageData
+from lenstronomy.Data.psf import PSF
+from lenstronomy.LightModel.light_model import LightModel
+from lenstronomy.PointSource.point_source import PointSource
+from lenstronomy.ImSim.image_model import ImageModel
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.Workflow.fitting_sequence import FittingSequence
+from lenstronomy.Plots.model_plot import ModelPlot
+from lenstronomy.Plots import chain_plot
+from lenstronomy.Sampling.parameters import Param
+from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
+
+import time
+
+import os
+path = os.getcwd()
+ID = path.split('/')[-3][2:]
+
+ID = ID+'_vis05_redo'
+t1 = time.time()
+
+lens_image = pyfits.getdata('../{0}_cutout.fits'.format(ID))   #!!!need to change
+lens_rms = pyfits.getdata('../{0}_stdd.fits'.format(ID))    #!!!need to change
+lens_mask = 1-cr_mask(lens_image, filename='../lens_mask.reg')
+
+framesize = 101
+ct = int((len(lens_image) - framesize)/2)
+lens_image = lens_image[ct:-ct,ct:-ct]
+lens_rms = lens_rms[ct:-ct,ct:-ct]
+lens_mask = lens_mask[ct:-ct,ct:-ct]
+
[…]

### 2020-03-17 manuscript/manuscript.tex
Update paper before metting TT tomorrow

@@
 \author[X. Ding et al.]{
-Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
-Tommaso Treu,$^{1}$
-Simon Birrer,$^{1, 2}$
-Dominique Sluse,\newauthor
-Chris Fassnacht,
-Matthew W. Auger,
-Kenneth C. Wong,
-Sherry H. Suyu,\newauthor
-Takahiro Morshita,
-and et al. $^{3}$
+Xuheng Ding$^{1}$\thanks{E-mail: dxh@astro.ucla.edu},
+Tommaso Treu$^{1}$,
+Simon Birrer$^{2}$,
+Dominique Sluse$^{3}$,\newauthor
+Chris Fassnacht$^{4}$,
+Matthew W. Auger$^{5}$,
+Kenneth C. Wong$^{6}$,
+Sherry H. Suyu$^{7,8,9}$,\newauthor
+Takahiro Morshita$^{10}$,
+and et al.
 \\
@@
 $^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
-$^{3}$xxx
+$^{3}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
+$^{4}$Department of Physics, University of California, Davis, CA 95616, USA\\
+$^{5}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{6}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+$^{7}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
+$^{8}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
+$^{9}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
+$^{10}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
 }
@@
 \begin{abstract}
-Strong lensed AGN has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies.
-In this work, we have adopted eight strongly lensed system from the H0LiCOW collaboration.
-The deep \hst\ data and adopt the \lenstronomy\ to reconstruct the image of the source.
+\todo{Needs to be rewritten.}
+Strong lensed active galactic nuclei (AGN) has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies.
+In this work, we have adopted eight strongly lensed system from our collaboration.
+The deep {\it Hubble Space Telescope}(\hst) data and adopt the \lenstronomy\ to reconstruct the image of the source.
 Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on the assumed stellar population.
@@
 \section{Introduction}
-\todo{Check abbreviation}\\
-The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}.
-The origin of the scaling relations is till unclear so far.
+The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}, whose origin is till unclear so far.
 In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
@@
 It is crucial to extend the correlation studies to higher redshift to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}.
-Recently, based on a sample of 32 AGNs, \citet{Ding2020a} (hereafter, D20) measured the scaling relations at redshift range up to $1.2<z<1.7$ using \hst/WFC3.
-Comparing to the published samples at local and intermediate redshift range, they confirm the an evolution scenario that the growth of BHs evolution predates than the host galaxy bulge.
+Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations at redshift range up to $1.2<z<1.7$ using \hst\ imaging with WFC3.
+Combining with the published samples in both local and intermediate redshift range, they confirm the evolution scenario that the growth of BHs evolution predates than the bulge component of the host galaxy.
 In a following up work, \citep{Ding2020b} compared their measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
 The tightness of the observed scaling relations at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations.
-Apparently, a larger sample at higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
+Apparently, a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
 
-Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs provide a unique tool to make progress in this study~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
-To test the fidelity of the modern lens modelling technique, \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration.
-This work verified that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
-As a following up effort, \citet{Ding2017b} has applied the advanced techniques to two strongly lensed systems to study their \mbh-\lhost\ relations and obtained consistent results to the ones in the literature.
+Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs have been used as unique tool to make progress in study the scaling relations at the distance universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
+Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration.
+This work confirms that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
+With a following up effort, \citet{Ding2017b} applied the advanced techniques to two strongly lensed systems analyzed by the H0LiCOW collaboration~\citep{Suyu2013, Wong2017} to study their \mbh-\lhost\ relations and obtained consistent scaling relations compared with the samples from the literature.
 
-In this work, we aim to make progress by completing the analysis of the entire eight systems.
-We would adopt a new independent approach to achieve a one-step inference of the photometry of the eight lensed host galaxies.
-We adopt the a set of extended modelling choices to assure the accuracy of our measurements.
-We will compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check.
-Besides, 3/8 of our objects have available multi-band \hst\ imaging and we are able to infer their host color so as to assess an accurate inference of the stellar mass.
-We also adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample.
+In this work, we intend to make progress by deriving the measurements of the \mbh-\mstar\ relation using the entire eight systems as introduced in \citet{Ding2017a}.
+We develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs.
+We adopt a set of extended modelling choices to assure the accuracy of our measurements.
+We compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check.
+To assess an accurate inference of stellar mass, we utilize the imaging data taken with the \hst\ multi-band filter to obtain the color information for 3/8 of our targets.
+Besides, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample.
 The extended range of the eight systems would help us to make a direct comparison to the latest measurements by D20.
@@
 This paper is structured as follows.
-In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and their BH masses.
+In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data condition and the BH masses.
 In Section~\ref{sec:lens_model}, we describe our approach that designed to infer the lens models and reconstruct the host galaxy.
-We use the inferred photometry  to derive the stellar mass and the scaling relations to compare to the contrast sample in Section~\ref{sec:result}.
-The discussion and conclusions are drawed in Section~\ref{sec:diss&conc}.
+We use the inferred photometry to derive the stellar mass and the scaling relations and combine with contrast sample to study the evolution in Section~\ref{sec:result}.
+The discussion and conclusions are drawed in Section~\ref{sec:diss} and~\ref{sec:con}.
 Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
@@
 
-\section{Sample Selection}\label{sec:sample_select}
+\section{Sample Selection and Black Hole Mass Estimates}\label{sec:sample_select}
 We adopt eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914.
-We refer to ref[H0licow1 and Ding2017a] for the descriptions of these data.
+We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data.
 We summarized the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
-For conciseness, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).
+For conciseness, in the rest of this paper, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).
 
-Based on the observational data of these eight systems, \citet{Ding2017a} has performed the extensive and realistic simulation exercise to understand the fidelity of the source reconstruction and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
-Thus, this work is mainly based on the imaging data listed in Table~\ref{data_set}.
-Moreover, as will show in Section~\ref{sec:mstar}, 3/8 systems also have the multi-band \hst\ imaging data which  enables us to apply more accurate stellar population to estimate their \mstar.
+Based on the observational data of these eight systems, \citet{Ding2017a} performed the extensive and realistic simulation exercise using the \hst\ image data of these eight systems and confirm that the source reconstruction using the state-of-the-art modelling technique is trustworthy.
+% when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
+Here, we re-summarized the imaging data information and listed in Table~\ref{data_set}.
+Besides the image data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems.
+As will show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to estimate their accurate \mstar.
 
-While we note that the sample size by this work (i.e., eight systems) is quite limited.
-Rather than using them to constrain the evolution of the scaling relation, we simply derive their scaling relations so as to make a direct comparison to the recent efforts in D20, which includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}.
-It is worth noting that they are so far the largest \hst\ imaging AGN samples with redshift range up to $z\sim1.9$.
+While we note that the sample size by this work (i.e., eight systems) is limited.
+Rather than using our measurement to constrain the evolution of the scaling relation, we plan to use our data and make a direct comparison to the recent efforts in D20, which includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}.
+It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.
 
@@
 
-To assure the validity of the comparison, we adopt a class of self-consistent recipes to estimate the \mbh\ of our sample.
-For the entire systems, we follow D20 and adopt the following virial formalism:
+To assure the consistency of the \mbh\ between the usage of different board lines, we adopt a class of self-consistent recipes to estimate the \mbh.
+For the entire AGN systems, we follow D20 and adopt the following virial formalism:
 \begin{eqnarray}
@@
 The board line information of our samples are adopted from the literature \citep{Sluse2012, Peng2006, Shen2011}.
-The \mbh\ measurement, together with the properties of the board-line are listed in Table~\ref{mbh}.
+The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}.
 The uncertainty of the \mbh\ are expected as $0.4$~dex.
@@
 \begin{tablenotes}
+\small
 \item Note: $-$ The reference for the board line information. \\
@@
 
-\section{surface photometry with lensing technique}\label{sec:lens_model}
+\section{surface photometry inference}\label{sec:lens_model}
 We perform the study of the lens modelling to reconstruct the photometry of the lensed host galaxies in this section.
-Our lens systems are a part of the H0LiCOW project, and the lens models of 4/8 systems, including HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019}, have been derived.
-Aiming at the strong lensing time-delay cosmography~\citet{Treu2016}, these works mainly focused on deriving the precise and accurate lens models, while the reconstruction of the reconstructed host galaxies for these works can be considered as a by-product.
+Our lens systems are a part of the H0LiCOW project, and the lens models of 4/8 systems, including HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been derived.
+Aiming at the strong lensing time-delay cosmography~\citep{Treu2016}, these works mainly focused on deriving the precise and accurate lens models, while the reconstruction of the reconstructed host galaxies from these works can be considered as a by-product.
 In this work, we apply the state-of-the-art lens modelling technique and perform an independent effort focusing on recovering the photometry of the host galaxy.
-As will show, our approach would allow us to obtain a one-step host magnitude as defined by \sersic\ surface brightness profile; thus our measurements would be more consistent to the ones in the literature.
-Furthermore, for the 4/8 systems which has been studied in H0LiCOW project, we will make comparison to understand the accuracy of our analysis.
+As will show, our approach would allow us to obtain a one-step host magnitude as defined by \sersic\ surface brightness profile; thus the measurements of the host galaxy properties would be more consistent to the ones in the literature.
+For the 4/8 systems which has been studied in H0LiCOW project, we will make comparison to understand the accuracy of our analysis.
 
@@
 The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}.
-We then adopt the {\sc photutils} by Python to model the 2-D global background light using SExtractor algorithm based on {\sc photutils} by Python.
+We then adopt the {\sc photutils} by Python to model the global background light in 2-D based on SExtractor algorithm.
 We remove the background light and cut the clear image data into postage stamp at a suitable size.
-We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see Figure~\ref{fig:image_inference}.
+We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.
 
@@
 For any extended objects including the lensing galaxy and source galaxy, we assume their photometry can be described by the 2-D elliptical \sersic\ profile.
-We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component.
+We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiply component.
 For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in~\citet{Ding2017a} that setting \sersic\ $n$ as this prior value would result in a consistent host magnitude inference compared to a prior with fixing $n$ to the truth.}.
-The bright AGNs are unsolved and modelled by a scaled point spread function (PSF).
+The bright nuclei is unsolved and modelled by a scaled point spread function (PSF).
 We also jointly fit the AGN position to the center of its host galaxy.
-We adopt the elliptical Power-law model to describe the surface mass density of the deflector; an external shear component is also added.
+We adopt the elliptical Power-law model to define the surface mass density of the deflector; an external shear component is also added.
 
 We employ the imaging modelling tool \lenstronomy~\citep{lenstronomy} to perform the fitting task.
-For each system, we adopt different modelling choices to perform the fitting.
+Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting for each system.
 The distribution of the fitting inference by the overall choices are supposed to sufficiently cover the truth.
-We then apply a statistical measurement and perform weighting algorithm to derive the final inference and the uncertainty level.
+We then apply a statistical measurement and perform weighting algorithm to derive the final inference and estimate the uncertainty level.
 The different modelling choices are selected based on the following options:
@@
 \item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF.
-Each selected star is considered as a initial PSF choice to input to the fitting.
+Each selected star is considered as an initial PSF to input to the fitting.
 \item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF.
-To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite (noise boost); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} (PSF iteration).
+To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
 \item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
@@
 In general, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting.
-After all sets of fittings are completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value.
-Since there is no evidence of any better performance for the options between noise boost and PSF iteration, we selected top-4 fittings from both of them and combining these two options equally to derive the final results and to evaluate the uncertainties.
-The weighting algorithm is introduced by D20 defined as follows:
+After all sets of fittings completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value.
+Since there is no evidence of an better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from both of them and then combining their best-fit results based on the weighting algorithm introduced by D20.
+The weights are defined by:
 \begin{eqnarray}
@@
 \end{eqnarray}
-We aim to use this recipe to weight each choice based on their relative goodness of fit, while ensuring at least 8 (i.e., $4+4$) are used to capture the range of systematic uncertainties.
-Similar to Ding20, we also tested that our finally inference would not change significantly if we chose a different number of top ranked choices.
 
-Finally, the value of host properties and the root-mean-square error (i.e., $\sigma$ level) would be calculated based on the weights of the 8 top ranked choices by:
+Then, the results by {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
 \begin{eqnarray}
@@
 
+Our approach uses the relative goodness of fit and ensures that at least 8 sets of best-fits are used to capture the range of systematic uncertainties.
+
 \subsection{Photometry Inference}\label{sec:photometry}
@@
 The modelling of HE0435 is performed based on the approach described in the previous section.
-We select 5 isolated stars in this field initial PSFs to input to the fitting with in total of 60 fittings for this system.
-Based on the top-eight choices, we perform the weighting algorithm and measure the host-to-total flux ratio, host magnitude, effective radius and \sersic\ index.
-The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(5) columns.
+We select 5 isolated stars in this field as initial PSFs to input to the fitting, with in total of 60 times fittings.
+Based on the top-eight choices, we perform the weighting algorithm and measure the host flux, host-to-total flux ratio, effective radius and \sersic\ index.
+The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
 
 The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a).
-Not surprisingly, we note that the residual level reveals are appears to be larger than the ones as presented by~\citet{Wong2017}.
-This is majorly due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique by {\sc Glee} or the shapelet functions as adopted by \lenstronomy~\citep{Refregier2003, Birrer2015}.
+Not surprisingly, we note that the residual level reveals in the normalized plot are appears to be larger than the ones as presented by~\citet{Wong2017}.
+This is majorly due to the fact that the surface brightness of the host galaxy by our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet functions as adopted by \lenstronomy~\citep{Refregier2003, Birrer2015}.
 The smooth feature of \sersic\ profile could not capture the clumps in the host galaxy such as the star-forming regions.
-Nevertheless, our approach is more effective to derive the global host light in terms of the \sersic\ flux, which is consistent to measurements in the comparison sample.
+Nevertheless, our approach is more effective to derive a one-step inference of the global host light in terms of the \sersic\ flux, which is more consistent to measurements in the comparison sample.
 
 For cross-check propose, we compare our host magnitude to the inference in~\citet{Ding2017b}, in which they inferred the \sersic\ magnitude of the pixelized host galaxy as reconstructed by~\citet{Wong2017}.
-The host magnitude measured in ~\citet{Ding2017b} is: $mag = 21.75 \pm 0.13$, %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
+The host magnitude measured in ~\citet{Ding2017b} is: $mag = 21.75 \pm 0.13$.
+%, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
 Compared to our inference, i.e. $mag = 21.50 \pm 0.35$, the offset is well within $1-\sigma$ level.
@@
 The host galaxy of this system is lensed to a spacious arc with a boundary line between the dominated area of bulge and disk could be clearly seen.
-Thus, we set the host galaxy is composed of two \sersic\ with index value $n$ fixed to $1$ and $4$ to mimic the light distribution of the disk and bulge, respectively.
-Besides, same as~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and fitting as the SIS and \sersic\ for its mass and light, respectively.
+Thus, we set the host galaxy is composed of two \sersic\ with index value $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge.
+In addition, same as~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and fitting as the SIS and \sersic\ for its mass and light, respectively.
 
-The photometry of the RXJ1131 host galaxy is inferred using 4 initial PSFs.
+The photometry of the RXJ1131 host galaxy is fitted with a sets of 4 initial PSFs.
 The results is summarized in Table~\ref{tab:host_measure}, with the best-fit result shown in Figure~\ref{fig:image_inference}-(b).
@@
 Compared to our inference in Table~\ref{tab:host_measure}, our inferred bulge magnitude ($21.80\pm0.21$) are very consistent.
-However, we our inferred disk magnitude ($19.33\pm0.16$) is much brighter.
-This is probably because the definition of our host galaxy have extended regions to collect the disk light till larger radius compared to Glee by~\citet{Suyu2013} who perform the lens modelling using a smaller lens mask (see Figure~4 therein).
+However, our inferred disk magnitude ($19.33\pm0.16$) is much brighter.
+This is likely because the reconstruction of our host galaxy have more extended regions to collect the disk light till larger radius compared with~\citet{Suyu2013} who perform the lens modelling using a smaller lens mask based on {\sc Glee} (see Figure~4 therein).
 
 \subsubsection{WFI2033}
-WFI2033 is the last quads in our sample whose lens model has been recently investigated by~\citet{Rusu2019}.
+WFI2033 is the last quadruply lensed system in our sample whose lens model has been recently investigated by~\citet{Rusu2019}.
 There is a satellite galaxy in the north.
-However, as noted in~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light based on the \sersic\ model.
-We select in total of 8 initial PSF-stars selected to modelling this system.
+However, as noted in~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using \sersic\ model.
+We select in total of 8 initial PSF-stars to modelling this system.
 
@@
 We compare our inference to the previous reconstructed host galaxies.
-Fitting the reconstructed host by~\citet{Rusu2019}, (i.e., the Figure 4 bottom-right plane) as a \sersic\ profile, we infer the $mag = 21.98 \pm 0.15$, which is consistent to our inference (i.e., $mag = 21.78 \pm 0.25$).
+Modelling the reconstructed host by~\citet{Rusu2019}, (i.e., the Figure~4 bottom-right plane therein) as a \sersic\ profile, we infer the $mag = 21.98 \pm 0.15$, which is very consistent to our inference (i.e., $mag = 21.78 \pm 0.25$).
 
@@
 Same as~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbations.
-Moreover, as noted in~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible (see Figure 1 in that paper).
+Moreover, as noted in~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible (see Figure~1 in \citet{Birrer2019}).
 We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids.
-One can see the visible residuals in the fitted lensed arcs using a single \sersic\ model as host, however, we find a double \sersic\ couldn't significantly improve the goodness of the fitting.
-Thus, we adopt the single \sersic\ model in our final inference.
 
@@
 It is worth noting that we adopt the same imaging modelling tool with~\citet{Birrer2019} using a similar manner.
+We find a visible residuals at the fitted lensed arcs region using a single \sersic\ model as host, however, a double \sersic\ model couldn't significantly improve the goodness of the fitting.
+Thus, we adopt the single \sersic\ model in our final inference.
 Our inferred results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(d).
@@
 \subsubsection{HE1104}
-As a typical doubly lensed image, the lens model of HE1104 is modelled by us for the first time.
+As a typical doubly lensed image, HE1104 is modelled by us for the first time.
 We have selected in total of 5 initial PSFs to perform the fitting.
+There is an object at the northeast.
+However, without knowing the redshift of this object and considering it is further away from the lens, we use mask to block its pixels in the fitting.
+
 The inference of the image is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
@@
 \subsubsection{SDSS0246}
-Imaged with WFC3-UVIS/F814W, the resolution of the remaining three systems are much higher with drizzled pixel scaled as $0\farcs{}03$.
-However, their arc is much fainter compare to the IR band and the available pixels that could be used to fitting the arc are much limited.
-With in total 3 initial PSF selected, the host is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) with inference list in Table~\ref{tab:host_measure}.
+Imaged with WFC3-UVIS/F814W, the resolution of this systems (together with the remaining two systems) are much higher with drizzled pixel scale as $0\farcs{}03$.
+However, their arcs are much fainter compared with the IR band.
+As a result, the available pixels that could be used to fitting the arc are actually much limited.
+Nevertheless, with in total 3 initial PSF selected, the host inference is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
 
 \subsubsection{HS2209}
-HS2209 imaging data have be observed by \hst\ with two visits.
+HS2209 have be imaged by \hst\ through two visits ($vis05$ and $vis06$).
 We modelled both two visited data separately and find that the identical host magnitude could be obtained.
-Moreover, we note that the data by the {\it vis06} can be derived with better goodness level, and thus the result by {\it vis06} was finally adopted (based on 7 intial PSF stars), as listed in Table~\ref{tab:host_measure}.
+Moreover, we note that the data by the {\it vis06} can be modelled with the better goodness level; thus the result by {\it vis06} was finally adopted (using 7 initial PSF stars), as listed in Table~\ref{tab:host_measure}.
 The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g).
@@
 Across all the systems, the lensed arc image can be clearly seen by in the fifth panel, indicating a strong evidence of a detection.
+In panel (3) and (4), we use white regions to indicate the area where the noise level is boosted.
 }
@@
 (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) \\    
-Object ID & intrinsic Magnitude & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & adopted AGE & $\log (M_{*}$)  \\
- & (source plane) & (image plane) & ($\%$) & (arcsec) & & (Gyr) & (M$_{\odot}$) \\ \hline
+Object ID & intrinsic Magnitude & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & stellar population & $\log (M_{*}$)  \\
+ & (source plane) & (image plane) & ($\%$) & (arcsec) & & age (Gyr) & (M$_{\odot}$) \\ \hline
 HE0435 & $21.49\substack{+0.40\\-0.29}$ & $18.58\substack{+0.30\\-0.23}$ & $36.0\pm11.1$ & $0.28\pm0.02$ & $2.71\pm0.20$ & $1.50$ & $10.91\substack{+0.12\\-0.16}$ \\
@@
       \item Note: $-$ Inference of the host galaxy properties.
-Column (2)-(6): photometry inference derived using the imaging data in Table~\ref{data_set}.
+Column (2)-(6): photometry inference derived using the imaging data in listed Table~\ref{data_set}.
 Column (7): age of adopted stellar population with stellar metallicity.
@@
 \section{Results}\label{sec:result}
-In this section, we describe the approaches and assumptions to estimate the stellar populations to our sample.
-Then, we adopt the populations to derive their stellar mass of our sample.
-We study the \mbh-\mstar\ scaling relations and compare our measurements to the ones the literature to study the evolution.
+In this section, we describe the approaches and assumptions as used to estimate the stellar populations to our sample.
+Then, we adopt the population templates to derive their stellar mass of our sample.
+We study the \mbh-\mstar\ relations and compare our measurements with the ones in the literature to study the evolution.
 
@@
 %[] Color inference for the first three cases to decide their stellar template. 
-Besides the imaging data we studied in last section, some of the systems also have other band observations by the \hst, which could provide the color information.
-Given that the data observed by other band has less exposure time with lower SNR, we note that we only study the color of the lensed host to determine a decent stellar populations for these systems.
-Then, these templates would be applied to the inferred host photometry in Table~\ref{tab:host_measure} column (2), to derive the final stellar mass.
+Besides the imaging data we analyzed in last section, some of the systems also imaged by the \hst\ through other bands, which could provide the color information.
+Given that the data observed by other band has less exposure time with lower signal-to-noise (SNR) level, we highlight that we only study the color of the lensed host to determine a decent stellar populations for these systems.
+Then, these population templates would be applied with the inferred host magnitude (i.e., Table~\ref{tab:host_measure} column (2)) to derive the final stellar mass.
 
@@
 We adopted the same approach to modelling the data separately at these two band.
-Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light, it should be less dependent on the lens model.
-We expect its magnitude in the image plane could be obtained with higher accuracy.
+Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy.
 Thus, we infer the color of the lensed arcs in the image plane.
-Having derived their magnitudes, we find a 1.5 Gyr stellar population with solar metallicity could well match this color.
+Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color.
 More detailed information is presented in Appendix~\ref{app:HE0435}.
@@
 {\bf RXJ1131} ~ The host galaxy of RXJ1131 is lensed to a very extended arc in the image plane, which is resolved to the AGNs.
-We directly perform the SED fitting of the arc in the image plane.
-Combining the \hst\ imaging data through three filter F814W and F555W and F160W, we adopt the SED fitting by~\citet{Ding2017b} with the stellar populations of 3 Gyr and 1.5 Gyr and solar metallicity for its bulge and disk, respectively.
+The SED fitting of the arc in the image plane can be directly performed using the imaging data.
+Using the \hst\ imaging data through three filter F814W and F555W and F160W, we adopt the SED fitting result by~\citet{Ding2017b} with the stellar populations of 3 Gyr and 1.5 Gyr (solar metallicity) for its bulge and disk, respectively.
 
 {\bf WFI2033} ~ Besides the F160W filter, four filters including F125W, F140W, F555W, F814W are also available in the \hst\ archive, which has been employed to obtain the color of the host galaxy.
-Same as the analysis of HE0435, we derive the host magnitude and infer the host color through five band in the image plane.
-We find a stellar popultion with 0.625 Gyr could well match its color (Appendix~\ref{app:WFI2033}).
+Same as the analysis of HE0435, we derive their host magnitudes and infer the host color in the image plane.
+We find a stellar population with 0.625 Gyr could well match its color (Appendix~\ref{app:WFI2033}).
 
@@
 However, given limited exposure time in these two bands, the lensed arcs is too faint to be detected; thus, we couldn't infer the color of the host for HE1104.
-For the other systems, they only have the single band data and the color information is also unknown.
+For the other systems, they do not have the multi-band observation by \hst.
 For these cases, we adopt the criteria by D20 to assign their stellar populations, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
@@
 A summary of the adopted stellar populations is given in Table~\ref{tab:host_measure}, column~(7).
-Applying these templates to the filter magnitudes obtained in last section, we derive the stellar mass of our system.
-Considering that we are able to obtain the very consistent host magnitude for the HE0435, RXJ1131 and WFI2033 to previous results using the independent approach, the fidelity of the inferred magnitude are considered to be high.
-The uncertainty of the \mstar\ estimation are considered as the typical level $0.2$~dex.
+Applying these templates to the filter magnitudes obtained in last section, we derive the stellar mass of our system, Table~\ref{tab:host_measure}, column~(8).
+Considering the simulating tests by~\citet{Ding2017a} and the fact that we are able to obtain the very consistent host magnitude for the HE0435, RXJ1131 and WFI2033 using the independent approaches, the fidelity of the inferred magnitude are expected to be high.
+The uncertainty of the \mstar\ estimation are considered as a typical level of $0.2$~dex.
 
 \subsection{The \mbh-\mstar\ relation}\label{sec:relation}
-We plot the scaling relation of the \mstar-\mbh\ of our sample, together with the comparison sample as introduced in Section~\ref{sec:sample_select} in Figures~\ref{fig:scaling_relation}-(a).
+We plot the scaling relation of the \mbh-\mstar\ of our sample, together with the comparison sample as introduced in Section~\ref{sec:sample_select}, in Figures~\ref{fig:scaling_relation}-(a).
 For the entire sample, we expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget.
@@
 \end{eqnarray} 
-where the $\Delta \log \mathcal M_{\rm BH}$ if the offset of the \mbh\ to the local baseline.
+where the $\Delta \log \mathcal M_{\rm BH}$ is the offset of the \mbh\ to the local baseline.
 To make a direct comparison, we first recover the offset plot of Figure~8 in D20.
-We add the plot using our new measurement and show in Figure~\ref{fig:scaling_relation}-(b).
-We find that the evolution of the offset our sample are well matched to the evolution trend as discovered by the previous inference.
-Given that we only obtain the measurements from eight lens systems, it is insufficient to fit the offset value quantitively.
-Nevertheless, the obvious consistency between the sample confirm the fidelity of our measurement and verify previous offset conclusions by D20.
+Then we add the data points using our new measurement and show in Figure~\ref{fig:scaling_relation}-(b).
+We find that the evolution of the offset our sample are well matched to the evolution trend as demonstrated the contrast sample.
+%Given that we only obtain the measurements from eight lens systems, it is insufficient to fit the offset value quantitively.
+Nevertheless,
+The apparent consistency in the samples verify the fidelity of our measurement. This result is also support the evolution conclusions drawn by D20.
 
@@
 We then plot our new measurement on top of the figure to make direct comparison.
-\todo{This Figures are still ugly so far, which need to be updated. Errorbar needs to be considered}}
+\todo{HS2209 need to be added. Error bars need to be remarked.}}
 \end{figure*}
@@
 Of course, with different weighting manner, the combined result would be different.
-However, as we inspected the results on each choices for each systems, the dispersion of the results by the top ranked choices is usually small and the effect by different weighting choice is quite limited ($<0.1$~dex).
-Moreover, we adopt simple stellar population to derive their stellar mass.
-5/8 systems in our sample doesn't have the color information, and a criteria was adopted to define their stellar population would could also introduce the uncertainty in the inferred \mstar.
+However, as we inspected the results on each choices for each systems, the dispersion of the results by the top ranked choices is usually small and the effect by using different weighting choice is trivial ($<0.1$~dex).
+In addition, we adopt simple stellar population to derive their stellar mass.
+5/8 systems in our sample do not have the color information, and a criteria was adopted to define their stellar population based on their redshift, which would could also introduce the uncertainty in the inferred \mstar.
 
@@
 We adopt the modern lens modelling techniques to estimate the magnitude host galaxy, defined by the \sersic\ profile.
-We estimated the \mbh\ of our sample using a set of self-consistent single-epoch estimators to assure the consistency.
+We estimated the \mbh\ of our sample using a set of self-consistent single-epoch estimators to assure the consistency of the correlation.
 
-We directly compare our sample to the recent measurements by~\citet{Ding2020a}, who used the similar approaches to derive the \mstar\ and calibrated the \mbh\ using the consistent recipes.
+We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the similar approaches to derive the \mstar\ and calibrated the \mbh\ using the consistent recipes.
 The \mbh-\mstar\ of our sample shows the very consistent evolution trend as discovered by D20, as shown in Figure~\ref{fig:scaling_relation}.
@@
 We note that these effects will have to be modelled in the future if the lensed sample is used to infer the evolution.
-\todo{polish the re-writting:} Looking at the future, the sample of lensed quasars that can be analyzed with high fidelity is going to grow.
-The sample of lensed quasars and their hosts that can be studied at high fidelity is likely to continue to grow as more such systems are discovered in wide field imaging and spectroscopic surveys~\citep[e.g.][]{Agn++15,Mor++16,Sch++16,Ost++17}.
-The forthcoming launch of the James Webb Space Telescope and the first light of adaptive optics-assisted extremely large telescopes may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$).
+The detection of the lensed quasars is going to grow rapidly and sample size of lensed AGNs with the hosts that can be recovered with high fidelity is likely to continue to grow in wide field imaging and spectroscopic surveys~\citep[e.g.,][]{Oguri2010, Agn++15,Mor++16,Sch++16,Ost++17}.
+The forthcoming launch of the {\it James Webb Space Telescope} and the first light of adaptive optics-assisted extremely large telescopes may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$).
 
@@
 acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
-\todo{update the Acknowledgements}
+\todo{To be updated.}
 
@@
 We derive the magnitude of the lensed galaxy and infer the color of the host in the image plane.
-To save computer time, we only adopt the PSF iteration approach and fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}.
-We illustrate the lens model for the other two band in Figure~\ref{fig:app_HE0435}, (a), (b).
-The inferred magnitude of the host galaxy in the image plane is considered to be robust, and we consider them the have the same uncertainty as the F160W band inference.
+To save computer time, we only adopt the {\it PSF iteration} approach and fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}.
+We illustrate the lens model for the other two band in Figure~\ref{fig:app_HE0435}-(a), (b).
+The accuracy of the inferred host magnitude in the image plane is considered to be robust, and we consider them to have the same uncertainty as the F160W band inference.
 Having obtained the magnitude of the lensed host at three band, we use {\sc gsf} package to select the best stellar population from a range of [0.625, 0.8, 1.0, 1.5, 2.0, 3.0] Gyr with solar metallicity.
-Finally, a stellar population with age of 1.5 Gyr demonstrated the best matching to the color, which is selected to the final inference, see Figure~\ref{fig:app_HE0435}, (c).
+Finally, a stellar population with age of 1.5 Gyr demonstrated the best matching to the color, which is selected to the final inference, see Figure~\ref{fig:app_HE0435}-(c).
 
@@
 Similar to Section~\ref{app:HE0435}, the inference of the lensed arcs of WFI2033 have been fitted through five band.
-The lensed models are presented in the Figure~\ref{fig:app_WFI2033}, (a)-(d).
-Note that, limited by its exposure time, the data quality by F125W is quite poora and the host information is not well extracted.
+The lensed models are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d).
+Note that, limited by its exposure time, the data quality by F125W is not ideal and the host information could not be well extracted.
 Thus, we does not take the inference by F125W into account in the color inference.
-We find the stellar population with 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}, (e).
+Finally, we find the stellar population with 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}-(e).
 \begin{figure*}

### 2020-03-17 Stellar_mass_estimate/0_HE0435_filter_plot/plot_spec_filter.py

@@ -12,6 +12,9 @@ import matplotlib.pyplot as plt
 from specutils import Spectrum1D
 import glob
 
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
 #%%To estimate the AB mag for a given stellar template
 #filename  = 'SED_files/summary_*_PA00.fits'
 #filename = glob.glob(filename)[0]
@@ -35,7 +38,7 @@ mel_idx = [i for i in range(len(name)) if 'Z_MW' in str(name[i])][0]
 mel = str(round(10**table[1][mel_idx],3)) # 'Mel:' Z*/Z_sun
 
 #%%
-spec1d = hdul_sum = pyfits.open("/Users/Dartoon/Astro/Packages/gsf/gsf/example/templates/gsf_spec_0435.fits")  
+spec1d = pyfits.open("/Users/Dartoon/Astro/Packages/gsf/gsf/example/templates/gsf_spec_0435.fits")  
 name_spec = spec1d[1].columns
 table_spec = spec1d[1].data
 array_spec = np.zeros((len(table_spec), 7))
@@ -74,10 +77,10 @@ xmin, xmax, ymin, ymax = plt.axis()
 plt.text( (xmax-xmin)*0.7, (ymax-ymin)*0.6, 'stellar population with:', fontsize=17)
 plt.text( (xmax-xmin)*0.8, (ymax-ymin)*0.53, 'z={0}'.format(z), fontsize=17)
 plt.text( (xmax-xmin)*0.8, (ymax-ymin)*0.45, 'age={0:.1f} Gyr'.format(float(age)), fontsize=17)
-plt.text( (xmax-xmin)*0.8, (ymax-ymin)*0.37, 'Z*/Z_sun={0} '.format(mel), fontsize=17)
+plt.text( (xmax-xmin)*0.8, (ymax-ymin)*0.37, 'Z$_*$/Z$_\odot$={0}'.format(mel), fontsize=17)
 plt.legend(prop={'size':15})
 plt.tick_params(labelsize=15)
 plt.xlabel("um",fontsize=27)
-plt.ylabel(r"f$_\lambda$ $10^{-17}$ erg/s/cm$^2$/A",fontsize=27)
+plt.ylabel(r"f$_\lambda$ 10$^{\rm -17}$ erg/s/cm$^2$/$\AA$",fontsize=27)
 #plt.yticks([])
 plt.savefig('HE0435_host_color.pdf')

### 2020-03-17 Stellar_mass_estimate/2_WFI2033_filter_plot/plot_spec_filter.py

@@ -12,6 +12,9 @@ import matplotlib.pyplot as plt
 from specutils import Spectrum1D
 import glob
 
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
 #%%To estimate the AB mag for a given stellar template
 #filename  = 'SED_files/summary_*_PA00.fits'
 #filename = glob.glob(filename)[0]
@@ -35,7 +38,7 @@ mel_idx = [i for i in range(len(name)) if 'Z_MW' in str(name[i])][0]
 mel = str(round(10**table[1][mel_idx],3)) # 'Mel:' Z*/Z_sun
 
 #%%
-spec1d = hdul_sum = pyfits.open("/Users/Dartoon/Astro/Packages/gsf/gsf/example/templates/gsf_spec_2033.fits")  
+spec1d = pyfits.open("/Users/Dartoon/Astro/Packages/gsf/gsf/example/templates/gsf_spec_2033.fits")  
 name_spec = spec1d[1].columns
 table_spec = spec1d[1].data
 array_spec = np.zeros((len(table_spec), 7))
@@ -46,10 +49,6 @@ for i in range(len(table_spec)):
 plt.figure(figsize=(10, 6))
 array_spec[:,2] =  array_spec[:,2]/ array_spec[:,2].max() * 2.65
 plt.plot(array_spec[:,0]/10000., array_spec[:,2])
-
-f140w_fil = np.loadtxt('/Users/Dartoon/Astro/Packages/gsf/gsf/example/filter/204.fil')
-f140w_fil[:,2] = f140w_fil[:,2]/f140w_fil[:,2].max()* array_spec[:,2].max()/6
-plt.plot(f140w_fil[:,1]/10000., f140w_fil[:,2], label='F140W response')
 
 f160w_fil = np.loadtxt('/Users/Dartoon/Astro/Packages/gsf/gsf/example/filter/205.fil')
 f160w_fil[:,2] = f160w_fil[:,2]/f160w_fil[:,2].max()* array_spec[:,2].max()/6
@@ -62,6 +61,11 @@ plt.plot(f555w_fil[:,1]/10000., f555w_fil[:,2], label='F555W response')
[…]

### 2020-03-17 material/plot_append_WFI2033.py

@@ -27,7 +27,7 @@ IDs = ['2_WFI2033']
 #0 = int(0ut("Which source:\n"))
 ID = IDs[0][2:]
 filters = ['f125w', 'f140w', 'f555w', 'f814w'] 
-file_info = '/{0}_model/fit_PSFi_PSFrecons/result_PSF0_*_gammafix1.9*.pkl'.format(filters[3])
+file_info = '/{0}_model/fit_PSFi_PSFrecons/result_PSF0_*_gammafix1.9*.pkl'.format(filters[1])
 #
 filename = glob.glob('../'+IDs[0]+file_info )
 #filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_PSFrecons/result_PSF0_*_gammafix2.1_subg2.pkl')
@@ -101,6 +101,7 @@ else:
 modelPlot.data_plot(ax=axes[0], no_arrow=no_arrow)
 modelPlot.model_plot(ax=axes[1], no_arrow=no_arrow)
 #modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6)
+#Multe the arrow in: /Users/Dartoon/Astro/Packages/lenstronomy/lenstronomy/Plots/model_band_plot.py
 modelPlot.subtract_from_data_plot(ax=axes[2], point_source_add=True,lens_light_add=True, source_add=False, 
                                   text='Residual of lensed arcs')#, no_arrow=no_arrow)
 modelPlot.decomposition_plot(ax=axes[3], text='Modelled source light', source_add=True)#, no_arrow=no_arrow)

### 2020-04-06 manuscript/manuscript.tex
Update manuscript.tex
Update project

@@
 
-Our work, once again, confirmed the fidelity of using strong lensing as a tool to study the scaling relation at high redshift.
+Our work, one more time, confirmed the fidelity of using strong lensing as a tool to study the scaling relation at high redshift.
 The lensed AGN host galaxy can be accurately recovered using the state-of-the-art lens modelling technique.
@@
 \centering
-\subfloat[WFI2033 F125W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
-\subfloat[WFI2033 F140W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
+\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
+\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
 \subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\

### 2020-04-06 0_HE0435/model/3_summary.py

@@ -126,21 +126,25 @@ if label0 != label1 or bars!= label0:
     raise ValueError("The labels is wrong for some reason")
 color = ['green', 'orange']
 
-count_n = 8 #len(labels) * 20 /100
-chisq = [float(chisq[i]) for i in range(len(chisq))]
-sort_chisq = np.argsort(np.asarray(chisq))    
-Chisq_best = chisq[sort_chisq[0]]
-#Chisq_last= chisq[sort_chisq[-1]]
-Chisq_last= chisq[sort_chisq[count_n-1]]
-weight = np.zeros(len(chisq))
-inf_alp = (Chisq_last-Chisq_best) / (2*2.* Chisq_best)
-for i in sort_chisq[:count_n]:
-#for i in range(len(sort_chisq)):
-#    weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best))
-    weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best* inf_alp))
-weighted_value = np.sum(np.array(fit_value_m)*weight) / np.sum(weight)
-rms_value = np.sqrt(np.sum((np.array(fit_value_m)-weighted_value)**2*weight) / np.sum(weight))
-print("weighted_value, rms_value:", weighted_value, rms_value, 'used sets:', count_n)
+#count_n = 8 #len(labels) * 20 /100
+#chisq = [float(chisq[i]) for i in range(len(chisq))]
+#sort_chisq = np.argsort(np.asarray(chisq))    
+#Chisq_best = chisq[sort_chisq[0]]
+##Chisq_last= chisq[sort_chisq[-1]]
+#Chisq_last= chisq[sort_chisq[count_n-1]]
+#weight = np.zeros(len(chisq))
+#inf_alp = (Chisq_last-Chisq_best) / (2*2.* Chisq_best)
+#for i in sort_chisq[:count_n]:
+##for i in range(len(sort_chisq)):
+##    weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best))
+#    weight[i] = np.exp(-1/2. * (chisq[i]-Chisq_best)/(Chisq_best* inf_alp))
+#weighted_value = np.sum(np.array(fit_value_m)*weight) / np.sum(weight)
+#rms_value = np.sqrt(np.sum((np.array(fit_value_m)-weighted_value)**2*weight) / np.sum(weight))
[…]

### 2020-04-06 share_tools/read_inference.py

@@ -30,7 +30,7 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
         filename = ID+'_3rd_run_summary.pkl'
     else:
         filename = ID+'_2nd_run_summary.pkl'
-    result = pickle.load(open('../share_tools/'+filename,'rb'),encoding="latin1")
+    result = pickle.load(open('/Users/Dartoon/Astro/Projects/lens_host_reconstruction/share_tools/'+filename,'rb'),encoding="latin1")
     fit_values, chisq, labels, pick_names = result
     sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
     fit_value_l_list, fit_value_m_list, fit_value_h_list = fit_values

### 2020-05-01 manuscript/manuscript.tex
Include HS2209 MBH and update the figures.

--- 2020-03-17 manuscript/manuscript.tex
@@
 % Keep the title short and informative.
-\title[Mass relations by lensed AGN hosts]{The Mass Relations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGN Systems.}
+\title[Mass relations by lensed AGN hosts]{Testing the evolution of the correlations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGNs.}
 
@@
 $^{10}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
+$^{11}$TBC
 }
@@
 \begin{abstract}
-\todo{Needs to be rewritten.}
 Strong lensed active galactic nuclei (AGN) has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies.
@@
 \section{Introduction}
-The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}, whose origin is till unclear so far.
-In theory, cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
-On the other hand, without any physical coupling, the pure statistical convergence by galaxy mergers alone could also reproduce the observed correlations at local universe~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
+The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}.
+Cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
+However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic megers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
 
-It is crucial to extend the correlation studies to higher redshift to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}.
-Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations at redshift range up to $1.2<z<1.7$ using \hst\ imaging with WFC3.
-Combining with the published samples in both local and intermediate redshift range, they confirm the evolution scenario that the growth of BHs evolution predates than the bulge component of the host galaxy.
-In a following up work, \citep{Ding2020b} compared their measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
-The tightness of the observed scaling relations at high-$z$ supports the hypothesis that AGN feedback as a promising driver for the scaling correlations.
-Apparently, a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
+A powerful way to understand the origin of the correlations is to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}.
+Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging.
+Combining the new sample with published samples in both local and intermediate redshift range, they strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy.
+With the goal of testing theoretial ideas, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
+The observed tightness of the  scaling relations at high-$z$ is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature.
+%, a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
 
@@
 SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
-HS2209 & xxx & xxx & xxx &  xxx  \\
+HS2209 & \Mgii & 3245 & 45.71 & 8.75 \\
 HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
@@
 \small
-\item Note: $-$ The reference for the board line information. \\
+\item Note: $-$ The reference for the board line information. For HS2209, its board line is estimated in this work using the same approach as~\citet{Sluse2012}.\\
 $^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect.
@@
 We then plot our new measurement on top of the figure to make direct comparison.
-\todo{HS2209 need to be added. Error bars need to be remarked.}}
+}
 \end{figure*}

### 2020-05-01 MBH_estimator/est_MBH.py

@@ -1,6 +1,6 @@
 import numpy as np
 MBH_by_Domini =  {'HE0435': [8.76, 0.44], 'RXJ1131': [7.9, 0.6], 'WFI2033': [8.63, 0.35], 'SDSS1206': [8.62, 0.24], 
-               'HE1104': [9.37, 0.5], 'SDSS0246': [8.59, 0.36], 'HE0047': [8.83, 0.23]}#,'HS2209': [None, None],}
+               'HE1104': [9.37, 0.5], 'SDSS0246': [8.59, 0.36], 'HE0047': [8.83, 0.23],'HS2209': [None, None],}
 
 #HE1104 From Peng 06: Arxiv: 0603248 #For Civ: F_A*2.99792*10**5/(1+z)/1549 F_A = 103.0 , z = 2.32 (Table 3)
 
@@ -10,7 +10,7 @@ MBH_by_Domini =  {'HE0435': [8.76, 0.44], 'RXJ1131': [7.9, 0.6], 'WFI2033': [8.6
 
 #For Dominique's sample
 #For bolometric correction. 
-#Lbol for Mgii should be -np.log10(5.15)
+#Lbol for Mgii should be -np.log10(5.15)  # In Dominique, it is the Lbol measured, and one should change it to L_3000. For HS2209, Dominique direct provide me the L_3000.
 #Lbol for Hb should be -np.log10(9.6), 
 #Lbol for Civ should be -np.log10(3.81), 
 
@@ -21,8 +21,8 @@ BL_info =  {'HE0435': {'Mgii': {'L': [45.7 -np.log10(5.15), 46.0 -np.log10(5.15)
                  'SDSS1206': {'Mgii': {'L': [(44.23-2.22)/0.909 -np.log10(4.)], 'FWHM':   5632.4}},
                  'HE1104':  {'Civ': {'L': [46.18], 'FWHM':   6004.0}}, 
                  'SDSS0246': {'Mgii': {'L': [46.0-np.log10(5.15), 45.8-np.log10(5.15)], 'FWHM':   3700.0}},
-                 'HE0047': {'Mgii': {'L': [46.3-np.log10(5.15), 46.3-np.log10(5.15)], 'FWHM':   4145.0}}}
-#                 'HS2209': [None, None]} 
+                 'HE0047': {'Mgii': {'L': [46.3-np.log10(5.15), 46.3-np.log10(5.15)], 'FWHM':   4145.0}},
[…]

### 2020-05-01 material/print_table.py

@@ -51,7 +51,7 @@ sys.path.insert(0,'../MBH_estimator/')
 from est_MBH import BL_info, cal_MBH
 print("Object ID & Line(s) used & FWHM & log($L_\\lambda$) & $\\log$\\mbh \\\\")
 print("& & (\\kms) & ($[\\rm erg~s^[-1]]$) & (M$_{\\odot}$) \\\\ \\hline")
-for ID in ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '7_HE0047']:
+for ID in ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']:
     ID = ID[2:]
     line_infor = BL_info[ID]
 #   for key in BL_info[ID].keys():

### 2020-05-01 relation_plots/MM_32QSO.py

@@ -239,9 +239,9 @@ if inp_Cis ==1:
 # if inp_Knud ==1:
 #     plt.scatter(Knud[:,4], Knud[:,2],c='blue',marker="o",s=180,zorder=101, edgecolors='white')
 
-tx, ty = 11.85, 7.
-plt.text(tx, ty, "intermediate\n  sample\nuncertainties",  fontsize=20)
-plt.errorbar(tx+0.2,ty-0.08, xerr=0.2, yerr=0.4, color='darkseagreen',ecolor='black', fmt='^',zorder=-500,markersize=10)
+tx, ty = 11.8, 7.3
+plt.text(tx, ty, " non-local\n sample\n uncertainty\n level:",  fontsize=20)
+plt.errorbar(tx+0.4,ty-0.4, xerr=0.2, yerr=0.4, color='darkseagreen',ecolor='black', fmt='^',zorder=-500,markersize=0.1)
 #%%
 #==============================================================================
 # My new inference
@@ -293,26 +293,32 @@ Mstar_err = np.array([[-0.15,  0.19], [-0.15,  0.19], [-0.14,  0.16], [-0.14,  0
                       [-0.12,  0.12], [-0.24,  0.48], [-0.17,  0.23], [-0.12,  0.12], 
                       [-0.14,  0.16], [-0.19,  0.28], [-0.25,  0.53], [-0.14,  0.16], 
                       [-0.18,  0.25], [-0.18,  0.24], [-0.15,  0.18], [-0.15,  0.18]])
-plt.scatter(Mstar,MBs,c='lawngreen',s=320,marker="*",zorder=100, edgecolors='k')
-#plt.errorbar(Mstar,MBs, xerr=[np.abs(Mstar_err)[:,0], np.abs(Mstar_err)[:,1]], yerr=0.4, color='blue',ecolor='orange', fmt='.',zorder=-500,markersize=1)
+plt.scatter(Mstar,MBs,c='lightsalmon',s=420,marker=".",zorder=100, edgecolors='k', alpha = 0.8)
+# plt.errorbar(Mstar,MBs, xerr=[np.abs(Mstar_err)[:,0], np.abs(Mstar_err)[:,1]], yerr=0.4, color='blue',ecolor='orange', fmt='.',zorder=-500,markersize=1, alpha = 0.4)
 
 #%%
[…]

### 2020-05-01 relation_plots/MM_vz_32QSO.py

@@ -316,17 +316,16 @@ yerr_highz = [((m_ml*Mstar_err[:,0])**2+0.4**2)**0.5, ((m_ml*Mstar_err[:,1])**2+
 # if style ==1:
 plt.errorbar(np.log10(1+ss[:,0]),ss[:,2]-(m_ml*ss[:,1]+b_ml),yerr=(0.4**2+(m_ml*0.2)**2)**0.5,fmt='^',color='darkseagreen',markersize=9)
 plt.errorbar(np.log10(1+b11[:,0]),b11[:,2]-(m_ml*b11[:,1]+b_ml),yerr=(0.4**2+(m_ml*0.2)**2)**0.5,fmt='^',color='darkseagreen',markersize=9)  
-
 plt.errorbar(np.log10(1+cis11[:,0]),cis11[:,1]-(m_ml*cis11[:,2]+b_ml),yerr=(0.4**2+(m_ml*0.35)**2)**0.5,fmt='^',color='darkseagreen',markersize=9) 
 
 #    plt.errorbar(np.log10(1+Knud[:,0]),Knud[:,2]-(m_ml*Knud[:,4]+b_ml),yerr=0,fmt='o',color='blue',markersize=9) 
 
 
-plt.scatter(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),c='lawngreen',
-            s=280,marker="*",zorder=300, vmin=0.3, vmax=5, edgecolors='k')
+plt.scatter(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),c='lightsalmon',
+            s=420,marker=".",zorder=300, vmin=0.3, vmax=5, edgecolors='k', alpha = 0.8)
 plt.errorbar(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),
              yerr= yerr_highz,
-             color='lawngreen',ecolor='olivedrab', fmt='.',markersize=1)    
+             color='lightsalmon', fmt='.',markersize=1)    
 
 #plt.scatter(np.log10(1+zs[9]),0,facecolors='none',
 #            s=280,marker="o",zorder=900, edgecolors='blue', linewidth=6, alpha=0.5)    
@@ -415,7 +414,7 @@ value,sig=round(b_ml_offset,2),round((np.percentile(samples,84,axis=0)[0]-np.per
 
 #%%
[…]

### 2020-05-15 manuscript/manuscript.tex
Before pass the ball to Tommaso

@@
 % Keep the title short and informative.
-\title[Mass relations by lensed AGN hosts]{Testing the evolution of the correlations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGNs.}
+\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed AGNs}
 
@@
 Simon Birrer$^{2}$,
-Dominique Sluse$^{3}$,\newauthor
-Chris Fassnacht$^{4}$,
-Matthew W. Auger$^{5}$,
-Kenneth C. Wong$^{6}$,
-Sherry H. Suyu$^{7,8,9}$,\newauthor
-Takahiro Morshita$^{10}$,
+Adriano Agnello$^{3}$,\newauthor
+Dominique Sluse$^{4}$,
+Chris Fassnacht$^{5}$,
+Matthew W. Auger$^{6}$,
+Kenneth C. Wong$^{7}$, \newauthor
+Sherry H. Suyu$^{8,9,10}$,
+Takahiro Morshita$^{11}$,
 and et al.
+\\
 \\
@@
 $^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
-$^{3}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
-$^{4}$Department of Physics, University of California, Davis, CA 95616, USA\\
-$^{5}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
-$^{6}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{7}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
-$^{8}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
-$^{9}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
-$^{10}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
+$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
+$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
+$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
+$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
+$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
+$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
+$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
+$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
 $^{11}$TBC
@@
 \begin{abstract}
-Strong lensed active galactic nuclei (AGN) has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies.
-In this work, we have adopted eight strongly lensed system from our collaboration.
-The deep {\it Hubble Space Telescope}(\hst) data and adopt the \lenstronomy\ to reconstruct the image of the source.
-Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on the assumed stellar population.
-The \mbh\ are estimated using the board emission line.
-We compare our inference to the ones in the literature and find a consistent result.
-The consistent scaling resolutions derived from our sample confirm the evolution conclusion and confirm the the power of using strong lensed AGNs.
-The number of the detection of the lensed AGNs are supposed to increase rapidly leave this topic with a bright future...
+  One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution.
+The magnification of strongly lensed quasars provide a way to effectively increase instrumental resolution and thus overcome this challenge.
+In this work, we study eight strong lens systems with deep {\it Hubble Space Telescope}(\hst) imaging, using the state-of-the-art \lenstronomy\ code to reconstruct the image of the source.
+Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models.
+  \mbh\ are estimated from broad emission line using standard methods.
+Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolve over cosmic time.
+At the moment, the \pink{sample size of lensed AGN is small and thus} provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN.
+However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and may become a key diagnostic of black hole and galaxy co-evolution.
 \end{abstract}
@@
 Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging.
-Combining the new sample with published samples in both local and intermediate redshift range, they strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy.
-With the goal of testing theoretial ideas, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
+Combining the new sample with published samples in both local and intermediate redshift range, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy.
+In a follow-up paper, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
 The observed tightness of the  scaling relations at high-$z$ is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature.
-%, a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
+% , a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
 
-Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs have been used as unique tool to make progress in study the scaling relations at the distance universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
-Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration.
-This work confirms that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
-With a following up effort, \citet{Ding2017b} applied the advanced techniques to two strongly lensed systems analyzed by the H0LiCOW collaboration~\citep{Suyu2013, Wong2017} to study their \mbh-\lhost\ relations and obtained consistent scaling relations compared with the samples from the literature.
+As the samples of AGN grow to increase statistical power, it is very important to make sure that systematics do not dominate the error budget.
+One of the main potential source of systematics is the finite resolution of \hst\ images.
+Even with state of the art techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution.
+This is the goal of this work.
 
-In this work, we intend to make progress by deriving the measurements of the \mbh-\mstar\ relation using the entire eight systems as introduced in \citet{Ding2017a}.
-We develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs.
+It has been long recognized that lensed AGNs, by virtue of magnification, can provide unique insights inro the scaling relations the distant universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
+Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration.
+They confirm that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
+Then, \citet{Ding2017b} applied the advanced techniques to two strongly lensed systems analyzed by the H0LiCOW collaboration~\citep{Suyu2013, Wong2017} to study their \mbh-\lhost\ relations and obtained consistent scaling relations compared with the samples from the literature.
+
+In this work, we expand the measurements of the \mbh-\mstar\ relation using the full sample of eight lensed AGN introduced by \citet{Ding2017a}.
+In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs.
 We adopt a set of extended modelling choices to assure the accuracy of our measurements.
@@
 To assess an accurate inference of stellar mass, we utilize the imaging data taken with the \hst\ multi-band filter to obtain the color information for 3/8 of our targets.
-Besides, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample.
-The extended range of the eight systems would help us to make a direct comparison to the latest measurements by D20.
+Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20.
+Given the similar redshift range, the high data quality, and consistent state of the art techniques, this sample of lensed AGN provides an excellent verfication of the D20 results.
 
 This paper is structured as follows.
-In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data condition and the BH masses.
-In Section~\ref{sec:lens_model}, we describe our approach that designed to infer the lens models and reconstruct the host galaxy.
-We use the inferred photometry to derive the stellar mass and the scaling relations and combine with contrast sample to study the evolution in Section~\ref{sec:result}.
-The discussion and conclusions are drawed in Section~\ref{sec:diss} and~\ref{sec:con}.
+In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses.
+In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy.
+We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}.
+Discussion and conclusions are drawn in Section~\ref{sec:diss} and~\ref{sec:con}.
 Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
 Magnitudes are presented in the AB system.
-A Chabrier initial mass function (IMF) is employed for the entire sample consistently.
+A Chabrier initial mass function (IMF) is employed for the sample, consistently with D20.
 
@@
 Besides the image data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems.
-As will show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to estimate their accurate \mstar.
+As we show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to improve the accuracy of the estimate of \mstar.
 
-While we note that the sample size by this work (i.e., eight systems) is limited.
-Rather than using our measurement to constrain the evolution of the scaling relation, we plan to use our data and make a direct comparison to the recent efforts in D20, which includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}.
+The sample of lensed AGN is too limited in size to constrain evolution by itself.
+Therefore, we use it primarily to verify the results of D20.
+The D20 sample includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}.
 It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.
@@
       \small
-      \item Note: $-$ The observational information is also presented in~\citet{Ding2017a}. 
-      \item $^a$: For HS2209, it is visited by \hst\ twice ({\it vis05} and {\it vis06}). The exposure time is thus given separately.
+      \item Note: $-$ The observational information is also given by~\citet{Ding2017a}. 
+      \item $^a$: HS2209, was visited by \hst\ twice ({\it vis05} and {\it vis06}) at different orientations. The exposure time is thus given separately.
 \end{tablenotes}  
@@
 
-To assure the consistency of the \mbh\ between the usage of different board lines, we adopt a class of self-consistent recipes to estimate the \mbh.
-For the entire AGN systems, we follow D20 and adopt the following virial formalism:
+To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt a the following set of self-consistent recipes following D20:
 \begin{eqnarray}
@@
 %
-The board line information of our samples are adopted from the literature \citep{Sluse2012, Peng2006, Shen2011}.
+The broad line properties of our samples are \pink{mostly} adopted from the literature. % \citep{Sluse2012, Peng2006, Shen2011}.
+\pink{For SDSS1206, the line properties have been inferred by~\citet{Shen2011}.
+However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered.
+We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work.
+For the rest of the lens sample except HS2209, their broad line properties are adopted from the literatures~\citep{Sluse2012, Peng2006} with lensing magnification effect considered.
+For HS2209, the spectrum data was observed from ESI in September 2015.
+We derived the line properties using the same approach as~\citep{Sluse2012}.
+\todo{Dominique and Chris can give more details here.} }.
 The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}.
-The uncertainty of the \mbh\ are expected as $0.4$~dex.
+The uncertainty of the \mbh\ are estimated to be $0.4$~dex.
 
@@
 %\begin{threeparttable}
-\caption{Summary of \mbh\ estimates.}\label{mbh}
+\caption{Summary of \mbh\ estimates, \pink{based on equation~\eqref{recipe}.}}\label{mbh}
 \resizebox{8.5cm}{!}{
-     \begin{tabular}{ccccc}
+     \begin{tabular}{cccccc}
         \hline
-Object ID & Line(s) used & FWHM & log($L_\lambda$) & $\log$\mbh \\
+Object ID & Line(s) & FWHM & log($L_\lambda$) & $\log$\mbh & ref.  \\
 & & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
-HE0435 & \Mgii & 4930 & 45.14 & 8.54 \\
-RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 \\
-WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
-SDSS1206 & \Mgii & 5632 & 45.61$^a$ & 8.88 \\
-HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
-SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
-HS2209 & \Mgii & 3245 & 45.71 & 8.75 \\
-HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
+HE0435 & \Mgii & 4930 & 45.14 & 8.54 & (1) \\
+RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 & (1)\\
+WFI2033 & \Mgii & 3960 & 45.19 & 8.38 & (1) \\
+SDSS1206 & \Mgii & 5632 & 45.01 & 8.77 & (2) \\
+HE1104 & \Civ & 6004 & 46.18 & 9.03 & (3) \\
+SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
+HS2209 & \Mgii & 3245 & 45.71 & 8.75 & \pink{here}  \\
+HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
         \hline
@@
 \small
-\item Note: $-$ The reference for the board line information. For HS2209, its board line is estimated in this work using the same approach as~\citet{Sluse2012}.\\
-$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect.
+\item Note: $-$ The broad line properties.\\ %For HS2209, the properties are derived in this work using the same approach as~\citet{Sluse2012}.
+\pink{Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.}\\
+%$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect {\bf [TT: how about the others?].}
 \end{tablenotes}  
@@
 \section{surface photometry inference}\label{sec:lens_model}
-We perform the study of the lens modelling to reconstruct the photometry of the lensed host galaxies in this section.
-Our lens systems are a part of the H0LiCOW project, and the lens models of 4/8 systems, including HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been derived.
-Aiming at the strong lensing time-delay cosmography~\citep{Treu2016}, these works mainly focused on deriving the precise and accurate lens models, while the reconstruction of the reconstructed host galaxies from these works can be considered as a by-product.
-In this work, we apply the state-of-the-art lens modelling technique and perform an independent effort focusing on recovering the photometry of the host galaxy.
-As will show, our approach would allow us to obtain a one-step host magnitude as defined by \sersic\ surface brightness profile; thus the measurements of the host galaxy properties would be more consistent to the ones in the literature.
-For the 4/8 systems which has been studied in H0LiCOW project, we will make comparison to understand the accuracy of our analysis.
+%
+In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account.
+Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project.
+The goal of those models was strong lens time-delay cosmography~\citep{Treu2016}, and the reconstruction of the host galaxy light (pixelized or via shapelets) was a byproduct.
+\citet{Ding2017b} used those reconstructions for two of the systems, including HE0435 and RXJ1131, and then fitted a simply parametrized surface brightness profile to the reconstruction to mimic what is done in non-lensed AGN.
+
+In this work, in order to reproduce more closely and uniformly what is
+done in non-lensed AGN we develope a strategy to obtain a one step
+measurement of the host galaxy light described by a \sersic surface
+brightness profile. For the 4/8 systems already studied by the H0LiCOW
+project, we will make a comparison to characterize systematic
+uncertainties related to modelling techniques.
 
 \subsection{Data Preparation and Modelling Setup}
+
 We following the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information.
 The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}.
-We then adopt the {\sc photutils} by Python to model the global background light in 2-D based on SExtractor algorithm.
+We then adopt the {\sc Photutils} by Python to model the global background light in 2-D based on SExtractor algorithm.
 We remove the background light and cut the clear image data into postage stamp at a suitable size.
@@
 
-We carry out the forward modelling process to constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy, simultaneously.
-For any extended objects including the lensing galaxy and source galaxy, we assume their photometry can be described by the 2-D elliptical \sersic\ profile.
+We carry out a forward modelling process to simultaneously constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy.
+For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile.
 We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiply component.
-For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in~\citet{Ding2017a} that setting \sersic\ $n$ as this prior value would result in a consistent host magnitude inference compared to a prior with fixing $n$ to the truth.}.
-The bright nuclei is unsolved and modelled by a scaled point spread function (PSF).
-We also jointly fit the AGN position to the center of its host galaxy.
-We adopt the elliptical Power-law model to define the surface mass density of the deflector; an external shear component is also added.
+For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been studied in~\citet{Ding2017a} that choosing the prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}.
+The bright nucleus is unresolved and modelled by a scaled point spread function (PSF) in the image plane.
+We also impose that the AGN and its host galaxy have the same center.
+Following standard practice that has show to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical Power-law density profiles to define the surface mass density of the deflector, with an external shear.
 
-We employ the imaging modelling tool \lenstronomy~\citep{lenstronomy} to perform the fitting task.
+We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task.
 Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting for each system.
-The distribution of the fitting inference by the overall choices are supposed to sufficiently cover the truth.
-We then apply a statistical measurement and perform weighting algorithm to derive the final inference and estimate the uncertainty level.
-The different modelling choices are selected based on the following options:
+We then apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty level, including the contribution of modelling choices.
+The modelling choices that we consider include the follows.
 \begin{enumerate}
-\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF.
-Each selected star is considered as an initial PSF to input to the fitting.
-\item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF.
+\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
+\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF.
 To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
-\item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
-\item Using the lensing imaging alone is difficult to constrain the power-law slope. To mitigate the overfitting of the slope value, we fix it with three optional values $[1.9, 2.0, 2.1]$.
+\item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
+\item Using the lensing imaging alone is difficult to constrain the power-law slope.
+To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
 \end{enumerate}
 
-In general, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting.
-After all sets of fittings completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value.
-Since there is no evidence of an better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from both of them and then combining their best-fit results based on the weighting algorithm introduced by D20.
+In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2 \times2 \times3$) fits.
+After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value.
+Since there is no evidence of an better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20.
 The weights are defined by:
@@
 \end{eqnarray} 
-where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter literally means that it has to be larger than~$1$.
-If $\alpha<1$, introducing the $\alpha$ would have a side-effect because the relative likelihood between different the selected choices would be too close.} so that when $i=4$:
+where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter it is assumed that it is larger than ~$1$, so as to err on the side of caution and include more choices that would be allowed strictly by statistical noise considerations.} so that when $i=4$:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-
 Then, the results by {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
@@
 
-Our approach uses the relative goodness of fit and ensures that at least 8 sets of best-fits are used to capture the range of systematic uncertainties.
+Our approach uses the relative goodness of fit and ensures that at least 8 sets of best-fits are used to estimate the range of systematic uncertainties.
 
@@
 \subsubsection{HE0435}
-The modelling of HE0435 is performed based on the approach described in the previous section.
-We select 5 isolated stars in this field as initial PSFs to input to the fitting, with in total of 60 times fittings.
+We follow the approach described in the previous section.
+We select 5 isolated stars in this field as initial PSFs to input to the fitting, for a total of 60 fits.
 Based on the top-eight choices, we perform the weighting algorithm and measure the host flux, host-to-total flux ratio, effective radius and \sersic\ index.
@@
 The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a).
-Not surprisingly, we note that the residual level reveals in the normalized plot are appears to be larger than the ones as presented by~\citet{Wong2017}.
-This is majorly due to the fact that the surface brightness of the host galaxy by our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet functions as adopted by \lenstronomy~\citep{Refregier2003, Birrer2015}.
+Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}.
+This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Refregier2003, Birrer2015}.
 The smooth feature of \sersic\ profile could not capture the clumps in the host galaxy such as the star-forming regions.
-Nevertheless, our approach is more effective to derive a one-step inference of the global host light in terms of the \sersic\ flux, which is more consistent to measurements in the comparison sample.
+Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e.
+the quantity commonly measured in the the literature for non-lensed samples.
 
-For cross-check propose, we compare our host magnitude to the inference in~\citet{Ding2017b}, in which they inferred the \sersic\ magnitude of the pixelized host galaxy as reconstructed by~\citet{Wong2017}.
-The host magnitude measured in ~\citet{Ding2017b} is: $mag = 21.75 \pm 0.13$.
+As a cross-check, we compare our host magnitude to the inference by~\citet{Ding2017b}.
+They inferred the \sersic\ magnitude by fitting to the pixelized host galaxy as reconstructed by~\citet{Wong2017}.
+The host magnitude measured by~\citet{Ding2017b} is: $mag = 21.75 \pm 0.13$.
 %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
-Compared to our inference, i.e. $mag = 21.50 \pm 0.35$, the offset is well within $1-\sigma$ level.
+The results are in excellent agreement with the measurement reported here, i.e. $mag = 21.50 \pm 0.35$.
 
 \subsubsection{RXJ1131}
-The lens model of RXJ1131 observed with ACS/F814W has been well studied in~\citet{Suyu2013}.
-The host galaxy of this system is lensed to a spacious arc with a boundary line between the dominated area of bulge and disk could be clearly seen.
-Thus, we set the host galaxy is composed of two \sersic\ with index value $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge.
-In addition, same as~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and fitting as the SIS and \sersic\ for its mass and light, respectively.
+A lens model of RXJ1131 based on ACS/F814W data has been presented by~\citet{Suyu2013}.
+The host galaxy of this system is lensed to an extended arc.
+A clear bulge and disk component can be identified.
+Thus, we describe the host galaxy with two \sersic\ with index value $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge.
+In addition, following~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and describe it as a SIS and \sersic\ for its mass and light, respectively.
 
 The photometry of the RXJ1131 host galaxy is fitted with a sets of 4 initial PSFs.
-The results is summarized in Table~\ref{tab:host_measure}, with the best-fit result shown in Figure~\ref{fig:image_inference}-(b).
+The results are summarized in Table~\ref{tab:host_measure}, with the best-fit result shown in Figure~\ref{fig:image_inference}-(b).
 
-We also compare our measurement to the previous reconstructions in \citet{Ding2017b}.
+We also compare our measurement to the previous reconstructions by \citet{Ding2017b}.
 Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$.
-Compared to our inference in Table~\ref{tab:host_measure}, our inferred bulge magnitude ($21.80\pm0.21$) are very consistent.
-However, our inferred disk magnitude ($19.33\pm0.16$) is much brighter.
-This is likely because the reconstruction of our host galaxy have more extended regions to collect the disk light till larger radius compared with~\citet{Suyu2013} who perform the lens modelling using a smaller lens mask based on {\sc Glee} (see Figure~4 therein).
+The results are in excellent agreement with our inferred bulge magnitude ($21.80\pm0.21$)   shown in Table~\ref{tab:host_measure}.
+However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}.
+This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
+The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
+While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time delay cosmography.
 
 \subsubsection{WFI2033}
-WFI2033 is the last quadruply lensed system in our sample whose lens model has been recently investigated by~\citet{Rusu2019}.
+WFI2033 is the last quadruply lensed system in our sample whose lens model has been previously investigated \citep{Rusu2019}.
 There is a satellite galaxy in the north.
-However, as noted in~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using \sersic\ model.
-We select in total of 8 initial PSF-stars to modelling this system.
+However, as noted by~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using a \sersic\ model.
+We select a total of 8 initial PSF-stars to model this system.
 
-The final inference are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c).
-We compare our inference to the previous reconstructed host galaxies.
+The final inference results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c).
+We compare our inference to the previously reconstructed host galaxies.
 Modelling the reconstructed host by~\citet{Rusu2019}, (i.e., the Figure~4 bottom-right plane therein) as a \sersic\ profile, we infer the $mag = 21.98 \pm 0.15$, which is very consistent to our inference (i.e., $mag = 21.78 \pm 0.25$).
@@
 \subsubsection{SDSS1206}
-SDSS1206 is an unique system -- the AGN is a doubly images by the deflector while most of the host is falls inside the inner caustic thus being quadruply imaged.
-Same as~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbations.
-Moreover, as noted in~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible (see Figure~1 in \citet{Birrer2019}).
+SDSS1206 is an unique system -- the AGN is a doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged.
+Following~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbation.
+Moreover, as noted by~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible \citep[see Figure~1 in][]{Birrer2019}.
 We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids.
+It is worth noting that we are using the same imaging modelling tool as~\citet{Birrer2019}.
 
-Due to limit of stars in the filed of view, there are only 2 stars available as initial PSF.
+Due to the limited number of stars in the field of view, there are only 2 stars available as initial PSF.
 To expand the volume of modelling options, we also take the stack of the two bright stars as derived by~\citet{Birrer2019}, as a third initial PSF.
-It is worth noting that we adopt the same imaging modelling tool with~\citet{Birrer2019} using a similar manner.
-We find a visible residuals at the fitted lensed arcs region using a single \sersic\ model as host, however, a double \sersic\ model couldn't significantly improve the goodness of the fitting.
+We find a visible residuals at the fitted lensed arcs region using a single \sersic\ model as host.
+However, a double \sersic\ model does not significantly improve the goodness of fit.
 Thus, we adopt the single \sersic\ model in our final inference.
@@
 \subsubsection{HE1104}
-As a typical doubly lensed image, HE1104 is modelled by us for the first time.
-We have selected in total of 5 initial PSFs to perform the fitting.
+HE1104 is a typical doubly imaged quasar and has no recent models.
+We have selected in total of 5 initial PSFs to perform the fit.
 There is an object at the northeast.
-However, without knowing the redshift of this object and considering it is further away from the lens, we use mask to block its pixels in the fitting.
+However, since we do not know its redshift and considering it is further away from the lens we do not model it explicitly but just mask it out in the fitting.
 
-The inference of the image is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
-With the best-fitting model, the lensed arcs could be clearly seen from the bottom-left panel, indicating a strong evidence of the detection of the host galaxy.
+The inference is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
+the lensed arcs can be clearly seen from the bottom-left panel, indicating that the host galaxy is well detected.
 
 \subsubsection{SDSS0246}
-Imaged with WFC3-UVIS/F814W, the resolution of this systems (together with the remaining two systems) are much higher with drizzled pixel scale as $0\farcs{}03$.
-However, their arcs are much fainter compared with the IR band.
-As a result, the available pixels that could be used to fitting the arc are actually much limited.
-Nevertheless, with in total 3 initial PSF selected, the host inference is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
+Imaged with WFC3-UVIS/F814W, the resolution of this systems (together with the remaining two systems) are much higher than for those imaged in the IR, with drizzled pixel scale as $0\farcs{}03$.
+However, the arcs are much fainter compared with those of other systems imaged in the IR band.
+As a result, fewer pixels with signal are available for the fit than for other systems.
+Nevertheless, the host inference is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure} (3 initial PSF guesses were adopted).
 
 \subsubsection{HS2209}
-HS2209 have be imaged by \hst\ through two visits ($vis05$ and $vis06$).
-We modelled both two visited data separately and find that the identical host magnitude could be obtained.
-Moreover, we note that the data by the {\it vis06} can be modelled with the better goodness level; thus the result by {\it vis06} was finally adopted (using 7 initial PSF stars), as listed in Table~\ref{tab:host_measure}.
-The inference of this system is summarized in Figure~\ref{fig:image_inference}-(g).
+HS2209 was imaged by \hst\ during two visits ($vis05$ and $vis06$) at different orientations.
+We modelled the two visits separately and recovered mutually consistent host galaxy magnitudes.
+However, we found that the data from {\it vis06} can be modelled with smaller residualsl; thus the inference based on {\it vis06} was adopted as our best estimate (using 7 initial PSF stars), as listed in Table~\ref{tab:host_measure}.
+The inference for this system is summarized in Figure~\ref{fig:image_inference}-(g).
 
@@
 The results, based on 3 initial PSFs, are summarized in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
-The subtracted lensed host in the residual map its only half-seen among the noises.
-Thus, the host magnitude of the HE0047 should be taken with larger error budget.
+The host magnitude of the HE0047 system has a relatively large uncertainty as reflected in the error bars.
 
@@
       \item Note: $-$ Inference of the host galaxy properties.
-Column (2)-(6): photometry inference derived using the imaging data in listed Table~\ref{data_set}.
-Column (7): age of adopted stellar population with stellar metallicity.
+Column (2)-(6): photometry iderived using the imaging data in listed Table~\ref{data_set}.
+Column (7): age of adopted stellar population with solar metallicity.
 Column (8): inferred stellar mass.
@@
 \section{Results}\label{sec:result}
-In this section, we describe the approaches and assumptions as used to estimate the stellar populations to our sample.
-Then, we adopt the population templates to derive their stellar mass of our sample.
-We study the \mbh-\mstar\ relations and compare our measurements with the ones in the literature to study the evolution.
+In this section, we describe the approaches and assumptions used to estimate the stellar populations to our sample.
+Then, we adopt stellar population templates to derive their stellar mass of our sample.
+We study the \mbh-\mstar\ relations and compare our measurements with ones taken from the literature.
 
@@
 %[] Color inference for the first three cases to decide their stellar template. 
-Besides the imaging data we analyzed in last section, some of the systems also imaged by the \hst\ through other bands, which could provide the color information.
-Given that the data observed by other band has less exposure time with lower signal-to-noise (SNR) level, we highlight that we only study the color of the lensed host to determine a decent stellar populations for these systems.
-Then, these population templates would be applied with the inferred host magnitude (i.e., Table~\ref{tab:host_measure} column (2)) to derive the final stellar mass.
+Besides the imaging data analyzed in the last section, some of the systems have also imaged by \hst\ through other bands, providing color information.
+Given that we have used the highest signal to noise data for our primary models,  the analysis of the other bands has lower fidelity and we use it only to infer the colors so as to assist in the estimation of the stellar mass (i.e., Table~\ref{tab:host_measure} column (2)).
 
-{\bf HE0435} ~ Besides the imaging data by F160W, this system has been observed by the \hst\ through F814W and F555W filters.
-We adopted the same approach to modelling the data separately at these two band.
-Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy.
+{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W \pink{The multi-band imaging data provides us the opportunity to estimate the host color and derive an accurate stellar population.
+We adopted the lensing modelling approach as introduced in Section~\ref{sec:photometry} to infer the host photometry at F814W and F555W two bands.
+Based on the three band host magnitudes, we find a 1.5~Gyr age and solar metallicity stellar population could well match the color.
+More detailed information is presented in Appendix~\ref{app:HE0435}.}
+%Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy.
 Thus, we infer the color of the lensed arcs in the image plane.
 Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color.
-More detailed information is presented in Appendix~\ref{app:HE0435}.
+More detailed information is presented in Appendix~\ref{app:HE0435}.}
 
-{\bf RXJ1131} ~ The host galaxy of RXJ1131 is lensed to a very extended arc in the image plane, which is resolved to the AGNs.
-The SED fitting of the arc in the image plane can be directly performed using the imaging data.
-Using the \hst\ imaging data through three filter F814W and F555W and F160W, we adopt the SED fitting result by~\citet{Ding2017b} with the stellar populations of 3 Gyr and 1.5 Gyr (solar metallicity) for its bulge and disk, respectively.
+{\bf RXJ1131} ~ The host galaxy of RXJ1131 is lensed to a very extended arc in the image plane.
+The spectral energy distribution of the arc can be directly inferred in the image plane, since lens is achromatic.
+Based on the \hst\ imaging data through the three filters F814W and F555W and F160W, we adopt the SED estimated by~\citet{Ding2017b} with stellar populations of 3 Gyr and 1.5 Gyr (solar metallicity) for its bulge and disk, respectively.
 
-{\bf WFI2033} ~ Besides the F160W filter, four filters including F125W, F140W, F555W, F814W are also available in the \hst\ archive, which has been employed to obtain the color of the host galaxy.
-Same as the analysis of HE0435, we derive their host magnitudes and infer the host color in the image plane.
-We find a stellar population with 0.625 Gyr could well match its color (Appendix~\ref{app:WFI2033}).
+{\bf WFI2033} ~ In addition to the F160W filter, images through the four filters F125W, F140W, F555W, F814W are also available in the \hst\ archive.
+As for HE0435, we infer the host color in the image plane.
+We find a stellar population with 0.625 Gyr is a good matchi to the colors (more details see Appendix~\ref{app:WFI2033}).
 
-{\bf HE1104 and the other systems} ~ The imaging data of HE1104 has also been observed by \hst\ through F555W and F814W band.
-However, given limited exposure time in these two bands, the lensed arcs is too faint to be detected; thus, we couldn't infer the color of the host for HE1104.
-For the other systems, they do not have the multi-band observation by \hst.
-For these cases, we adopt the criteria by D20 to assign their stellar populations, i.e., the 1 Gyr and 0.625 Gyr stellar population would be adopted for systems as $z<1.44$ and $z>1.44$, respectively.
+{\bf HE1104 and the other systems} ~ HE1104 has also been observed by \hst\ through the F555W and F814W bands.
+However, given the limited exposure time in these two bands, the lensed arcs is too faint to be detected; thus, we are not able to infer the color of the host for HE1104.
+No multi-band information is available for the other systems.
+Thus, for these cases, we follow D20 and assume a typical stellar population age, i.e.
+1 Gyr and 0.625 Gyr for systems as $z<1.44$ and $z>1.44$, respectively.
+Of course this choice is not unique.
+However, we stress that as we are mostly interested in the comparison with D20 this strategy is meant to minimize differences between the two approaches.
 
-A summary of the adopted stellar populations is given in Table~\ref{tab:host_measure}, column~(7).
+A summary of the adopted stellar population ages is given in Table~\ref{tab:host_measure}, column~(7).
 Applying these templates to the filter magnitudes obtained in last section, we derive the stellar mass of our system, Table~\ref{tab:host_measure}, column~(8).
-Considering the simulating tests by~\citet{Ding2017a} and the fact that we are able to obtain the very consistent host magnitude for the HE0435, RXJ1131 and WFI2033 using the independent approaches, the fidelity of the inferred magnitude are expected to be high.
-The uncertainty of the \mstar\ estimation are considered as a typical level of $0.2$~dex.
+Considering the simulations by~\citet{Ding2017a} and the fact that we are able to obtain very consistent host magnitudes for the HE0435, RXJ1131 and WFI2033 using the independent approaches, the fidelity of the inferred magnitude is expected to be well characterized by the quoted uncertainties.
+We adopt a typical uncertainty of 0.2 dex for the \mstar\ estimates.
 
 \subsection{The \mbh-\mstar\ relation}\label{sec:relation}
-We plot the scaling relation of the \mbh-\mstar\ of our sample, together with the comparison sample as introduced in Section~\ref{sec:sample_select}, in Figures~\ref{fig:scaling_relation}-(a).
-For the entire sample, we expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget.
-Following D20, we fit the local \mbh-\mstar\ sample as the baseline with a linear relation as:
+In Figures~\ref{fig:scaling_relation}-(a) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.
+We expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget for the entire sample.
+Following D20, we adopt as baseline a local \mbh-\mstar\ of the form:
 \begin{eqnarray}
 \label{eq:MMlocal}
-\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}).
+\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}),
   \end {eqnarray}
-Comparing with the local sample, we find that our lensed systems appeared to have a slimier offset to the local relations which is consistent to the 32 AGNs by D20 with similar redshift range, indicating a trend of evolution.
-To study the evolution based on the sample redshift, we parameterize the evolution term as the linear relation by:
+\pink{with calibrated value as  $\alpha = 0.27$, $\beta = 0.98$ based on the 55 local sample.} We find that our lensed systems are above the local relation, consistent with the inference from the 32  non-lensed AGNs published by D20 in a  similar redshift range.
+To quantify the evolution as a function of redshift, we parameterize it as:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-where the $\Delta \log \mathcal M_{\rm BH}$ is the offset of the \mbh\ to the local baseline.
-To make a direct comparison, we first recover the offset plot of Figure~8 in D20.
-Then we add the data points using our new measurement and show in Figure~\ref{fig:scaling_relation}-(b).
-We find that the evolution of the offset our sample are well matched to the evolution trend as demonstrated the contrast sample.
-%Given that we only obtain the measurements from eight lens systems, it is insufficient to fit the offset value quantitively.
-Nevertheless,
-The apparent consistency in the samples verify the fidelity of our measurement. This result is also support the evolution conclusions drawn by D20.
+where the $\Delta \log \mathcal M_{\rm BH}$ is the offset of \mbh\ with respect to the local baseline at fixed \mstar.
+To make a direct comparison, we reproduce the plot shown in Figure~8 of D20.
+Then, we add our new lensed AGN measurement and show the result in Figure~\ref{fig:scaling_relation}-(b).
+We find that the offset from the local relationship is indistinguishable for the two samples.
+\pink{Based on Equation~\eqref{eq:offset}, we estimate the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which overlaps with D20's inference ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.} This consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20\pink{that the observed value of \mbh\ at a fixed \mstar\ tend to be larger at higher redshift than the ones in the local universe.}
+
+\pink{The lensed AGN systems in this work are directly taken from the H0LiCOW collaboration.
+We note that selection function of our sample is irrelevant to D20's sample.
+Given that the eight lensed AGN sample is relatively a small size, in this work we only take them for consistency check with the previous studies.
+The selection effect of the lensed sample will be investigated when the volume of the lens systems is large enough with statistical significance.}
 
@@
 \caption{\label{fig:scaling_relation} 
-(left): BH masses vs. stellar mass relations (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval based on the Equation~\ref{eq:MMlocal}.
+(left): BH masses vs. stellar mass correlation (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval based on Equation~\ref{eq:MMlocal}.
 (right): offset of $\log(\mathcal M_{\rm BH})$ (vs.
-\mstar) as a function of redshift based on the D20 data using Equation~\ref{eq:offset}.
-We then plot our new measurement on top of the figure to make direct comparison.
+\mstar) as a function of redshift.
+\pink{We plot our new measurements on top of the figure to make direct comparison.
+The red line and shaded region are the best-fit and $1-\sigma$ offset fitting by Equation~\eqref{eq:offset} using the 32 high-z AGNs in D20, while the blue line and region are the fitting based on the eight lensed systems.} \blue{Xuheng: Let me know if it's better to remove the blue line and region.}
 }
@@
 \section{Systematic Errors}\label{sec:diss}
-We selected to use a set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices.
-In particular, we treat the two different modelling approaches, i.e., central mask and PSF iteration equally, to derive the averaged results.
-Of course, with different weighting manner, the combined result would be different.
-However, as we inspected the results on each choices for each systems, the dispersion of the results by the top ranked choices is usually small and the effect by using different weighting choice is trivial ($<0.1$~dex).
-In addition, we adopt simple stellar population to derive their stellar mass.
-5/8 systems in our sample do not have the color information, and a criteria was adopted to define their stellar population based on their redshift, which would could also introduce the uncertainty in the inferred \mstar.
 
-In any case, we point out that it is the uncertainty of the single-epoch black hole mass estimates (i.e., 0.4~dex) that dominate the error budget in the scaling relations.
+We considered set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices.
+In particular, we treat the two different modelling approaches, i.e., {\it noise boost} and {\it PSF iteration} equally, to derive the averaged results.
+Of course, the results are somewhat dependent on the weighting scheme.
+However, the dependency is smaller than other sources of uncertainty.
+For example, the dispersion of the results by the top ranked choices and thus using different weighting schemes would only change the results marginally ($<0.1$~dex).
+
+In addition, we adopt simple stellar populations to derive the stellar mass.
+For 5/8 systems in our sample we did not have color information, and we used instead a fixed age depending on redshift.
+The lack of color information by necessity increases the in the inferred \mstar.
+However, once again the uncertainty is smaller than the estimated uncertainty in the  black hole mass (0.4 dex), which dominates the overall error budget.
 
 \section{Conclusion}\label{sec:con}
-Using eight strongly lensed AGN systems from the H0LiCOW collaboration, we presented the new measurements of the correlations of the supermassive black hole masses and the stellar masses of their host galaxy.
-We adopt the modern lens modelling techniques to estimate the magnitude host galaxy, defined by the \sersic\ profile.
-We estimated the \mbh\ of our sample using a set of self-consistent single-epoch estimators to assure the consistency of the correlation.
+Using eight strongly lensed AGN systems, we presented a new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy.
+We adopt state-of-the-art lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile.
+We estimated the \mbh\ of our sample using a set of calibrated single-epoch estimators to assure self-consistency and consistency with the comparison samples taken from the literature.
 
-We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the similar approaches to derive the \mstar\ and calibrated the \mbh\ using the consistent recipes.
-The \mbh-\mstar\ of our sample shows the very consistent evolution trend as discovered by D20, as shown in Figure~\ref{fig:scaling_relation}.
-The consistent result by our sample confirm the evolution of the D20 that the growth of a black hole predates that of its host galaxy.
+We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the similar approaches to derive the \mstar\ and calibrated the \mbh\ using consistent recipes.
+The \mbh-\mstar\ correlation and its evolution with cosmic time is in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
+The consistent result by our sample confirms\pink{the conclusion of evolution of the D20 as follows.
+First of all, the growth of the supermassive black hole predates that of its host galaxy during their co-evolution.
+Besides, for the high-$z$ sample, it is the total stellar masses that are measured and compared.
+Note that the actual morphologies of these hosts could be more complicated, such as disk and bulge component (system RXJ1131 for example).
+However, the local sample are bulge-dominated galaxies and the entire local \mstar\ adopted is their bulge mass.
+If the high-$z$ sample could be all resolved to focus the comparison on the bulge, the compared \mstar\ would be smaller (i.e., disk mass removed).
+As a result, the inferred evolution for the \mbh-bulge relation would be much even stronger.
+Taken together, these results suggest a scenario in which the stellar mass is transferred from disk to the bulge at a faster rate than the growth of \mbh\ since $z\sim2$.}
 
-Our work, one more time, confirmed the fidelity of using strong lensing as a tool to study the scaling relation at high redshift.
-The lensed AGN host galaxy can be accurately recovered using the state-of-the-art lens modelling technique.
-Even more, with a higher lens magnification effect, the lensed arc by the quadruply imaged sample has demonstrate the higher SNR level (see the Figure~\ref{fig:image_inference}, ``Residual of the lensed arcs'' panel).
-Apparently, the lensed AGNs have a great potential to extend to study the \mbh-\mstar\ at even higher redshift range.
+Our work based on highly magnified AGN showcases the power of lensing to effectively increase the resolution of a telescope and shows that uncertainties related to lens modelling are subdominant with respect to other sources of uncertainty like black hole mass.
+Furthermore, our work provides a powerful verification of the fidelity of the host galaxy reconstruction in non-lensed AGN.
 
-%Finally, we did not consider the selection effect.
-Besides the mass function, the selection function of the lensed AGNs is also non-trivial.
-We note that these effects will have to be modelled in the future if the lensed sample is used to infer the evolution.
-The detection of the lensed quasars is going to grow rapidly and sample size of lensed AGNs with the hosts that can be recovered with high fidelity is likely to continue to grow in wide field imaging and spectroscopic surveys~\citep[e.g.,][]{Oguri2010, Agn++15,Mor++16,Sch++16,Ost++17}.
+In conclusion, lensed AGNs have great potential to extend to study of the \mbh-\mstar\ correlation at even higher redshifts than those considered here.
+So far, this kind of work has been limited by sample size.
+However, given the pace of discovery of lensed quasars in imaging and spectroscopic surveys ~\citep[e.g.,][]{Oguri2010, Agn++15,Mor++16,Sch++16,Ost++17,Tre++18, Ang++18, Lem++20}, the samples of lensed AGNs with hosts that can be recovered with high fidelity is likely to continue to grow in wide field imaging and spectroscopic surveys.
 The forthcoming launch of the {\it James Webb Space Telescope} and the first light of adaptive optics-assisted extremely large telescopes may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$).
+
+\todo{Tommaso please confirm the reference for Treu2010, Auger2010, Tre++18, Ang++18, Lem++20}
 
@@
 
-\section{Color inference of the host}
-We describe the details of the inference of the stellar population in this section. The template would be then adopted to the photometry by Section~\ref{sec:photometry} to infer the stellar mass.
+\section{Estimate of the color of the host}
+In this section, we describe the details of how we select the stellar population of the host used in the computation of the stellar mass estimate.
+
 \subsection{HE0435}\label{app:HE0435}
-The HE0435 system are also modelled through ACS/F814W and ACS/F555W (GO-9744; PI: C.
+\pink{Besides WFC3/F160W, HE0435 has also been observed through bands ACS/F814W and ACS/F555W (GO-9744; PI: C.
 S.
 Kochanek).
-We derive the magnitude of the lensed galaxy and infer the color of the host in the image plane.
-To save computer time, we only adopt the {\it PSF iteration} approach and fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}.
-We illustrate the lens model for the other two band in Figure~\ref{fig:app_HE0435}-(a), (b).
-The accuracy of the inferred host magnitude in the image plane is considered to be robust, and we consider them to have the same uncertainty as the F160W band inference.
-Having obtained the magnitude of the lensed host at three band, we use {\sc gsf} package to select the best stellar population from a range of [0.625, 0.8, 1.0, 1.5, 2.0, 3.0] Gyr with solar metallicity.
-Finally, a stellar population with age of 1.5 Gyr demonstrated the best matching to the color, which is selected to the final inference, see Figure~\ref{fig:app_HE0435}-(c).
+Our aim is to derive the brightness of the host galaxy through all the three band to investigate the color and stellar population in the image plane.
+We use the modelling approach introduced in Section~\ref{sec:photometry} to perform this inference for the F814W and F555W bands.
+To save computer time, we only use the {\it PSF iteration} approach.
+We also fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}.
+The inference of the fittings are shown in Figure~\ref{fig:app_HE0435}-(a), (b).
+Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}} \todo{cite Morishita's paper if any.} to perform the SED fitting.
+The stellar population with 1.5 Gyr and solar metallicity could provide the best fitting to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c), which is finally taken to estimate th host stellar mass.}
 
@@
 \caption{\label{fig:app_HE0435} 
-Illustrations of the inference of HE0435 using the data at the other two bands.
+Illustrations of the inference of HE0435 using the multi-band data.
 Top two panels: best-fit model of the lensed arcs shown as Figure~\ref{fig:image_inference}.
-Bottom panel: SED inference of the color using the three band inference.}
+Bottom panel: SED inference.
+\pink{The red points with error are the inferred host flux at the three bands in the image plane}.}
 \end{figure*}
@@
 \subsection{WFI2033}\label{app:WFI2033}
-WFI2033 is also observed by other four band data including WFC3/F125W (GO-12874; PI: D.
+\pink{In addition to the WFC3/F160W, WFI2033 has been observed by \hst\ in other four bands, including WFC3/F125W (GO-12874; PI: D.
 Floyd), WFC3/F140W (GO-13732; PI: A.
@@
 Kochanek).
-Similar to Section~\ref{app:HE0435}, the inference of the lensed arcs of WFI2033 have been fitted through five band.
-The lensed models are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d).
-Note that, limited by its exposure time, the data quality by F125W is not ideal and the host information could not be well extracted.
-Thus, we does not take the inference by F125W into account in the color inference.
-Finally, we find the stellar population with 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}-(e).
+Similar to Section~\ref{app:HE0435}, the lens modelling and the host photometry of WFI2033 have been inferred through these four bands.
+The results are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d).
+Unfortunately, limited by its exposure time, the data quality through F125W is not ideal and the host information could not be well extracted.
+Thus, we does not take the inference by F125W into account in the SED fitting.
+Using four-band photometry, we find the stellar population of 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}-(e).}
 \begin{figure*}
 \centering
-\subfloat[WFI2033 F125W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
-\subfloat[WFI2033 F140W \todo{remove arrows}]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
+\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
+\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
 \subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
@@
 \caption{\label{fig:app_WFI2033} 
-Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The inference of the lensed arcs is not clear in the F125W data, and thus the SED fitting is done through the other four bands.}
+Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. \pink{The inference of the host photometry is not clear using the F125W data, and thus the SED fitting is perform without this band.}}
 \end{figure*} 

### 2020-05-15 MBH_estimator/est_MBH.py

@@ -18,7 +18,7 @@ BL_info =  {'HE0435': {'Mgii': {'L': [45.7 -np.log10(5.15), 46.0 -np.log10(5.15)
                  'RXJ1131': {'Mgii': {'L': [45.0-np.log10(5.15)], 'FWHM':  5630.0},
                              'Hb': {'L': [45.0-np.log10(9.6)], 'FWHM':  4545.0}},  #Should -np.loq10(9.6)
                  'WFI2033':  {'Mgii': {'L': [46.0-np.log10(5.15),  45.8-np.log10(5.15)], 'FWHM':   3960.0}},
-                 'SDSS1206': {'Mgii': {'L': [(44.23-2.22)/0.909 -np.log10(4.)], 'FWHM':   5632.4}},
+                 'SDSS1206': {'Mgii': {'L': [(44.23-2.22)/0.909 -np.log10(4.)*2.], 'FWHM':   5632.4}},  #-np.log10(4.)/2. is for the magnification correction.
                  'HE1104':  {'Civ': {'L': [46.18], 'FWHM':   6004.0}}, 
                  'SDSS0246': {'Mgii': {'L': [46.0-np.log10(5.15), 45.8-np.log10(5.15)], 'FWHM':   3700.0}},
                  'HE0047': {'Mgii': {'L': [46.3-np.log10(5.15), 46.3-np.log10(5.15)], 'FWHM':   4145.0}},

### 2020-05-15 relation_plots/MM_32QSO.py

@@ -311,7 +311,7 @@ for i in range(len(h0licow)):
     ID = h0licow[i]
     Mstar = np.log10(read_mstar(ID, count_n=[4, 4])[0][0])
     MBs = MBH_dic[ID]
-    plt.scatter(Mstar, MBs, c='orangered',s=280,marker=ma[i],zorder=100, edgecolors='k', label = ID)
+    plt.scatter(Mstar, MBs, c='cornflowerblue',s=280,marker=ma[i],zorder=100, edgecolors='k', label = ID)
     # texts.append( plt.text(Mstar+0.1, MBs, ID, fontsize=15, zorder=200) )
 first_legend = plt.legend(loc=2,prop={'size':17,'family': 'Arial'},ncol=4) 
 ax = plt.gca().add_artist(first_legend)

### 2020-05-15 relation_plots/MM_vz_32QSO.py

@@ -320,7 +320,7 @@ plt.errorbar(np.log10(1+cis11[:,0]),cis11[:,1]-(m_ml*cis11[:,2]+b_ml),yerr=(0.4*
 
 #    plt.errorbar(np.log10(1+Knud[:,0]),Knud[:,2]-(m_ml*Knud[:,4]+b_ml),yerr=0,fmt='o',color='blue',markersize=9) 
 
-
+ding20_sample = np.log10(1+zs),MBs-(m_ml*Mstar+b_ml)
 plt.scatter(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),c='lightsalmon',
             s=420,marker=".",zorder=300, vmin=0.3, vmax=5, edgecolors='k', alpha = 0.8)
 plt.errorbar(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),
@@ -333,8 +333,8 @@ plt.errorbar(np.log10(1+zs),MBs-(m_ml*Mstar+b_ml),
 #            s=280,marker="o",zorder=900, edgecolors='blue', linewidth=6, alpha=0.5)    
 #plt.arrow(np.log10(1+zs[9]),0, 0, +0.19, zorder=800, head_length=0.05,head_width=0.005,fc='k',ec='k')
 
-#####fit the evolution##########
-################################
+# #####fit the evolution##########
+# ################################
 z_ss, y_ss = ss[:,0], ss[:,2]-(m_ml*ss[:,1]+b_ml)
 
 z_b11, y_b11 = b11[:,0], b11[:,2]-(m_ml*b11[:,1]+b_ml)
@@ -344,11 +344,11 @@ z_cis, y_cis = cis11[:,0], cis11[:,1]-(m_ml*cis11[:,2]+b_ml)
 z_cosmos, y_cosmos = zs, MBs-(m_ml*Mstar+b_ml)
 yerr_hz = (yerr_highz[0]+ yerr_highz[1])/2
                               
-z=np.concatenate((z_ss, z_b11, z_cis, z_cosmos),axis=0)
-y=np.concatenate((y_ss, y_b11, y_cis, y_cosmos),axis=0)
-yerr_imd= np.zeros(len(z_ss)+len(z_b11))+(0.4**2+(m_ml*0.2)**2)**0.5   # the error for the fitting
-yerr_cis = np.zeros(len(z_cis)) + (0.4**2+(m_ml*0.35)**2)**0.5 
[…]

### 2020-05-15 manuscript/manuscript.tex
updates

@@
 
-{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W \pink{The multi-band imaging data provides us the opportunity to estimate the host color and derive an accurate stellar population.
+{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W.
+\pink{The multi-band imaging data provides us the opportunity to estimate the host color and derive an accurate stellar population.
 We adopted the lensing modelling approach as introduced in Section~\ref{sec:photometry} to infer the host photometry at F814W and F555W two bands.
@@
 \pink{We plot our new measurements on top of the figure to make direct comparison.
-The red line and shaded region are the best-fit and $1-\sigma$ offset fitting by Equation~\eqref{eq:offset} using the 32 high-z AGNs in D20, while the blue line and region are the fitting based on the eight lensed systems.} \blue{Xuheng: Let me know if it's better to remove the blue line and region.}
+The red line and shaded region are the best-fit and $1-\sigma$ offset fitting by Equation~\eqref{eq:offset} using the 32 high-z AGNs in D20, while the blue line and region are the fitting based on the eight lensed systems.} \blue{[Xuheng: Let me know if your don't like the current plots.]}
 }
@@
 
-\todo{Tommaso please confirm the reference for Treu2010, Auger2010, Tre++18, Ang++18, Lem++20}
+\todo{Xuheng: Hi Tommaso please confirm if I cite the right reference including Treu2010, Auger2010, Tre++18, Ang++18, Lem++20}
 

### 2020-05-15 relation_plots/MM_vz_32QSO.py

@@ -149,7 +149,7 @@ elif style ==1:
     ty=xl*0
     ty1=xl*0+np.std(y-(m_ml*x+b_ml))
     ty2=xl*0-np.std(y-(m_ml*x+b_ml))
-    plt.fill_between(xl,ty1,ty2,color='linen',zorder=-50)
+    plt.fill_between(xl,ty1,ty2,color='lightgray',zorder=-50, alpha = 0.5)
 
 Bkc=mlines.Line2D([], [], color='gray', ls='', marker='.', markersize=15)
 Hkc=mlines.Line2D([], [], color='black', ls='', marker='.', markersize=15)
@@ -512,7 +512,7 @@ plt.legend([Bkc, Hkc, SS13, ding_sample],[
 "Intermediate redshift AGNs",
 "$1.2<z<1.7$ AGNs by D20"
 ],scatterpoints=1,numpoints=1,loc=3,prop={'size':22,'family': 'Arial'},ncol=2,handletextpad=0)
-# plt.savefig("MBH-Mstar_vz.pdf")
+plt.savefig("MBH-Mstar_vz.pdf")
 plt.show()
 
 # #%% KS test on the distributions:

### 2020-05-15 manuscript/manuscript.tex
Pull from Tommaso's edits

@@
 % Keep the title short and informative.
-\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed AGNs}
+\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed quasars}
 
@@
   One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution.
-The magnification of strongly lensed quasars provide a way to effectively increase instrumental resolution and thus overcome this challenge.
-In this work, we study eight strong lens systems with deep {\it Hubble Space Telescope}(\hst) imaging, using the state-of-the-art \lenstronomy\ code to reconstruct the image of the source.
+Strong lensing magnification effectively increases instrumental resolution and thus addresses this challenge.
+In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope}(\hst) imaging, using the state-of-the-art \lenstronomy\ code to reconstruct the image of the source.
 Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models.
   \mbh\ are estimated from broad emission line using standard methods.
-Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolve over cosmic time.
-At the moment, the \pink{sample size of lensed AGN is small and thus} provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN.
-However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and may become a key diagnostic of black hole and galaxy co-evolution.
+Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolves over cosmic time.
+At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN.
+However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and they may become a key diagnostic of black hole and galaxy co-evolution.
 \end{abstract}
@@
 %
-The broad line properties of our samples are \pink{mostly} adopted from the literature. % \citep{Sluse2012, Peng2006, Shen2011}.
-\pink{For SDSS1206, the line properties have been inferred by~\citet{Shen2011}.
+The broad line properties of our samples are adopted from the literature, with a few corrections/exceptions. % \citep{Sluse2012, Peng2006, Shen2011}.
+The line properties of SDSS1206 have been inferred by~\citet{Shen2011}.
 However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered.
 We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work.
-For the rest of the lens sample except HS2209, their broad line properties are adopted from the literatures~\citep{Sluse2012, Peng2006} with lensing magnification effect considered.
-For HS2209, the spectrum data was observed from ESI in September 2015.
-We derived the line properties using the same approach as~\citep{Sluse2012}.
-\todo{Dominique and Chris can give more details here.} }.
+For the rest of the lens sample except HS2209, their broad line properties are adopted from the literature~\citep{Sluse2012, Peng2006} taking into account lensing magnification.
+For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015.
+We derived the line properties from the spectrum using the same approach as~\citep{Sluse2012}.
+\todo{Dominique and Chris can give more details here.} .
 The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}.
@@
 {\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W.
-\pink{The multi-band imaging data provides us the opportunity to estimate the host color and derive an accurate stellar population.
-We adopted the lensing modelling approach as introduced in Section~\ref{sec:photometry} to infer the host photometry at F814W and F555W two bands.
-Based on the three band host magnitudes, we find a 1.5~Gyr age and solar metallicity stellar population could well match the color.
-More detailed information is presented in Appendix~\ref{app:HE0435}.}
+The multi-band imaging data provides us with the opportunity to estimate the host color and improve the stellar mass estimate.
+We adopted the lensing modelling approach described in Section~\ref{sec:photometry} to infer the host photometry through the F814W and F555W bands.
+Based on the three band host magnitudes, we find that a 1.5~Gyr age and solar metallicity stellar population provides a good match to the color.
+More detailed information is presented in Appendix~\ref{app:HE0435}.
 %Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy.
@@
   \end {eqnarray}
-\pink{with calibrated value as  $\alpha = 0.27$, $\beta = 0.98$ based on the 55 local sample.} We find that our lensed systems are above the local relation, consistent with the inference from the 32  non-lensed AGNs published by D20 in a  similar redshift range.
+with  $\alpha = 0.27$, $\beta = 0.98$ based on the local sample of 55 objects measured in a consistent manner.
+We find that our lensed systems are above the local relation, consistent with the inference from the 32  non-lensed AGNs published by D20 in a  similar redshift range.
 To quantify the evolution as a function of redshift, we parameterize it as:
@@
 We find that the offset from the local relationship is indistinguishable for the two samples.
-\pink{Based on Equation~\eqref{eq:offset}, we estimate the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which overlaps with D20's inference ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.} This consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20\pink{that the observed value of \mbh\ at a fixed \mstar\ tend to be larger at higher redshift than the ones in the local universe.}
+Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
+The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the observed value of \mbh\ at a fixed \mstar\ tend to be larger at higher redshift than the ones in the local universe.
 
-\pink{The lensed AGN systems in this work are directly taken from the H0LiCOW collaboration.
-We note that selection function of our sample is irrelevant to D20's sample.
-Given that the eight lensed AGN sample is relatively a small size, in this work we only take them for consistency check with the previous studies.
-The selection effect of the lensed sample will be investigated when the volume of the lens systems is large enough with statistical significance.}
+The lensed AGN systems analyzed in this work were selected for time delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy.
+This is a different selection function that that adopted by D20.
+It is thus reassuring that the two samples present the same apparent evolution.
+Naturally, inferring the true underlying evolution requires modeling the selection function (as done by D20), which is not justified given the small sample size of lensed quasars sample.
+At this stage thus, the lensed quasars should be considered as a check on possible systematic measurements error in the D20 analysis rather than a stand-alone measurement.
 
@@
 \begin{tabular}{c c}
-{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar.pdf}}&
-{\includegraphics[height=0.5\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
+{\includegraphics[height=0.45\textwidth]{fig/MBH-Mstar.pdf}}&
+{\includegraphics[height=0.45\textwidth]{fig/MBH-Mstar_vz.pdf}}\\
 \end{tabular}
 \caption{\label{fig:scaling_relation} 
-(left): BH masses vs. stellar mass correlation (\mbh-\mstar). The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval based on Equation~\ref{eq:MMlocal}.
-(right): offset of $\log(\mathcal M_{\rm BH})$ (vs.
-\mstar) as a function of redshift.
-\pink{We plot our new measurements on top of the figure to make direct comparison.
-The red line and shaded region are the best-fit and $1-\sigma$ offset fitting by Equation~\eqref{eq:offset} using the 32 high-z AGNs in D20, while the blue line and region are the fitting based on the eight lensed systems.} \blue{[Xuheng: Let me know if your don't like the current plots.]}
-}
+(left): BH masses vs.
+stellar mass correlation (\mbh-\mstar).
+The black line and the gray shaded region indicate the best-fit and 1$\sigma$ confidence interval of the form given by Equation~\ref{eq:MMlocal}.
+(right): Offset of $\log(\mathcal M_{\rm BH})$ at fixed \mstar as a function of redshift.
+Our new measurements are overlayed on samples of non-lensed AGNs taken from the literature and measured in a self consistent way to facilitate a direct comparison.
+The red line and shaded region are the best-fit and $1-\sigma$ results of fitting  Equation~\eqref{eq:offset} to the 32 high-z AGNs measured by D20.
+The blue line and region are the results based on the eight lensed systems presented in this work.
+The blue and red areas are in agreement within the errors.}
 \end{figure*}
@@
 
-We considered set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices.
+We considered a set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices.
 In particular, we treat the two different modelling approaches, i.e., {\it noise boost} and {\it PSF iteration} equally, to derive the averaged results.
@@
 
-\section{Conclusion}\label{sec:con}
+\section{Conclusions}\label{sec:con}
 Using eight strongly lensed AGN systems, we presented a new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy.
@@
 
-We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the similar approaches to derive the \mstar\ and calibrated the \mbh\ using consistent recipes.
+We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the same approache to derive the \mstar\ and calibrated the \mbh\ using consistent recipes.
 The \mbh-\mstar\ correlation and its evolution with cosmic time is in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
-The consistent result by our sample confirms\pink{the conclusion of evolution of the D20 as follows.
-First of all, the growth of the supermassive black hole predates that of its host galaxy during their co-evolution.
-Besides, for the high-$z$ sample, it is the total stellar masses that are measured and compared.
-Note that the actual morphologies of these hosts could be more complicated, such as disk and bulge component (system RXJ1131 for example).
-However, the local sample are bulge-dominated galaxies and the entire local \mstar\ adopted is their bulge mass.
-If the high-$z$ sample could be all resolved to focus the comparison on the bulge, the compared \mstar\ would be smaller (i.e., disk mass removed).
-As a result, the inferred evolution for the \mbh-bulge relation would be much even stronger.
-Taken together, these results suggest a scenario in which the stellar mass is transferred from disk to the bulge at a faster rate than the growth of \mbh\ since $z\sim2$.}
+Thus, the present analysis further strengthens the conclusion of D20, which can be summarized as follows.
+First, the growth of the supermassive black hole predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
+However, the actual morphologies of these hosts is likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131.
+In contrast, the galaxies in the local sample are typically bulge-dominated and the bulge mass is adopted as their  \mstar\.
+Thus, the reported evolution is weaker than what would be inferred by comparing \mbh to bulge \mstar at all redshifts \citep{Bennert++2011}.
+Taken together, these results are consistent with a scenario in which the stellar mass is transferred from disk to the bulge at a faster rate than the growth of \mbh\ since $z\sim2$.
 
-Our work based on highly magnified AGN showcases the power of lensing to effectively increase the resolution of a telescope and shows that uncertainties related to lens modelling are subdominant with respect to other sources of uncertainty like black hole mass.
+Our work based on highly magnified AGN showcases the power of strong lensing to effectively increase the resolution of a telescope and shows that uncertainties related to lens modelling are subdominant with respect to other sources of uncertainty like black hole mass.
 Furthermore, our work provides a powerful verification of the fidelity of the host galaxy reconstruction in non-lensed AGN.
@@
 
-\todo{Xuheng: Hi Tommaso please confirm if I cite the right reference including Treu2010, Auger2010, Tre++18, Ang++18, Lem++20}
-
 \section*{Acknowledgements}
@@
 acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
-\todo{To be updated.}
+\todo{To be updated.
+Add silverman's grant.}
 
@@
 \subsection{HE0435}\label{app:HE0435}
-\pink{Besides WFC3/F160W, HE0435 has also been observed through bands ACS/F814W and ACS/F555W (GO-9744; PI: C.
+In addition to WFC3/F160W, HE0435 has been observed through bands ACS/F814W and ACS/F555W (GO-9744; PI: C.
 S.
@@
 Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}} \todo{cite Morishita's paper if any.} to perform the SED fitting.
-The stellar population with 1.5 Gyr and solar metallicity could provide the best fitting to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c), which is finally taken to estimate th host stellar mass.}
+A stellar population with 1.5 Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
+This stellar population is used to estimate the host stellar mass.
 
@@
 Bottom panel: SED inference.
-\pink{The red points with error are the inferred host flux at the three bands in the image plane}.}
+The red points with error bars represent the inferred image plane host flux in the three bands.}
 \end{figure*}
@@
 \subsection{WFI2033}\label{app:WFI2033}
-\pink{In addition to the WFC3/F160W, WFI2033 has been observed by \hst\ in other four bands, including WFC3/F125W (GO-12874; PI: D.
+In addition to WFC3/F160W, WFI2033 has been observed by \hst\ in  four bands, i.e.
+WFC3/F125W (GO-12874; PI: D.
 Floyd), WFC3/F140W (GO-13732; PI: A.
@@
 The results are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d).
-Unfortunately, limited by its exposure time, the data quality through F125W is not ideal and the host information could not be well extracted.
-Thus, we does not take the inference by F125W into account in the SED fitting.
-Using four-band photometry, we find the stellar population of 0.625 Gyr age could well matched the color, i.e., Figure~\ref{fig:app_WFI2033}-(e).}
+Unfortunately, the  F125W data are too shallow to robustly detect the host.
+Thus, we does not use the F125W band for the SED fitting.
+Using four-band photometry, we find a stellar population of 0.625 Gyr age provides a good match to the colors, as shown in Figure~\ref{fig:app_WFI2033}-(e).
 \begin{figure*}
@@
 \caption{\label{fig:app_WFI2033} 
-Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. \pink{The inference of the host photometry is not clear using the F125W data, and thus the SED fitting is perform without this band.}}
+Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The F125W dare are too shallow to detect the host and are thus omitted in the fit.}
 \end{figure*} 

### 2020-05-19 manuscript/manuscript.tex
before test auto-aff

@@
 Takahiro Morshita$^{11}$,
+Aymeric Galan$^{12}$,
 and et al.
+\\
 \\
@@
 $^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
-$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
-$^{11}$TBC
+$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
+$^{12}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
+F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
+Switzerland\\
+$^{13}$TBC
 }
@@
 Cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
-However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic megers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
+However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic mergers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
 
@@
 
-It has been long recognized that lensed AGNs, by virtue of magnification, can provide unique insights inro the scaling relations the distant universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
-Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration.
+It has been long recognized that lensed AGNs, by virtue of magnification, can provide unique insights into the scaling relations the distant universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
+Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW\footnote{\url{http://www.h0licow.org/}}, PI: Suyu) collaboration.
 They confirm that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
@@
 Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20.
-Given the similar redshift range, the high data quality, and consistent state of the art techniques, this sample of lensed AGN provides an excellent verfication of the D20 results.
+Given the similar redshift range, the high data quality, and consistent state of the art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.
 
@@
 Discussion and conclusions are drawn in Section~\ref{sec:diss} and~\ref{sec:con}.
-Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
+Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, \pink{to compute the luminosity distance and estimate the host absolute brightness}.
 Magnitudes are presented in the AB system.
@@
 \section{Sample Selection and Black Hole Mass Estimates}\label{sec:sample_select}
-We adopt eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914.
+We adopt eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914.
 We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data.
@@
 
-To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt a the following set of self-consistent recipes following D20:
+To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt the following set of self-consistent recipes following D20:
 \begin{eqnarray}
@@
 $b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
-$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
+$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
 %
@@
 For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015.
-We derived the line properties from the spectrum using the same approach as~\citep{Sluse2012}.
+We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012},\pink{ based on \Mgii}.
 \todo{Dominique and Chris can give more details here.} .
-The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}.
+The \mbh\ measurements, together with the properties of the board-line, are listed in Table~\ref{mbh}.
 The uncertainty of the \mbh\ are estimated to be $0.4$~dex.
@@
 %\begin{threeparttable}
-\caption{Summary of \mbh\ estimates, \pink{based on equation~\eqref{recipe}.}}\label{mbh}
+\caption{Summary of \mbh\ estimates, based on equation~\eqref{recipe}.}\label{mbh}
 \resizebox{8.5cm}{!}{
@@
 SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
-HS2209 & \Mgii & 3245 & 45.71 & 8.75 & \pink{here}  \\
+HS2209 & \Mgii & 3245 & 45.71 & 8.75 & here  \\
 HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
@@
 \item Note: $-$ The broad line properties.\\ %For HS2209, the properties are derived in this work using the same approach as~\citet{Sluse2012}.
-\pink{Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.}\\
+Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.\\
 %$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect {\bf [TT: how about the others?].}
@@
 Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project.
-The goal of those models was strong lens time-delay cosmography~\citep{Treu2016}, and the reconstruction of the host galaxy light (pixelized or via shapelets) was a byproduct.
-\citet{Ding2017b} used those reconstructions for two of the systems, including HE0435 and RXJ1131, and then fitted a simply parametrized surface brightness profile to the reconstruction to mimic what is done in non-lensed AGN.
+The goal of those models was strong lens time-delay cosmography~\citep{Treu2016}, and the reconstruction of the host galaxy light\pink{(via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003})} was a byproduct.
+\citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to\pink{measure the host properties as the non-lensed AGN case}.
+% mimic what is done in non-lensed AGN.
 
 In this work, in order to reproduce more closely and uniformly what is
-done in non-lensed AGN we develope a strategy to obtain a one step
-measurement of the host galaxy light described by a \sersic surface
+done in non-lensed AGN, we develop a strategy to obtain a one step
+measurement of the host galaxy light described by a \sersic\ surface
 brightness profile. For the 4/8 systems already studied by the H0LiCOW
@@
 
-We following the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information.
+We follow the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information.
 The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}.
-We then adopt the {\sc Photutils} by Python to model the global background light in 2-D based on SExtractor algorithm.
+We then adopt the {\sc Photutils}~\citep{photutils} by Python to model the global background light in 2-D based on \texttt{SExtractor} algorithm.
 We remove the background light and cut the clear image data into postage stamp at a suitable size.
-We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.
+We draw the image mask for each systems to define the region in which the pixels are used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.
 
@@
 For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile.
-We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiply component.
+We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiple component.
 For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been studied in~\citet{Ding2017a} that choosing the prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}.
@@
 We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task.
-Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting for each system.
-We then apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty level, including the contribution of modelling choices.
+Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting\pink{ for each system, repeatedly.
+Then, based on the fittings using different choices,} we apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty \pink{level}.
 The modelling choices that we consider include the follows.
@@
 \item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
-\item Using the lensing imaging alone is difficult to constrain the power-law slope.
+\item Using the lensing imaging alone is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}.
 To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
@@
 After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value.
-Since there is no evidence of an better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20.
+Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20.
 The weights are defined by:
@@
 \label{eq:weights}
-w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
+w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
 \end{eqnarray} 
@@
 
-\subsubsection{HE0435}
+\subsubsection{HE0435}\label{subsec:HE0435}
 We follow the approach described in the previous section.
@@
 Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}.
-This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Refregier2003, Birrer2015}.
+This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}.
 The smooth feature of \sersic\ profile could not capture the clumps in the host galaxy such as the star-forming regions.
 Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e.
-the quantity commonly measured in the the literature for non-lensed samples.
+the quantity commonly measured in the literature for non-lensed samples.
 
@@
 However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}.
-This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
-The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
-While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time delay cosmography.
+This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).\pink{ Though \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, their inferred host surface brightness is computed by collecting the \sersic\ light within a region where host was reconstructed, which is defined by the mask region in the image plane.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
+While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.
 
@@
 \subsubsection{SDSS1206}
-SDSS1206 is an unique system -- the AGN is a doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged.
+SDSS1206 is a unique system -- the AGN is doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged.
 Following~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbation.
@@
 We modelled the two visits separately and recovered mutually consistent host galaxy magnitudes.
-However, we found that the data from {\it vis06} can be modelled with smaller residualsl; thus the inference based on {\it vis06} was adopted as our best estimate (using 7 initial PSF stars), as listed in Table~\ref{tab:host_measure}.
+However, we found that the data from {\it vis06} can be modelled with smaller residuals; thus the inference based on {\it vis06} was adopted as our best estimate (using 7 initial PSF stars), as listed in Table~\ref{tab:host_measure}.
 The inference for this system is summarized in Figure~\ref{fig:image_inference}-(g).
@@
       \item Note: $-$ Inference of the host galaxy properties.
-Column (2)-(6): photometry iderived using the imaging data in listed Table~\ref{data_set}.
+Column (2)-(6): photometry derived using the imaging data in listed Table~\ref{data_set}.
 Column (7): age of adopted stellar population with solar metallicity.
@@
 As for HE0435, we infer the host color in the image plane.
-We find a stellar population with 0.625 Gyr is a good matchi to the colors (more details see Appendix~\ref{app:WFI2033}).
+We find a stellar population with 0.625 Gyr is a good match to the colors (more details see Appendix~\ref{app:WFI2033}).
 
@@
 
-The lensed AGN systems analyzed in this work were selected for time delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy.
-This is a different selection function that that adopted by D20.
+The lensed AGN systems analyzed in this work were selected for time-delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy.
+This is a different selection function that adopted by D20.
 It is thus reassuring that the two samples present the same apparent evolution.
-Naturally, inferring the true underlying evolution requires modeling the selection function (as done by D20), which is not justified given the small sample size of lensed quasars sample.
+Naturally, inferring the true underlying evolution requires modelling the selection function (as done by D20), which is not justified given the small sample size of lensed quasars sample.
 At this stage thus, the lensed quasars should be considered as a check on possible systematic measurements error in the D20 analysis rather than a stand-alone measurement.
@@
 (right): Offset of $\log(\mathcal M_{\rm BH})$ at fixed \mstar as a function of redshift.
-Our new measurements are overlayed on samples of non-lensed AGNs taken from the literature and measured in a self consistent way to facilitate a direct comparison.
+Our new measurements are overlaid on samples of non-lensed AGNs taken from the literature and measured in a self consistent way to facilitate a direct comparison.
 The red line and shaded region are the best-fit and $1-\sigma$ results of fitting  Equation~\eqref{eq:offset} to the 32 high-z AGNs measured by D20.
@@
 
+\pink{To estimate the host stellar mass, we use \sersic\ model to measure the total brightness of the host galaxy.
+The \sersic\ profile is relatively simple and smooth which could not capture the clumps in the host galaxy, which lead to the high residuals as appeared in the fittings in Figure~\ref{fig:image_inference}.
+Nevertheless, the host inference is still reliable.
+As mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples which are measured using the same manner.
+Note that the total flux of a galaxy would be relatively settled, once a surface brightness profile is chosen.
+}
+
 In addition, we adopt simple stellar populations to derive the stellar mass.
 For 5/8 systems in our sample we did not have color information, and we used instead a fixed age depending on redshift.
-The lack of color information by necessity increases the in the inferred \mstar.
-However, once again the uncertainty is smaller than the estimated uncertainty in the  black hole mass (0.4 dex), which dominates the overall error budget.
+The lack of color information by necessity increases the error budget in the inferred \mstar.
+
+\pink{Most importantly, the uncertainty is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.}
 
@@
 
-We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the same approache to derive the \mstar\ and calibrated the \mbh\ using consistent recipes.
+We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the same approach to derive the \mstar\ and calibrated the \mbh\ using consistent recipes.
 The \mbh-\mstar\ correlation and its evolution with cosmic time is in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
@@
 However, the actual morphologies of these hosts is likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131.
-In contrast, the galaxies in the local sample are typically bulge-dominated and the bulge mass is adopted as their  \mstar\.
-Thus, the reported evolution is weaker than what would be inferred by comparing \mbh to bulge \mstar at all redshifts \citep{Bennert++2011}.
+In contrast, the galaxies in the local sample are typically bulge-dominated and the bulge mass is adopted as their  \mstar.
+Thus, the reported evolution is weaker than what would be inferred by comparing \mbh\ to bulge \mstar\ at all redshifts \citep{Bennert++2011}.
 Taken together, these results are consistent with a scenario in which the stellar mass is transferred from disk to the bulge at a faster rate than the growth of \mbh\ since $z\sim2$.
@@
 Furthermore, our work provides a powerful verification of the fidelity of the host galaxy reconstruction in non-lensed AGN.
+
+\pink{The strong lensing can help to extend the measurements of the AGN host to even higher redshift.
+It is worth noting that the lensed AGN adopted by this study are adopted from the H0LiCOW project which only focuses on the moment of the peak of the AGN luminosity function.
+In fact, the observation of \hst\ could even unveil the lensed AGN host of  BRI0952$-$0115 at $z=4.5$.}
 
@@
 \section*{Acknowledgements}
-%This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib} and standard Python libraries.
+\pink{We are grateful to Frederic Courbin, Leon Koopmans for useful comments
+and suggestions that improved this manuscript.}
 
@@
 acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
-\todo{To be updated.
-Add silverman's grant.}
+This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+
+This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib}
+and standard Python libraries.
 
@@
 The inference of the fittings are shown in Figure~\ref{fig:app_HE0435}-(a), (b).
-Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}} \todo{cite Morishita's paper if any.} to perform the SED fitting.
+Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}}~\citep{Morishita2019} to perform the SED fitting.
 A stellar population with 1.5 Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).

### 2020-05-20 manuscript/manuscript.tex
Update paper with Chris's comments

@@
 \newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
-\newcommand{\pink}[1]{{ \textcolor{magenta}{#1}}}
+\newcommand{\pink}[1]{{\textcolor{magenta}{#1}}}
 
@@
   One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution.
-Strong lensing magnification effectively increases instrumental resolution and thus addresses this challenge.
-In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope}(\hst) imaging, using the state-of-the-art \lenstronomy\ code to reconstruct the image of the source.
+Strong lensing magnification effectively increases instrumental resolution and thus helps to address this challenge.
+In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope}(\hst) imaging, using the \pink{lens modelling code} \lenstronomy\ to reconstruct the image of the source.
 Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models.
-  \mbh\ are estimated from broad emission line using standard methods.
+  \mbh\ are estimated from broad emission lines using standard methods.
 Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolves over cosmic time.
@@
 Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging.
-Combining the new sample with published samples in both local and intermediate redshift range, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy.
+Combining the new sample with published samples in both local and intermediate \pink{(i.e., $0.35<z\lesssim1.2$)} redshift ranges, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy.
 In a follow-up paper, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
-The observed tightness of the  scaling relations at high-$z$ is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature.
+The observed tightness of the  scaling relations at high redshift is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature.
 % , a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.
@@
 One of the main potential source of systematics is the finite resolution of \hst\ images.
-Even with state of the art techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution.
+Even with \pink{the modern} techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution.
 This is the goal of this work.
@@
 It has been long recognized that lensed AGNs, by virtue of magnification, can provide unique insights into the scaling relations the distant universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived.
-Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW\footnote{\url{http://www.h0licow.org/}}, PI: Suyu) collaboration.
+Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring \citep[H0LiCOW\footnote{\url{http://www.h0licow.org/}},][]{Suyu2017} collaboration.
 They confirm that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty.
@@
 In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs.
-We adopt a set of extended modelling choices to assure the accuracy of our measurements.
-We compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check.
-To assess an accurate inference of stellar mass, we utilize the imaging data taken with the \hst\ multi-band filter to obtain the color information for 3/8 of our targets.
-Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20.
-Given the similar redshift range, the high data quality, and consistent state of the art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.
+We adopt a set of extended modelling choices to \pink{estimate the host property uncertainty level and} ensure the accuracy of our measurements.
+We compare the inference of our new measurements to the ones that have been modelled by the H0LiCOW collaboration to make the cross-check.
+To obtain an accurate inference of stellar mass, we utilize the multi-band imaging data taken with the \hst\ to obtain the color information for 3/8 of our targets.
+\pink{We assume a typical stellar population for the rest 5/8 of the sample.} Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20.
+Given the similar redshift range, the high data quality, and consistent state-of-the-art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.
 
@@
 Magnitudes are presented in the AB system.
-A Chabrier initial mass function (IMF) is employed for the sample, consistently with D20.
+A Chabrier initial mass function (IMF) is employed for the sample, to be consistent with D20.
 
@@
 We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data.
-We summarized the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
+We summarize the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
 For conciseness, in the rest of this paper, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).
 
-Based on the observational data of these eight systems, \citet{Ding2017a} performed the extensive and realistic simulation exercise using the \hst\ image data of these eight systems and confirm that the source reconstruction using the state-of-the-art modelling technique is trustworthy.
-% when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN.
-Here, we re-summarized the imaging data information and listed in Table~\ref{data_set}.
-Besides the image data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems.
+Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy.
+Here, we re-summarize the imaging data information and list them in Table~\ref{data_set}.
+Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems.
 As we show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to improve the accuracy of the estimate of \mstar.
@@
 Therefore, we use it primarily to verify the results of D20.
-The D20 sample includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}.
-It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.
+The D20 sample includes 32 AGN measurements in the redshift range $1.2<z<1.9$.
+\pink{They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}.} It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.
 
@@
 \caption{Summary of lensed AGN observational details.}\label{data_set}
-\resizebox{13cm}{!}{
-     \begin{tabular}{cccccccc}
+\resizebox{15cm}{!}{
+     \begin{tabular}{ccccccccc}
         \hline
-Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale \\
- & & & & time (s) &&& (drizzled) \\ \hline
-HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
-RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ \\
-WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
-SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ \\
-HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ \\
-SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$ \\
-HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ \\
-HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ \\
+Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale & References \\
+ & & & & time (s) &&& (drizzled) & \\ \hline
+HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ & (1), (2)\\
+RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ &(3), (4)\\
+WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ & (5), (2) \\
+SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ & (6), (7)\\
+HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ & (8), (9)\\
+SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$& (10), (11) \\
+HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ & (12), (13) \\
+HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ & (14), (15) \\
         \hline
@@
       \item $^a$: HS2209, was visited by \hst\ twice ({\it vis05} and {\it vis06}) at different orientations. The exposure time is thus given separately.
+      \item References:$-$ (1) \citet{HE0435_discover}; (2) \citet{Sluse2012}; (3) \citet{1131_discover}; (4) \citet{1131_redshift}; (5) \citet{2033_discover}; (6) \citet{1206_discover}; (7) \citet{Eul++13}; (8) \citet{HE1104_discover}; (9) \citet{1104_d_redshift}; (10) \citet{0246_discover}; (11) \citet{0246_redshift}; (12) \citet{2209_discover};  (13) \citet{2209_more}; (14) \citet{0047_discover}; (15) \citet{Ofe++06};
+
 \end{tablenotes}  
@@
 \end {eqnarray}
+\pink{where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:}
 %
-with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
+$a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
 $b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
@@
 For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015.
-We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012},\pink{ based on \Mgii}.
+We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, \pink{based on \Mgii}.
 \todo{Dominique and Chris can give more details here.} .
@@
 Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project.
-The goal of those models was strong lens time-delay cosmography~\citep{Treu2016}, and the reconstruction of the host galaxy light\pink{(via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003})} was a byproduct.
-\citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to\pink{measure the host properties as the non-lensed AGN case}.
+The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light \pink{(via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003})} was a byproduct.
+\citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to \pink{measure the host properties as the non-lensed AGN case}.
 % mimic what is done in non-lensed AGN.
@@
 project, we will make a comparison to characterize systematic
-uncertainties related to modelling techniques.
+uncertainties related to the modelling techniques.
 
@@
 We follow the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information.
-The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}.
-We then adopt the {\sc Photutils}~\citep{photutils} by Python to model the global background light in 2-D based on \texttt{SExtractor} algorithm.
+The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolutions are listed in Table~\ref{data_set}.
+We then adopt the {\sc Photutils}~\citep{photutils} Python package to model the global background light in 2-D, based on the \texttt{SExtractor} algorithm.
 We remove the background light and cut the clear image data into postage stamp at a suitable size.
-We draw the image mask for each systems to define the region in which the pixels are used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.
+We draw \pink{an aperture of mask} for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.
 
@@
 For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile.
-We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiple component.
-For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been studied in~\citet{Ding2017a} that choosing the prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}.
+We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate multiple components.
+For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been shown in~\citet{Ding2017a} that choosing this prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}.
 The bright nucleus is unresolved and modelled by a scaled point spread function (PSF) in the image plane.
 We also impose that the AGN and its host galaxy have the same center.
-Following standard practice that has show to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical Power-law density profiles to define the surface mass density of the deflector, with an external shear.
+Following standard practice that has been shown to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical power-law density profiles to define the surface mass density of the deflector, with an external shear.
 
 We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task.
-Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting\pink{ for each system, repeatedly.
+Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting \pink{for each system, repeatedly.
 Then, based on the fittings using different choices,} we apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty \pink{level}.
@@
 \item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
-\item Using the lensing imaging alone is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}.
+\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}.
 To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
@@
 
-In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2 \times2 \times3$) fits.
+In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2$ modelling options $\times~2$ oversampling $\times~3$ slopes) fits.
 After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value.
@@
 \end{eqnarray} 
-Then, the results by {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
+Then, the results for {\it noise boost} and {\it PSF iteration} are combined equally to derive the value of host properties and the root-mean-square error (i.e., $\sigma$ level) based on the weights of the $4+4$ (i.e., {\it noise boost} and {\it PSF iteration}) options by:
 \begin{eqnarray}
@@
 
-Our approach uses the relative goodness of fit and ensures that at least 8 sets of best-fits are used to estimate the range of systematic uncertainties.
+Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties.
 
@@
 Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}.
-This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as the \sersic\ profile, which is relatively simple and smooth compare to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}.
-The smooth feature of \sersic\ profile could not capture the clumps in the host galaxy such as the star-forming regions.
+This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as a \sersic\ profile, which is relatively simple and smooth compared to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}.
+The smooth features of \sersic\ profile can not capture the clumps in the host galaxy, such as the star-forming regions.
 Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e.
@@
 
-As a cross-check, we compare our host magnitude to the inference by~\citet{Ding2017b}.
+As a cross-check, we compare our host magnitude to the inference of HE0435 by~\citet{Ding2017b}.
 They inferred the \sersic\ magnitude by fitting to the pixelized host galaxy as reconstructed by~\citet{Wong2017}.
@@
 A clear bulge and disk component can be identified.
-Thus, we describe the host galaxy with two \sersic\ with index value $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge.
+Thus, we describe the host galaxy with two \sersic\ profiles with index values $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge.
 In addition, following~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and describe it as a SIS and \sersic\ for its mass and light, respectively.
 
-The photometry of the RXJ1131 host galaxy is fitted with a sets of 4 initial PSFs.
+The photometry of the RXJ1131 host galaxy is fitted with a set of 4 initial PSFs.
 The results are summarized in Table~\ref{tab:host_measure}, with the best-fit result shown in Figure~\ref{fig:image_inference}-(b).
@@
 However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}.
-This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).\pink{ Though \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, their inferred host surface brightness is computed by collecting the \sersic\ light within a region where host was reconstructed, which is defined by the mask region in the image plane.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
+This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
+\pink{Despite that \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, their inferred host surface brightness is computed by collecting the \sersic\ light within a aperture where host was reconstructed; the aperture size is decided by the mask region in the image plane.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
 While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.
@@
 However, as noted by~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using a \sersic\ model.
-We select a total of 8 initial PSF-stars to model this system.
+We select a total of 8 initial PSF stars to model this system.
 
@@
 \subsubsection{HE1104}
-HE1104 is a typical doubly imaged quasar and has no recent models.
+HE1104 is a typical doubly imaged quasar.
 We have selected in total of 5 initial PSFs to perform the fit.
@@
 
+\pink{It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data.
+Their inferred host magnitude is $20.14\pm0.3$ in Vega system, which is also consistent to our inference ($20.00\pm0.15$ in Vega).}
+%zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
+%HE1104 mag:  21.25 (AB)  --> 20.00 (Vega)
+
 \subsubsection{SDSS0246}
-Imaged with WFC3-UVIS/F814W, the resolution of this systems (together with the remaining two systems) are much higher than for those imaged in the IR, with drizzled pixel scale as $0\farcs{}03$.
+Having been imaged with WFC3-UVIS/F814W, the resolution of the data for this system (together with the remaining two systems) is much higher than for those imaged in the IR, with a drizzled pixel scale of $0\farcs{}03$.
 However, the arcs are much fainter compared with those of other systems imaged in the IR band.
@@
 \caption{\label{fig:image_inference} 
-Illustrations of the inference using the best-fit lens model for each system using AGN center noise level boosted approach.
-For each figure, the panels from left to right are the follows: Top raw: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the variance; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
-Across all the systems, the lensed arc image can be clearly seen by in the fifth panel, indicating a strong evidence of a detection.
+Illustrations of the inference using the best-fit lens model for each system using the AGN center noise level boosted approach.
+For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
+Across all the systems, the lensed arc \pink{feature} can be clearly seen in the \pink{fourth} panel, indicating strong evidence of a detection.
 In panel (3) and (4), we use white regions to indicate the area where the noise level is boosted.
@@
 (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) \\    
-Object ID & intrinsic Magnitude & Magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & stellar population & $\log (M_{*}$)  \\
+Object ID & intrinsic magnitude & magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & stellar population & $\log (M_{*}$)  \\
  & (source plane) & (image plane) & ($\%$) & (arcsec) & & age (Gyr) & (M$_{\odot}$) \\ \hline
@@
 RXJ1131$_{\rm disk}$ & $19.33\substack{+0.17\\-0.15}$ & $17.14\substack{+0.08\\-0.07}$ & $69.2\pm10.1$ & $0.90\pm0.06$ & fix to 1 & $1.50$ & $11.08\substack{+0.06\\-0.07}$ \\
-WFI2033 & $21.78\substack{+0.28\\-0.23}$ & $19.07\substack{+0.35\\-0.26}$ & $19.6\pm4.5$ & $0.28\pm0.02$ & $0.52\pm0.01$ & $0.62$ & $10.51\substack{+0.09\\-0.11}$ \\
-SDSS1206 & $21.31\substack{+0.23\\-0.19}$ & $18.30\substack{+0.05\\-0.05}$ & $33.3\pm6.4$ & $0.11\pm0.02$ & $4.57\pm0.53$ & $0.62$ & $10.77\substack{+0.08\\-0.09}$ \\
-HE1104 & $21.25\substack{+0.16\\-0.14}$ & $19.16\substack{+0.02\\-0.02}$ & $14.0\pm2.0$ & $0.27\pm0.02$ & $1.05\pm0.04$ & $0.63$ & $11.05\substack{+0.06\\-0.07}$ \\
-SDSS0246 & $23.44\substack{+0.28\\-0.22}$ & $20.85\substack{+0.08\\-0.07}$ & $4.0\pm0.9$ & $0.44\pm0.08$ & $4.96\pm0.08$ & $0.63$ & $10.75\substack{+0.09\\-0.11}$ \\
+WFI2033 & $21.78\substack{+0.28\\-0.23}$ & $19.07\substack{+0.35\\-0.26}$ & $19.6\pm4.5$ & $0.28\pm0.02$ & $0.52\pm0.01$ & $0.625$ & $10.51\substack{+0.09\\-0.11}$ \\
+SDSS1206 & $21.31\substack{+0.23\\-0.19}$ & $18.30\substack{+0.05\\-0.05}$ & $33.3\pm6.4$ & $0.11\pm0.02$ & $4.57\pm0.53$ & $0.625$ & $10.77\substack{+0.08\\-0.09}$ \\
+HE1104 & $21.25\substack{+0.16\\-0.14}$ & $19.16\substack{+0.02\\-0.02}$ & $14.0\pm2.0$ & $0.27\pm0.02$ & $1.05\pm0.04$ & $0.625$ & $11.05\substack{+0.06\\-0.07}$ \\
+SDSS0246 & $23.44\substack{+0.28\\-0.22}$ & $20.85\substack{+0.08\\-0.07}$ & $4.0\pm0.9$ & $0.44\pm0.08$ & $4.96\pm0.08$ & $0.625$ & $10.75\substack{+0.09\\-0.11}$ \\
 HS2209 & $20.72\substack{+0.26\\-0.21}$ & $19.20\substack{+0.04\\-0.04}$ & $12.5\pm2.7$ & $1.96\pm1.28$ & $3.15\pm1.40$ & $1.00$ & $11.04\substack{+0.08\\-0.10}$ \\
-HE0047 & $22.92\substack{+0.48\\-0.33}$ & $20.37\substack{+0.20\\-0.17}$ & $2.3\pm0.8$ & $0.32\pm0.15$ & $4.18\pm0.75$ & $0.62$ & $10.91\substack{+0.13\\-0.19}$ \\
+HE0047 & $22.92\substack{+0.48\\-0.33}$ & $20.37\substack{+0.20\\-0.17}$ & $2.3\pm0.8$ & $0.32\pm0.15$ & $4.18\pm0.75$ & $0.625$ & $10.91\substack{+0.13\\-0.19}$ \\
 \hline
@@
 Column (2)-(6): photometry derived using the imaging data in listed Table~\ref{data_set}.
-Column (7): age of adopted stellar population with solar metallicity.
-Column (8): inferred stellar mass.
+Column (7): \pink{age of stellar population with solar metallicity.
+We adopt simple stellar population templates in this work, and the uncertainty of the age is not considered.} Column (8): inferred stellar mass.
 \end{tablenotes}    
@@
 \section{Results}\label{sec:result}
-In this section, we describe the approaches and assumptions used to estimate the stellar populations to our sample.
-Then, we adopt stellar population templates to derive their stellar mass of our sample.
+In this section, we describe the approaches and assumptions used to estimate the stellar populations in our sample.
+Then, we adopt stellar population templates to derive the stellar mass.
 We study the \mbh-\mstar\ relations and compare our measurements with ones taken from the literature.
@@
 Besides the imaging data analyzed in the last section, some of the systems have also imaged by \hst\ through other bands, providing color information.
-Given that we have used the highest signal to noise data for our primary models,  the analysis of the other bands has lower fidelity and we use it only to infer the colors so as to assist in the estimation of the stellar mass (i.e., Table~\ref{tab:host_measure} column (2)).
+Given that we have used the highest signal-to-noise ratio data for our primary models,  the analysis of the other bands has lower fidelity and we use it only to infer the colors so as to assist in the estimation of the stellar mass (i.e., Table~\ref{tab:host_measure} column (2)).
 
@@
 {\bf RXJ1131} ~ The host galaxy of RXJ1131 is lensed to a very extended arc in the image plane.
-The spectral energy distribution of the arc can be directly inferred in the image plane, since lens is achromatic.
+The spectral energy distribution of the arc can be directly inferred in the image plane, since lensing is achromatic.
 Based on the \hst\ imaging data through the three filters F814W and F555W and F160W, we adopt the SED estimated by~\citet{Ding2017b} with stellar populations of 3 Gyr and 1.5 Gyr (solar metallicity) for its bulge and disk, respectively.
+\pink{We refer the interested reader to that paper for more details.}
 
@@
 \subsection{The \mbh-\mstar\ relation}\label{sec:relation}
-In Figures~\ref{fig:scaling_relation}-(a) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.
+In Figure~\ref{fig:scaling_relation}-(a) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.
 We expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget for the entire sample.
-Following D20, we adopt as baseline a local \mbh-\mstar\ of the form:
+Following D20, we adopt, as baseline, a local \mbh-\mstar\ of the form:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-where the $\Delta \log \mathcal M_{\rm BH}$ is the offset of \mbh\ with respect to the local baseline at fixed \mstar.
+where $\Delta \log \mathcal M_{\rm BH}$ is the offset of \mbh\ with respect to the local baseline at fixed \mstar.
 To make a direct comparison, we reproduce the plot shown in Figure~8 of D20.
-Then, we add our new lensed AGN measurement and show the result in Figure~\ref{fig:scaling_relation}-(b).
-We find that the offset from the local relationship is indistinguishable for the two samples.
+Then, we add our new lensed AGN measurements and show the result in Figure~\ref{fig:scaling_relation}-(b).
+We find that the offset from the local relationship is similar for the two samples.
 Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
@@
 In particular, we treat the two different modelling approaches, i.e., {\it noise boost} and {\it PSF iteration} equally, to derive the averaged results.
-Of course, the results are somewhat dependent on the weighting scheme.
+Of course, the results are somewhat dependent on the weighting scheme, for example, the dispersion of the results by the top ranked choices.
 However, the dependency is smaller than other sources of uncertainty.
-For example, the dispersion of the results by the top ranked choices and thus using different weighting schemes would only change the results marginally ($<0.1$~dex).
+Thus, using different weighting schemes would only change the results marginally ($<0.1$~dex).
 
@@
 The \sersic\ profile is relatively simple and smooth which could not capture the clumps in the host galaxy, which lead to the high residuals as appeared in the fittings in Figure~\ref{fig:image_inference}.
-Nevertheless, the host inference is still reliable.
-As mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples which are measured using the same manner.
+However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples which are measured using the same manner.
 Note that the total flux of a galaxy would be relatively settled, once a surface brightness profile is chosen.
+Thus, the inferred host light can be considered as reliable.
 }
@@
 
+\pink{In this work, some options and assumptions have been made to measure the evolution of \mstar-\mbh.
+For example, a Chabrier IMF was assumed to measure the stellar mass, rather than the Salpeter one.
+To compare our high redshift measurements with the local ones, we adopt the local sample from~\citet{Bennert++2011, H+R04}, rather than the other ones in the literature.
+We adopt our own recipes to calibrate the \mbh.
+Of course, different options would shift the absolute \mstar\ and \mbh\ that were inferred.
+However, since the entire sample is self-consistent, a different assumption does not affect the measurement of the evolution, since it only shifts the global \mstar-\mbh together, leaving the offset value the same.
+More details can be found in D20, Section 6.}
+
 \section{Conclusions}\label{sec:con}
 Using eight strongly lensed AGN systems, we presented a new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy.
-We adopt state-of-the-art lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile.
+We adopt \pink{up-to-date} lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile.
 We estimated the \mbh\ of our sample using a set of calibrated single-epoch estimators to assure self-consistency and consistency with the comparison samples taken from the literature.
@@
 acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
-This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+\pink{This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+}
 
-This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib}
-and standard Python libraries.
+\pink{This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib} and standard Python libraries.}
 
@@
 Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}}~\citep{Morishita2019} to perform the SED fitting.
-A stellar population with 1.5 Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
+\pink{A set of age grids (up to 3.0 Gyr) are used in this fitting with a constant SFR and a flexible form for star formation histories.
+Finally, a} stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
 This stellar population is used to estimate the host stellar mass.

### 2020-05-22 manuscript/manuscript.tex
Update manuscript.tex
Update paper

@@
 \author[X. Ding et al.]{
-Xuheng Ding$^{1}$\thanks{E-mail: dxh@astro.ucla.edu},
-Tommaso Treu$^{1}$,
-Simon Birrer$^{2}$,
-Adriano Agnello$^{3}$,\newauthor
-Dominique Sluse$^{4}$,
-Chris Fassnacht$^{5}$,
-Matthew W. Auger$^{6}$,
-Kenneth C. Wong$^{7}$, \newauthor
-Sherry H. Suyu$^{8,9,10}$,
-Takahiro Morshita$^{11}$,
-Aymeric Galan$^{12}$,
+Xuheng Ding,$^{1}$\thanks{E-mail: dxh@astro.ucla.edu}
+Tommaso Treu,$^{1}$
+Simon Birrer,$^{2}$
+Adriano Agnello,$^{3}$\newauthor
+Dominique Sluse,$^{4}$
+Chris Fassnacht,$^{5}$
+Matthew W. Auger,$^{6}$
+Kenneth C. Wong,$^{7}$ \newauthor
+Sherry H. Suyu,$^{8,9,10}$
+Takahiro Morishita,$^{11}$
+\pink{
+Cristian E. Rusu,$^{12,13,14}$
+Aymeric Galan,$^{15}$}\newauthor
 and et al.
@@
 $^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA\\
-$^{12}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
+$^{12}$National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan\\
+$^{13}$Subaru Telescope, National Astronomical Observatory of Japan, 650 N Aohoku Pl, Hilo, HI 96720\\
+$^{14}$Department of Physics, University of California, Davis, 1 Shields Avenue, Davis, CA 95616, USA\\
+$^{15}$Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
 F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
@@
 We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}.
-Discussion and conclusions are drawn in Section~\ref{sec:diss} and~\ref{sec:con}.
+Discussion and conclusions are drawn in Sections~\ref{sec:diss} and~\ref{sec:con}.
 Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, \pink{to compute the luminosity distance and estimate the host absolute brightness}.
@@
 \section{Sample Selection and Black Hole Mass Estimates}\label{sec:sample_select}
-We adopt eight lens systems from our H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914.
+We adopt eight lens systems from the H0LiCOW collaboration including HE0435$-$1223, RXJ1131$-$1231, WFI2033$-$4723, HE1104$-$1805, SDSS1206$+$4332, SDSS0246$-$0825, HE0047$-$1756 and HS2209$+$1914.
 We refer to~\citet{Suyu2017, Ding2017a} for the descriptions of these data.
-We summarize the information for the eight systems, including their redshift and data conditions in Table~\ref{data_set}.
 For conciseness, in the rest of this paper, we abbreviate each lens name to four digits (e.g., HE0435$-$1223 to HE0435).
@@
 Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy.
-Here, we re-summarize the imaging data information and list them in Table~\ref{data_set}.
+We summarize the information for the eight systems, including \pink{their redshift, data conditions and the references} in Table~\ref{data_set}.
 Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems.
@@
         \hline
-Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale & References \\
+Object ID & $z_s$ & camera & Filter & exposure & Program ID & PI & pixel scale & References \\
  & & & & time (s) &&& (drizzled) & \\ \hline
@@
 $b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
-$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
+$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\} ($\AA$).
 %
@@
 We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, \pink{based on \Mgii}.
-\todo{Dominique and Chris can give more details here.} .
 The \mbh\ measurements, together with the properties of the board-line, are listed in Table~\ref{mbh}.
@@
 We remove the background light and cut the clear image data into postage stamp at a suitable size.
-We draw \pink{an aperture of mask} for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.
+We draw the image mask for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-\pink{middle} panel in each subplot in Figure~\ref{fig:image_inference}.
 
@@
 To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
-\item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
+\item To calculate the ray tracing under a higher resolution grid, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
 \item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}.
@@
 
-In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2$ modelling options $\times~2$ oversampling $\times~3$ slopes) fits.
+In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ \pink{(i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits}.
 After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value.
@@
 Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties.
+\pink{Note that the lens mass slope is fixed in each fitting, and the statistical uncertainty is much smaller than the systematic one.}
 
@@
 Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}.
-This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as a \sersic\ profile, which is relatively simple and smooth compared to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}.
+This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as a \sersic\ profile, which is relatively simple and smooth compared to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10, Suyu2012} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}.
 The smooth features of \sersic\ profile can not capture the clumps in the host galaxy, such as the star-forming regions.
@@
 \pink{It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data.
-Their inferred host magnitude is $20.14\pm0.3$ in Vega system, which is also consistent to our inference ($20.00\pm0.15$ in Vega).}
+Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).}
 %zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
@@
 Illustrations of the inference using the best-fit lens model for each system using the AGN center noise level boosted approach.
-For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
+For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level.
+\pink{Some of the residual looks clumpy; however, they do not affect the host property measurements, for more details see Section~\ref{sec:diss}} ; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
 Across all the systems, the lensed arc \pink{feature} can be clearly seen in the \pink{fourth} panel, indicating strong evidence of a detection.
@@
 (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) \\    
-Object ID & intrinsic magnitude & magnitude & Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & stellar population & $\log (M_{*}$)  \\
- & (source plane) & (image plane) & ($\%$) & (arcsec) & & age (Gyr) & (M$_{\odot}$) \\ \hline
+Object ID & intrinsic magnitude & magnitude & Host Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & stellar population & $\log (M_{*}$)  \\
+ & (source plane) & (image plane) & ( $\%$, \pink{Total = Host + AGN}) & (arcsec) & & age (Gyr) & (M$_{\odot}$) \\ \hline
 HE0435 & $21.49\substack{+0.40\\-0.29}$ & $18.58\substack{+0.30\\-0.23}$ & $36.0\pm11.1$ & $0.28\pm0.02$ & $2.71\pm0.20$ & $1.50$ & $10.91\substack{+0.12\\-0.16}$ \\
@@
       \item Note: $-$ Inference of the host galaxy properties.
-Column (2)-(6): photometry derived using the imaging data in listed Table~\ref{data_set}.
-Column (7): \pink{age of stellar population with solar metallicity.
-We adopt simple stellar population templates in this work, and the uncertainty of the age is not considered.} Column (8): inferred stellar mass.
+Column (2)-(6): photometry derived using the imaging data is listed Table~\ref{data_set}.
+Column (7): \pink{adopted age of stellar population with solar metallicity.} Column (8): inferred stellar mass.
 \end{tablenotes}    
@@
 %[] Color inference for the first three cases to decide their stellar template. 
-Besides the imaging data analyzed in the last section, some of the systems have also imaged by \hst\ through other bands, providing color information.
+Besides the imaging data analyzed in the last section, some of the systems have been also imaged by \hst\ through other bands, providing color information.
 Given that we have used the highest signal-to-noise ratio data for our primary models,  the analysis of the other bands has lower fidelity and we use it only to infer the colors so as to assist in the estimation of the stellar mass (i.e., Table~\ref{tab:host_measure} column (2)).
@@
 \subsection{The \mbh-\mstar\ relation}\label{sec:relation}
-In Figure~\ref{fig:scaling_relation}-(a) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.
+In Figure~\ref{fig:scaling_relation}-(left) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.
 We expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget for the entire sample.
@@
 To make a direct comparison, we reproduce the plot shown in Figure~8 of D20.
-Then, we add our new lensed AGN measurements and show the result in Figure~\ref{fig:scaling_relation}-(b).
+Then, we add our new lensed AGN measurements and show the result in Figure~\ref{fig:scaling_relation}-(right).
 We find that the offset from the local relationship is similar for the two samples.
 Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
-The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the observed value of \mbh\ at a fixed \mstar\ tend to be larger at higher redshift than the ones in the local universe.
+The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the observed value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
 
@@
 Naturally, inferring the true underlying evolution requires modelling the selection function (as done by D20), which is not justified given the small sample size of lensed quasars sample.
-At this stage thus, the lensed quasars should be considered as a check on possible systematic measurements error in the D20 analysis rather than a stand-alone measurement.
+At this stage, the lensed quasars should thus be considered as a check on possible systematic measurements error in the D20 analysis rather than a stand-alone measurement.
 
@@
 \pink{To estimate the host stellar mass, we use \sersic\ model to measure the total brightness of the host galaxy.
-The \sersic\ profile is relatively simple and smooth which could not capture the clumps in the host galaxy, which lead to the high residuals as appeared in the fittings in Figure~\ref{fig:image_inference}.
-However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples which are measured using the same manner.
+The \sersic\ profile is relatively simple and smooth, which could not capture the clumps in the host galaxy, which lead to the high residuals as appeared in the fittings in Figure~\ref{fig:image_inference}.
+However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same manner.
 Note that the total flux of a galaxy would be relatively settled, once a surface brightness profile is chosen.
-Thus, the inferred host light can be considered as reliable.
+Thus, the inferred host light is considered to be reliable.
 }
@@
 The lack of color information by necessity increases the error budget in the inferred \mstar.
+\pink{Once again, the same approach is adopted in D20, and thus our stellar masses are consistent with the D20's 32 high redshift AGN regarding this point.}
+\pink{We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies.
+As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104.
+For HE1104 the estimated extinction is negative, while for HE0435 and WFI2033 the authors do not report an extinction value because standard extinction laws did not fit the data.
+We interpret this as due to the small effect by dust being overshadowed by chromatic microlensing or variability.}
 
-\pink{Most importantly, the uncertainty is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.}
+\pink{Most importantly, the uncertainty of the \mstar\ is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.}
 
@@
 For example, a Chabrier IMF was assumed to measure the stellar mass, rather than the Salpeter one.
-To compare our high redshift measurements with the local ones, we adopt the local sample from~\citet{Bennert++2011, H+R04}, rather than the other ones in the literature.
+To compare our high redshift measurements with the local ones, we adopt the local sample from~\citet{Bennert++2011, H+R04}, rather than the other local ones in the literature.
 We adopt our own recipes to calibrate the \mbh.
-Of course, different options would shift the absolute \mstar\ and \mbh\ that were inferred.
-However, since the entire sample is self-consistent, a different assumption does not affect the measurement of the evolution, since it only shifts the global \mstar-\mbh together, leaving the offset value the same.
+Of course, different options would shift the absolute value of the inferred \mstar\ and \mbh.
+However, since the entire sample is self-consistent, a different assumption would only shifts the global \mstar-\mbh\ together, leaving the offset value and the evolution conclusion the same.
 More details can be found in D20, Section 6.}
@@
 First, the growth of the supermassive black hole predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
-However, the actual morphologies of these hosts is likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131.
+However, the actual morphologies of these hosts are likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131.
 In contrast, the galaxies in the local sample are typically bulge-dominated and the bulge mass is adopted as their  \mstar.
@@
 \pink{This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
-}
+SHS thanks the Max Planck Society for support through the Max Planck Research Group.}
 
@@
 \pink{A set of age grids (up to 3.0 Gyr) are used in this fitting with a constant SFR and a flexible form for star formation histories.
+Note that there is a degeneracy in the age and metallicity; however, this degeneracy has little affect on the \mstar\ inference.
+In this work, we fix the metallicity to infer the age, and the uncertainty of the age is not considered.
 Finally, a} stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).

### 2020-05-22 0_HE0435/model/3_summary.py

@@ -217,9 +217,9 @@ def plt_result(fixgamma, chisq=chisq):
     image  = image.reshape(fig.canvas.get_width_height()[::-1] + (3,))
     return image
 
-import imageio
-kwargs_write = {'fps':1.0, 'quantizer':'nq'}
-imageio.mimsave('fig_result_{0}_PSF.gif'.format(pick_names[pick]), [plt_result(fix_gamma) for fix_gamma in  ['1.9', '2.0', '2.1']], fps=1)
+# import imageio
+# kwargs_write = {'fps':1.0, 'quantizer':'nq'}
+# imageio.mimsave('fig_result_{0}_PSF.gif'.format(pick_names[pick]), [plt_result(fix_gamma) for fix_gamma in  ['1.9', '2.0', '2.1']], fps=1)
 
 #
 

### 2020-05-22 material/(Xuheng_mod)model_band_plot.py

@@ -327,7 +327,7 @@ class ModelBandPlot(object):
         if 'no_arrow' not in kwargs or not kwargs['no_arrow']:
             plot_util.coordinate_arrows(ax, self._frame_size, self._coords, color='w',
                               arrow_size=self._arrow_size, font_size=font_size)
-            plot_util.text_description_2(ax, d_s, text=text, color="w", backgroundcolor='k',
+            plot_util.text_description(ax, d_s, text=text, color="w", backgroundcolor='k',
                          flipped=False, font_size=font_size)
         if point_source_position is True:
             ra_source, dec_source = self.bandmodel.PointSource.source_position(self._kwargs_ps_partial, self._kwargs_lens_partial)

### 2020-05-22 material/(Xuheng_mod)plot_util.py

@@ -1,0 +1,141 @@
+import numpy as np
+import math
+
+
+def sqrt(inputArray, scale_min=None, scale_max=None):
+    """Performs sqrt scaling of the input numpy array.
+
+    @type inputArray: numpy array
+    @param inputArray: image data array
+    @type scale_min: float
+    @param scale_min: minimum data value
+    @type scale_max: float
+    @param scale_max: maximum data value
+    @rtype: numpy array
+    @return: image data array
+
+    """
+
+    imageData = np.array(inputArray, copy=True)
+
+    if scale_min is None:
+        scale_min = imageData.min()
+    if scale_max is None:
+        scale_max = imageData.max()
+
+    imageData = imageData.clip(min=scale_min, max=scale_max)
+    imageData = imageData - scale_min
+    indices = np.where(imageData < 0)
+    imageData[indices] = 0.0
+    imageData = np.sqrt(imageData)
+    imageData = imageData / math.sqrt(scale_max - scale_min)
+    return imageData
+
+
+def text_description(ax, d, text, color='w', backgroundcolor='k',
+                     flipped=False, font_size=20):
+    c_vertical =  2.5/20
+    c_horizontal = 1./20
+    if flipped:
+        ax.text(d - d * c_horizontal, d - d * c_vertical, text, color=color,
+                fontsize=20,
+                backgroundcolor=backgroundcolor)
+    else:
+        ax.text(d * c_horizontal, d - d * c_vertical, text, color=color, fontsize=20,
+                backgroundcolor=backgroundcolor)
+def text_description_2(ax, d, text, color='w', backgroundcolor='k',
+                     flipped=False, font_size=20):
+    c_vertical =  4/20
+    c_horizontal = 1./20
+    if flipped:
+        ax.text(d - d * c_horizontal, d - d * c_vertical, text, color=color,
+                fontsize=20,
+                backgroundcolor=backgroundcolor)
+    else:
+        ax.text(d * c_horizontal, d - d * c_vertical, text, color=color, fontsize=20,
+                backgroundcolor=backgroundcolor)
+
+
[…]

### 2020-05-22 material/plot_fitting.py

@@ -5,7 +5,7 @@ Created on Fri Feb 21 11:50:31 2020
 
 @author: Dartoon
 """
-
+#!!! For the Lenstronomy version 1.5.0
 
 import numpy as np
 import astropy.io.fits as pyfits
@@ -18,6 +18,17 @@ sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
 from flux_profile import cr_mask
 import glob
 
+
+# # =============================================================================
+# # To reproduce
+# # =============================================================================
+# In lenstronomy version 1.3.0
+# 1.Replae model_band_plot
+# to change label size:
+# 2.in plot._util.py
+# change text_description()   
+
+
 #%% Find the one with lowest Chisq
 IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
 
@@ -25,12 +36,12 @@ IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS02
 #for i in range(len(IDs)):
 #    print(i, ':', IDs[i])
 #inp = int(input("Which source:\n"))
-inp = 1
+inp = 6
 ID = IDs[inp][2:]
 if ID == 'SDSS1206':
     folder_0 = '_singel_host_run_summary.pkl'
     folder_1 = 'singel_fit'
-if ID == 'HS2209' or ID == 'RXJ1131':
+elif ID == 'HS2209' or ID == 'RXJ1131':
     folder_0 = '_3rd_run_summary.pkl'
     folder_1 = '3rd_fit'    
 else:
@@ -75,7 +86,6 @@ from lenstronomy.ImSim.image_linear_solve import ImageLinearFit
 from lenstronomy.Plots import chain_plot
 import lenstronomy.Plots.chain_plot as out_plot
 #%%
-#!!! For the Lenstronomy version 1.3.0
 kwargs_result, chain_list = fit_result
 if 'e1' in kwargs_result['kwargs_lens'][1].keys():
     g1 = kwargs_result['kwargs_lens'][1]['e1']
@@ -114,51 +124,17 @@ modelPlot.model_plot(ax=axes[0,1])
 modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6)
 modelPlot.subtract_from_data_plot(ax=axes[1, 0], #v_max=1, 
[…]

### 2020-05-22 relation_plots/MM_vz_32QSO.py

@@ -407,7 +407,7 @@ for i in range(100):
     posi=np.random.uniform(16,84)
     b=np.percentile(samples,posi,axis=0)[0]    
     #print b
-    plt.plot(xl, xl*0+xl*b, color="pink", alpha=0.05,linewidth=7.0,zorder=-1)
+    plt.plot(xl, xl*0+xl*b, color="pink", alpha=0.1,linewidth=7.0,zorder=-1+np.random.normal(0,0.02))
 # value=round(b_ml_offset,2)
 #####################
 value,sig=round(b_ml_offset,2),round((np.percentile(samples,84,axis=0)[0]-np.percentile(samples,16,axis=0)[0])/2,2)
@@ -420,7 +420,7 @@ from mstar_inference import mstar_dict
 sys.path.insert(0,'../MBH_estimator')
 from est_MBH import MBH_dic
 sys.path.insert(0,'../share_tools')
-from lens_information import lens_redshift
+from lens_information import lens_redshift, filter_dict
 from read_inference import read_mstar
 
 ma = ['o','d','p','<','>','^','v','P','X' ]
@@ -432,6 +432,13 @@ for i in range(len(h0licow)):
     Mstar = np.log10(read_Mstar[0][0])
     if ID == 'RXJ1131':
         Mstar = np.log10(read_Mstar[0][0] + read_Mstar[1][0] )
+    
+    #Extinction effect based on the Edi's Email:
+    if filter_dict[ID] == 'F814W':
+        Mstar = Mstar + 0.25 * 0.4
+    elif filter_dict[ID] == 'F160W':
+        Mstar = Mstar + 0.1 * 0.4
+        
     MBs = MBH_dic[ID]
 #    plt.scatter(Mstar, MBs[0], c='blue',s=580,marker=".",zorder=100, edgecolors='k')
     plt.scatter(np.log10(1+lens_redshift[ID]),MBs-(m_ml*Mstar+b_ml),c='cornflowerblue',
@@ -458,7 +465,7 @@ for i in range(100):
     posi=np.random.uniform(16,84)
     b=np.percentile(samples,posi,axis=0)[0]    
     #print b
-    plt.plot(xl, xl*0+xl*b, color="cornflowerblue", alpha=0.05,linewidth=7.0,zorder=-1)
[…]

### 2020-05-22 share_tools/read_inference.py

@@ -105,7 +105,7 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
             result.append([round(weighted_value,rod), round(rms_value,rod)])            
     return result
 #result = read_inf('HE0435', prop = 0)
-#print(read_inf('RXJ1131', prop = 4, count_n=[4, 4]))
+# print(read_inf('RXJ1131', prop = 4, count_n=[4, 4]))
 #print(read_inf('HS2209', prop = 1, count_n=8))
 #print(read_inf('HS2209',  count_n=8))    
 
@@ -140,7 +140,7 @@ def read_fnu(ID, count_n=[4, 4]):
 
 
 
-def read_mstar(ID, count_n=[4, 4], rod = 5):
+def read_mstar(ID, count_n=[4, 4]):
     result = []
     org_fnu = {'HE0435' :  [29.32598834079476],
         'RXJ1131' :  [14.808995717960412, 189.5940277253136],
@@ -179,5 +179,50 @@ def read_mstar(ID, count_n=[4, 4], rod = 5):
             m_star = [m_star_org/ org_fnu[ID][j] * new_fnw[j][0], m_star_org/ org_fnu[ID][j] * new_fnw[j][0] * (new_fnw[j][1]/new_fnw[j][0])]
             result.append(m_star)
     return result
-#result = read_mstar('HE0435',  count_n=8)
-#result = read_mstar('RXJ1131',  count_n=8)
+
+def read_slope(ID, prop=0 , count_n=[4, 4], rod = 3):
+    '''
+    Return the slope of the fitting.
+    Parameter
+    --------
+        count_n: if a singel number, combine QSO_mask and PSF_recon. If list, combining them separately.
+    Return
+    --------
+        A sth sth
+    '''
+    if ID == "SDSS1206" :
+        filename = ID+'_singel_host_run_summary.pkl'
+    elif ID == 'HS2209' or ID == 'RXJ1131':
+        filename = ID+'_3rd_run_summary.pkl'
+    else:
+        filename = ID+'_2nd_run_summary.pkl'
+    result = pickle.load(open('/Users/Dartoon/Astro/Projects/lens_host_reconstruction/share_tools/'+filename,'rb'),encoding="latin1")
+    fit_values, chisq, labels, pick_names = result
+    sort_label_type=['subg_2, PSFrecons', ', subg_2, QSOmask', 'subg_3, PSFrecons',', subg_3, QSOmask']
[…]

### 2020-05-22 manuscript/manuscript.tex
Pass ball to TT

@@
 Cristian E. Rusu,$^{12,13,14}$
-Aymeric Galan,$^{15}$}\newauthor
-and et al.
-\\
+Aymeric Galan,$^{15}$}
 \\
@@
 F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
-Switzerland\\
-$^{13}$TBC
+Switzerland
 }
@@
 
-\subsection{Data Preparation and Modelling Setup}
+\subsection{Data Preparation and Modelling Setup}\label{sec:Modelling}
 
@@
 This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
-\pink{Despite that \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, their inferred host surface brightness is computed by collecting the \sersic\ light within a aperture where host was reconstructed; the aperture size is decided by the mask region in the image plane.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
+\pink{Note that \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, and then the inferred host surface brightness is computed by collecting the \sersic\ light within the aperture where host was reconstructed.
+This aperture in the source plane is decided by the mask region in the image plane, thus a smaller mask region could lead the inference of the host brightness fainter.
+For a consistency check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (here) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
 While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.
@@
 
+\pink{In this work, we used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling.
+Then, we used our weighting algorithm introduced in Section~\ref{sec:Modelling} to estimate the systematic uncertainty of our inference and assumed it covers the truth.
+We apply this method to the entire systems to allow the self-consistency within our sample, despite that four systems (HE0435, RXJ1131, WFI2033, and SDSS1206) have been analyzed by H0LiCOW collaboration with slope value provided.
+For a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW's inference.
+The results are the following (here {\it V.S.} H0LiCOW): HE0435~($2.032\pm 0.07$ {\it V.S.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it V.S.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it V.S.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it V.S.} $\sim1.95$).
+These consistent results demonstrate the efficiency of the systematic uncertainty estimates in this work.}
+
 \pink{To estimate the host stellar mass, we use \sersic\ model to measure the total brightness of the host galaxy.
@@
 \pink{Once again, the same approach is adopted in D20, and thus our stellar masses are consistent with the D20's 32 high redshift AGN regarding this point.}
+
 \pink{We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies.
-As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104.
+As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104 through filter F160W.
 For HE1104 the estimated extinction is negative, while for HE0435 and WFI2033 the authors do not report an extinction value because standard extinction laws did not fit the data.
+If we focus on the 13 ellipticals from~\citet{1999ApJ...523..617F}, the total median extinction is -0.03, which justifies our point.
 We interpret this as due to the small effect by dust being overshadowed by chromatic microlensing or variability.}
@@
 
-\pink{The strong lensing can help to extend the measurements of the AGN host to even higher redshift.
+\pink{The strong lensing can even help to extend the measurements of the AGN host to higher redshift.
 It is worth noting that the lensed AGN adopted by this study are adopted from the H0LiCOW project which only focuses on the moment of the peak of the AGN luminosity function.

### 2020-05-22 relation_plots/MM_vz_32QSO.py

@@ -433,11 +433,11 @@ for i in range(len(h0licow)):
     if ID == 'RXJ1131':
         Mstar = np.log10(read_Mstar[0][0] + read_Mstar[1][0] )
     
-    #Extinction effect based on the Edi's Email:
-    if filter_dict[ID] == 'F814W':
-        Mstar = Mstar + 0.25 * 0.4
-    elif filter_dict[ID] == 'F160W':
-        Mstar = Mstar + 0.1 * 0.4
+    # #Extinction effect based on the Edi's Email, but not used.
+    # if filter_dict[ID] == 'F814W':
+    #     Mstar = Mstar + 0.25 * 0.4
+    # elif filter_dict[ID] == 'F160W':
+    #     Mstar = Mstar + 0.1 * 0.4
         
     MBs = MBH_dic[ID]
 #    plt.scatter(Mstar, MBs[0], c='blue',s=580,marker=".",zorder=100, edgecolors='k')
@@ -465,7 +465,7 @@ for i in range(100):
     posi=np.random.uniform(16,84)
     b=np.percentile(samples,posi,axis=0)[0]    
     #print b
-    plt.plot(xl, xl*0+xl*b, color="cornflowerblue", alpha=0.15,linewidth=7.0,zorder=-1+np.random.normal(0,0.02))
+    plt.plot(xl, xl*0+xl*b, color="cornflowerblue", alpha=0.2,linewidth=7.0,zorder=-1+np.random.normal(0,0.02))
 #####################
 value,sig=round(b_ml_offset,2),round((np.percentile(samples,84,axis=0)[0]-np.percentile(samples,16,axis=0)[0])/2,2)
 print(value,sig)
@@ -519,7 +519,7 @@ plt.legend([Bkc, Hkc, SS13, ding_sample],[
 "Intermediate redshift AGNs",
 "$1.2<z<1.7$ AGNs by D20"
 ],scatterpoints=1,numpoints=1,loc=3,prop={'size':22,'family': 'Arial'},ncol=2,handletextpad=0)
-# plt.savefig("MBH-Mstar_vz.pdf")
+plt.savefig("MBH-Mstar_vz.pdf")
 plt.show()
 
 # #%% KS test on the distributions:

### 2020-05-23 manuscript/manuscript.tex
Before re-circulating

@@
 % Keep the title short and informative.
-\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed quasars}
+\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed Quasars}
 
@@
 Takahiro Morishita,$^{11}$
-\pink{
 Cristian E. Rusu,$^{12,13,14}$
-Aymeric Galan,$^{15}$}
+Aymeric Galan,$^{15}$
 \\
@@
 One of the main potential source of systematics is the finite resolution of \hst\ images.
-Even with \pink{the modern} techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution.
+Even with modern techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution.
 This is the goal of this work.
@@
 Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy.
-We summarize the information for the eight systems, including \pink{their redshift, data conditions and the references} in Table~\ref{data_set}.
+We summarize the information for the eight systems, including \pink{their redshift, data properties, and references} in Table~\ref{data_set}.
 Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems.
@@
 We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task.
-Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting \pink{for each system, repeatedly.
-Then, based on the fittings using different choices,} we apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty \pink{level}.
+Building on D20, we adopt a set of  modelling choices and fit each system multiple times.
+Then, we do a statistical analysis of the measurements, and apply a weighting algorithm to derive the final inference and estimate the uncertainty level.
 The modelling choices that we consider include the follows.
@@
 \item To calculate the ray tracing under a higher resolution grid, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
-\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially the model of our host surface brightness is much simplified}.
+\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially with our simplified model of the host light distribution}.
 To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
@@
 Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties.
-\pink{Note that the lens mass slope is fixed in each fitting, and the statistical uncertainty is much smaller than the systematic one.}
+\pink{Note that the slope of the mass profile of the deflector is fixed in each fit, and that the statistical uncertainty is much smaller than the systematic one.}
 
@@
 This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
-\pink{Note that \citet{Ding2017b} used a \sersic\ to model the reconstructions by~\citet{Suyu2013}, and then the inferred host surface brightness is computed by collecting the \sersic\ light within the aperture where host was reconstructed.
-This aperture in the source plane is decided by the mask region in the image plane, thus a smaller mask region could lead the inference of the host brightness fainter.
-For a consistency check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (here) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
+\pink{Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the source plane reconstructions by~\citet{Suyu2013}, based on pixellated grid in the source plane.
+We checked that finite grid effects did not introduce any substantial difference.
+As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
 While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.
@@
 Then, we used our weighting algorithm introduced in Section~\ref{sec:Modelling} to estimate the systematic uncertainty of our inference and assumed it covers the truth.
-We apply this method to the entire systems to allow the self-consistency within our sample, despite that four systems (HE0435, RXJ1131, WFI2033, and SDSS1206) have been analyzed by H0LiCOW collaboration with slope value provided.
-For a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW's inference.
-The results are the following (here {\it V.S.} H0LiCOW): HE0435~($2.032\pm 0.07$ {\it V.S.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it V.S.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it V.S.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it V.S.} $\sim1.95$).
-These consistent results demonstrate the efficiency of the systematic uncertainty estimates in this work.}
+We apply this method to the entire sample to ensure self-consistency within our sample, even though four systems (HE0435, RXJ1131, WFI2033, and SDSS1206) have been analyzed by H0LiCOW collaboration, and have high precision slope measurements available.
+As a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW inference.
+The results are as following (here {\it V.S.} H0LiCOW): HE0435~($2.032\pm 0.07$ {\it V.S.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it V.S.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it V.S.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it V.S.} $1.95\pm0.05$).
+The consistency of the results supports the robustness of the systematic uncertainty estimated in this work.}
 
-\pink{To estimate the host stellar mass, we use \sersic\ model to measure the total brightness of the host galaxy.
-The \sersic\ profile is relatively simple and smooth, which could not capture the clumps in the host galaxy, which lead to the high residuals as appeared in the fittings in Figure~\ref{fig:image_inference}.
+\pink{Following standard practice in galaxy evolution studies, we use a \sersic\ model to describe the surface brightness of the host galaxy.
+The \sersic\ profile is relatively simple and smooth, and cannot capture the clumps in the host galaxy.
+Thus the smoothness of the \sersic\ profile leads to the relatively large residuals shown in Figure~\ref{fig:image_inference}.
 However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same manner.
-Note that the total flux of a galaxy would be relatively settled, once a surface brightness profile is chosen.
-Thus, the inferred host light is considered to be reliable.
+In fact, it is common to have significant residuals when fitting say a \sersic\ profile to a galaxy (e.g.
+D20).
+Although these residuals of course affect the quality of the fit and are reflected in the uncertainties, those are much smaller than our target precision of 0.4 dex.
+The difference in residuals between this work and the H0LiCOW analysis is once again a reflection of the different purposes of the two studies.
+Whereas fitting the host surface brightness of the host to the noise level is important to determine the gravitational potential with sufficient precision to infer the Hubble constant, it is not necessary when the goal is to infer the luminosity of the host.
 }
@@
 For 5/8 systems in our sample we did not have color information, and we used instead a fixed age depending on redshift.
-The lack of color information by necessity increases the error budget in the inferred \mstar.
-\pink{Once again, the same approach is adopted in D20, and thus our stellar masses are consistent with the D20's 32 high redshift AGN regarding this point.}
+The lack of color information is reflected in an increases of the uncertainty in the inferred \mstar.
+\pink{It is important to stress once again, that the main goal of this work is provide an independent test of the D20 measurement.
+Since we are using the same stellar population models, any uncertainty in the models or other stellar population assumptions will cause an absolute change, but those will cancel out when looking at relative consistency between this work and D20.}
 
@@
 For HE1104 the estimated extinction is negative, while for HE0435 and WFI2033 the authors do not report an extinction value because standard extinction laws did not fit the data.
-If we focus on the 13 ellipticals from~\citet{1999ApJ...523..617F}, the total median extinction is -0.03, which justifies our point.
-We interpret this as due to the small effect by dust being overshadowed by chromatic microlensing or variability.}
+If we focus on the 13 ellipticals from~\citet{1999ApJ...523..617F}, the total median extinction is -0.03, which justifies our choice to not apply any correction.
+We interpret the negative values reported in the literature as due to the small effect by dust being overshadowed by chromatic microlensing or variability.}
 
-\pink{Most importantly, the uncertainty of the \mstar\ is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.}
-
-\pink{In this work, some options and assumptions have been made to measure the evolution of \mstar-\mbh.
-For example, a Chabrier IMF was assumed to measure the stellar mass, rather than the Salpeter one.
-To compare our high redshift measurements with the local ones, we adopt the local sample from~\citet{Bennert++2011, H+R04}, rather than the other local ones in the literature.
+\pink{In this work, some assumptions have been made to measure the evolution of \mstar-\mbh.
+For example, a Chabrier IMF was assumed to measure the stellar mass for all samples.
+To compare our high redshift measurements with the local ones, we adopted the local sample from~\citet{Bennert++2011, H+R04}, rather than other samples available in the literature.
 We adopt our own recipes to calibrate the \mbh.
@@
 
+\pink{In summary, considering all random and systematic effects, the uncertainty of \mstar\ relative to that measured by D20 is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.}
+
 \section{Conclusions}\label{sec:con}
 Using eight strongly lensed AGN systems, we presented a new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy.
-We adopt \pink{up-to-date} lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile.
+We adopt state-of-the-art lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile.
 We estimated the \mbh\ of our sample using a set of calibrated single-epoch estimators to assure self-consistency and consistency with the comparison samples taken from the literature.
@@
 
-\pink{The strong lensing can even help to extend the measurements of the AGN host to higher redshift.
-It is worth noting that the lensed AGN adopted by this study are adopted from the H0LiCOW project which only focuses on the moment of the peak of the AGN luminosity function.
-In fact, the observation of \hst\ could even unveil the lensed AGN host of  BRI0952$-$0115 at $z=4.5$.}
+%\pink{Strong lensing can also help to extend the measurements of the AGN hosts to higher redshift.}
 
-In conclusion, lensed AGNs have great potential to extend to study of the \mbh-\mstar\ correlation at even higher redshifts than those considered here.
+In conclusion, lensed AGNs have great potential to extend the study of the \mbh-\mstar\ correlation to higher redshifts than those considered here.
 So far, this kind of work has been limited by sample size.
@@
 Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}}~\citep{Morishita2019} to perform the SED fitting.
-\pink{A set of age grids (up to 3.0 Gyr) are used in this fitting with a constant SFR and a flexible form for star formation histories.
-Note that there is a degeneracy in the age and metallicity; however, this degeneracy has little affect on the \mstar\ inference.
+\pink{A set of age grids (up to 3.0 Gyr) are used in this fit with a constant SFR and a flexible form for star formation histories.
+Note that there is a degeneracy in the age and metallicity; however, this degeneracy has little affect on the \mstar\ inference~\citep{Bell2001}.
 In this work, we fix the metallicity to infer the age, and the uncertainty of the age is not considered.

### 2020-05-26 manuscript/manuscript.tex
Push to Overleaf for the final check by TT

@@
 Strong lensing magnification effectively increases instrumental resolution and thus helps to address this challenge.
-In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope}(\hst) imaging, using the \pink{lens modelling code} \lenstronomy\ to reconstruct the image of the source.
+In this work, we study eight strongly lensed active galactic nuclei (AGN) with deep {\it Hubble Space Telescope} (\hst) imaging, using the lens modelling code \lenstronomy\ to reconstruct the image of the source.
 Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models.
@@
 Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging.
-Combining the new sample with published samples in both local and intermediate \pink{(i.e., $0.35<z\lesssim1.2$)} redshift ranges, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy.
+Combining the new sample with published samples in both local and intermediate (i.e., $0.35<z\lesssim1.2$) redshift ranges, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy.
 In a follow-up paper, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}.
@@
 In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs.
-We adopt a set of extended modelling choices to \pink{estimate the host property uncertainty level and} ensure the accuracy of our measurements.
+We adopt a set of extended modelling choices to estimate the host property uncertainty level and ensure the accuracy of our measurements.
 We compare the inference of our new measurements to the ones that have been modelled by the H0LiCOW collaboration to make the cross-check.
 To obtain an accurate inference of stellar mass, we utilize the multi-band imaging data taken with the \hst\ to obtain the color information for 3/8 of our targets.
-\pink{We assume a typical stellar population for the rest 5/8 of the sample.} Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20.
+We assume a typical stellar population for the rest 5/8 of the sample.
+Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20.
 Given the similar redshift range, the high data quality, and consistent state-of-the-art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.
@@
 Discussion and conclusions are drawn in Sections~\ref{sec:diss} and~\ref{sec:con}.
-Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, \pink{to compute the luminosity distance and estimate the host absolute brightness}.
+Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$, to compute the luminosity distance and estimate the host absolute brightness.
 Magnitudes are presented in the AB system.
@@
 Based on the observational data of these eight systems, \citet{Ding2017a} performed an extensive and realistic simulation exercise using the \hst\ image data and confirmed that the source reconstruction using the lens modelling technique is trustworthy.
-We summarize the information for the eight systems, including \pink{their redshift, data properties, and references} in Table~\ref{data_set}.
+We summarize the information for the eight systems, including their redshift, data properties, and references in Table~\ref{data_set}.
 Besides the imaging data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems.
@@
 The D20 sample includes 32 AGN measurements in the redshift range $1.2<z<1.9$.
-\pink{They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}.} It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.
+They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}.
+It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.
 
@@
 \end {eqnarray}
-\pink{where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:}
+where $\lambda_{\rm line}$ is the reference wavelength of the local continuum luminosities for different emission lines. The following values are adopted:
 %
@@
 $b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
-$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\} ($\AA$).
+$\lambda_{\rm line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}~(\AA).
 %
@@
 For HS2209, the spectrum was observed at the Keck-II Telescope in September 2015.
-We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, \pink{based on \Mgii}.
-The \mbh\ measurements, together with the properties of the board-line, are listed in Table~\ref{mbh}.
+We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, based on \Mgii.
+\pink{The magnification correction on these systems are not self-consistent, which could introduce some systematics on the intrinsic value the $\log(L_\lambda)$.
+However, these errors only have limited effect on the \mbh\ estimations, given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.}
+The \mbh\ measurements, together with the properties of the broad-line, are listed in Table~\ref{mbh}. 
 The uncertainty of the \mbh\ are estimated to be $0.4$~dex.
@@
 WFI2033 & \Mgii & 3960 & 45.19 & 8.38 & (1) \\
-SDSS1206 & \Mgii & 5632 & 45.01 & 8.77 & (2) \\
+SDSS1206 & \Mgii & 5632 & 45.01 & 8.60 & (2) \\
 HE1104 & \Civ & 6004 & 46.18 & 9.03 & (3) \\
 SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
-HS2209 & \Mgii & 3245 & 45.71 & 8.75 & here  \\
+HS2209 & \Mgii & 3245 & 45.71 & 8.45 & here  \\
 HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
@@
 Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project.
-The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light \pink{(via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003})} was a byproduct.
-\citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to \pink{measure the host properties as the non-lensed AGN case}.
+The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light (via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003}) was a byproduct.
+\citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to measure the host properties as the non-lensed AGN case.
 % mimic what is done in non-lensed AGN.
@@
 We remove the background light and cut the clear image data into postage stamp at a suitable size.
-We draw the image mask for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-\pink{middle} panel in each subplot in Figure~\ref{fig:image_inference}.
+We draw the image mask for each system to define the region in which the pixels will be used to calculate the likelihood; see the top-middle panel in each subplot in Figure~\ref{fig:image_inference}.
 
@@
 
-We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task.
+We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task, \pink{in which we use the optimization algorithm based on the ``particle swarm optimizer''}.
 Building on D20, we adopt a set of  modelling choices and fit each system multiple times.
@@
 \item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF.
-To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
-\item To calculate the ray tracing under a higher resolution grid, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
-\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, \pink{especially with our simplified model of the host light distribution}.
-To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
+To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boosting the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~performing the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
+\item To calculate the ray tracing under a higher resolution grid \pink{relative to the pixel sizes in the image plane}, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
+\item Using the lensing imaging alone, it is difficult to constrain the power-law slope, especially with our simplified model of the host light distribution.
+To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Koopmans2006, Auger2010}.
 \end{enumerate}
 
-In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ \pink{(i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits}.
+In general, for one lens system with a number of $N$ initial PSF guesses, we perform in total $N\times12$ (i.e., $2$ by (ii) $\times~2$ by (iii) $\times~3$ by (iv)) fits.
 After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value.
 Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20.
-The weights are defined by:
+\pink{The degrees of freedom is the same for each of the model, which validates this weighting process.} The weights are defined by:
 \begin{eqnarray}
 \label{eq:weights}
-w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
+w_i = {\rm exp} \big(- \alpha \frac{ (\chi_i ^2 - \chi_{\rm best} ^2 )}{2 \chi_{\rm best} ^2} \big),
 \end{eqnarray} 
@@
 \label{eq:alpha}
-\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
+\alpha \frac{ \chi_{i=4} ^2 - \chi_{\rm best} ^2 }{2 \chi_{\rm best} ^2} = 2.
 \end{eqnarray} 
@@
 Our approach uses the relative goodness of fit and ensures that at least 8 sets of best fits are used to estimate the range of systematic uncertainties.
-\pink{Note that the slope of the mass profile of the deflector is fixed in each fit, and that the statistical uncertainty is much smaller than the systematic one.}
+Note that the slope of the mass profile of the deflector is fixed in each fit, and that the statistical uncertainty is much smaller than the systematic one.
 
@@
 This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
-\pink{Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the source plane reconstructions by~\citet{Suyu2013}, based on pixellated grid in the source plane.
-We checked that finite grid effects did not introduce any substantial difference.
-As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.} The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
+Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the \pink{pixellated source reconstructed by~\citet{Suyu2013} in the source plane.} We checked that finite grid effects did not introduce any substantial difference.
+As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.
+The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
 While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.
@@
 There is a satellite galaxy in the north.
-However, as noted by~\citet{Rusu2019}, the satellite galaxy has much smaller mass than the main deflector, thus we ignore its influence on the magnification but only fit its light using a \sersic\ model.
+However, the satellite galaxy has much smaller mass than the main deflector.
+\pink{In addition, there is a galaxy located in the west which could has an impact on the modelling, which also has small effect on the total macro-magnification $(<10\%)$.
+Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy} using a \sersic\ model.
 We select a total of 8 initial PSF stars to model this system.
@@
 
-\pink{It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data.
-Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).}
+It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data.
+Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).
 %zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
@@
 For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level.
-\pink{Some of the residual looks clumpy; however, they do not affect the host property measurements, for more details see Section~\ref{sec:diss}} ; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
-Across all the systems, the lensed arc \pink{feature} can be clearly seen in the \pink{fourth} panel, indicating strong evidence of a detection.
+Some of the residual looks clumpy; however, they do not affect the host property measurements, for more details see Section~\ref{sec:diss} ; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
+Across all the systems, the lensed arc feature can be clearly seen in the fourth panel, indicating strong evidence of a detection.
 In panel (3) and (4), we use white regions to indicate the area where the noise level is boosted.
@@
 Object ID & intrinsic magnitude & magnitude & Host Flux Ratio (to Total) & \reff\ & \sersic\ $n$ & stellar population & $\log (M_{*}$)  \\
- & (source plane) & (image plane) & ( $\%$, \pink{Total = Host + AGN}) & (arcsec) & & age (Gyr) & (M$_{\odot}$) \\ \hline
+ & (source plane) & (image plane) & ( $\%$, Total = Host + AGN) & (arcsec) & & age (Gyr) & (M$_{\odot}$) \\ \hline
 HE0435 & $21.49\substack{+0.40\\-0.29}$ & $18.58\substack{+0.30\\-0.23}$ & $36.0\pm11.1$ & $0.28\pm0.02$ & $2.71\pm0.20$ & $1.50$ & $10.91\substack{+0.12\\-0.16}$ \\
@@
 Column (2)-(6): photometry derived using the imaging data is listed Table~\ref{data_set}.
-Column (7): \pink{adopted age of stellar population with solar metallicity.} Column (8): inferred stellar mass.
+Column (7): adopted age of stellar population with solar metallicity.
+Column (8): inferred stellar mass.
 \end{tablenotes}    
@@
 Then, we adopt stellar population templates to derive the stellar mass.
+\pink{In this step, we infer the color information for the multi-band imaging data taken with the \hst\ in Appendix~\ref{app:a}.
+}
 We study the \mbh-\mstar\ relations and compare our measurements with ones taken from the literature.
@@
 More detailed information is presented in Appendix~\ref{app:HE0435}.
-%Considering that the lensed host light in the image plane can be considered as the subtraction of the AGNs and deflectors light which should be less dependent on the lens model, we expect its magnitude in the image plane could be obtained with higher accuracy.
-Thus, we infer the color of the lensed arcs in the image plane.
-Based a their magnitudes in three bands, we find a 1.5 Gyr stellar population with solar metallicity could well match this color.
-More detailed information is presented in Appendix~\ref{app:HE0435}.}
 
@@
 Based on the \hst\ imaging data through the three filters F814W and F555W and F160W, we adopt the SED estimated by~\citet{Ding2017b} with stellar populations of 3 Gyr and 1.5 Gyr (solar metallicity) for its bulge and disk, respectively.
-\pink{We refer the interested reader to that paper for more details.}
+We refer the interested reader to that paper for more details.
 
@@
 {\bf HE1104 and the other systems} ~ HE1104 has also been observed by \hst\ through the F555W and F814W bands.
-However, given the limited exposure time in these two bands, the lensed arcs is too faint to be detected; thus, we are not able to infer the color of the host for HE1104.
+However, given the limited exposure time in these two bands, the lensed arcs are too faint to be detected; thus, we are not able to infer the color of the host for HE1104.
 No multi-band information is available for the other systems.
@@
 We find that the offset from the local relationship is similar for the two samples.
-Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain $\gamma=1.49\pm0.43$, which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
+Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain \pink{$\gamma=1.05\pm0.44$,} which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
 The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the observed value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
@@
 
-\pink{In this work, we used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling.
+In this work, we used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling.
 Then, we used our weighting algorithm introduced in Section~\ref{sec:Modelling} to estimate the systematic uncertainty of our inference and assumed it covers the truth.
@@
 As a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW inference.
-The results are as following (here {\it V.S.} H0LiCOW): HE0435~($2.032\pm 0.07$ {\it V.S.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it V.S.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it V.S.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it V.S.} $1.95\pm0.05$).
-The consistency of the results supports the robustness of the systematic uncertainty estimated in this work.}
+The results are the following (here {\it v.s.} H0LiCOW, \pink{the error bars are the $1-\sigma$ level}): HE0435~($2.032\pm 0.07$ {\it v.s.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it v.s.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it v.s.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it v.s.} $1.95\pm0.05$).
+The consistency of the results supports the robustness of the systematic uncertainty estimated in this work.
 
-\pink{Following standard practice in galaxy evolution studies, we use a \sersic\ model to describe the surface brightness of the host galaxy.
+Following standard practice in galaxy evolution studies, we use a \sersic\ model to describe the surface brightness of the host galaxy.
 The \sersic\ profile is relatively simple and smooth, and cannot capture the clumps in the host galaxy.
 Thus the smoothness of the \sersic\ profile leads to the relatively large residuals shown in Figure~\ref{fig:image_inference}.
-However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same manner.
-In fact, it is common to have significant residuals when fitting say a \sersic\ profile to a galaxy (e.g.
-D20).
-Although these residuals of course affect the quality of the fit and are reflected in the uncertainties, those are much smaller than our target precision of 0.4 dex.
+However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same \pink{methodology}.
+\pink{Note that, the methodology has to be consistent between lensed and unlensed AGNs, since the use of a different host model may introduce systematic errors.} In fact, it is common to have significant residuals when fitting say a \sersic\ profile to a galaxy (e.g., D20).
+These residuals of course affect the quality of the fit \pink{and could increase the systematics.
+However, these systematics} are much smaller than our target precision of 0.4 dex.
 The difference in residuals between this work and the H0LiCOW analysis is once again a reflection of the different purposes of the two studies.
-Whereas fitting the host surface brightness of the host to the noise level is important to determine the gravitational potential with sufficient precision to infer the Hubble constant, it is not necessary when the goal is to infer the luminosity of the host.
-}
+Whereas fitting the host surface brightness to the noise level is important to determine the gravitational potential with sufficient precision to infer the Hubble constant, it is not necessary when the goal is to infer the luminosity of the host.
 
@@
 The lack of color information is reflected in an increases of the uncertainty in the inferred \mstar.
-\pink{It is important to stress once again, that the main goal of this work is provide an independent test of the D20 measurement.
-Since we are using the same stellar population models, any uncertainty in the models or other stellar population assumptions will cause an absolute change, but those will cancel out when looking at relative consistency between this work and D20.}
+It is important to stress once again, that the main goal of this work is provide an independent test of the D20 measurement.
+Since we are using the same stellar population models, any uncertainty in the models or other stellar population assumptions will cause an absolute change, but those will cancel out when looking at relative consistency between this work and D20.
 
-\pink{We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies.
+We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies.
 As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104 through filter F160W.
@@
 If we focus on the 13 ellipticals from~\citet{1999ApJ...523..617F}, the total median extinction is -0.03, which justifies our choice to not apply any correction.
-We interpret the negative values reported in the literature as due to the small effect by dust being overshadowed by chromatic microlensing or variability.}
+We interpret the negative values reported in the literature as due to the small effect by dust being overshadowed by chromatic microlensing or variability.
 
-\pink{In this work, some assumptions have been made to measure the evolution of \mstar-\mbh.
+In this work, some assumptions have been made to measure the evolution of \mstar-\mbh.
 For example, a Chabrier IMF was assumed to measure the stellar mass for all samples.
@@
 However, since the entire sample is self-consistent, a different assumption would only shifts the global \mstar-\mbh\ together, leaving the offset value and the evolution conclusion the same.
-More details can be found in D20, Section 6.}
+More details can be found in D20, Section 6.
 
-\pink{In summary, considering all random and systematic effects, the uncertainty of \mstar\ relative to that measured by D20 is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.}
+In summary, considering all random and systematic effects, the uncertainty of \mstar\ relative to that measured by D20 is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.
 
@@
 \section*{Acknowledgements}
-\pink{We are grateful to Frederic Courbin, Leon Koopmans for useful comments
-and suggestions that improved this manuscript.}
+We are grateful to Frederic Courbin, Leon Koopmans for useful comments
+and suggestions that improved this manuscript.
 
@@
 acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
-\pink{This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
-SHS thanks the Max Planck Society for support through the Max Planck Research Group.}
+This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 787886).
+SHS thanks the Max Planck Society for support through the Max Planck Research Group.
 
-\pink{This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib} and standard Python libraries.}
+This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib} and standard Python libraries.
 
@@
 
-\section{Estimate of the color of the host}
+\section{Estimate of the color of the host}\label{app:a}
 In this section, we describe the details of how we select the stellar population of the host used in the computation of the stellar mass estimate.
@@
 Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}}~\citep{Morishita2019} to perform the SED fitting.
-\pink{A set of age grids (up to 3.0 Gyr) are used in this fit with a constant SFR and a flexible form for star formation histories.
+A set of age grids (up to 3.0 Gyr) are used in this fit with a constant SFR and a flexible form for star formation histories.
 Note that there is a degeneracy in the age and metallicity; however, this degeneracy has little affect on the \mstar\ inference~\citep{Bell2001}.
 In this work, we fix the metallicity to infer the age, and the uncertainty of the age is not considered.
-Finally, a} stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
+Finally, a stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
 This stellar population is used to estimate the host stellar mass.
@@
 Unfortunately, the  F125W data are too shallow to robustly detect the host.
-Thus, we does not use the F125W band for the SED fitting.
+Thus, we do not use the F125W band for the SED fitting.
 Using four-band photometry, we find a stellar population of 0.625 Gyr age provides a good match to the colors, as shown in Figure~\ref{fig:app_WFI2033}-(e).

### 2020-05-26 2_WFI2033/model/3_read_result.py

@@ -14,7 +14,7 @@ import pickle
 from matplotlib.colors import LogNorm
 import copy
 import sys
-sys.path.insert(0,'/Users/Dartoon/Astro/my_code/py_tools/')
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
 from flux_profile import cr_mask
 
 

### 2020-05-26 2_WFI2033/model/3_summary.py

@@ -119,8 +119,6 @@ if label0 != label1 or bars!= label0:
     raise ValueError("The labels is wrong for some reason")
 color = ['green', 'orange']
 
-color = ['green', 'orange']
-
 #count_n =len(labels) * 10 /100
 chisq = [float(chisq[i]) for i in range(len(chisq))]
 sort_chisq = np.argsort(np.asarray(chisq))    

### 2020-05-26 MBH_estimator/est_MBH.py

@@ -32,15 +32,15 @@ def cal_MBH(line, L, FWHM):
         b = 0.5
         logM=a + b*(L-44.) +2 * np.log10(FWHM/1000.)
     if line == 'Mgii':
-        #Dominique recipe. (note L - 5.15.) for his calbration:
-        a, b = 7.13, 0.5 # 1.51 * FWHM_term
-        logM=a + b*(L-44.) + 1.51 * np.log10(FWHM/1000.)
+        # #Dominique recipe. (note L - 5.15.) for his calbration:
+        # a, b = 7.13, 0.5 # 1.51 * FWHM_term
+        # logM=a + b*(L-44.) + 1.51 * np.log10(FWHM/1000.)
 #        #Shen 2011 recipe. L - 5.15 for correction.:
 #        a, b = 6.74, 0.62
 #        logM=a + b*(L-44.) + 2.0 * np.log10(FWHM/1000.)
 #        
-#        a, b = 6.623, 0.47  #Final adopted receipe
-#        logM=a + b*(L-44.) +2 * np.log10(FWHM/1000.)
+        a, b = 6.623, 0.47  #Final adopted receipe
+        logM=a + b*(L-44.) +2 * np.log10(FWHM/1000.)
 #        a, b = 7.13, 0.5 #Dominique;s paper
 #        logM=a + b*(L-44.) + 1.51 * np.log10(FWHM/1000.)
 #        a, b = 0.74, 0.62 #Shen 2011 recipe

### 2020-05-26 relation_plots/MM_vz_32QSO.py

@@ -458,14 +458,14 @@ samples = sampler.chain[:, 50:, :].reshape((-1, ndim))
 b_ml_offset, _ =np.percentile(samples, 50,axis=0)
 #print "lnlike=",lnlike(theta=[b_ml_offset, sint_mid],x=x, y=y, yerr=yerr)
 xl = np.linspace(0, 5, 100)
-plt.plot(xl, xl*0+xl*b_ml_offset, color="blue", linewidth=4.0,zorder=0)
+plt.plot(xl, xl*0+xl*b_ml_offset, color="blue", linewidth=3.0,zorder=0)
 b=np.percentile(samples,50,axis=0)[0]
 #print samples[:,1][samples[:,0]==find_n(samples[:,0],m)]
 for i in range(100):
     posi=np.random.uniform(16,84)
     b=np.percentile(samples,posi,axis=0)[0]    
     #print b
-    plt.plot(xl, xl*0+xl*b, color="cornflowerblue", alpha=0.2,linewidth=7.0,zorder=-1+np.random.normal(0,0.02))
+    plt.plot(xl, xl*0+xl*b, color="cornflowerblue", alpha=0.2,linewidth=7.0,zorder=-3+np.random.normal(0,0.02))
 #####################
 value,sig=round(b_ml_offset,2),round((np.percentile(samples,84,axis=0)[0]-np.percentile(samples,16,axis=0)[0])/2,2)
 print(value,sig)

### 2020-05-26 share_tools/read_inference.py

@@ -52,16 +52,18 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
             picks = []
         else:
             picks = [4]
-    elif prop == 3: #AGN flux
+    elif prop == 3: #AGN flux source
         if 'Disk' in pick_names[2]:
             picks = [3]
         else:
             picks = [2]
-    elif prop == 4 :  #Flux image plane
+    elif prop == 4 :  #Host Flux image plane
         if 'Disk' in pick_names[2]:
             picks = [1,2]
         else:
             picks = [1]            
+    elif prop == 5: #AGN flux image
+            picks = [0]            
 #    print(ID, pick_names)
     result = []
 #    print(filename)
@@ -104,7 +106,7 @@ def read_inf(ID, prop=0 , count_n=[4, 4], rod = 3):
             rms_value = np.sqrt(np.sum((np.array(fit_value_m)-weighted_value)**2*weight) / np.sum(weight))
             result.append([round(weighted_value,rod), round(rms_value,rod)])            
     return result
-#result = read_inf('HE0435', prop = 0)
+# result = read_inf('HE0435', prop = 0)
 # print(read_inf('RXJ1131', prop = 4, count_n=[4, 4]))
 #print(read_inf('HS2209', prop = 1, count_n=8))
 #print(read_inf('HS2209',  count_n=8))    
@@ -225,4 +227,4 @@ def read_slope(ID, prop=0 , count_n=[4, 4], rod = 3):
         rms_value = np.sqrt(np.sum((np.array(fit_value_m)-weighted_value)**2*weight) / np.sum(weight))
         result.append([round(weighted_value,rod), round(rms_value,rod)])            
     return result
-print(read_slope('HE0435', count_n=[4, 4]))
+# print(read_slope('HE0435', count_n=[4, 4]))

### 2020-05-26 manuscript/manuscript.tex
Before submit to MN

@@
 % Keep the title short and informative.
-\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed Quasars}
+\title[Mass correlations of lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed Quasars}
 
@@
 We adopt a set of extended modelling choices to estimate the host property uncertainty level and ensure the accuracy of our measurements.
-We compare the inference of our new measurements to the ones that have been modelled by the H0LiCOW collaboration to make the cross-check.
+We compare the inference of our new measurements to the ones that have been modelled by the H0LiCOW collaboration to make a cross-check.
 To obtain an accurate inference of stellar mass, we utilize the multi-band imaging data taken with the \hst\ to obtain the color information for 3/8 of our targets.
-We assume a typical stellar population for the rest 5/8 of the sample.
+We assume a typical stellar population for the rest 5/8 of the sample, consistent with D20.
 Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20.
-Given the similar redshift range, the high data quality, and consistent state-of-the-art techniques, this sample of lensed AGN provides an excellent verification of the D20 results.
+Given the similar redshift range, the high data quality, and consistent techniques, this sample of lensed AGN provides an excellent validation of the D20 results.
 
@@
 We derived the line properties from the spectrum using the same approach as~\citet{Sluse2012}, based on \Mgii.
-\pink{The magnification correction on these systems are not self-consistent, which could introduce some systematics on the intrinsic value the $\log(L_\lambda)$.
-However, these errors only have limited effect on the \mbh\ estimations, given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.}
 The \mbh\ measurements, together with the properties of the broad-line, are listed in Table~\ref{mbh}. 
 The uncertainty of the \mbh\ are estimated to be $0.4$~dex.
+\pink{We note that the magnification correction for these systems are not fully self-consistent, in the sense that the magnification is slightly different for the host galaxy light and the black holes mass.
+This difference could  in principle introduce some systematics on the correlations.
+However, these errors are smaller than the calibration error on \mbh (0.4 dex), given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.}
 
@@
 
-We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task, \pink{in which we use the optimization algorithm based on the ``particle swarm optimizer''}.
+We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task, \pink{using the ``particle swarm optimizer'' mode}.
 Building on D20, we adopt a set of  modelling choices and fit each system multiple times.
@@
 Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20.
-\pink{The degrees of freedom is the same for each of the model, which validates this weighting process.} The weights are defined by:
+\pink{The degrees of freedom are the same for each of the model, ensuring that the weighting scheme is internally self-consistent.} The weights are defined by:
 \begin{eqnarray}
@@
 WFI2033 is the last quadruply lensed system in our sample whose lens model has been previously investigated \citep{Rusu2019}.
-There is a satellite galaxy in the north.
+There is a satellite galaxy North of the lens.
 However, the satellite galaxy has much smaller mass than the main deflector.
-\pink{In addition, there is a galaxy located in the west which could has an impact on the modelling, which also has small effect on the total macro-magnification $(<10\%)$.
+\pink{In addition, there is a galaxy west of the main target, which also has a small effect on the total macro-magnification $(<10\%)$.
 Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy} using a \sersic\ model.
@@
 Then, we adopt stellar population templates to derive the stellar mass.
-\pink{In this step, we infer the color information for the multi-band imaging data taken with the \hst\ in Appendix~\ref{app:a}.
+\pink{For this step, we infer the color information for the multi-band imaging data taken with \hst\ in Appendix~\ref{app:a}.
 }
@@
 The lensed AGN systems analyzed in this work were selected for time-delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy.
-This is a different selection function that adopted by D20.
+This is a different selection function than that used by D20.
 It is thus reassuring that the two samples present the same apparent evolution.
@@
 
-In this work, we used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling.
+We used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling.
 Then, we used our weighting algorithm introduced in Section~\ref{sec:Modelling} to estimate the systematic uncertainty of our inference and assumed it covers the truth.
@@
 However, given the pace of discovery of lensed quasars in imaging and spectroscopic surveys ~\citep[e.g.,][]{Oguri2010, Agn++15,Mor++16,Sch++16,Ost++17,Tre++18, Ang++18, Lem++20}, the samples of lensed AGNs with hosts that can be recovered with high fidelity is likely to continue to grow in wide field imaging and spectroscopic surveys.
-The forthcoming launch of the {\it James Webb Space Telescope} and the first light of adaptive optics-assisted extremely large telescopes may provide high-quality imaging data of AGNs at higher redshift (up to $z\sim7$).
+The forthcoming launch of the {\it James Webb Space Telescope} and the first light of adaptive optics-assisted extremely large telescopes may provide high-quality imaging data of AGNs up to the highest redshift at which they have been discovered.
 
@@
 We are grateful to Frederic Courbin, Leon Koopmans for useful comments
-and suggestions that improved this manuscript.
+and suggestions that improved this manuscript. We thank John Silverman and Vardha Bennert for many conversations on the topic of galaxy and black hole co-evolution.
 

### 2020-05-26 manuscript/manuscript.tex
remove pink color

@@
 The uncertainty of the \mbh\ are estimated to be $0.4$~dex.
-\pink{We note that the magnification correction for these systems are not fully self-consistent, in the sense that the magnification is slightly different for the host galaxy light and the black holes mass.
+We note that the magnification correction for these systems are not fully self-consistent, in the sense that the magnification is slightly different for the host galaxy light and the black holes mass.
 This difference could  in principle introduce some systematics on the correlations.
-However, these errors are smaller than the calibration error on \mbh (0.4 dex), given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.}
+However, these errors are smaller than the calibration error on \mbh (0.4 dex), given that the virial relations depend on roughly the square root of the $\log(L_\lambda)$.
 
@@
 
-We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task, \pink{using the ``particle swarm optimizer'' mode}.
+We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task, using the ``particle swarm optimizer'' mode.
 Building on D20, we adopt a set of  modelling choices and fit each system multiple times.
@@
 To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boosting the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~performing the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
-\item To calculate the ray tracing under a higher resolution grid \pink{relative to the pixel sizes in the image plane}, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
+\item To calculate the ray tracing under a higher resolution grid relative to the pixel sizes in the image plane, we choose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
 \item Using the lensing imaging alone, it is difficult to constrain the power-law slope, especially with our simplified model of the host light distribution.
@@
 Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20.
-\pink{The degrees of freedom are the same for each of the model, ensuring that the weighting scheme is internally self-consistent.} The weights are defined by:
+The degrees of freedom are the same for each of the model, ensuring that the weighting scheme is internally self-consistent.
+The weights are defined by:
 \begin{eqnarray}
@@
 This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
-Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the \pink{pixellated source reconstructed by~\citet{Suyu2013} in the source plane.} We checked that finite grid effects did not introduce any substantial difference.
+Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the pixellated source reconstructed by~\citet{Suyu2013} in the source plane.
+We checked that finite grid effects did not introduce any substantial difference.
 As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.
@@
 However, the satellite galaxy has much smaller mass than the main deflector.
-\pink{In addition, there is a galaxy west of the main target, which also has a small effect on the total macro-magnification $(<10\%)$.
-Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy} using a \sersic\ model.
+In addition, there is a galaxy west of the main target, which also has a small effect on the total macro-magnification $(<10\%)$.
+Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy using a \sersic\ model.
 We select a total of 8 initial PSF stars to model this system.
@@
 Then, we adopt stellar population templates to derive the stellar mass.
-\pink{For this step, we infer the color information for the multi-band imaging data taken with \hst\ in Appendix~\ref{app:a}.
-}
+For this step, we infer the color information for the multi-band imaging data taken with \hst\ in Appendix~\ref{app:a}.
 We study the \mbh-\mstar\ relations and compare our measurements with ones taken from the literature.
@@
 We find that the offset from the local relationship is similar for the two samples.
-Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain \pink{$\gamma=1.05\pm0.44$,} which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
+Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain $\gamma=1.05\pm0.44$, which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
 The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the observed value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
@@
 As a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW inference.
-The results are the following (here {\it v.s.} H0LiCOW, \pink{the error bars are the $1-\sigma$ level}): HE0435~($2.032\pm 0.07$ {\it v.s.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it v.s.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it v.s.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it v.s.} $1.95\pm0.05$).
+The results are the following (here {\it v.s.} H0LiCOW, the error bars are the $1-\sigma$ level): HE0435~($2.032\pm 0.07$ {\it v.s.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it v.s.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it v.s.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it v.s.} $1.95\pm0.05$).
 The consistency of the results supports the robustness of the systematic uncertainty estimated in this work.
@@
 Thus the smoothness of the \sersic\ profile leads to the relatively large residuals shown in Figure~\ref{fig:image_inference}.
-However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same \pink{methodology}.
-\pink{Note that, the methodology has to be consistent between lensed and unlensed AGNs, since the use of a different host model may introduce systematic errors.} In fact, it is common to have significant residuals when fitting say a \sersic\ profile to a galaxy (e.g., D20).
-These residuals of course affect the quality of the fit \pink{and could increase the systematics.
-However, these systematics} are much smaller than our target precision of 0.4 dex.
+However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same methodology.
+Note that, the methodology has to be consistent between lensed and unlensed AGNs, since the use of a different host model may introduce systematic errors.
+In fact, it is common to have significant residuals when fitting say a \sersic\ profile to a galaxy (e.g., D20).
+These residuals of course affect the quality of the fit and could increase the systematics.
+However, these systematics are much smaller than our target precision of 0.4 dex.
 The difference in residuals between this work and the H0LiCOW analysis is once again a reflection of the different purposes of the two studies.

### 2020-08-10 manuscript/manuscript.tex
Receive referee report and before sec editing
Git push before sharing to TT

@@
 \newcommand{\red}[1]{{ \textcolor{red}{#1}}}
-\newcommand{\blue}[1]{{ \textcolor{blue}{#1}}}
+\newcommand{\blue}[1]{{\bf \textcolor{blue}{#1}}}
 \newcommand{\pink}[1]{{\textcolor{magenta}{#1}}}
@@
 \\
-\\
 % List of institutions
@@
 \mbh\ are estimated from broad emission lines using standard methods.
-Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolves over cosmic time.
+Our results are in good agreement with recent work based on non-lensed AGN, \blue{demonstrating the great potential of using strongly lensed AGNs to extend the study of the correlations to higher redshifts.}
 At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN.
@@
 The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}.
-Cosmological simulations of structure formation are able to reproduce the local tight relation based on physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
+Cosmological simulations of structure formation are able to reproduce the local tight relation based on {\bf the} physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
 However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic mergers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
@@
 As the samples of AGN grow to increase statistical power, it is very important to make sure that systematics do not dominate the error budget.
-One of the main potential source of systematics is the finite resolution of \hst\ images.
+One of the main potential {\bf sources} of systematics is the finite resolution of \hst\ images.
 Even with modern techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution.
@@
 Therefore, we use it primarily to verify the results of D20.
-The D20 sample includes 32 AGN measurements in the redshift range $1.2<z<1.9$.
+The D20 sample includes 32 AGN measurements in the redshift range {\bf of} $1.2<z<1.9$.
 They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}.
@@
 The \mbh\ measurements, together with the properties of the broad-line, are listed in Table~\ref{mbh}. 
-The uncertainty of the \mbh\ are estimated to be $0.4$~dex.
+The uncertainty of the \mbh\ {\bf is} estimated to be $0.4$~dex.
 We note that the magnification correction for these systems are not fully self-consistent, in the sense that the magnification is slightly different for the host galaxy light and the black holes mass.
@@
 The goal of those models was strong lens time-delay cosmography~\citep{Refsdal1966, Treu2016}, and the reconstruction of the host galaxy light (via pixellated distribution~\citep{Suy++06} or shapelets~\citep{Refregier2003}) was a byproduct.
-\citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131), and then fitted a simply parametrized surface brightness profile to the reconstruction to measure the host properties as the non-lensed AGN case.
+\citet{Ding2017b} used those reconstructions for two of the systems (HE0435 and RXJ1131) and then fitted a simply parametrized surface brightness profile to the reconstruction to measure the host properties as the non-lensed AGN case.
 % mimic what is done in non-lensed AGN.
@@
 In this work, in order to reproduce more closely and uniformly what is
-done in non-lensed AGN, we develop a strategy to obtain a one step
+done in non-lensed AGN, we develop a strategy to obtain a one-step
 measurement of the host galaxy light described by a \sersic\ surface
@@
 For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile.
-We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate multiple components.
+We start with a single \sersic\ profile and consider {\bf using} two \sersic\ if any significant residual {\bf indicates} multiple components.
 For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been shown in~\citet{Ding2017a} that choosing this prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}.
@@
 After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value.
-Since there is no evidence of a better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combine their best-fit results based on the weighting algorithm introduced by D20.
+Since there is no evidence of better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then {\bf combined} their best-fit results based on the weighting algorithm introduced by D20.
 The degrees of freedom are the same for each of the model, ensuring that the weighting scheme is internally self-consistent.
@@
 
-\subsection{Photometry Inference}\label{sec:photometry}
-In this subsection, we describe the details of the fitting for each system and present the inference of the photometry of the host galaxy.
-
-\subsubsection{HE0435}\label{subsec:HE0435}
-We follow the approach described in the previous section.
-We select 5 isolated stars in this field as initial PSFs to input to the fitting, for a total of 60 fits.
-Based on the top-eight choices, we perform the weighting algorithm and measure the host flux, host-to-total flux ratio, effective radius and \sersic\ index.
-The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
-
-The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a).
-Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}.
-This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as a \sersic\ profile, which is relatively simple and smooth compared to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10, Suyu2012} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}.
-The smooth features of \sersic\ profile can not capture the clumps in the host galaxy, such as the star-forming regions.
-Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e.
-the quantity commonly measured in the literature for non-lensed samples.
-
-As a cross-check, we compare our host magnitude to the inference of HE0435 by~\citet{Ding2017b}.
-They inferred the \sersic\ magnitude by fitting to the pixelized host galaxy as reconstructed by~\citet{Wong2017}.
-The host magnitude measured by~\citet{Ding2017b} is: $mag = 21.75 \pm 0.13$.
-%, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
-The results are in excellent agreement with the measurement reported here, i.e. $mag = 21.50 \pm 0.35$.
-
-\subsubsection{RXJ1131}
-A lens model of RXJ1131 based on ACS/F814W data has been presented by~\citet{Suyu2013}.
-The host galaxy of this system is lensed to an extended arc.
-A clear bulge and disk component can be identified.
-Thus, we describe the host galaxy with two \sersic\ profiles with index values $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge.
-In addition, following~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and describe it as a SIS and \sersic\ for its mass and light, respectively.
-
-The photometry of the RXJ1131 host galaxy is fitted with a set of 4 initial PSFs.
-The results are summarized in Table~\ref{tab:host_measure}, with the best-fit result shown in Figure~\ref{fig:image_inference}-(b).
-
-We also compare our measurement to the previous reconstructions by \citet{Ding2017b}.
-Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$.
-The results are in excellent agreement with our inferred bulge magnitude ($21.80\pm0.21$)   shown in Table~\ref{tab:host_measure}.
-However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}.
-This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
-Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the pixellated source reconstructed by~\citet{Suyu2013} in the source plane.
-We checked that finite grid effects did not introduce any substantial difference.
-As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.
-The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
-While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.
-
-\subsubsection{WFI2033}
-WFI2033 is the last quadruply lensed system in our sample whose lens model has been previously investigated \citep{Rusu2019}.
-There is a satellite galaxy North of the lens.
-However, the satellite galaxy has much smaller mass than the main deflector.
-In addition, there is a galaxy west of the main target, which also has a small effect on the total macro-magnification $(<10\%)$.
-Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy using a \sersic\ model.
-We select a total of 8 initial PSF stars to model this system.
-
-The final inference results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c).
-We compare our inference to the previously reconstructed host galaxies.
-Modelling the reconstructed host by~\citet{Rusu2019}, (i.e., the Figure~4 bottom-right plane therein) as a \sersic\ profile, we infer the $mag = 21.98 \pm 0.15$, which is very consistent to our inference (i.e., $mag = 21.78 \pm 0.25$).
-
-\subsubsection{SDSS1206}
-SDSS1206 is a unique system -- the AGN is doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged.
-Following~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbation.
-Moreover, as noted by~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible \citep[see Figure~1 in][]{Birrer2019}.
-We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids.
-It is worth noting that we are using the same imaging modelling tool as~\citet{Birrer2019}.
-
-Due to the limited number of stars in the field of view, there are only 2 stars available as initial PSF.
-To expand the volume of modelling options, we also take the stack of the two bright stars as derived by~\citet{Birrer2019}, as a third initial PSF.
-We find a visible residuals at the fitted lensed arcs region using a single \sersic\ model as host.
-However, a double \sersic\ model does not significantly improve the goodness of fit.
-Thus, we adopt the single \sersic\ model in our final inference.
-Our inferred results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(d).
-
-\subsubsection{HE1104}
-HE1104 is a typical doubly imaged quasar.
-We have selected in total of 5 initial PSFs to perform the fit.
-There is an object at the northeast.
-However, since we do not know its redshift and considering it is further away from the lens we do not model it explicitly but just mask it out in the fitting.
-
-The inference is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
-the lensed arcs can be clearly seen from the bottom-left panel, indicating that the host galaxy is well detected.
-
-It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data.
-Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).
-%zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
-%HE1104 mag:  21.25 (AB)  --> 20.00 (Vega)
-
-\subsubsection{SDSS0246}
-Having been imaged with WFC3-UVIS/F814W, the resolution of the data for this system (together with the remaining two systems) is much higher than for those imaged in the IR, with a drizzled pixel scale of $0\farcs{}03$.
-However, the arcs are much fainter compared with those of other systems imaged in the IR band.
-As a result, fewer pixels with signal are available for the fit than for other systems.
-Nevertheless, the host inference is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure} (3 initial PSF guesses were adopted).
-
-\subsubsection{HS2209}
-HS2209 was imaged by \hst\ during two visits ($vis05$ and $vis06$) at different orientations.
-We modelled the two visits separately and recovered mutually consistent host galaxy magnitudes.
-However, we found that the data from {\it vis06} can be modelled with smaller residuals; thus the inference based on {\it vis06} was adopted as our best estimate (using 7 initial PSF stars), as listed in Table~\ref{tab:host_measure}.
-The inference for this system is summarized in Figure~\ref{fig:image_inference}-(g).
-
-\subsubsection{HE0047}
-HE0047 is the most challenging system in our sample with the lowest SNR of the lensed arcs.
-The results, based on 3 initial PSFs, are summarized in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
-The host magnitude of the HE0047 system has a relatively large uncertainty as reflected in the error bars.
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_inference.png}}&
-\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_inference.png}}\\
-\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_inference.png}}&
-\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_inference.png}}\\
-\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_inference.png}}&
-\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_inference.png}}\\
-\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_inference.png}}&
-\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_inference.png}}\\
-\end{tabular}
-\caption{\label{fig:image_inference} 
-Illustrations of the inference using the best-fit lens model for each system using the AGN center noise level boosted approach.
-For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level.
-Some of the residual looks clumpy; however, they do not affect the host property measurements, for more details see Section~\ref{sec:diss} ; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
-Across all the systems, the lensed arc feature can be clearly seen in the fourth panel, indicating strong evidence of a detection.
-In panel (3) and (4), we use white regions to indicate the area where the noise level is boosted.
-}
-\end{figure*}
+\blue{The inferred photometry of the host galaxy for all the eight systems are listed in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
+The detailed information of the fitting process for each system is in Appendix~\ref{sec:photometry}.}
 
@@
  & (source plane) & (image plane) & ( $\%$, Total = Host + AGN) & (arcsec) & & age (Gyr) & (M$_{\odot}$) \\ \hline
-HE0435 & $21.49\substack{+0.40\\-0.29}$ & $18.58\substack{+0.30\\-0.23}$ & $36.0\pm11.1$ & $0.28\pm0.02$ & $2.71\pm0.20$ & $1.50$ & $10.91\substack{+0.12\\-0.16}$ \\
-RXJ1131$_{\rm bulge}$ & $21.80\substack{+0.23\\-0.19}$ & $18.70\substack{+0.07\\-0.06}$ & $7.1\pm1.4$ & $0.13\pm0.02$ & fix to 4 & $3.00$ & $10.39\substack{+0.08\\-0.09}$ \\
-RXJ1131$_{\rm disk}$ & $19.33\substack{+0.17\\-0.15}$ & $17.14\substack{+0.08\\-0.07}$ & $69.2\pm10.1$ & $0.90\pm0.06$ & fix to 1 & $1.50$ & $11.08\substack{+0.06\\-0.07}$ \\
-WFI2033 & $21.78\substack{+0.28\\-0.23}$ & $19.07\substack{+0.35\\-0.26}$ & $19.6\pm4.5$ & $0.28\pm0.02$ & $0.52\pm0.01$ & $0.625$ & $10.51\substack{+0.09\\-0.11}$ \\
-SDSS1206 & $21.31\substack{+0.23\\-0.19}$ & $18.30\substack{+0.05\\-0.05}$ & $33.3\pm6.4$ & $0.11\pm0.02$ & $4.57\pm0.53$ & $0.625$ & $10.77\substack{+0.08\\-0.09}$ \\
-HE1104 & $21.25\substack{+0.16\\-0.14}$ & $19.16\substack{+0.02\\-0.02}$ & $14.0\pm2.0$ & $0.27\pm0.02$ & $1.05\pm0.04$ & $0.625$ & $11.05\substack{+0.06\\-0.07}$ \\
-SDSS0246 & $23.44\substack{+0.28\\-0.22}$ & $20.85\substack{+0.08\\-0.07}$ & $4.0\pm0.9$ & $0.44\pm0.08$ & $4.96\pm0.08$ & $0.625$ & $10.75\substack{+0.09\\-0.11}$ \\
-HS2209 & $20.72\substack{+0.26\\-0.21}$ & $19.20\substack{+0.04\\-0.04}$ & $12.5\pm2.7$ & $1.96\pm1.28$ & $3.15\pm1.40$ & $1.00$ & $11.04\substack{+0.08\\-0.10}$ \\
-HE0047 & $22.92\substack{+0.48\\-0.33}$ & $20.37\substack{+0.20\\-0.17}$ & $2.3\pm0.8$ & $0.32\pm0.15$ & $4.18\pm0.75$ & $0.625$ & $10.91\substack{+0.13\\-0.19}$ \\
+HE0435 & $21.49\substack{+0.40\\-0.29}$ & $18.58\substack{+0.30\\-0.23}$ & $36.0\pm11.1$ & $0.28\pm0.02$ & $2.71\pm0.20$ & $1.50$ & $10.91$ \\
+RXJ1131$_{\rm bulge}$ & $21.80\substack{+0.23\\-0.19}$ & $18.70\substack{+0.07\\-0.06}$ & $7.1\pm1.4$ & $0.13\pm0.02$ & fix to 4 & $3.00$ & $10.39$ \\
+RXJ1131$_{\rm disk}$ & $19.33\substack{+0.17\\-0.15}$ & $17.14\substack{+0.08\\-0.07}$ & $69.2\pm10.1$ & $0.90\pm0.06$ & fix to 1 & $1.50$ & $11.08$ \\
+WFI2033 & $21.78\substack{+0.28\\-0.23}$ & $19.07\substack{+0.35\\-0.26}$ & $19.6\pm4.5$ & $0.28\pm0.02$ & $0.52\pm0.01$ & $0.625$ & $10.51$ \\
+SDSS1206 & $21.31\substack{+0.23\\-0.19}$ & $18.30\substack{+0.05\\-0.05}$ & $33.3\pm6.4$ & $0.11\pm0.02$ & $4.57\pm0.53$ & $0.625$ & $10.77$ \\
+HE1104 & $21.25\substack{+0.16\\-0.14}$ & $19.16\substack{+0.02\\-0.02}$ & $14.0\pm2.0$ & $0.27\pm0.02$ & $1.05\pm0.04$ & $0.625$ & $11.05$ \\
+SDSS0246 & $23.44\substack{+0.28\\-0.22}$ & $20.85\substack{+0.08\\-0.07}$ & $4.0\pm0.9$ & $0.44\pm0.08$ & $4.96\pm0.08$ & $0.625$ & $10.75$ \\
+HS2209 & $20.72\substack{+0.26\\-0.21}$ & $19.20\substack{+0.04\\-0.04}$ & $12.5\pm2.7$ & $1.96\pm1.28$ & $3.15\pm1.40$ & $1.00$ & $11.04$ \\
+HE0047 & $22.92\substack{+0.48\\-0.33}$ & $20.37\substack{+0.20\\-0.17}$ & $2.3\pm0.8$ & $0.32\pm0.15$ & $4.18\pm0.75$ & $0.625$ & $10.91$ \\
 \hline
@@
 Column (8): inferred stellar mass.
+\blue{The uncertainty level for \mstar\ is 0.2 dex}.
 \end{tablenotes}    
@@
 Then, we adopt stellar population templates to derive the stellar mass.
-For this step, we infer the color information for the multi-band imaging data taken with \hst\ in Appendix~\ref{app:a}.
+For this step, we infer the color information for the multi-band imaging data {\bf taken with \hst.}
 We study the \mbh-\mstar\ relations and compare our measurements with ones taken from the literature.
@@
 %[] Color inference for the first three cases to decide their stellar template. 
-Besides the imaging data analyzed in the last section, some of the systems have been also imaged by \hst\ through other bands, providing color information.
-Given that we have used the highest signal-to-noise ratio data for our primary models,  the analysis of the other bands has lower fidelity and we use it only to infer the colors so as to assist in the estimation of the stellar mass (i.e., Table~\ref{tab:host_measure} column (2)).
+Besides the imaging data analyzed in the last section, some of the systems have {\bf also been} imaged by \hst\ through other bands, providing color information.
+Given that we have used the highest signal-to-noise ratio data for our primary models,  the analysis of the other bands has lower fidelity and we use it only to infer the colors so as to assist in the estimation of the stellar mass, i.e., Table~\ref{tab:host_measure} column (2).
 
-{\bf HE0435} ~ In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W.
+{\bf HE0435} ~ {\color{blue}
+%In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W.
 The multi-band imaging data provides us with the opportunity to estimate the host color and improve the stellar mass estimate.
@@
 Based on the three band host magnitudes, we find that a 1.5~Gyr age and solar metallicity stellar population provides a good match to the color.
-More detailed information is presented in Appendix~\ref{app:HE0435}.
+In addition to WFC3/F160W, HE0435 has been observed through bands ACS/F814W and ACS/F555W (GO-9744; PI: C.
+S.
+Kochanek).
+Our aim is to derive the brightness of the host galaxy through all the three bands to investigate the color and stellar population in the image plane.
+We use the modelling approach introduced in Section~\ref{sec:photometry} to perform this inference for the F814W and F555W bands.
+To save computer time, we only use the {\it PSF iteration} approach.
+We also fix the lens mass slope value to 1.9 since it is closer to the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}.
+The inference of the fittings are shown in Figure~\ref{fig:app_HE0435}-(a), (b).
+Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}}~\citep{Morishita2019} to perform the SED fitting.
+A set of age grids (up to 3.0 Gyr) are used in this fit with a constant SFR and a flexible form for star formation histories.
+Note that there is a degeneracy in the age and metallicity; however, this degeneracy has little effect on the \mstar\ inference~\citep{Bell2001}.
+In this work, we fix the metallicity to infer the age, and the uncertainty of the age is not considered.
+Finally, a stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
+This stellar population is used to estimate the host stellar mass.
+
+\begin{figure*}
+\centering
+\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
+\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}\\
+\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/HE0435_host_color.pdf}}\\
+\caption{\label{fig:app_HE0435} 
+Illustrations of the inference of HE0435 using the multi-band data.
+Top two panels: best-fit model of the lensed arcs shown as Figure~\ref{fig:image_inference}.
+Bottom panel: SED inference.
+The red points with error bars represent the inferred image plane host flux in the three bands.}
+\end{figure*} 
+}
 
@@
 
-{\bf WFI2033} ~ In addition to the F160W filter, images through the four filters F125W, F140W, F555W, F814W are also available in the \hst\ archive.
+{\bf WFI2033} ~ 
+{\color{blue}
+%In addition to the F160W filter, images through the four filters F125W, F140W, F555W, F814W are also available in the \hst\ archive.
 As for HE0435, we infer the host color in the image plane.
-We find a stellar population with 0.625 Gyr is a good match to the colors (more details see Appendix~\ref{app:WFI2033}).
+We find a stellar population with 0.625 Gyr is a good match to the colors.
+In addition to WFC3/F160W, WFI2033 has been observed by \hst\ in  four bands, i.e.
+WFC3/F125W (GO-12874; PI: D.
+Floyd), WFC3/F140W (GO-13732; PI: A.
+Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C.
+S.
+Kochanek).
+Similar to HE0435, the lens modelling and the host photometry of WFI2033 have been inferred through these four bands.
+The results are presented in Figure~\ref{fig:app_WFI2033}-(a)$-$(d).
+Unfortunately, the  F125W data are too shallow to robustly detect the host.
+Thus, we do not use the F125W band for the SED fitting.
+Using four-band photometry, we find a stellar population of 0.625 Gyr age provides a good match to the colors, as shown in Figure~\ref{fig:app_WFI2033}-(e).
+\begin{figure*}
+\centering
+\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
+\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
+\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
+\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
+\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
+\caption{\label{fig:app_WFI2033} 
+Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The F125W dare are too shallow to detect the host and are thus omitted in the fit.}
+\end{figure*} 
+}
 
@@
 1 Gyr and 0.625 Gyr for systems as $z<1.44$ and $z>1.44$, respectively.
-Of course this choice is not unique.
-However, we stress that as we are mostly interested in the comparison with D20 this strategy is meant to minimize differences between the two approaches.
+Of course, this choice is not unique.
+However, we stress that as we are mostly interested in comparison with D20 this strategy is meant to minimize differences between the two approaches.
 
@@
 Applying these templates to the filter magnitudes obtained in last section, we derive the stellar mass of our system, Table~\ref{tab:host_measure}, column~(8).
+
 Considering the simulations by~\citet{Ding2017a} and the fact that we are able to obtain very consistent host magnitudes for the HE0435, RXJ1131 and WFI2033 using the independent approaches, the fidelity of the inferred magnitude is expected to be well characterized by the quoted uncertainties.
-We adopt a typical uncertainty of 0.2 dex for the \mstar\ estimates.
+\blue{
+Most of our systems do not have multi-band information to constrain the stellar template (e.g., star formation histories). We adopted a simple stellar population template to calculate the \mstar.
+The uncertainties of the stellar populations could translate the substantial uncertainties into the \mstar.
+According to the investigation by \citet{Bell2001}, we estimate a typical level of 0.2~dex for the \mstar\ uncertainties.}
 
 \subsection{The \mbh-\mstar\ relation}\label{sec:relation}
-In Figure~\ref{fig:scaling_relation}-(left) we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.
+In Figure~\ref{fig:scaling_relation}-(left), we plot \mbh\ vs \mstar\ for our sample, together with the comparison sample introduced in Section~\ref{sec:sample_select}.
 We expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget for the entire sample.
-Following D20, we adopt, as baseline, a local \mbh-\mstar\ of the form:
+Following D20, we adopt, as {\bf a} baseline, a local \mbh-\mstar\ of the form:
 \begin{eqnarray}
@@
 Based on Equation~\eqref{eq:offset}, we fit the evolution of the eight lensed systems and obtain $\gamma=1.05\pm0.44$, which agrees with the results of D20 ($\gamma=1.03\pm0.25$ using 32 AGN) within $1-\sigma$ level.
-The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the observed value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
+The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the {\it observed} value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
 
-The lensed AGN systems analyzed in this work were selected for time-delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy.
+\blue{
+Note that this apparent evolution is obtained directly using the observed sample, which does not consider the selection effect yet~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
+For instance, adopting the framework introduced in~\citet{Schulze2015}, D20 estimated an expected bias of $+2.1$~dex in their observed \mbh\ for their 32 AGN sample, and the offset would be reduced to $\gamma=0.50\pm0.25$ after correcting for the selection bias.
+While in this work, the
+lensed AGN systems were selected for time-delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy.
 This is a different selection function than that used by D20.
 It is thus reassuring that the two samples present the same apparent evolution.
-Naturally, inferring the true underlying evolution requires modelling the selection function (as done by D20), which is not justified given the small sample size of lensed quasars sample.
-At this stage, the lensed quasars should thus be considered as a check on possible systematic measurements error in the D20 analysis rather than a stand-alone measurement.
+Naturally, inferring the true underlying evolution requires modelling the selection function (as studied by D20), which is not justified given the small sample size of lensed quasars sample.
+At this stage, the lensed quasars should thus be considered as a check on possible systematic measurement error in the D20 analysis rather than a stand-alone measurement.}
 
@@
 
-\section{Systematic Errors}\label{sec:diss}
-
-We considered a set of modelling choices to perform the fitting and the final inference is based on a weighting of top ranked choices.
-In particular, we treat the two different modelling approaches, i.e., {\it noise boost} and {\it PSF iteration} equally, to derive the averaged results.
-Of course, the results are somewhat dependent on the weighting scheme, for example, the dispersion of the results by the top ranked choices.
-However, the dependency is smaller than other sources of uncertainty.
-Thus, using different weighting schemes would only change the results marginally ($<0.1$~dex).
-
-We used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling.
-Then, we used our weighting algorithm introduced in Section~\ref{sec:Modelling} to estimate the systematic uncertainty of our inference and assumed it covers the truth.
-We apply this method to the entire sample to ensure self-consistency within our sample, even though four systems (HE0435, RXJ1131, WFI2033, and SDSS1206) have been analyzed by H0LiCOW collaboration, and have high precision slope measurements available.
-As a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW inference.
-The results are the following (here {\it v.s.} H0LiCOW, the error bars are the $1-\sigma$ level): HE0435~($2.032\pm 0.07$ {\it v.s.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it v.s.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it v.s.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it v.s.} $1.95\pm0.05$).
-The consistency of the results supports the robustness of the systematic uncertainty estimated in this work.
-
-Following standard practice in galaxy evolution studies, we use a \sersic\ model to describe the surface brightness of the host galaxy.
-The \sersic\ profile is relatively simple and smooth, and cannot capture the clumps in the host galaxy.
-Thus the smoothness of the \sersic\ profile leads to the relatively large residuals shown in Figure~\ref{fig:image_inference}.
-However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same methodology.
-Note that, the methodology has to be consistent between lensed and unlensed AGNs, since the use of a different host model may introduce systematic errors.
-In fact, it is common to have significant residuals when fitting say a \sersic\ profile to a galaxy (e.g., D20).
-These residuals of course affect the quality of the fit and could increase the systematics.
-However, these systematics are much smaller than our target precision of 0.4 dex.
-The difference in residuals between this work and the H0LiCOW analysis is once again a reflection of the different purposes of the two studies.
-Whereas fitting the host surface brightness to the noise level is important to determine the gravitational potential with sufficient precision to infer the Hubble constant, it is not necessary when the goal is to infer the luminosity of the host.
-
-In addition, we adopt simple stellar populations to derive the stellar mass.
-For 5/8 systems in our sample we did not have color information, and we used instead a fixed age depending on redshift.
-The lack of color information is reflected in an increases of the uncertainty in the inferred \mstar.
-It is important to stress once again, that the main goal of this work is provide an independent test of the D20 measurement.
-Since we are using the same stellar population models, any uncertainty in the models or other stellar population assumptions will cause an absolute change, but those will cancel out when looking at relative consistency between this work and D20.
-
-We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies.
-As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104 through filter F160W.
-For HE1104 the estimated extinction is negative, while for HE0435 and WFI2033 the authors do not report an extinction value because standard extinction laws did not fit the data.
-If we focus on the 13 ellipticals from~\citet{1999ApJ...523..617F}, the total median extinction is -0.03, which justifies our choice to not apply any correction.
-We interpret the negative values reported in the literature as due to the small effect by dust being overshadowed by chromatic microlensing or variability.
-
-In this work, some assumptions have been made to measure the evolution of \mstar-\mbh.
-For example, a Chabrier IMF was assumed to measure the stellar mass for all samples.
-To compare our high redshift measurements with the local ones, we adopted the local sample from~\citet{Bennert++2011, H+R04}, rather than other samples available in the literature.
-We adopt our own recipes to calibrate the \mbh.
-Of course, different options would shift the absolute value of the inferred \mstar\ and \mbh.
-However, since the entire sample is self-consistent, a different assumption would only shifts the global \mstar-\mbh\ together, leaving the offset value and the evolution conclusion the same.
-More details can be found in D20, Section 6.
-
-In summary, considering all random and systematic effects, the uncertainty of \mstar\ relative to that measured by D20 is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.
+\blue{
+We consider all random and systematic effects in Appendix~\ref{sec:diss}.
+To summarize, the uncertainty level of the \mstar\ in this work is assumed as 0.2~dex  as mentioned in the previous section.
+The uncertainty in the black hole mass estimates is at a level of 0.4~dex, which dominates the overall error budget.
+}
 
 \section{Conclusions}\label{sec:con}
-Using eight strongly lensed AGN systems, we presented a new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy.
+Using eight strongly lensed AGN systems, we presented new measurements of the correlations of the mass of supermassive black hole with the stellar masses of their host galaxy.
 We adopt state-of-the-art lens modelling techniques to estimate the magnitude host galaxy, in terms of a standard \sersic\ profile.
@@
 We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the same approach to derive the \mstar\ and calibrated the \mbh\ using consistent recipes.
-The \mbh-\mstar\ correlation and its evolution with cosmic time is in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
-Thus, the present analysis further strengthens the conclusion of D20, which can be summarized as follows.
-First, the growth of the supermassive black hole predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
+The \mbh-\mstar\ correlation and its evolution with cosmic time {\bf are} in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
+\blue{Currently, the sample size of lensed AGN (i.e., eight systems) is quite limited; as a result, their selection effect has not been considered.
+Nevertheless, the present analysis of this good agreement with D20 in the \mbh-\mstar\ correlations strengthens conclusion in D20}, which can be summarized as follows.
+First, the growth of the supermassive black hole \blue{mildly} predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
 However, the actual morphologies of these hosts are likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131.
@@
 \section*{Acknowledgements}
+{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved this paper.}
 We are grateful to Frederic Courbin, Leon Koopmans for useful comments
@@
 This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 787886).
+{\bf C.D.F. acknowledge support for this work from the National Science Foundation under Grant Numbers AST-1312329 and AST-1907396.}
 SHS thanks the Max Planck Society for support through the Max Planck Research Group.
@@
 
-\section{Estimate of the color of the host}\label{app:a}
-In this section, we describe the details of how we select the stellar population of the host used in the computation of the stellar mass estimate.
+{\color{blue}
+\section{Photometry Inference}\label{sec:photometry}
+We describe the details of the fitting for each system and present the inference of the photometry of the host galaxy.
 
-\subsection{HE0435}\label{app:HE0435}
-In addition to WFC3/F160W, HE0435 has been observed through bands ACS/F814W and ACS/F555W (GO-9744; PI: C.
-S.
-Kochanek).
-Our aim is to derive the brightness of the host galaxy through all the three band to investigate the color and stellar population in the image plane.
-We use the modelling approach introduced in Section~\ref{sec:photometry} to perform this inference for the F814W and F555W bands.
-To save computer time, we only use the {\it PSF iteration} approach.
-We also fix the lens mass slope value to 1.9 since it is closer the inference by~\citet[][i.e., $\gamma\sim1.93$]{Wong2017}.
-The inference of the fittings are shown in Figure~\ref{fig:app_HE0435}-(a), (b).
-Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}}~\citep{Morishita2019} to perform the SED fitting.
-A set of age grids (up to 3.0 Gyr) are used in this fit with a constant SFR and a flexible form for star formation histories.
-Note that there is a degeneracy in the age and metallicity; however, this degeneracy has little affect on the \mstar\ inference~\citep{Bell2001}.
-In this work, we fix the metallicity to infer the age, and the uncertainty of the age is not considered.
-Finally, a stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
-This stellar population is used to estimate the host stellar mass.
+\subsection{HE0435}\label{subsec:HE0435}
+We follow the approach described in the previous section.
+We select 5 isolated stars in this field as initial PSFs to input to the fitting, for a total of 60 fits.
+Based on the top-eight choices, we perform the weighting algorithm and measure the host flux, host-to-total flux ratio, effective radius and \sersic\ index.
+The inference results are shown in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
+
+The inference by the best-fit lens model for HE0435 is shown in Figure~\ref{fig:image_inference}-(a).
+Not surprisingly, we note that the residuals level in the normalized plot appears to be larger than the ones presented by~\citet{Wong2017}.
+This is primarily due to the fact that the surface brightness of the host galaxy in our model is defined as a \sersic\ profile, which is relatively simple and smooth compared to the pixellated reconstruction technique adopted by {\sc Glee}~\citep{Suy++06, Halk2008, S+H10, Suyu2012} or the shapelet technique adopted by \lenstronomy~\citep{Birrer2015}.
+The smooth features of \sersic\ profile can not capture the clumps in the host galaxy, such as the star-forming regions.
+Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e.
+the quantity commonly measured in the literature for non-lensed samples.
+
+As a cross-check, we compare our host magnitude to the inference of HE0435 by~\citet{Ding2017b}.
+They inferred the \sersic\ magnitude by fitting to the pixelized host galaxy as reconstructed by~\citet{Wong2017}.
+The host magnitude measured by~\citet{Ding2017b} is: $mag = 21.75 \pm 0.13$.
+%, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
+The results are in excellent agreement with the measurement reported here, i.e. $mag = 21.50 \pm 0.35$.
+
+\subsection{RXJ1131}
+A lens model of RXJ1131 based on ACS/F814W data has been presented by~\citet{Suyu2013}.
+The host galaxy of this system is lensed to an extended arc.
+A clear bulge and disk component can be identified.
+Thus, we describe the host galaxy with two \sersic\ profiles with index values $n$ fixed to $1$ and $4$, respectively, to mimic the light distribution of the disk and bulge.
+In addition, following~\citet{Suyu2013}, we consider the perturbations by the small object ($0\farcs{5}$ in the north) and describe it as a SIS and \sersic\ for its mass and light, respectively.
+
+The photometry of the RXJ1131 host galaxy is fitted with a set of 4 initial PSFs.
+The results are summarized in Table~\ref{tab:host_measure}, with the best-fit result shown in Figure~\ref{fig:image_inference}-(b).
+
+We also compare our measurement to the previous reconstructions by \citet{Ding2017b}.
+Based on the reconstructions by~\citet{Suyu2013}, the inference of the host magnitudes by~\citet{Ding2017b} are $mag_{\rm bulge} = 21.81 \pm 0.28$ and $mag_{\rm disk} = 20.07\pm0.06$.
+The results are in excellent agreement with our inferred bulge magnitude ($21.80\pm0.21$)   shown in Table~\ref{tab:host_measure}.
+However, our inferred disk magnitude ($19.33\pm0.16$) is brighter than that reported by \citet{Ding2017b}.
+This difference is not surprising because our reconstruction of the host galaxy is based on a much more extended region to collect the disk light, compared with~\citet{Suyu2013} who performed the lens modelling using a smaller lens mask (see Figure~4 therein).
+Note that, at variance with the procedure described here, \citet{Ding2017b} used a \sersic\ to fit the pixellated source reconstructed by~\citet{Suyu2013} in the source plane.
+We checked that finite grid effects did not introduce any substantial difference.
+As a sanity check, we find that our inferred effective radius is very consistent, $0\farcs{}90 \pm 0\farcs{}06$ (this paper) and $0\farcs{}84 \pm 0\farcs09$~\citep{Ding2017b}.
+The difference between the \citet{Suyu2013} reconstruction and the one presented here makes sense in terms of the different goals of the two studies.
+While our primary aim is to reconstruct the host galaxy photometry, for \citet{Suyu2013} it was only a byproduct on the way to time-delay cosmography.
+
+\subsection{WFI2033}
+WFI2033 is the last quadruply lensed system in our sample whose lens model has been previously investigated \citep{Rusu2019}.
+There is a satellite galaxy in the north of the lens.
+However, the satellite galaxy has a much smaller mass than the main deflector.
+In addition, there is a galaxy west of the main target, which also has a small effect on the total macro-magnification $(<10\%)$.
+Thus, we ignore their influence on the magnification but only fit the light of the satellite galaxy using a \sersic\ model.
+We select a total of 8 initial PSF stars to model this system.
+
+The final inference results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(c).
+We compare our inference to the previously reconstructed host galaxies.
+Modelling the reconstructed host by~\citet{Rusu2019}, (i.e., the Figure~4 bottom-right plane therein) as a \sersic\ profile, we infer the $mag = 21.98 \pm 0.15$, which is very consistent to our inference (i.e., $mag = 21.78 \pm 0.25$).
+
+\subsection{SDSS1206}
+SDSS1206 is a unique system -- the AGN is doubly imaged by the deflector while most of the host falls inside the inner caustic and ends up being quadruply imaged.
+Following~\citet{Birrer2019}, we consider the galaxy triplet group at the north-west and use a single SIS model to denote their overall mass perturbation.
+Moreover, as noted by~\citet{Birrer2019}, a sub-clump is located in the north which is hardly visible \citep[see Figure~1 in][]{Birrer2019}.
+We model this sub-clump as a SIS mass model and a circular \sersic\ light model with joint centroids.
+It is worth noting that we are using the same imaging modelling tool as~\citet{Birrer2019}.
+
+Due to the limited number of stars in the field of view, there are only 2 stars available as initial PSF.
+To expand the volume of modelling options, we also take the stack of the two bright stars as derived by~\citet{Birrer2019}, as a third initial PSF.
+We find visible residuals at the fitted lensed arcs region using a single \sersic\ model as host.
+However, a double \sersic\ model does not significantly improve the goodness of fit.
+Thus, we adopt the single \sersic\ model in our final inference.
+Our inferred results are presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(d).
+
+\subsection{HE1104}
+HE1104 is a typical doubly imaged quasar.
+We have selected in total of 5 initial PSFs to perform the fit.
+There is an object in the northeast.
+However, since we do not know its redshift and considering it is further away from the lens we do not model it explicitly but just mask it out in the fitting.
+
+The inference is presented in Table~\ref{tab:host_measure} and Figure~\ref{fig:image_inference}-(e).
+the lensed arcs can be clearly seen from the bottom-left panel, indicating that the host galaxy is well detected.
+
+It is worth noting that the HE1104 has been modelled by~\citet{Peng2006} based on the \hst/NICMOS H-band (F160W) imaging data.
+Their inferred host light is $20.14\pm0.30$ mag in Vega system, which is also consistent to our inference ($20.00\pm0.15$ mag in Vega).
+%zeropoint 25.9463(AB) - 24.6949(Vega) = 1.2514
+%HE1104 mag:  21.25 (AB)  --> 20.00 (Vega)
+
+\subsection{SDSS0246}
+Having been imaged with WFC3-UVIS/F814W, the resolution of the data for this system (together with the remaining two systems) is much higher than for those imaged in the IR, with a drizzled pixel scale of $0\farcs{}03$.
+However, the arcs are much fainter compared with those of other systems imaged in the IR band.
+As a result, fewer pixels with signal are available for the fit than for other systems.
+Nevertheless, the host inference is successfully reconstructed as shown in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure} (3 initial PSF guesses were adopted).
+
+\subsection{HS2209}
+HS2209 was imaged by \hst\ during two visits ($vis05$ and $vis06$) at different orientations.
+We modelled the two visits separately and recovered mutually consistent host galaxy magnitudes.
+However, we found that the data from {\it vis06} can be modelled with smaller residuals; thus the inference based on {\it vis06} was adopted as our best estimate (using 7 initial PSF stars), as listed in Table~\ref{tab:host_measure}.
+The inference for this system is summarized in Figure~\ref{fig:image_inference}-(g).
+
+\subsection{HE0047}
+HE0047 is the most challenging system in our sample with the lowest SNR of the lensed arcs.
+The results, based on 3 initial PSFs, are summarized in Figure~\ref{fig:image_inference}-(f) and Table~\ref{tab:host_measure}.
+The host magnitude of the HE0047 system has a relatively large uncertainty as reflected in the error bars.
 
@@
 \centering
-\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
-\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}\\
-\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/HE0435_host_color.pdf}}\\
-\caption{\label{fig:app_HE0435} 
-Illustrations of the inference of HE0435 using the multi-band data.
-Top two panels: best-fit model of the lensed arcs shown as Figure~\ref{fig:image_inference}.
-Bottom panel: SED inference.
-The red points with error bars represent the inferred image plane host flux in the three bands.}
+\begin{tabular}{c c}
+\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_inference.png}}&
+\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_inference.png}}\\
+\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_inference.png}}&
+\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_inference.png}}\\
+\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_inference.png}}&
+\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_inference.png}}\\
+\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_inference.png}}&
+\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_inference.png}}\\
+\end{tabular}
+\caption{\label{fig:image_inference} 
+Illustrations of the inference using the best-fit lens model for each system using the AGN center noise level boosted approach.
+For each figure, the panels from left to right are the follows: Top row: (left to right): (1) observed data, (2) best-fit model (3) residuals divided by the uncertainty level.
+Some of the residual looks clumpy; however, they do not affect the host property measurements, for more details see Section~\ref{sec:diss} ; Bottom row: (left to right): (4) data minus the model PSF and deflector  (i.e., pure lensed arc image), (5) the model of the lensed arc, (6) reconstructed host galaxy in the source plane with caustic line drawn as yellow line.
+Across all the systems, the lensed arc feature can be clearly seen in the fourth panel, indicating strong evidence of a detection.
+In panel (3) and (4), we use white regions to indicate the area where the noise level is boosted.
+}
 \end{figure*}
 
-%\subsection{RXJ1131}\label{app:RXJ1131}
-%Using the three band data including  ACS/F814W and ACS/F555W and NIC2/F160W (GO-9744; PI: C.
-S.
-Kochanek), we preform the SED fitting in the imaging plane directly pixel by pixel in Figure~\ref{fig:app_RXJ1131}.
-\ding{This part is actually done by Takahiro in~\citep{Ding2017b}.
-The image of the fitted age looks noisy, but it is in the range of the [9.25 - 9.50] (logAge), i.e.
-[1.5, 3.0] (Gyr).
-We can remove this A2 but only mention the fitting is done 2017 in that paper.}
-%\begin{figure}
-%\centering
-%{\includegraphics[width=0.25\textwidth]{fig/map_age_zRXJ_1131.pdf}}\\
-%\caption{\label{fig:app_RXJ1131} 
-%Illustrations of the SED fitting of the galaxy age pixel by pixel.  }
-%\end{figure}
+\section{Systematic Errors}\label{sec:diss}
 
-\subsection{WFI2033}\label{app:WFI2033}
-In addition to WFC3/F160W, WFI2033 has been observed by \hst\ in  four bands, i.e.
-WFC3/F125W (GO-12874; PI: D.
-Floyd), WFC3/F140W (GO-13732; PI: A.
-Nierenberg), ACS/F555W+F814W  (GO-9744; PI: C.
-S.
-Kochanek).
-Similar to Section~\ref{app:HE0435}, the lens modelling and the host photometry of WFI2033 have been inferred through these four bands.
-The results are presented in the Figure~\ref{fig:app_WFI2033}-(a)$-$(d).
-Unfortunately, the  F125W data are too shallow to robustly detect the host.
-Thus, we do not use the F125W band for the SED fitting.
-Using four-band photometry, we find a stellar population of 0.625 Gyr age provides a good match to the colors, as shown in Figure~\ref{fig:app_WFI2033}-(e).
-\begin{figure*}
-\centering
-\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
-\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
-\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
-\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
-\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
-\caption{\label{fig:app_WFI2033} 
-Same as Figure~\ref{fig:app_WFI2033} but for WFI2033. The F125W dare are too shallow to detect the host and are thus omitted in the fit.}
-\end{figure*} 
+We considered a set of modelling choices to perform the fitting and the final inference is based on a weighting of top-ranked choices.
+In particular, we treat the two different modelling approaches, i.e., {\it noise boost} and {\it PSF iteration} equally, to derive the averaged results.
+Of course, the results are somewhat dependent on the weighting scheme, for example, the dispersion of the results by the top-ranked choices.
+However, the dependency is smaller than other sources of uncertainty.
+Thus, using different weighting schemes would only change the results marginally ($<0.1$~dex).
+
+We used a range of mass slope values (i.e., 1.9, 2.0, 2.1) to perform the lens modelling.
+Then, we used our weighting algorithm introduced in Section~\ref{sec:Modelling} to estimate the systematic uncertainty of our inference and assumed it covers the truth.
+We apply this method to the entire sample to ensure self-consistency within our sample, even though four systems (HE0435, RXJ1131, WFI2033, and SDSS1206) have been analyzed by H0LiCOW collaboration, and have high precision slope measurements available.
+As a sanity check, we calculate the weighted slope value and make a direct comparison to the H0LiCOW inference.
+The results are the following (here {\it v.s.} H0LiCOW, the error bars are the $1-\sigma$ level): HE0435~($2.032\pm 0.07$ {\it v.s.} $1.93\pm0.02$), RXJ1131~($2.02\pm 0.06$ {\it v.s.}$1.95\pm0.045$), WFI2033~($1.94\pm 0.07$ {\it v.s.} $1.95\pm0.02$), SDSS1206~($1.98\pm 0.06$ {\it v.s.} $1.95\pm0.05$).
+The consistency of the results supports the robustness of the systematic uncertainty estimated in this work.
+
+Following standard practice in galaxy evolution studies, we use a \sersic\ model to describe the surface brightness of the host galaxy.
+The \sersic\ profile is relatively simple and smooth, and cannot capture the clumps in the host galaxy.
+Thus the smoothness of the \sersic\ profile leads to the relatively large residuals shown in Figure~\ref{fig:image_inference}.
+However, as mention in Section~\ref{subsec:HE0435}, our goal to derive a self-consistent one-step inference of the host properties to make comparison with the measurements of the non-lensed AGN samples, which are measured using the same methodology.
+Note that, the methodology has to be consistent between lensed and unlensed AGNs, since the use of a different host model may introduce systematic errors.
+In fact, it is common to have significant residuals when fitting say a \sersic\ profile to a galaxy (e.g., D20).
+These residuals of course affect the quality of the fit and could increase the systematics.
+However, these systematics are much smaller than our target precision of 0.4 dex.
+The difference in residuals between this work and the H0LiCOW analysis is once again a reflection of the different purposes of the two studies.
+Whereas fitting the host surface brightness to the noise level is important to determine the gravitational potential with sufficient precision to infer the Hubble constant, it is not necessary when the goal is to infer the luminosity of the host.
+
+In addition, we adopt simple stellar populations to derive the stellar mass.
+For 5/8 systems in our sample we did not have color information, and we used instead a fixed age depending on redshift.
+The lack of color information is reflected in an increase of the uncertainty in the inferred \mstar.
+It is important to stress once again that the main goal of this work is to provide an independent test of the D20 measurement.
+Since we are using the same stellar population models, any uncertainty in the models or other stellar population assumptions will cause an absolute change, but those will cancel out when looking at relative consistency between this work and D20.
+
+We do not expect foreground extinction to be significant, because the deflectors are all massive elliptical galaxies.
+As a sanity check, \citet{1999ApJ...523..617F} and \citet{2008A&A...485..403O} report estimates for HE0435, WFI2033 and HE1104 through filter F160W.
+For HE1104 the estimated extinction is negative, while for HE0435 and WFI2033 the authors do not report an extinction value because standard extinction laws did not fit the data.
+If we focus on the 13 ellipticals from~\citet{1999ApJ...523..617F}, the total median extinction is -0.03, which justifies our choice not to apply any correction.
+We interpret the negative values reported in the literature as due to the small effect by dust being overshadowed by chromatic microlensing or variability.
+
+In this work, some assumptions have been made to measure the evolution of \mstar-\mbh.
+For example, a Chabrier IMF was assumed to measure the stellar mass for all samples.
+To compare our high redshift measurements with the local ones, we adopted the local sample from~\citet{Bennert++2011, H+R04}, rather than other samples available in the literature.
+We adopt our own recipes to calibrate the \mbh.
+Of course, different options would shift the absolute value of the inferred \mstar\ and \mbh.
+However, since the entire sample is self-consistent, a different assumption would only shift the global \mstar-\mbh\ together, leaving the offset value and the evolution conclusion the same.
+More details can be found in D20, Section 6.
+
+%In summary, considering all random and systematic effects, the uncertainty of \mstar\ relative to that measured by D20 is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-08-14 manuscript/manuscript.tex
Merge with TT's edits

@@
 \mbh\ are estimated from broad emission lines using standard methods.
-Our results are in good agreement with recent work based on non-lensed AGN, \blue{demonstrating the great potential of using strongly lensed AGNs to extend the study of the correlations to higher redshifts.}
+Our results are in good agreement with recent work based on non-lensed AGN, \blue{demonstrating the potential of using strongly lensed AGNs to extend the study of the correlations to higher redshifts.}
 At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN.
@@
 
-\blue{The inferred photometry of the host galaxy for all the eight systems are listed in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
-The detailed information of the fitting process for each system is in Appendix~\ref{sec:photometry}.}
+\blue{The inferred photometric properties of the host galaxy for all the eight systems are listed in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
+Detailed information on the fitting process for each system is given in Appendix~\ref{sec:photometry}.}
 
@@
 Column (8): inferred stellar mass.
-\blue{The uncertainty level for \mstar\ is 0.2 dex}.
+\blue{The uncertainty of \mstar\ is estimated to be 0.2 dex}.
 \end{tablenotes}    
@@
 Having obtained the magnitude of the lensed host in the three bands, we use the {\sc Gsf} package\footnote{\url{https://github.com/mtakahiro/gsf}}~\citep{Morishita2019} to perform the SED fitting.
-A set of age grids (up to 3.0 Gyr) are used in this fit with a constant SFR and a flexible form for star formation histories.
-Note that there is a degeneracy in the age and metallicity; however, this degeneracy has little effect on the \mstar\ inference~\citep{Bell2001}.
-In this work, we fix the metallicity to infer the age, and the uncertainty of the age is not considered.
-Finally, a stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c).
+A range of ages (up to 3.0 Gyr) is used in this fit with a constant SFR and a flexible form for star formation histories.
+Note that there is a well-known degeneracy between age and metallicity; however, this degeneracy has little effect on the \mstar\ inference~\citep{Bell2001}.
+In this work, we fix the metallicity to infer the age.
+In the end, a stellar population with 1.5~Gyr of age and solar metallicity provides the best fit to the colors, as shown in Figure~\ref{fig:app_HE0435}-(c), although this choice is by no means unique.
 This stellar population is used to estimate the host stellar mass.
@@
 \blue{
-Most of our systems do not have multi-band information to constrain the stellar template (e.g., star formation histories). We adopted a simple stellar population template to calculate the \mstar.
-The uncertainties of the stellar populations could translate the substantial uncertainties into the \mstar.
-According to the investigation by \citet{Bell2001}, we estimate a typical level of 0.2~dex for the \mstar\ uncertainties.}
+Our systems do not have sufficient multi-band information to constrain their metallicity and star formation histories.
+Therefore, we adopted a simple stellar population template to calculate \mstar, but reflect the lack of information in the associated uncertainty.
+Following \citet{Bell2001}, we estimate a typical uncertainty of 0.2~dex for all the \mstar\ measurements in this paper.}
 
@@
 \blue{
-Note that this apparent evolution is obtained directly using the observed sample, which does not consider the selection effect yet~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
-For instance, adopting the framework introduced in~\citet{Schulze2015}, D20 estimated an expected bias of $+2.1$~dex in their observed \mbh\ for their 32 AGN sample, and the offset would be reduced to $\gamma=0.50\pm0.25$ after correcting for the selection bias.
-While in this work, the
-lensed AGN systems were selected for time-delay cosmography work, based on the availability of a time delay and the known detectability of the host galaxy.
-This is a different selection function than that used by D20.
-It is thus reassuring that the two samples present the same apparent evolution.
-Naturally, inferring the true underlying evolution requires modelling the selection function (as studied by D20), which is not justified given the small sample size of lensed quasars sample.
-At this stage, the lensed quasars should thus be considered as a check on possible systematic measurement error in the D20 analysis rather than a stand-alone measurement.}
+Note that this apparent evolution is obtained directly using the observed sample, before considering selection effects~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
+For instance, adopting the framework introduced in~\citet{Schulze2015}, D20 estimated that accounting for selection biases would yield a more modest evolution $\gamma=0.50\pm0.25$.
+The lensed AGN systems considered in this work were selected for time-delay cosmography, based on the availability of a time delay and the known detectability of the host galaxy.
+This is a complex selection function, different than the one used by D20.
+Although it is encouraging that the two samples present the same apparent evolution, inferring the true underlying evolution requires modelling the selection function, as studied by D20.
+A full modelling of the complex selection function is not warranted given the small size of the lensed quasars sample.
+Thus, at this stage, the lensed quasars should be considered as a check on possible systematic measurement error in the D20 analysis rather than a stand-alone measurement.}
 
@@
 The \mbh-\mstar\ correlation and its evolution with cosmic time {\bf are} in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
-\blue{Currently, the sample size of lensed AGN (i.e., eight systems) is quite limited; as a result, their selection effect has not been considered.
-Nevertheless, the present analysis of this good agreement with D20 in the \mbh-\mstar\ correlations strengthens conclusion in D20}, which can be summarized as follows.
-First, the growth of the supermassive black hole \blue{mildly} predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
+\blue{Currently, the sample of lensed AGN (i.e., eight systems) is quite limited in size; as a result, given the statistical errors it is not worth modelling selection effect.} Nevertheless, the good agreement with the D20 sample strengthens their conclusions, which can be summarized as follows.
+First, the growth of the supermassive black hole \blue{somewhat} predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
 However, the actual morphologies of these hosts are likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131.

### 2020-09-03 manuscript/manuscript_nonbold.tex
Submit paper backup

--- 2020-08-14 manuscript/manuscript.tex
@@
 \\
+\\
 % List of institutions
@@
 \mbh\ are estimated from broad emission lines using standard methods.
-Our results are in good agreement with recent work based on non-lensed AGN, \blue{demonstrating the potential of using strongly lensed AGNs to extend the study of the correlations to higher redshifts.}
+Our results are in good agreement with recent work based on non-lensed AGN, demonstrating the potential of using strongly lensed AGNs to extend the study of the correlations to higher redshifts.
 At the moment, the sample size of lensed AGN is small and thus they provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN.
@@
 The tight correlations between the masses (\mbh) of supermassive black holes (BHs) and their host galaxies properties including stellar mass (\mstar), stellar velocity dispersion ($\sigma_*$) and luminosity (\lhost), known as scaling relations, are usually considered as a result of their co-evolution ~\citep[e.g.,][]{Mag++98, F+M00, Geb++01b, M+H03, Gul++09,Beifi2012, H+R04, Gra++2011}.
-Cosmological simulations of structure formation are able to reproduce the local tight relation based on {\bf the} physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
+Cosmological simulations of structure formation are able to reproduce the local tight relation based on the physical mechanism by invoking active galactic nucleus (AGN) feedback as the physical connection~\citep{Springel2005, Hopkins2008, Matteo2008, DeG++15} or having them share a common gas supply~\citep{Cen2015, Menci2016}.
 However, it has also been suggested that the correlations arise statistically, without any physical coupling, as a result of stochastic mergers~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
@@
 As the samples of AGN grow to increase statistical power, it is very important to make sure that systematics do not dominate the error budget.
-One of the main potential {\bf sources} of systematics is the finite resolution of \hst\ images.
+One of the main potential sources of systematics is the finite resolution of \hst\ images.
 Even with modern techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution.
@@
 Therefore, we use it primarily to verify the results of D20.
-The D20 sample includes 32 AGN measurements in the redshift range {\bf of} $1.2<z<1.9$.
+The D20 sample includes 32 AGN measurements in the redshift range of $1.2<z<1.9$.
 They also collected 59 intermediate redshift (i.e., $0.35<z\lesssim1.2$) AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 local (i.e., $z\lesssim0.007$) measurements~\citep{Bennert++2011, H+R04}.
@@
 The \mbh\ measurements, together with the properties of the broad-line, are listed in Table~\ref{mbh}. 
-The uncertainty of the \mbh\ {\bf is} estimated to be $0.4$~dex.
+The uncertainty of the \mbh\ is estimated to be $0.4$~dex.
 We note that the magnification correction for these systems are not fully self-consistent, in the sense that the magnification is slightly different for the host galaxy light and the black holes mass.
@@
 For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile.
-We start with a single \sersic\ profile and consider {\bf using} two \sersic\ if any significant residual {\bf indicates} multiple components.
+We start with a single \sersic\ profile and consider using two \sersic\ if any significant residual indicates multiple components.
 For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been shown in~\citet{Ding2017a} that choosing this prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}.
@@
 After all fits are completed, we rank their performance based on their best-fitted $\chi^2$ value.
-Since there is no evidence of better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then {\bf combined} their best-fit results based on the weighting algorithm introduced by D20.
+Since there is no evidence of better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from each of them and then combined their best-fit results based on the weighting algorithm introduced by D20.
 The degrees of freedom are the same for each of the model, ensuring that the weighting scheme is internally self-consistent.
@@
 
-\blue{The inferred photometric properties of the host galaxy for all the eight systems are listed in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
-Detailed information on the fitting process for each system is given in Appendix~\ref{sec:photometry}.}
+The inferred photometric properties of the host galaxy for all the eight systems are listed in Table~\ref{tab:host_measure}, (2)$-$(6) columns.
+Detailed information on the fitting process for each system is given in Appendix~\ref{sec:photometry}.
 
@@
 Column (8): inferred stellar mass.
-\blue{The uncertainty of \mstar\ is estimated to be 0.2 dex}.
+The uncertainty of \mstar\ is estimated to be 0.2 dex.
 \end{tablenotes}    
@@
 Then, we adopt stellar population templates to derive the stellar mass.
-For this step, we infer the color information for the multi-band imaging data {\bf taken with \hst.}
+For this step, we infer the color information for the multi-band imaging data taken with \hst.
 We study the \mbh-\mstar\ relations and compare our measurements with ones taken from the literature.
@@
 %[] Color inference for the first three cases to decide their stellar template. 
-Besides the imaging data analyzed in the last section, some of the systems have {\bf also been} imaged by \hst\ through other bands, providing color information.
+Besides the imaging data analyzed in the last section, some of the systems have also been imaged by \hst\ through other bands, providing color information.
 Given that we have used the highest signal-to-noise ratio data for our primary models,  the analysis of the other bands has lower fidelity and we use it only to infer the colors so as to assist in the estimation of the stellar mass, i.e., Table~\ref{tab:host_measure} column (2).
 
-{\bf HE0435} ~ {\color{blue}
+{\bf HE0435} ~
 %In addition to the F160W data, this system has been observed by \hst\ through filters F814W and F555W.
@@
 \end{figure*}
-}
 
@@
 {\bf WFI2033} ~ 
-{\color{blue}
 %In addition to the F160W filter, images through the four filters F125W, F140W, F555W, F814W are also available in the \hst\ archive.
@@
 We find a stellar population with 0.625 Gyr is a good match to the colors.
-In addition to WFC3/F160W, WFI2033 has been observed by \hst\ in  four bands, i.e.
-WFC3/F125W (GO-12874; PI: D.
+In addition to WFC3/F160W, WFI2033 has been observed by \hst\ in  four bands, i.e., WFC3/F125W (GO-12874; PI: D.
 Floyd), WFC3/F140W (GO-13732; PI: A.
@@
 No multi-band information is available for the other systems.
-Thus, for these cases, we follow D20 and assume a typical stellar population age, i.e.
-1 Gyr and 0.625 Gyr for systems as $z<1.44$ and $z>1.44$, respectively.
+Thus, for these cases, we follow D20 and assume a typical stellar population age, i.e., 1 Gyr and 0.625 Gyr for systems as $z<1.44$ and $z>1.44$, respectively.
 Of course, this choice is not unique.
@@
 Considering the simulations by~\citet{Ding2017a} and the fact that we are able to obtain very consistent host magnitudes for the HE0435, RXJ1131 and WFI2033 using the independent approaches, the fidelity of the inferred magnitude is expected to be well characterized by the quoted uncertainties.
-\blue{
 Our systems do not have sufficient multi-band information to constrain their metallicity and star formation histories.
-Therefore, we adopted a simple stellar population template to calculate \mstar, but reflect the lack of information in the associated uncertainty.
-Following \citet{Bell2001}, we estimate a typical uncertainty of 0.2~dex for all the \mstar\ measurements in this paper.}
+Therefore, we adopt a simple stellar population template to calculate \mstar, but reflect the lack of information in the associated uncertainty.
+Following \citet{Bell2001}, we estimate a typical uncertainty of 0.2~dex for all the \mstar\ measurements in this paper.
 
@@
 We expect that the uncertainty of the \mbh\ (i.e., $0.4~$dex) dominates the error budget for the entire sample.
-Following D20, we adopt, as {\bf a} baseline, a local \mbh-\mstar\ of the form:
+Following D20, we adopt, as a baseline, a local \mbh-\mstar\ of the form:
 \begin{eqnarray}
@@
 
-\blue{
 Note that this apparent evolution is obtained directly using the observed sample, before considering selection effects~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.
@@
 A full modelling of the complex selection function is not warranted given the small size of the lensed quasars sample.
-Thus, at this stage, the lensed quasars should be considered as a check on possible systematic measurement error in the D20 analysis rather than a stand-alone measurement.}
+Thus, at this stage, the lensed quasars should be considered as a check on possible systematic measurement error in the D20 analysis rather than a stand-alone measurement.
 
@@
 
-\blue{
 We consider all random and systematic effects in Appendix~\ref{sec:diss}.
@@
 The uncertainty in the black hole mass estimates is at a level of 0.4~dex, which dominates the overall error budget.
-}
 
@@
 We directly compare our sample to the recent measurements by~\citet[][D20]{Ding2020a}, who used the same approach to derive the \mstar\ and calibrated the \mbh\ using consistent recipes.
-The \mbh-\mstar\ correlation and its evolution with cosmic time {\bf are} in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
-\blue{Currently, the sample of lensed AGN (i.e., eight systems) is quite limited in size; as a result, given the statistical errors it is not worth modelling selection effect.} Nevertheless, the good agreement with the D20 sample strengthens their conclusions, which can be summarized as follows.
-First, the growth of the supermassive black hole \blue{somewhat} predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
+The \mbh-\mstar\ correlation and its evolution with cosmic time are in excellent agreement with the results obtained by D20, as shown in Figure~\ref{fig:scaling_relation}.
+Currently, the sample of lensed AGN (i.e., eight systems) is quite limited in size; as a result, given the statistical errors it is not worth modelling selection effect.
+Nevertheless, the good agreement with the D20 sample strengthens their conclusions, which can be summarized as follows.
+First, the growth of the supermassive black hole somewhat predates that of its host galaxy during their co-evolution, even when considering total stellar mass, as it is often done at high redshift.
 However, the actual morphologies of these hosts are likely to be more complex, including a disk and bulge component, as in the case of  RXJ1131.
@@
 \section*{Acknowledgements}
-{\bf The authors thank the anonymous referee for helpful suggestions and comments which improved this paper.}
+The authors thank the anonymous referee for helpful suggestions and comments which improved this paper.
 We are grateful to Frederic Courbin, Leon Koopmans for useful comments
@@
 This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 787886).
-{\bf C.D.F. acknowledge support for this work from the National Science Foundation under Grant Numbers AST-1312329 and AST-1907396.}
+C.D.F. acknowledge support for this work from the National Science Foundation under Grant Numbers AST-1312329 and AST-1907396.
 SHS thanks the Max Planck Society for support through the Max Planck Research Group.
@@
 This work has made use of \lenstronomy~\citep{lenstronomy}, {\sc Astropy}~\citep{Astropy}, {\sc photutils}~\citep{photutils}, {\sc Matplotlib}~\citep{Matplotlib} and standard Python libraries.
+
+\section*{Data Availability}
+The data underlying this article are available in the article and in its online supplementary material.
 
@@
 
-{\color{blue}
 \section{Photometry Inference}\label{sec:photometry}
@@
 \subsection{HE0435}\label{subsec:HE0435}
-We follow the approach described in the previous section.
+We follow the approach described in Section~\ref{sec:Modelling}.
 We select 5 isolated stars in this field as initial PSFs to input to the fitting, for a total of 60 fits.
@@
 The smooth features of \sersic\ profile can not capture the clumps in the host galaxy, such as the star-forming regions.
-Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e.
-the quantity commonly measured in the literature for non-lensed samples.
+Nevertheless, our approach is sufficient to derive a self-consistent one-step inference of the global host light in terms of the \sersic\ flux, i.e., the quantity commonly measured in the literature for non-lensed samples.
 
@@
 %, $R_{eff} = 0.82 \pm 0.14$ and $n = 3.94 \pm 0.14$.
-The results are in excellent agreement with the measurement reported here, i.e. $mag = 21.50 \pm 0.35$.
+The results are in excellent agreement with the measurement reported here, i.e., $mag = 21.50 \pm 0.35$.
 
@@
 %In summary, considering all random and systematic effects, the uncertainty of \mstar\ relative to that measured by D20 is smaller than the estimated uncertainty in the black hole mass (0.4~dex), which dominates the overall error budget.
-}
 

### 2020-09-03 material/read_def_mag.py
Create file to read deflectors' mag

@@ -1,0 +1,95 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Feb 21 11:50:31 2020
+
+@author: Dartoon
+"""
+#!!! For the Lenstronomy version 1.5.0
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import pickle
+from matplotlib.colors import LogNorm
+import copy
+import sys
+sys.path.insert(0,'/Users/Dartoon/Astro/Projects/my_code/py_tools/')
+from flux_profile import cr_mask
+import glob
+
+
+# # =============================================================================
+# # To reproduce
+# # =============================================================================
+# In lenstronomy version 1.3.0
+# 1.Replae model_band_plot
+# to change label size:
+# 2.in plot._util.py
+# change text_description()   
+
+
+#%% Find the one with lowest Chisq
+IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS0246', '6_HS2209', '7_HE0047']
+
+
+#for i in range(len(IDs)):
+#    print(i, ':', IDs[i])
+#inp = int(input("Which source:\n"))
+inp = 0
+ID = IDs[inp][2:]
+if ID == 'SDSS1206':
+    folder_0 = '_singel_host_run_summary.pkl'
+    folder_1 = 'singel_fit'
+elif ID == 'HS2209' or ID == 'RXJ1131':
+    folder_0 = '_3rd_run_summary.pkl'
+    folder_1 = '3rd_fit'    
+else:
+    folder_0 = '_2nd_run_summary.pkl'
+    folder_1 = '2nd_fit'
+filename = '../share_tools/'+ ID+ folder_0
+result = pickle.load(open(filename,'rb')) 
+fit_values, chisq, labels, _ = result
+chisq = [float(chisq[i]) for i in range(len(chisq))]
+
+mag_result = []
+for idx in range(len(chisq)):
+    label = labels[idx]
+    label = label.split(', ')
+    filename = glob.glob('../'+IDs[inp]+'/model/{4}_PSFi_{0}/result_{1}_*_gammafix{2}_subg{3}.pkl'.format(label[-1], label[0], label[1][-3:], label[2][-1],folder_1) )
+    readfile = filename[0] 
[…]

### 2020-09-20 manuscript/manuscript.tex
Final update to the paper, after the final review.

@@
 The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the {\it observed} value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
+{\bf It is possible that the uncertainty of the \mstar\ could be higher than our estimation (i.e., 0.2~dex), given that the star formation histories could vary widely at high redshift ($z\sim$2).
+However, even when our stellar mass uncertainty is boosted, the evolution inferred using the eight lensed systems is still robust --- $\gamma=1.05\pm0.48$ assuming  $\Delta$\mstar = 0.3~dex, and $\gamma=1.03\pm0.53$ assuming $\Delta$\mstar = 0.4~dex.}
 
-\blue{
 Note that this apparent evolution is obtained directly using the observed sample, before considering selection effects~\citep{Tre++07,Schulze2011,Bennert++2011, Schulze2014,Park15}.

### 2020-09-20 relation_plots/MM_vz_32QSO.py

@@ -450,7 +450,7 @@ for i in range(len(h0licow)):
 lens_sample = np.array(lens_sample).T
 x = lens_sample[0]
 y = lens_sample[1]
-yerr = lens_sample[1]*0 + (0.4**2+0.2**2)**0.5
+yerr = lens_sample[1]*0 + (0.4**2+0.2**2)**0.5   #Tested to change 0.2 to 0.3 and 0.4
 
 sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x, y, yerr))
 sampler.run_mcmc(pos, 500)
@@ -519,7 +519,7 @@ plt.legend([Bkc, Hkc, SS13, ding_sample],[
 "Intermediate redshift AGNs",
 "$1.2<z<1.7$ AGNs by D20"
 ],scatterpoints=1,numpoints=1,loc=3,prop={'size':22,'family': 'Arial'},ncol=2,handletextpad=0)
-plt.savefig("MBH-Mstar_vz.pdf")
+# plt.savefig("MBH-Mstar_vz.pdf")
 plt.show()
 
 # #%% KS test on the distributions:

### 2020-09-25 manuscript/manuscript.tex
The final submission

@@
 $^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
-$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
+$^{5}$Department of Physics {\bf and Astronomy}, University of California, Davis, CA 95616, USA\\
 $^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
@@
 The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the {\it observed} value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
-{\bf It is possible that the uncertainty of the \mstar\ could be higher than our estimation (i.e., 0.2~dex), given that the star formation histories could vary widely at high redshift ($z\sim$2).
-However, even when our stellar mass uncertainty is boosted, the evolution inferred using the eight lensed systems is still robust --- $\gamma=1.05\pm0.48$ assuming  $\Delta$\mstar = 0.3~dex, and $\gamma=1.03\pm0.53$ assuming $\Delta$\mstar = 0.4~dex.}
+{\bf %It is possible that the uncertainty of the \mstar\ could be higher than our estimation (i.e., 0.2~dex), given that the star formation histories could vary widely at high redshift ($z\sim$2).
+However, even when our stellar mass uncertainty is boosted, the evolution inferred using the eight lensed systems is still robust --- $\gamma=1.05\pm0.48$ assuming  $\Delta$\mstar = 0.3~dex, and $\gamma=1.03\pm0.53$ assuming $\Delta$\mstar = 0.4~dex.
+It is possible that the uncertainty of the \mstar\ could be higher than our assumed 0.2 dex, given that the star formation histories could vary widely at high redshift ($z\sim$2).
+However, increasing the uncertainty on the stellar mass does not change significantly our conclusions, since the error budget is dominated by the uncertainty in black hole mass.
+For example, increasing the stellar mass uncertainty to $0.3$ ($0.4$)~dex, we find $\gamma = 1.05\pm0.48$ $(1.03\pm0.53)$.
+}
 
@@
 acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
-This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+{\bf This project is received support by the NSF through grant 1907208.} This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
 This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 787886).

### 2020-09-26 manuscript/manuscript.tex
Update to make bigger font in the paper

@@
 $^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
-$^{5}$Department of Physics {\bf and Astronomy}, University of California, Davis, CA 95616, USA\\
+$^{5}$Department of Physics and Astronomy, University of California, Davis, CA 95616, USA\\
 $^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
@@
 \centering
-\subfloat[HE0435 F555W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
-\subfloat[HE0435 F814W]{\includegraphics[ width=0.8\textwidth]{fig/HE0435_f814w_inference.pdf}}\\
-\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/HE0435_host_color.pdf}}\\
+\subfloat[HE0435 F555W]{\includegraphics[trim = 15mm 0mm 15mm 5mm, clip, width=0.9\textwidth]{fig/HE0435_f555w_inference.pdf}}\\
+\subfloat[HE0435 F814W]{\includegraphics[trim = 15mm 5mm 15mm 0mm, clip, width=0.9\textwidth]{fig/HE0435_f814w_inference.pdf}}\\
+\subfloat[Host galaxy stellar template inference]{\includegraphics[trim = 10mm 0mm 20mm 15mm, clip, width=0.6\textwidth]{fig/HE0435_host_color.pdf}}\\
 \caption{\label{fig:app_HE0435} 
@@
 \centering
-\subfloat[WFI2033 F125W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
-\subfloat[WFI2033 F140W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
-\subfloat[WFI2033 F555W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
-\subfloat[WFI2033 F814W]{\includegraphics[ width=0.8\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
-\subfloat[Host galaxy stellar template inference]{\includegraphics[ width=0.5\textwidth]{fig/WFI2033_host_color.pdf}}
+\subfloat[WFI2033 F125W]{\includegraphics[trim = 75mm 12mm 45mm 12mm, clip, width=0.9\textwidth]{fig/WFI2033_f125w_inference.pdf}}\\
+\subfloat[WFI2033 F140W]{\includegraphics[trim = 75mm 12mm 45mm 12mm, clip, width=0.9\textwidth]{fig/WFI2033_f140w_inference.pdf}}\\
+\subfloat[WFI2033 F555W]{\includegraphics[trim = 75mm 12mm 45mm 12mm, clip, width=0.9\textwidth]{fig/WFI2033_f555w_inference.pdf}}\\
+\subfloat[WFI2033 F814W]{\includegraphics[trim = 75mm 12mm 45mm 12mm, clip, width=0.9\textwidth]{fig/WFI2033_f814w_inference.pdf}}\\
+\subfloat[Host galaxy stellar template inference]{\includegraphics[trim = 10mm 0mm 20mm 15mm, clip, width=0.6\textwidth]{fig/WFI2033_host_color.pdf}}
 \caption{\label{fig:app_WFI2033} 
@@
 The consistency between the two measurements provides an important verification of the accuracy of the results and strengthens the conclusions drawn by D20 that the {\it observed} value of \mbh\ at a fixed \mstar\ tends to be larger at higher redshift than the ones in the local universe.
-{\bf %It is possible that the uncertainty of the \mstar\ could be higher than our estimation (i.e., 0.2~dex), given that the star formation histories could vary widely at high redshift ($z\sim$2).
-However, even when our stellar mass uncertainty is boosted, the evolution inferred using the eight lensed systems is still robust --- $\gamma=1.05\pm0.48$ assuming  $\Delta$\mstar = 0.3~dex, and $\gamma=1.03\pm0.53$ assuming $\Delta$\mstar = 0.4~dex.
 It is possible that the uncertainty of the \mstar\ could be higher than our assumed 0.2 dex, given that the star formation histories could vary widely at high redshift ($z\sim$2).
@@
 For example, increasing the stellar mass uncertainty to $0.3$ ($0.4$)~dex, we find $\gamma = 1.05\pm0.48$ $(1.03\pm0.53)$.
-}
 
@@
 acknowledge support by the Packard Foundation through a Packard Research fellowship to T.T.
-{\bf This project is received support by the NSF through grant 1907208.} This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+This project is received support by the NSF through grant 1907208.
+This work is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
 This project has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No 787886).
@@
 \begin{tabular}{c c}
-\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_inference.png}}&
-\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_inference.png}}\\
-\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_inference.png}}&
-\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_inference.png}}\\
-\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_inference.png}}&
-\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_inference.png}}\\
-\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_inference.png}}&
-\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_inference.png}}\\
+\subfloat[HE0435]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_inference.png}}&
+\subfloat[RXJ1131]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_inference.png}}\\
+\subfloat[WFI2033]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_inference.png}}&
+\subfloat[SDSS1206]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_inference.png}}\\
+\subfloat[HE1104]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_inference.png}}&
+\subfloat[SDSS0246]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_inference.png}}\\
+\subfloat[HS2209]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_inference.png}}&
+\subfloat[HE0047]{\includegraphics[trim = 60mm 25mm 20mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_inference.png}}\\
 \end{tabular}

### 2020-09-26 material/model_band_plot(Xuheng_mod).py

@@ -100,6 +100,7 @@ class ModelBandPlot(object):
         cax = divider.append_axes("right", size="5%", pad=0.05)
         cb = plt.colorbar(im, cax=cax, orientation='vertical')
         cb.set_label(colorbar_label, fontsize=font_size)
+        cb.ax.tick_params(labelsize=18)
         return ax
 
     def model_plot(self, ax, v_min=None, v_max=None, image_names=False,
@@ -133,7 +134,7 @@ class ModelBandPlot(object):
         cax = divider.append_axes("right", size="5%", pad=0.05)
         cb = plt.colorbar(im, cax=cax)
         cb.set_label(colorbar_label, fontsize=font_size)
-
+        cb.ax.tick_params(labelsize=18)
         #plot_line_set(ax, self._coords, self._ra_caustic_list, self._dec_caustic_list, color='b')
         #plot_line_set(ax, self._coords, self._ra_crit_list, self._dec_crit_list, color='r')
         if image_names is True:
@@ -206,6 +207,7 @@ class ModelBandPlot(object):
         cb = plt.colorbar(im, cax=cax)
         cb.set_label(colorbar_label,
                      fontsize=font_size)
+        cb.ax.tick_params(labelsize=18)
         return ax
 
     def absolute_residual_plot(self, ax, v_min=-1, v_max=1, font_size=15,
@@ -315,7 +317,7 @@ class ModelBandPlot(object):
         cax = divider.append_axes("right", size="5%", pad=0.05)
         cb = plt.colorbar(im, cax=cax)
         cb.set_label(colorbar_label, fontsize=font_size)
-
+        cb.ax.tick_params(labelsize=18)
         if with_caustics is True:
             ra_caustic_list, dec_caustic_list = self._caustics()
             plot_util.plot_line_set(ax, coords_source, ra_caustic_list,
@@ -327,7 +329,7 @@ class ModelBandPlot(object):
         if 'no_arrow' not in kwargs or not kwargs['no_arrow']:
             plot_util.coordinate_arrows(ax, self._frame_size, self._coords, color='w',
                               arrow_size=self._arrow_size, font_size=font_size)
-            plot_util.text_description_2(ax, d_s, text=text, color="w", backgroundcolor='k',
+            plot_util.text_description_2(ax, d_s, text=text, color="w",
                          flipped=False, font_size=font_size)
         if point_source_position is True:
[…]

### 2020-09-26 material/plot_append_HE0435.py

@@ -95,13 +95,13 @@ modelPlot = ModelPlot(multi_band_list, kwargs_model, kwargs_result,
                       arrow_size=0.02, cmap_string="gist_heat", likelihood_mask_list=[lens_mask])
 
 f, axes = plt.subplots(1, 4, figsize=(21, 4), sharex=False, sharey=False)
-modelPlot.data_plot(ax=axes[0])
-modelPlot.model_plot(ax=axes[1])
+modelPlot.data_plot(ax=axes[0], font_size=23)
+modelPlot.model_plot(ax=axes[1], font_size=23)
 #modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6)
 modelPlot.subtract_from_data_plot(ax=axes[2], point_source_add=True,lens_light_add=True, source_add=False, 
-                                  text='Residual of lensed arcs')
-modelPlot.decomposition_plot(ax=axes[3], text='Modelled source light', source_add=True)
-#f.tight_layout()
+                                  text='Residual of lensed arcs', font_size=22)
+modelPlot.decomposition_plot(ax=axes[3], text='Modelled source light', source_add=True, font_size=22)
+f.tight_layout()
 f.subplots_adjust(left=None, bottom=None, right=None, top=None, wspace=0., hspace=0.05)
 #
 plt.savefig('{0}_{1}_inference.pdf'.format(ID, (readfile.split('_model')[0])[-5:]))

### 2020-09-26 material/plot_append_WFI2033.py

@@ -27,7 +27,7 @@ IDs = ['2_WFI2033']
 #0 = int(0ut("Which source:\n"))
 ID = IDs[0][2:]
 filters = ['f125w', 'f140w', 'f555w', 'f814w'] 
-file_info = '/{0}_model/fit_PSFi_PSFrecons/result_PSF0_*_gammafix1.9*.pkl'.format(filters[1])
+file_info = '/{0}_model/fit_PSFi_PSFrecons/result_PSF0_*_gammafix1.9*.pkl'.format(filters[0])
 #
 filename = glob.glob('../'+IDs[0]+file_info )
 #filename = glob.glob('../5_SDSS0246/model/2nd_fit_PSFi_PSFrecons/result_PSF0_*_gammafix2.1_subg2.pkl')
@@ -94,17 +94,17 @@ modelPlot = ModelPlot(multi_band_list, kwargs_model, kwargs_result,
                       arrow_size=0.02, cmap_string="gist_heat", likelihood_mask_list=[lens_mask])
 
 f, axes = plt.subplots(1, 4, figsize=(21, 4), sharex=False, sharey=False)
-if filters[0] == 'f125w':
-    no_arrow=True
+if (readfile.split('_model')[0])[-5:] == 'f125w' or (readfile.split('_model')[0])[-5:] == 'f140w':
+    modelPlot.data_plot(ax=axes[0], no_arrow=True, font_size=23)
+    modelPlot.model_plot(ax=axes[1], no_arrow=True, font_size=23)
 else:
-    no_arror = False
-modelPlot.data_plot(ax=axes[0], no_arrow=no_arrow)
-modelPlot.model_plot(ax=axes[1], no_arrow=no_arrow)
-#modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6)
+    modelPlot.data_plot(ax=axes[0], font_size=23)
+    modelPlot.model_plot(ax=axes[1], font_size=23)
+    #modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6)
 #Multe the arrow in: /Users/Dartoon/Astro/Packages/lenstronomy/lenstronomy/Plots/model_band_plot.py
 modelPlot.subtract_from_data_plot(ax=axes[2], point_source_add=True,lens_light_add=True, source_add=False, 
-                                  text='Residual of lensed arcs')#, no_arrow=no_arrow)
[…]

### 2020-09-26 material/plot_fitting.py

@@ -36,7 +36,7 @@ IDs = ['0_HE0435', '1_RXJ1131', '2_WFI2033', '3_SDSS1206', '4_HE1104', '5_SDSS02
 #for i in range(len(IDs)):
 #    print(i, ':', IDs[i])
 #inp = int(input("Which source:\n"))
-inp = 6
+inp = 7
 ID = IDs[inp][2:]
 if ID == 'SDSS1206':
     folder_0 = '_singel_host_run_summary.pkl'
@@ -119,18 +119,18 @@ modelPlot = ModelPlot(multi_band_list, kwargs_model, kwargs_result,
                       arrow_size=0.02, cmap_string="gist_heat", likelihood_mask_list=[lens_mask])
 
 f, axes = plt.subplots(2, 3, figsize=(16, 8), sharex=False, sharey=False)
-modelPlot.data_plot(ax=axes[0,0])
-modelPlot.model_plot(ax=axes[0,1])
-modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6)
+modelPlot.data_plot(ax=axes[0,0], font_size=23)
+modelPlot.model_plot(ax=axes[0,1], font_size=23)
+modelPlot.normalized_residual_plot(ax=axes[0,2], v_min=-6, v_max=6, font_size=22)
 modelPlot.subtract_from_data_plot(ax=axes[1, 0], #v_max=1, 
                                   point_source_add=True,lens_light_add=True, source_add=False, 
-                                  text='Residual of arcs')
-modelPlot.decomposition_plot(ax=axes[1,1], text='Source light model', source_add=True)
+                                  text='Residual of arcs', font_size=23)
+modelPlot.decomposition_plot(ax=axes[1,1], text='Source light model', source_add=True, font_size=23)
 #modelPlot.decomposition_plot(ax=axes[1,2], text='Source light', source_add=True, unconvolved=True)
 #modelPlot.magnification_plot(ax=axes[1, 2])
 delta_list = [0.02, 0.1, 0.02, 0.05, 0.06, 0.02, 0.02, 0.02, 0.02]
 modelPlot.source_plot(ax=axes[1, 2], deltaPix_source=delta_list[inp], numPix=100, scale_size=0.5,
-                      text='Reconstrucerd host, \nsource plane',with_caustics=True)
+                      text='Reconstrucerd host, \nsource plane',with_caustics=True, font_size=21)
 #f.tight_layout()
[…]
